### 2021-02-12 outputs/paper/paper.Rmd
Add skeleton

---
title: "Reproducibility of COVID-19 research papers on bioRxiv and medRxiv"
subtitle: "TBD"
author: "Annie Collins, University of Toronto"
thanks: "Code and data are available at: https://github.com/anniecollins/reproducibility."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "We create a dataset of all the papers published on bioRxiv and medRxiv between X and Y. We extract the text from these papers and parse them for keywords to do with the availability of data and scripts underpinning the paper. We find that X per cent of papers have X. Our paper demonstrates the need for Y."
output:
  bookdown::pdf_document2:
toc: FALSE
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

# Introduction

...

We follow @weissgerber2021automated...

The remainder of this paper is structured as follows...

# Data

We construct our dataset by first using the APIs of bioRxiv and medRxiv to download any paper that:

# Model

We run our analysis in `R` [@citeR].

# Results

# Discussion

## First discussion point

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

# Appendix {-}

\newpage

# References

### 2021-02-12 scripts/00-Reproducibility.R

@@ -25,8 +25,8 @@ med_daily_sum <- med_results %>% group_by(date) %>% summarise(date = date, total
 med_plot <- med_daily_sum %>% ggplot() + geom_line(aes(x=date, y=total)) + geom_smooth(aes(x=date, y=total))
 
 # Set up folders for download and txt conversion
-med_pdf_folder = paste(getwd(), "/medRxiv PDFs", sep = "")
-med_txt_folder = paste(getwd(), "/medRxiv Text", sep = "")
+med_pdf_folder = paste(getwd(), "inputs/data/pdfs-medRxiv", sep = "")
+med_txt_folder = paste(getwd(), "outputs/data/text-medRxiv", sep = "")
 
 # Download first 500 papers and latest 500 and save to computer
 head(med_results, 500) %>% mx_download(directory = med_pdf_folder, create = FALSE)

### 2021-02-12 outputs/paper/paper.Rmd
Start cleanup of grabbing and parsing medrxiv and minor updates to paper

@@
 subtitle: "TBD"
-author: "Annie Collins, University of Toronto"
-thanks: "Code and data are available at: https://github.com/anniecollins/reproducibility."
+author: "Annie Collins^[University of Toronto.]"
+thanks: "We thank CANSSI... Code and data are available at: https://github.com/anniecollins/reproducibility."
 date: "`r format(Sys.time(), '%d %B %Y')`"
@@
 
-...
+Scientists use open repositories of papers to more quickly disseminate their research than is possible in traditional journals.
+These repositories, such as arxiv, bioRxiv, and medRxiv, are a critical component of science and many results build on the work published there.
+So it is important that the results that are published are credible.
+These repositories are not peer-reviewed, and, in general, anyone with appropriate academic credentials can submit a paper.
 
-We follow @weissgerber2021automated...
+While neither peer-review nor credentials are a panacea nor a guarantee of quality, given the importance of these repositories, it is important that scientists impose on themselves various standards for their results.
+Following @weissgerber2021automated we examine papers about COVID-19 published to bioRxiv and medRxiv during 2020.
+We search for markers of open science and reproducibility, such as X, Y, and Z.
+
+We find that A, B, and C.
 

### 2021-02-12 scripts/01-data_gathering-medrxiv.R

@@ -1,0 +1,55 @@
+#### Preamble ####
+# Purpose: Download papers from medrxiv that are related to COVID-19.
+# Author: Annie Collins and Rohan Alexander
+# Data: 12 February 2021
+# Contact: rohan.alexander@utoronto.ca
+# License: MIT
+# Pre-requisites: 
+# - Need the following packages:
+#   - devtools::install_github("mcguinlu/medrxivr")
+
+
+#### Workspace setup ####
+library(medrxivr)
+library(tidyverse)
+# citation('tidyverse')
+# citation('medrxivr')
+
+
+#### Get metadata ####
+# Download copy of current database
+med_data <- mx_api_content(from_date = "2019-12-01", to_date = "2021-01-31", server = "medrxiv") # n = 20,108 (31 Jan, 2021)
+
+# Raw stats as of 31 Jan, 2021
+# 12,776 COVID articles total
+# 9,931 in medRxiv
+# 2,845 in bioRxiv
+
+# Search database for COVID-19-related articles by keyword across title, abstract, and category. Sort results from oldest to newest.
+med_results <- mx_search(data = med_data, query = c("covid-19", "sars-cov-2", "coronavirus")) # n = 2,584 (31 Jan, 2021)
+med_results <- med_results[order(med_results$date),]
+
+# Sometimes a paper has multiple versions
+# Filter to only uniques and keep latest version of the paper
+# TODO
+
+# Summarise and graph by date
+med_daily_sum <- med_results %>% group_by(date) %>% summarise(date = date, total = n())
+med_plot <- med_daily_sum %>% ggplot() + geom_line(aes(x=date, y=total)) + geom_smooth(aes(x=date, y=total))
+
+
+#### Download relevant papers ####
+# Set up folders for download and txt conversion
+med_pdf_folder = paste(getwd(), "inputs/data/pdfs-medRxiv", sep = "")
+med_txt_folder = paste(getwd(), "outputs/data/text-medRxiv", sep = "")
+
+# Download first 500 papers and latest 500 and save to computer
+head(med_results, 500) %>% mx_download(directory = med_pdf_folder, create = FALSE)
+tail(med_results, 500) %>% mx_download(directory = med_pdf_folder, create = FALSE)
+
+# Convert PDFs to text and saves in new folder
+pdf_convert(med_pdf_folder, med_txt_folder)
+
+
+#### Clean up ####
+rm()

### 2021-02-12 scripts/02-data_clean_and_prep-medrxiv.R

@@ -1,0 +1,47 @@
+#### Preamble ####
+# Purpose: Download the txt files of the PDFs downloaded from medrxiv in 01-data_gathering_mexrxiv.R
+# Author: Annie Collins and Rohan Alexander
+# Data: 12 February 2021
+# Contact: rohan.alexander@utoronto.ca
+# License: MIT
+# Pre-requisites: 
+# - Need to have downloaded PDFs and converted them to txt files saved in outputs/data/
+
+
+#### Workspace setup ####
+# Use R Projects, not setwd().
+library(medrxivr)
+library(oddpub)
+library(tidyverse)
+
+# Read in the raw data. 
+# med_txt_folder = paste(getwd(), ", sep = "")
+# Load text files into list of string vectors for use in text mining algorithm.
+# Returns list of lists, with one list for each document (paper)
+med_text_sentences <- 
+  oddpub::pdf_load(here::here("outputs/data/text-medRxiv/")) # Requires closing backslash
+# TODO: We probably want to change this to purrr::map_dfr() or something else more mainstream.
+
+
+#### Identify open data markers ####
+med_open_data_results <- 
+  oddpub::open_data_search(med_text_sentences)
+# TODO: Again, probably want to change this to stringr::str_detect(). The documentation 
+# for this is weird. 'The algorithm searches...'. 
+# Also this takes ages. We want to re-write it so that it runs loudly.
+
+# Save it 
+# 'outputs/data/med_open_data_results.csv?'
+# TODO
+
+
+#### Summary statistics ####
+# Read in data
+# TODO
+
+# Counts
+med_open_data_results %>% 
+  count(is_open_data, is_open_code)
+
+
+

### 2021-02-13 scripts/02-data_clean_and_prep-medrxiv.R
Add saved version of the checked dataset so dont have to run each time. Minor updates to paper.

@@ -20,19 +20,29 @@ library(tidyverse)
 # Returns list of lists, with one list for each document (paper)
 med_text_sentences <- 
   oddpub::pdf_load(here::here("outputs/data/text-medRxiv/")) # Requires closing backslash
-# TODO: We probably want to change this to purrr::map_dfr() or something else more mainstream.
+
+# TODO: Maybe want to change this to something else more mainstream.
+# Example starts here
+# install.packages("readtext")
+# med_text <- 
+  # readtext::readtext(file = here::here("outputs/data/text-medRxiv/*.txt"))
+# This function can actually directly take PDFs so may want to consider that also eventually.
+# Example ends here
 
 
 #### Identify open data markers ####
 med_open_data_results <- 
   oddpub::open_data_search(med_text_sentences)
-# TODO: Again, probably want to change this to stringr::str_detect(). The documentation 
-# for this is weird. 'The algorithm searches...'. 
-# Also this takes ages. We want to re-write it so that it runs loudly.
+
+# TODO: Maybe want to see if we can re-write this to run faster?
+# Example starts here
+
+# Example ends here
+
 
 # Save it 
-# 'outputs/data/med_open_data_results.csv?'
-# TODO
+class(med_open_data_results)
+write_csv(med_open_data_results, 'outputs/data/med_open_data_results.csv')
 
 
 #### Summary statistics ####

### 2021-02-15 outputs/paper/paper.Rmd
Add saved version of the checked dataset so dont have to run each time. Minor updates to paper.
Updates to .txt files, paper, scripts

@@
 ---
-title: "Reproducibility of COVID-19 research papers on bioRxiv and medRxiv"
+title: "Reproducibility of COVID-19 research papers on medRxiv"
 subtitle: "TBD"
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+library(tidyverse)
+library(lubridate)
+library(knitr)
+library(here)
 
-library(tidyverse)
+knitr::opts_chunk$set(echo = FALSE, error = FALSE, message = FALSE, warning = FALSE)
+
 ```
@@
 
-# Data
+# Data & Methodology
 
-We construct our dataset by first using the APIs of bioRxiv and medRxiv to download any paper that:
+Our primary data set consists of information extracted from the medRxiv repository combined with output from running a sample of COVID-19-related pre-prints through the Open Data Detection in Publications (ODDPub) text mining algorithm.
+
+We constructed this data set by first creating a local copy of the medRxiv repository via the medRxiv API and then filtering for papers related to the COVID-19 pandemic through several keyword searches to create our sampling frame (n = 9,929, including only the most recent version of any given pre-print).
+This data includes the following variables for each pre-print in the repository: title, abstract, author(s), date posted, research field, DOI, version number, corresponding author, corresponding author's institutional affiliation, and published DOI (if the paper has since been published in a peer reviewed journal).
+
+We then selected a random sample of these papers (n = 1,200) to check for open data and code markers using the ODDPub algorithm.
+This required downloading each paper as a PDF, converting the PDFs to text files, and conducting the open data and code detecting procedure to produce a results table indicating the presence of open data or open code markers in each paper (with a value of TRUE or FALSE for each marker and the relevant open data or open code statements when applicable).
+
+Our final data set was formed by joining these two tables together via DOI to form a data set including all original, qualitative information for each pre-print alongside its open data and open code status and markers.
+
+# Sample Summaries
+```{r summary-table}
+# open data/open code count summary table
+med_open_data_results <- read_csv(here("outputs/data/med_open_data_results.csv"))
+med_open_data_results %>% 
+                    count(is_open_data, is_open_code) %>%
+                    kable(col.names = c("Contains Open Data Markers", "Contains Open Code Markers", "Count"))
+```
+
+```{r open-data-published-summary}
+med_open_data_results %>% 
+  group_by(published) %>% count(is_open_data) %>% 
+  pivot_wider(names_from = is_open_data, values_from = n) %>%
+  rename("Open Data Markers" = `TRUE`, "No Open Data Markers" = `FALSE`) %>%
+  kable()
+```
+
+```{r open-code-published-summary}
+med_open_data_results %>% 
+  group_by(published) %>% count(is_open_code) %>% 
+  pivot_wider(names_from = is_open_code, values_from = n) %>%
+  rename("No Open Code Markers" = `0`, "Open Code Markers" = `1`) %>%
+  kable()
+```
+
+```{r monthly-papers-total}
+include_graphics(here("outputs/figures/papers_posted_total.pdf"))
+```
+
+```{r monthly-papers-sample}
+include_graphics(here("outputs/figures/papers_posted_sample.pdf"))
+```
+
+```{r}
+include_graphics(here("outputs/figures/prop_open_per_month.pdf"))
+```
 
@@
 
+In this analysis we distinguish between *posting* (the event that a pre-print is uploaded to medRxiv) and *publishing* (the event that the pre-print has subsequently been published in a peer reviewed journal).
+
+```{r}
+# logit model: posting rate vs. open data, publication rate vs. open code
+```
+
+```{r}
+# logit model: open data/code vs. publication status
+# pub_model <- glm(published ~ is_open_data + is_open_code, family = binomial, data = med_open_data_results)
+```
+
 # Results
@@
 
-## First discussion point
+There are many factors that impact the ability of an author to post make their data available
 
-## Second discussion point
+## First discussion point - Time
+- How has open data/code shifted over the course of the pandemic?
+- How has open data/code changed with publication rate?
 
-## Third discussion point
+## Second discussion point - Eventual Publication
+- See weaknesses
+
+## Third discussion point - Type of Paper
+- A significantly higher proportion if
 
@@
 
-Weaknesses and next steps should also be included.
+- No open data/code was verified manually, all dependent on algorithm
+- Publication info has high rate of false negatives (i.e. medRxiv data seems to miss a lot of papers that go on to be published)
+- Want to look at geographic distribution and prevalence of open data/code - influence on open data policies and timing throughout pandemic
 
@@
 
+Include info here directly from package documentation (i.e. keywords/phrases used for text parsing)?
+
 \newpage

### 2021-02-15 scripts/01-data_gathering-medrxiv.R

@@ -12,13 +12,15 @@
 #### Workspace setup ####
 library(medrxivr)
 library(tidyverse)
+library(lubridate)
+library(oddpub)
 # citation('tidyverse')
 # citation('medrxivr')
 
 
 #### Get metadata ####
 # Download copy of current database
-med_data <- mx_api_content(from_date = "2019-12-01", to_date = "2021-01-31", server = "medrxiv") # n = 20,108 (31 Jan, 2021)
+med_data <- mx_snapshot()
 
 # Raw stats as of 31 Jan, 2021
 # 12,776 COVID articles total
@@ -26,26 +28,51 @@ med_data <- mx_api_content(from_date = "2019-12-01", to_date = "2021-01-31", ser
 # 2,845 in bioRxiv
 
 # Search database for COVID-19-related articles by keyword across title, abstract, and category. Sort results from oldest to newest.
-med_results <- mx_search(data = med_data, query = c("covid-19", "sars-cov-2", "coronavirus")) # n = 2,584 (31 Jan, 2021)
+# Output exclude duplicate title, abstract, and DOI
+med_data <- med_data %>% filter(date >= "2019-12-01", date <= "2021-01-31")
+med_results <- mx_search(data = med_data, query = c("COVID-19",
+                                                    "COVID 19",
+                                                    "covid-19",
+                                                    "covid 19",
+                                                    "SARS-CoV-2",
+                                                    "SARSCoV-2",
+                                                    "corona virus",
+                                                    "Corona Virus",
+                                                    "coronavirus", 
+                                                    "2019-nCoV",
+                                                    "coronavirus-2"), auto_caps = TRUE) # n = 9,9,929
 med_results <- med_results[order(med_results$date),]
 
-# Sometimes a paper has multiple versions
+# Save results - this is sampling frame (info for all medRxiv COVID-19 papers)
+write_csv(med_results, "outputs/data/med_results.csv")
+
+# Sometimes a paper has multiple versions - EXCLUDED IN PREVIOUS STEP, THIS IS MOOT
 # Filter to only uniques and keep latest version of the paper
-# TODO
+# med_results_unique <- med_results[!duplicated(med_results[c(2)]),]
 
 # Summarise and graph by date
[…]

### 2021-02-15 scripts/02-data_clean_and_prep-medrxiv.R

@@ -34,11 +34,28 @@ med_text_sentences <-
 med_open_data_results <- 
   oddpub::open_data_search(med_text_sentences)
 
+
 # TODO: Maybe want to see if we can re-write this to run faster?
 # Example starts here
 
 # Example ends here
 
+# Join med_sample to med_open_data_results and save as med_open_data_results
+med_open_data_results$join_id <- str_sub(med_open_data_results$article, -23, -5)
+med_sample$join_id <- str_sub(med_sample$doi, start = -19)
+med_open_data_results <- merge(med_sample, med_open_data_results, by = "join_id")
+
+# Reassign published values to 0 or 1 based on presence of publication
+med_open_data_results$published[!is.na(med_open_data_results$published)] <- 1
+med_open_data_results$published[is.na(med_open_data_results$published)] <- 0
+
+# Convert TRUE/FALSE in ODDPub output to 1/0
+med_open_data_results$is_open_code <- as.integer(med_open_data_results$is_open_code)
+med_open_data_results$is_open_data <- as.integer(med_open_data_results$is_open_data)
+
+# TODO: Add variable for type of paper - "machine learning", "model"/"modeling", "simulation", "simulate"?
+
+# Add variable 
 
 # Save it 
 class(med_open_data_results)

### 2021-02-15 scripts/03-data_gathering-biorxiv.R

@@ -1,0 +1,84 @@
+#### Preamble ####
+# Purpose: Download papers from medrxiv that are related to COVID-19.
+# Author: Annie Collins and Rohan Alexander
+# Data: 12 February 2021
+# Contact: rohan.alexander@utoronto.ca
+# License: MIT
+# Pre-requisites: 
+# - Need the following packages:
+#   - devtools::install_github("mcguinlu/medrxivr")
+
+
+#### Workspace setup ####
+library(medrxivr)
+library(tidyverse)
+# citation('tidyverse')
+# citation('medrxivr')
+
+
+#### Get metadata ####
+# Download copy of current database
+dates_2020 <- seq.Date(from = as.Date("2019-12-01"), to = as.Date("2020-12-31"), by = 2)
+dates_2021 <- seq.Date(from = as.Date("2021-01-01"), to = as.Date("2021-01-31"), by = "d")
+bio_data <- mx_api_content(from_date = as.character(dates_2020[1]), to_date = as.character(dates_2020[2]), server = "biorxiv")
+i <- 2
+j <- 1
+
+# Retrieve data from 2019-12-01 to 2020-12-31
+while (i < (length(dates_2020) - 1)) {
+  bio_data_next <- try(mx_api_content(from_date = as.character(dates_2020[i]), to_date = as.character(dates_2020[i+1]), server = "biorxiv"))
+  if("try-error" %in% class(bio_data_next)) {
+    bio_data_next <- mx_api_content(from_date = as.character(dates_2020[i]), to_date = as.character(dates_2020[i+2]), server = "biorxiv")
+    bio_data <- rbind(bio_data, bio_data_next)
+    i <- i + 2
+  } else {
+    bio_data <- rbind(bio_data, bio_data_next)
+    i <- i + 1
+  }
+}
+
+# Retrieve data from 2021-01-01 to 2021-01-31
+while (j < (length(dates_2021) - 1)) {
+  bio_data_next <- try(mx_api_content(from_date = as.character(dates_2021[j]), to_date = as.character(dates_2021[j]), server = "biorxiv"))
+  if("try-error" %in% class(bio_data_next)) {
+    bio_data_next <- mx_api_content(from_date = as.character(dates_2021[j]), to_date = as.character(dates_2021[j+1]), server = "biorxiv")
+    bio_data <- rbind(bio_data, bio_data_next)
+    j <- j + 2
+  } else {
+    bio_data <- rbind(bio_data, bio_data_next)
+    j <- j + 1
[…]

### 2021-02-15 scripts/04-data_clean_and_prep-biorxiv.R

@@ -1,0 +1,62 @@
+#### Preamble ####
+# Purpose: Download the txt files of the PDFs downloaded from biorxiv in 01-data_gathering_mexrxiv.R
+# Author: Annie Collins and Rohan Alexander
+# Data: 12 February 2021
+# Contact: rohan.alexander@utoronto.ca
+# License: MIT
+# Pre-requisites: 
+# - Need to have downloaded PDFs and converted them to txt files saved in outputs/data/
+
+
+#### Workspace setup ####
+# Use R Projects, not setwd().
+library(medrxivr)
+library(oddpub)
+library(tidyverse)
+
+# Read in the raw data. 
+# bio_txt_folder = paste(getwd(), ", sep = "")
+# Load text files into list of string vectors for use in text mining algorithm.
+# Returns list of lists, with one list for each document (paper)
+bio_text_sentences <- 
+  oddpub::pdf_load(here::here("outputs/data/text-bioRxiv/")) # Requires closing backslash
+
+
+# TODO: Maybe want to change this to something else more mainstream.
+# Example starts here
+# install.packages("readtext")
+# bio_text <- 
+# readtext::readtext(file = here::here("outputs/data/text-bioRxiv/*.txt"))
+# This function can actually directly take PDFs so may want to consider that also eventually.
+# Example ends here
+
+
+#### Identify open data markers ####
+bio_open_data_results <- 
+  oddpub::open_data_search(bio_text_sentences)
+
+# INTERIM SAVE
+class(bio_open_data_results)
+write_csv(bio_open_data_results, 'outputs/data/bio_open_data_results.csv')
+
+# TODO: Maybe want to see if we can re-write this to run faster?
+# Example starts here
+
+# Example ends here
+
+
+# Save it 
+class(bio_open_data_results)
+write_csv(bio_open_data_results, 'outputs/data/bio_open_data_results.csv')
+
+
+#### Summary statistics ####
+# Read in data
+# TODO
+
+# Counts
+bio_open_data_results %>% 
+  count(is_open_data, is_open_code)
+
+
+

### 2021-02-15 scripts/05-plots_tables.R

@@ -1,0 +1,61 @@
+# Load Data
+med_results <- read_csv("outputs/data/med_results.csv")
+med_open_data_results <- read_csv("outputs/data/med_open_data_results.csv")
+
+# Raw open data/code counts
+med_open_data_results <- read_csv(here("outputs/data/med_open_data_results.csv"))
+med_open_data_results %>% 
+  count(is_open_data, is_open_code) %>%
+  kable() %>%
+  save_kable("outputs/figures/initial_sum_table.pdf")
+
+# Summary Tables
+med_month_sum <- med_results %>% group_by(month = floor_date(date, "month")) %>% summarise(count=n())
+med_month_sum_cov <- med_open_data_results %>% 
+  group_by(month = floor_date(date, "month")) %>% 
+  summarise(count=n(), prop_open_code = sum(is_open_code)/n(), prop_open_data = sum(is_open_data)/n())
+num_days <- c(31, 29, 31, 30, 31, 30, 31, 31, 30, 31, 30, 31, 31)
+med_month_sum$daily_rate <- med_month_sum$count/num_days
+
+# Publication status with open data/code counts
+pub_data_count <- med_open_data_results %>% 
+  group_by(published) %>% count(is_open_data) %>% 
+  pivot_wider(names_from = is_open_data, values_from = n) %>%
+  rename("Open Data Markers" = `TRUE`, "No Data Code Markers" = `FALSE`)
+
+pub_code_count <- med_open_data_results %>% 
+  group_by(published) %>% count(is_open_code) %>% 
+  pivot_wider(names_from = is_open_code, values_from = n) %>%
+  rename("No Open Code Markers" = `0`, "Open Code Markers" = `1`)
+
+
+# Histogram of number of papers from sample in each month with total number of COVID papers published for each month
+# All COVID papers
+med_month_plot <- med_month_sum %>% ggplot(aes(month, count)) + geom_line(stat="identity") + ggtitle("COVID-19 Papers Posted (Total)")
+med_month_plot
+ggsave("outputs/figures/papers_posted_total.pdf")
+# Sampled COVID papers
+med_month_cov_plot <- med_month_sum_cov %>% ggplot(aes(month, count)) + geom_bar(stat="identity") + ggtitle("COVID-19 Papers Posted (Sample)")
+med_month_cov_plot
+ggsave("outputs/figures/papers_posted_sample.pdf")
+
+# % of papers with open data/code from sample per month
+colors <- c("Data" = "red", "Code" = "blue")
[…]

### 2021-02-16 outputs/paper/paper.Rmd
Add more plots, messy updates to plot script and paper

@@
                     count(is_open_data, is_open_code) %>%
-                    kable(col.names = c("Contains Open Data Markers", "Contains Open Code Markers", "Count"))
+                    mutate(prop_total = n/1200) %>%
+                    kable(col.names = c("Contains Open Data Markers", "Contains Open Code Markers", "Count", "Porportion of Total"))
 ```
@@
   pivot_wider(names_from = is_open_data, values_from = n) %>%
-  rename("Open Data Markers" = `TRUE`, "No Open Data Markers" = `FALSE`) %>%
+  rename("Open Data Markers" = `1`, "No Open Data Markers" = `0`) %>%
   kable()
@@
 ```{r monthly-papers-total}
+# Number of COVID-related papers posted each month in total
 include_graphics(here("outputs/figures/papers_posted_total.pdf"))
@@
 
-```{r monthly-papers-sample}
-include_graphics(here("outputs/figures/papers_posted_sample.pdf"))
+```{r monthly-papers-by-condition}
+# Number of papers posted each month from the sample
+# include_graphics(here("outputs/figures/papers_posted_sample.pdf"))
+# Likely don't need this anymore, see monthly-papers-sample-2
+```
+
+```{r proportion-of-open-data}
+# Proportion of papers posted with open data or open code each month
+include_graphics(here("outputs/figures/prop_open_per_month.pdf"))
+```
+
+```{r monthly-papers-by-condition}
+# Number of papers for each open data/code status per month
+include_graphics(here("outputs/figures/stack_conditions_plot.pdf"))
+```
+- Proportion of open data/code has fluctuated over time but shows no consistent overall increase or decrease over the course of the pandemic
+- Proportion of open data seems to be relatively unimpacted by the number of papers posted to medRxiv in any given month
+- Open code dipped in summer months when posting rate to medRxiv was high, bit questionable
+- Open code follows similar patterns of increase/decrease as data but ultimately is less prevelant in the repository
+
+# Publication
+```{r}
+med_open_data_results %>% 
+  group_by(published) %>% count(is_open_data) %>% 
+  pivot_wider(names_from = is_open_data, values_from = n) %>%
+  rename("Open Data Markers" = `1`, "No Data Code Markers" = `0`) %>% kable()
 ```
@@
 ```{r}
-include_graphics(here("outputs/figures/prop_open_per_month.pdf"))
+med_open_data_results %>% 
+  group_by(published) %>% count(is_open_code) %>% 
+  pivot_wider(names_from = is_open_code, values_from = n) %>%
+  rename("No Open Code Markers" = `0`, "Open Code Markers" = `1`) %>% kable()
 ```
+
+# Type of Paper
+```{r}
+# Number of open data/code papers by keyword for different types
+include_graphics(here("outputs/figures/paper_type_keywords_plot.pdf"))
+```
+- Once data is restricted to certain types of papers - those including modeling, simulation, or machine learning - the availability of open data and code becomes much higher than the data set overall
+- Relatively small sample size, but still important to note?
+- Also an expected result
 
@@
 
+## Open Data/Code in broader context
+- Discussion on open data/code in general and in life/medical sciences
+- Are these a good indicator of reproducibility? How much do these contribute to reproducibility?
+
 ## First discussion point - Time
-- How has open data/code shifted over the course of the pandemic?
-- How has open data/code changed with publication rate?
+- Important to note that time plays a role in geographic focus in this context - early cases/research in China, then east and Southeast Asia, differences in different local data practices/policies
+- On one hand good that there did not appear to be a drop in proportion of papers with open data/code as posting rates have risen, but also interesting to note that there has not been an overall increase
+-
 
@@
 ## Third discussion point - Type of Paper
-- A significantly higher proportion if
+- Public health modeling/simulation papers more important near beginning of pandemic when less was understood about COVID as a disease specifically
+- Perhaps contributed to the fact that the rate of open data/code from beginning of pandemic has been consistent throughout despite what we would hope is an increase in availability of COVID-19-related data?
 
@@
 - Want to look at geographic distribution and prevalence of open data/code - influence on open data policies and timing throughout pandemic
+- Extend research to other indicators of reproducibility
 

### 2021-02-16 scripts/05-plots_tables.R

@@ -1,6 +1,9 @@
+library(tidyverse)
+library(lubridate)
+
 # Load Data
-med_results <- read_csv("outputs/data/med_results.csv")
-med_open_data_results <- read_csv("outputs/data/med_open_data_results.csv")
+med_results <- read_csv("outputs/data/med_results.csv") # All COVID medRxiv papers (9,929)
+med_open_data_results <- read_csv("outputs/data/med_open_data_results.csv") # Papers with ODDPub results
 
 # Raw open data/code counts
 med_open_data_results <- read_csv(here("outputs/data/med_open_data_results.csv"))
@@ -21,12 +24,15 @@ med_month_sum$daily_rate <- med_month_sum$count/num_days
 pub_data_count <- med_open_data_results %>% 
   group_by(published) %>% count(is_open_data) %>% 
   pivot_wider(names_from = is_open_data, values_from = n) %>%
-  rename("Open Data Markers" = `TRUE`, "No Data Code Markers" = `FALSE`)
+  rename("Open Data Markers" = `0`, "No Data Code Markers" = `1`)
+pub_data_count
 
 pub_code_count <- med_open_data_results %>% 
   group_by(published) %>% count(is_open_code) %>% 
   pivot_wider(names_from = is_open_code, values_from = n) %>%
   rename("No Open Code Markers" = `0`, "Open Code Markers" = `1`)
+pub_code_count
+
 
 
 # Histogram of number of papers from sample in each month with total number of COVID papers published for each month
@@ -48,8 +54,52 @@ open_rate_plot <- med_month_sum_cov %>% ggplot() +
 open_rate_plot
 ggsave("outputs/figures/prop_open_per_month.pdf")
 
+# Papers with open code/data per month from sample
+# Create data frame
+open_status <- med_open_data_results %>% select(title, date, is_open_code, is_open_data) %>% mutate(condition = is_open_data + is_open_code)
+open_status$condition[open_status$condition == 2] <- "Both"
+open_status$condition[open_status$condition == 0] <- "Neither"
+open_status$condition[open_status$condition == 1 & open_status$is_open_code == 1] <- "Open Code"
+open_status$condition[open_status$condition == 1 & open_status$is_open_data == 1] <- "Open Data"
+
+stack_conditions_plot <- open_status %>% ggplot() + 
+  geom_bar(aes(x = factor(floor_date(date, "month")), fill=factor(condition, levels = c("Neither", "Open Code", "Open Data", "Both")), position = "stack"))
+stack_conditions_plot
[…]

### 2021-02-17 outputs/paper/paper.Rmd
Add abstract and update paper content and tables

@@
 ---
-title: "Reproducibility of COVID-19 research papers on medRxiv"
-subtitle: "TBD"
+title: "Reproducibility of COVID-19 pre-prints on medRxiv"
+subtitle: "Markers of open code or data not identified in 81 per cent of pre-prints"
 author: "Annie Collins^[University of Toronto.]"
-thanks: "We thank CANSSI... Code and data are available at: https://github.com/anniecollins/reproducibility."
+thanks: "Paper presented at Toronto Workshop on Reproducibility, 26 Februrary 2021.
+Collins thanks CANSSI Ontario for financial support.
+Code and data are available at: https://github.com/anniecollins/reproducibility."
 date: "`r format(Sys.time(), '%d %B %Y')`"
-abstract: "We create a dataset of all the papers published on bioRxiv and medRxiv between X and Y.
-We extract the text from these papers and parse them for keywords to do with the availability of data and scripts underpinning the paper.
-We find that X per cent of papers have X.
-Our paper demonstrates the need for Y."
+abstract: "We create a dataset of all the pre-prints published on medRxiv between between 28 January 2020 and 31 January 2021.
+We extract the text from these pre-prints and parse them looking for for keyword markers signalling the availability of the data and code underpinning the pre-print.
+We are unable to find markers of either open data or open code for 81 per cent of the pre-prints in our sample.
+Our paper demonstrates the need to have authors categorize the degree of openness of their pre-print as part of the medRxiv submissions process, and more broadly, the need to better integrate open science training into a wide range of fields."
 output:
@@
 ```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = FALSE, error = FALSE, message = FALSE, warning = FALSE)
+```
+
+```{r loadpackages, include=FALSE}
+library(here)
+library(knitr)
+library(lubridate)
 library(tidyverse)
-library(lubridate)
-library(knitr)
-library(here)
+```
 
-knitr::opts_chunk$set(echo = FALSE, error = FALSE, message = FALSE, warning = FALSE)
-
+```{r loaddata, include=FALSE}
+med_open_data_results <- read_csv(here("outputs/data/med_open_data_results.csv"))
 ```
@@
 
-Our primary data set consists of information extracted from the medRxiv repository combined with output from running a sample of COVID-19-related pre-prints through the Open Data Detection in Publications (ODDPub) text mining algorithm.
+Our primary data set consists of information extracted from the medRxiv repository combined with output from running a sample of COVID-19-related pre-prints through the Open Data Detection in Publications (ODDPub) text mining algorithm [@citePDDPub], using the `oddpub` package [@citeODDPubpackage].
 
@@
 This required downloading each paper as a PDF, converting the PDFs to text files, and conducting the open data and code detecting procedure to produce a results table indicating the presence of open data or open code markers in each paper (with a value of TRUE or FALSE for each marker and the relevant open data or open code statements when applicable).
+These PDFs were downloaded and converted to txt files using the `medrxivr` package [@citemedrxivr].
 
 Our final data set was formed by joining these two tables together via DOI to form a data set including all original, qualitative information for each pre-print alongside its open data and open code status and markers.
+Broadly, we are unable to find markers of either open data or open code for around 81 per cent of pre-prints (Table \@ref(tab:summarycounts)).
 
-# Sample Summaries
-```{r summary-table}
+```{r summarycounts}
 # open data/open code count summary table
-med_open_data_results <- read_csv(here("outputs/data/med_open_data_results.csv"))
 med_open_data_results %>% 
   count(is_open_data, is_open_code) %>%
-                    mutate(prop_total = n/1200) %>%
-                    kable(col.names = c("Contains Open Data Markers", "Contains Open Code Markers", "Count", "Porportion of Total"))
+  mutate(prop_total = n / sum(n)) %>%
+  mutate(is_open_data = ifelse(is_open_data == 0, "No", "Yes"),
+         is_open_code = ifelse(is_open_code == 0, "No", "Yes")) %>% 
+  kable(col.names = c("Contains Open Data Markers", "Contains Open Code Markers", "Count", "Proportion of Total"),
+        caption = "Counts and proportions of open data and code markers in our sample",
+        booktabs = TRUE,
+        digits = 2)
 ```
+
+We do not see a substantial difference in the presence of markers of open data or code between whether a pre-print ended up being published.
+There was a low number of papers that had markers of either open data or code in both those that were published and those that were not published (Tables \@ref(tab:open-data-published-summary) and \@ref(tab:open-code-published-summary)).
+It is important to note here that our dataset imperfectly characterises publication.
+In particular, it does not have the publication details for some papers that were published.
+And even if it were a perfect record, there is a publication lag that may skew the results.
 
@@
 med_open_data_results %>% 
-  group_by(published) %>% count(is_open_data) %>% 
+  group_by(published) %>% 
+  count(is_open_data) %>% 
   pivot_wider(names_from = is_open_data, values_from = n) %>%
-  rename("Open Data Markers" = `1`, "No Open Data Markers" = `0`) %>%
-  kable()
+  mutate(published = ifelse(published == 0, "No", "Yes")) %>%
+  rename("Open Data Markers" = `1`, 
+         "No Open Data Markers" = `0`,
+         Published = published) %>%
+  kable(caption = "Counts and proportions of open data markers by whether the pre-print was published",
+        booktabs = TRUE)
 ```
@@
   pivot_wider(names_from = is_open_code, values_from = n) %>%
-  rename("No Open Code Markers" = `0`, "Open Code Markers" = `1`) %>%
-  kable()
+  rename("No Open Code Markers" = `0`, 
+         "Open Code Markers" = `1`,
+         Published = published) %>%
+  kable(caption = "Counts and proportions of open code markers by whether the pre-print was published",
+        booktabs = TRUE) 
 ```
 
-```{r monthly-papers-total}
+The number of pre-prints posted by month reached its maximum in May 2020, and has remained reasonably steady at around 750 per month since around August 2020 (Figure \@ref(fig:monthly-papers-total)).
+
+```{r monthly-papers-total, fig.cap = "Number of pre-prints related to COVID-19 posted to medRxiv"}
 # Number of COVID-related papers posted each month in total
-include_graphics(here("outputs/figures/papers_posted_total.pdf"))
+med_results <- read_csv(here::here("outputs/data/med_results.csv")) # All COVID medRxiv papers (9,929)
+
+med_results %>% 
+  group_by(month = floor_date(date, "month")) %>% 
+  summarise(count=n()) %>% 
+  ggplot(aes(month, count)) + 
+  # geom_line(stat="identity") +
+  geom_col() + 
+  labs(x = "Month",
+       y = "Number of pre-prints") +
+  theme_minimal()
 ```
@@
 
-```{r monthly-papers-by-condition}
+```{r monthly-papers-by-condition-stack}
 # Number of papers for each open data/code status per month
@@
 # Publication
+
 ```{r}
@@
 # Type of Paper
+
 ```{r}
@@
 ```
+
 - Once data is restricted to certain types of papers - those including modeling, simulation, or machine learning - the availability of open data and code becomes much higher than the data set overall

### 2021-02-17 scripts/05-plots_tables.R

@@ -1,3 +1,4 @@
+library(kableExtra)
 library(tidyverse)
 library(lubridate)
 
@@ -13,35 +14,55 @@ med_open_data_results %>%
   save_kable("outputs/figures/initial_sum_table.pdf")
 
 # Summary Tables
-med_month_sum <- med_results %>% group_by(month = floor_date(date, "month")) %>% summarise(count=n())
-med_month_sum_cov <- med_open_data_results %>% 
+med_month_sum <- 
+  med_results %>% 
   group_by(month = floor_date(date, "month")) %>% 
-  summarise(count=n(), prop_open_code = sum(is_open_code)/n(), prop_open_data = sum(is_open_data)/n())
-num_days <- c(31, 29, 31, 30, 31, 30, 31, 31, 30, 31, 30, 31, 31)
-med_month_sum$daily_rate <- med_month_sum$count/num_days
+  summarise(count=n())
+
+med_month_sum_cov <- 
+  med_open_data_results %>% 
+  group_by(month = floor_date(date, "month")) %>% 
+  summarise(count=n(), prop_open_code = sum(is_open_code)/n(), prop_open_data = sum(is_open_data)/n()) %>% 
+  mutate(num_days = days_in_month(month),
+         daily_rate = count/num_days)
+# num_days <- c(31, 29, 31, 30, 31, 30, 31, 31, 30, 31, 30, 31, 31)
+# med_month_sum$daily_rate <- med_month_sum$count/num_days
 
 # Publication status with open data/code counts
-pub_data_count <- med_open_data_results %>% 
-  group_by(published) %>% count(is_open_data) %>% 
+pub_data_count <- 
+  med_open_data_results %>% 
+  group_by(published) %>% 
+  count(is_open_data) %>% 
   pivot_wider(names_from = is_open_data, values_from = n) %>%
   rename("Open Data Markers" = `0`, "No Data Code Markers" = `1`)
 pub_data_count
 
-pub_code_count <- med_open_data_results %>% 
-  group_by(published) %>% count(is_open_code) %>% 
+pub_code_count <- 
+  med_open_data_results %>% 
+  group_by(published) %>% 
+  count(is_open_code) %>% 
   pivot_wider(names_from = is_open_code, values_from = n) %>%
   rename("No Open Code Markers" = `0`, "Open Code Markers" = `1`)
 pub_code_count
 
 
-
 # Histogram of number of papers from sample in each month with total number of COVID papers published for each month
 # All COVID papers
[…]

### 2021-02-20 outputs/paper/paper.Rmd
Updates to paper and input docs

--- 2021-02-15 outputs/paper/paper.Rmd
@@
 Scientists use open repositories of papers to more quickly disseminate their research than is possible in traditional journals.
-These repositories, such as arxiv, bioRxiv, and medRxiv, are a critical component of science and many results build on the work published there.
-So it is important that the results that are published are credible.
+These repositories, such as arxiv, bioRxiv, and medRxiv, are a critical component of science and many results build on the work published there, thus it is important that the results that are published are credible.
+Pre-print repositories, specifically medRxiv, have drawn unprecedented attention in the context of the 2019 novel coronavirus (COVID-19) pandemic and the changes it has thrust upon the scientific community [@else2020].
 These repositories are not peer-reviewed, and, in general, anyone with appropriate academic credentials can submit a paper.
@@
 While neither peer-review nor credentials are a panacea nor a guarantee of quality, given the importance of these repositories, it is important that scientists impose on themselves various standards for their results.
-Following @weissgerber2021automated we examine papers about COVID-19 published to bioRxiv and medRxiv during 2020.
-We search for markers of open science and reproducibility, such as X, Y, and Z.
+Following @weissgerber2021automated we examine papers about COVID-19 published to medRxiv throughout 2020.
+We search for markers of open science as indicators of reproducibility, specifically open data and open code.
 
-We find that A, B, and C.
+We find that approximately 81 per cent of sampled papers contain neither open data nor open code markers.
+Examining trends over time, we find that the proportion of pre-prints containing open data or code markers has fluctuated but shown no obvious increasing or decreasing trend throughout the pandemic.
+We also find that the presence of open data or open code markers has little influence on a pre-print's future publication, while the subset of sampled pre-prints that has been published contains an overall lower proportion of papers with these markers.
+Finally, we briefly examine the presence of open data and code markers in specific types of pre-prints, namely modelling, simulation, and machine learning research.
 
-The remainder of this paper is structured as follows...
+The remainder of this paper is structured as follows: first, we discuss the process of constructing our data set through retrieving pre-prints from the medRxiv repository and mining them for open data and open code markers.
+Then we will explore some key findings in this raw data and explore some logistic regression models that support these findings.
+Lastly we will discuss the implications of these findings in the broader context of reproducibility and science during the COVID-19 pandemic, as well as next steps to expand on our findings and questions raised in the research process.
 
@@
 
-Our primary data set consists of information extracted from the medRxiv repository combined with output from running a sample of COVID-19-related pre-prints through the Open Data Detection in Publications (ODDPub) text mining algorithm.
+Our primary data set consists of information extracted from the medRxiv repository combined with output from running a sample of COVID-19-related pre-prints through the Open Data Detection in Publications (ODDPub) text mining algorithm [@citePDDPub], using the `oddpub` package [@citeODDPubpackage].
 
-We constructed this data set by first creating a local copy of the medRxiv repository via the medRxiv API and then filtering for papers related to the COVID-19 pandemic through several keyword searches to create our sampling frame (n = 9,929, including only the most recent version of any given pre-print).
+We constructed this data set by first creating a local copy of the medRxiv repository via the medRxiv API and then filtering for papers related to the COVID-19 pandemic through several keyword searches to create our sampling frame (N = 9,929, including only the most recent version of any given pre-print).
 This data includes the following variables for each pre-print in the repository: title, abstract, author(s), date posted, research field, DOI, version number, corresponding author, corresponding author's institutional affiliation, and published DOI (if the paper has since been published in a peer reviewed journal).
 
-We then selected a random sample of these papers (n = 1,200) to check for open data and code markers using the ODDPub algorithm.
+We then selected a random sample of these papers (N = 1,200) to check for open data and code markers using the ODDPub algorithm.
 This required downloading each paper as a PDF, converting the PDFs to text files, and conducting the open data and code detecting procedure to produce a results table indicating the presence of open data or open code markers in each paper (with a value of TRUE or FALSE for each marker and the relevant open data or open code statements when applicable).
+These PDFs were downloaded and converted to text files using the `medrxivr` package [@citemedrxivr].
 
@@
 
-# Sample Summaries
-```{r summary-table}
+```{r monthly-papers-total, fig.cap = "Number of pre-prints related to COVID-19 posted to medRxiv"}
+# Number of COVID-related papers posted each month in total
+med_results <- read_csv(here::here("outputs/data/med_results.csv")) # All COVID medRxiv papers (9,929)
+
+med_results %>% 
+  group_by(month = floor_date(date, "month")) %>% 
+  summarise(count=n()) %>% 
+  ggplot(aes(month, count)) + 
+  # geom_line(stat="identity") +
+  geom_col() + 
+  labs(title = "Pre-prints Posted per Month",
+       subtitle = "medRxiv, Total = 9,929",
+       x = "Month",
+       y = "Number of Pre-prints") +
+  theme_minimal()
+```
+
+The number of pre-prints posted per month increased dramatically between January and May 2020, reaching its maximum in May and subsequently decreasing.
+The number of pre-prints posted since August 2020 has remained reasonably steady at around 750 per month (Figure \@ref(fig:monthly-papers-total)).
+For context, COVID-19 was declared a pandemic by the World Health Organization (WHO) on March 11, 2020, at which point the number of cases globally had just surpassed 118,000 (primarily in east Asia) and the virus had been reported in 114 countries [@citeWHOtimeline].
+
+Broadly, we are unable to find markers of either open data or open code for around 81 per cent of the 1,200 sampled pre-prints.
+The remaining 19 per cent of pre-prints was comprised of 4 percent of the sample containing markers for open code, 8 percent of the sample with markers for open data, and 7 percent of the sample with markers for both open data and open code (Table \@ref(tab:summarycounts)).
+
+```{r summarycounts}
 # open data/open code count summary table
-med_open_data_results <- read_csv(here("outputs/data/med_open_data_results.csv"))
 med_open_data_results %>% 
   count(is_open_data, is_open_code) %>%
-                    kable(col.names = c("Contains Open Data Markers", "Contains Open Code Markers", "Count"))
+  mutate(prop_total = n / sum(n)) %>%
+  mutate(is_open_data = ifelse(is_open_data == 0, "No", "Yes"),
+         is_open_code = ifelse(is_open_code == 0, "No", "Yes")) %>% 
+  kable(col.names = c("Contains Open Data Markers", "Contains Open Code Markers", "Count", "Proportion of Total"),
+        caption = "Counts and proportions of open data and code markers in our sample",
+        booktabs = TRUE,
+        digits = 2)
 ```
 
-```{r open-data-published-summary}
+The distribution of total sampled pre-prints and sampled pre-prints with open data or code markers roughly follows that of COVID-19-related pre-prints posted in general (Figure \@ref(fig:monthly-papers-condition-stack)).
+The proportion of pre-prints with open data or code has fluctuated over time but shows no consistent overall increase or decrease throughout the course of the pandemic, nor in conjunction with increases or decreases in the total number of pre-prints posted to medRxiv (Figure \@ref(fig:monthly-proporiton-of-open).
+In our data set, only one pre-print was sampled for the month of January 2020.
+This pre-print contained neither open data nor open code markers, thus the 0 per cent rate of open data and code for this month should be treated as an outlier within the sample.
+
+```{r monthly-papers-condition-stack, fig.cap = "Number of pre-prints related to COVID-19 sampled from medRxiv, distinguished by presence of open data or code markers"}
+# Number of papers for each open data/code status per month
+open_status <- 
   med_open_data_results %>% 
-  group_by(published) %>% count(is_open_data) %>% 
-  pivot_wider(names_from = is_open_data, values_from = n) %>%
-  rename("Open Data Markers" = `TRUE`, "No Open Data Markers" = `FALSE`) %>%
-  kable()
+  select(title, date, is_open_code, is_open_data) %>% 
+  mutate(condition = is_open_data + is_open_code)
+open_status$condition[open_status$condition == 2] <- "Both"
+open_status$condition[open_status$condition == 0] <- "Neither"
+open_status$condition[open_status$condition == 1 & open_status$is_open_code == 1] <- "Open Code"
+open_status$condition[open_status$condition == 1 & open_status$is_open_data == 1] <- "Open Data"
+
+open_status %>% 
+  ggplot() + 
+  geom_bar(aes(x = factor(floor_date(date, "month")), 
+               fill=factor(condition, levels = c("Neither", "Open Code", "Open Data", "Both")), 
+               position = "stack")) +
+  labs(fill = "Type of Marker") +
+  scale_x_discrete(breaks=c("2020-01-01","2020-04-01","2020-07-01", "2020-10-01", "2021-01-01"), 
+                   labels=c("Jan 2020","Apr 2020","Jul 2020", "Oct 2020", "Jan 2021")) +
+  ylab("Number of Pre-prints") +
+  xlab("Month") +
+  labs(title="Sampled Pre-prints by Month", subtitle="medRxiv, Total = 1,200") +
+  theme_minimal()
 ```
 
-```{r open-code-published-summary}
+```{r proportion-of-open, fig.cap= "Proportion of pre-prints in sample with open data or open code markers by month"}
+# Proportion of papers posted with open data or open code each month
+colors <- c("Open Data" = "blue", "Open Code" = "green")
+med_month_sum_cov <- 
   med_open_data_results %>% 
-  group_by(published) %>% count(is_open_code) %>% 
-  pivot_wider(names_from = is_open_code, values_from = n) %>%
-  rename("No Open Code Markers" = `0`, "Open Code Markers" = `1`) %>%
-  kable()
+  group_by(month = floor_date(date, "month")) %>% 
+  summarise(count=n(), prop_open_code = sum(is_open_code)/n(), prop_open_data = sum(is_open_data)/n()) %>% 
+  mutate(num_days = days_in_month(month),
+         daily_rate = count/num_days)
+med_month_sum_cov %>%
+  ggplot() +
+  geom_line(data = med_month_sum_cov, aes(month, prop_open_data, color = "Open Data")) +
+  geom_line(data = med_month_sum_cov, aes(month, prop_open_code, color = "Open Code")) +
+  ggtitle("Proportion of Sampled Pre-prints with Open Data or Code Markers") +
+  xlab("Month") +
+  ylab("Proportion of Pre-prints") +
+  labs(colour = "Type of Marker") + 
+  theme_minimal()
 ```
 
-```{r monthly-papers-total}
-include_graphics(here("outputs/figures/papers_posted_total.pdf"))
+## Publication
+```{r open-published-summary}
+published_open_status <- 
+  med_open_data_results %>% 
+  select(title, date, published, is_open_code, is_open_data) %>% 
+  mutate(condition = is_open_data + is_open_code)
+published_open_status$condition[published_open_status$condition == 2] <- "Both"
+published_open_status$condition[published_open_status$condition == 0] <- "Neither"
+published_open_status$condition[published_open_status$condition == 1 & published_open_status$is_open_code == 1] <- "Open Code"
+published_open_status$condition[published_open_status$condition == 1 & published_open_status$is_open_data == 1] <- "Open Data"
+
+published_open_status %>% 
+  count(published, condition) %>% 
+  pivot_wider(names_from = condition, values_from = n) %>%
+  mutate(published = ifelse(published == 0, "No", "Yes"), `Proportion with Open Data and/or Code`= round((`Open Data` + `Open Code` + Both)/(`Open Data` + `Open Code` + Both + Neither), 2)) %>%
+  rename(Published = published) %>%
+  kable(caption = "Counts and proportions of open data markers by whether the pre-print was published",
+        booktabs = TRUE)
 ```
 
-```{r monthly-papers-sample}
-include_graphics(here("outputs/figures/papers_posted_sample.pdf"))
+```{r open-published-stack}
+published_open_status$published[published_open_status$published == 0] <- "Published"
+published_open_status$published[published_open_status$published == 1] <- "Unpublished"
+
+published_open_status %>% 
+  # mutate(published = ifelse(published == 0, "Unpublished", "Published")) +
+  ggplot() + 
+  geom_bar(aes(x = published, fill=factor(condition, levels = c("Neither", "Open Code", "Open Data", "Both")), position = "stack")) +
+  labs(fill = "Type of Marker") +
+  ylab("Number of Pre-prints") +
+  ggtitle("Pre-prints by Publication Status") +
+  theme_minimal()
 ```
 
-```{r}
-include_graphics(here("outputs/figures/prop_open_per_month.pdf"))
+We see that the proportion of pre-prints with open data or code markers among those that have been published is approximately 5 per cent lower than that of pre-prints which have not been published (Table \@ref(tab:open-published-summary)).
+There was a low number of papers that had markers of either open data or code in both those that were published and those that were not published (Figure \@ref(fig:open-published-stack)).
+It is important to note here that our data set imperfectly characterizes publication.
+In particular, it does not have the publication details for some papers that were published, and even if it were a perfect record, there is a publication lag (estimated at an average of 60 days) that may skew the results [@kwon2020].
+
+## Type of Pre-print
+
+```{r stack-by-type}
+# Number of open data/code papers by keyword for different types
+paper_type_keywords <- 
+  med_open_data_results %>% select(title, abstract, date, is_open_code, is_open_data) %>% 
+  mutate(condition = is_open_data + is_open_code)
+paper_type_keywords$condition[paper_type_keywords$condition == 2] <- "Both"
+paper_type_keywords$condition[paper_type_keywords$condition == 0] <- "Neither"
+paper_type_keywords$condition[paper_type_keywords$condition == 1 & open_status$is_open_code == 1] <- "Open Code"
+paper_type_keywords$condition[paper_type_keywords$condition == 1 & open_status$is_open_data == 1] <- "Open Data"
+paper_type_keywords$`Machine Learning` <- str_detect( paper_type_keywords$title, "machine learning") | 
+                                          str_detect( paper_type_keywords$abstract, "machine learning")
+paper_type_keywords$Simulation <- str_detect( paper_type_keywords$title, "simulate|simulation|simulating") | 
+                                    str_detect( paper_type_keywords$abstract, "simulate|simulation|simulating|simulated")
+paper_type_keywords$modelling <- str_detect( paper_type_keywords$title, "modelling|model|models|modeling") | 
+                                str_detect( paper_type_keywords$abstract, "modelling|model|models|modeling")
+paper_type_keywords <- paper_type_keywords %>% 
+  pivot_longer(cols = c("Machine Learning", "Simulation", "modelling"), names_to = "Type", values_to = "Value") %>%
+  filter(Value == TRUE)
+# Plot
+paper_type_keywords %>% ggplot() + 
+  geom_bar(aes(x = Type, fill=factor(condition, levels = c("Neither", "Open Code", "Open Data", "Both")), position = "stack")) +
+  labs(fill = "Type of Marker") +
+  scale_x_discrete(labels=c("Machine Learning", "modelling", "Simulation")) +
+  ylab("Number of Pre-prints") +
+  xlab("Month") +
+  ggtitle("Sampled Pre-prints by Month") +
+  theme_minimal()
+
 ```
+
+```{r summary-by-type}
+paper_type_keywords %>% 
+  count(Type, condition) %>% 
+  pivot_wider(names_from = condition, values_from = n, values_fill = 0) %>% 
+  mutate(`Proportion with Open Data and/or Code`= round((`Open Data` + `Open Code` + Both)/(`Open Data` + `Open Code` + Both + Neither), 2)) %>%
+  kable(booktabs = TRUE)
+```
+
+We performed some simple keyword searches within the titles and abstracts of our data set to examine potential differences in the prevalence of open data or code for specific types of papers.
+For pre-prints including the term "machine learning" (n = 21), the proportion of pre-prints with open data or code markers rose to 38 per cent, double that of the sample overall (Table \@ref(tab:summary-by-type)).
+Keywords relating to simulation appeared in 80 sampled pre-prints and keywords related to modelling appeared in over one third of our sampled pre-prints.
+The latter two categories did not contain pre-prints with open data or code markers at a rate much higher than the general sample, with 22 and 24 per cent of each type of paper containing either open data or open code markers compared to 19 per cent overall.
+Due to the significant role modelling has played in the context of COVID-19, it is likely that a simple keyword search is not exclusive enough for us to judge this subset as though it only contains pre-prints presenting their own, novel models.
 
@@
 We run our analysis in `R` [@citeR].
+We fit generalized linear models with open data and open code markers as binary variables (representing their presence or absence in a pre-print) as functions of the date at which a pre-print was posted.
 
-In this analysis we distinguish between *posting* (the event that a pre-print is uploaded to medRxiv) and *publishing* (the event that the pre-print has subsequently been published in a peer reviewed journal).
+The models below display in greater clarity the negligible role time appears to play in the proportion of pre-prints with open data or open code posted to medRxiv.
+Both models output negligibly small, non-significant coefficients on the date term, indicating limited influence of the date a pre-print was posted on its likelihood of containing open data or code markers.
 
-```{r}
-# logit model: posting rate vs. open data, publication rate vs. open code
+```{r data-time-model}
+glm(is_open_data ~ date, family = binomial, data = med_open_data_results) %>%
+  summary()
 ```
 
-```{r}
-# logit model: open data/code vs. publication status
-# pub_model <- glm(published ~ is_open_data + is_open_code, family = binomial, data = med_open_data_results)
+```{r code-time-model}
+glm(is_open_code ~ date, family = binomial, data = med_open_data_results) %>%
+  summary()
+```
+
+We get similar results for publication status as a function of open data or open code presence, however we do see a significant (p < 0.05) coefficient indicating that the presence of open code markers may have a negative influence on a pre-print's likelihood of eventual publication.
+It is unrealistic to assume that this means pre-prints with open code are less likely to be published on the basis of their code alone.
+There may be common cause factors involved, such as a disinclination of journals to publish purely computational work as has been the case with pre-print repositories like bioRxiv [@kwon2020].
+
+```{r data-published-model}
+glm(published ~ as.factor(is_open_data), family = binomial, data = med_open_data_results) %>%
+  summary()
+```
+```{r code-published-model}
+glm(published ~ as.factor(is_open_code), family = binomial, data = med_open_data_results) %>%
+  summary()
 ```
@@
 
+Less than 20 per cent of sampled pre-prints indicated any open data or code markers.
+Of those that did contain markers, 4 per cent contained open code markers only, 8 percent contained open data markers only, and 7 per cent contained both open data and code markers.
+
+We find that time has little influence over the likelihood of a pre-print to have open data or code markers.
+In the context of the COVID-19 pandemic, this means that the prevalence of open data and code markers has not consistently increased nor decreased over the course of the pandemic, and also appears to be unimpacted by the monthly rate of pre-prints posted to medRxiv (which increased dramatically between January and May 2020 and has fluctuated since).
+On one hand, it is encouraging to note that open data and code does not appear to have suffered in times of high publication rates, namely April through July 2020.
+On the other hand, one might hope that more data has become openly available throughout the course of the pandemic, or that the rate of availability of open data or code has improved as the scientific community has recognized the importance of global collaboration in combating the pandemic, neither of which appear to be the case.
+
+The presence of open data or code markers does not appear to have significant influence over whether or not a pre-print posted to medRxiv has subsequently been published in a peer reviewed journal, however the proportion of published pre-prints with open data or code markers appears to be slightly lower than those that have not been published (15 per cent versus 20 per cent).
+This is not necessarily a significant result given the size of our sample and the potential inaccuracies in the medRxiv API's attempts to identify publication, however it does provide a potential area of further study.
+
+The proportion of pre-prints with open data or code markers is significantly higher among pre-prints with keywords indicating machine learning-based research.
+This is a somewhat anticipated result, as machine learning tends to rely more heavily on computational and code-focused methodology, however the subset of sampled pre-prints with keywords relating to simulation is very small.
+On the other hand, the prevalence of pre-prints with open data or code markers only saw a slight increase in the subset of pre-prints with either modelling or simulation keywords.
+Since the pandemic has seen a rise in scientific and public focus on epidemiological modelling, it is likely that not all papers showing keywords for modelling actually propose their own models which would account for the minimal increase of open data and code markers in this context.
+
 # Discussion
 
-There are many factors that impact the ability of an author to post make their data available
+Transparency and reproducibility are two hallmarks of quality scientific research.
+Open data and open code contribute greatly to both in allowing the scientific community to more easily verify the authenticity of purported scientific discovery and its supporting evidence, which is especially important in cases where scientific research may quickly and directly impact clinical practice or policy such as during the COVID-19 pandemic.
+Among a myriad of other impacts on biomedical research, COVID-19 has dramatically increased in the popularity of pre-prints from both a production and consumption stand point.
+The number of COVID-19 pre-prints posted to medRxiv increased dramatically in the early stages of the pandemic while non-COVID-19 pre-print rates remained consistent.
+The same trends were apparent in abstracts accessed by medRxiv users, where COVID-19 pre-print abstracts were viewed over 15 times the rate of non-COVID-19 pre-print abstracts [@citeFraser].
+For these reasons, it is more important now than ever to examine open science standards and reproducibility within pre-print repositories.
 
-## First discussion point - Time
-- How has open data/code shifted over the course of the pandemic?
-- How has open data/code changed with publication rate?
+Open data is generally accepted to be beneficial to the scientific process, and to a paper's reproducibility potential, hence it is concerning that over 80 per cent of pre-prints in our sample contained no open data markers.
+This concern is slightly mitigated by recognition of challenges in working with biomedical data compared with data in other fields, notably privacy and ethics concerns when working with personal data [@Floca2014].
+The COVID-19 pandemic has seen an uptake in open science practices globally, as evidenced by the creation of open data repositories such as the dashboard maintained by the Center for Systems Science and Engineering at Johns Hopkins University [@citeCSSE] or the wave of publishers who have removed pay walls from published COVID-19 research [@gill2020].
+An important next step may compare open data and code availability in COVID-19 pre-prints with those from other topics posted to medRxiv to examine whether the pandemic has increased transparency from the previous norm.
 
-## Second discussion point - Eventual Publication
-- See weaknesses
+Open code as an open science marker is much more context and field-dependent, as not all biomedical research papers will rely on computational methods for their analyses.
+However in pre-prints where code comprises a large portion of the methodology or results, posting it openly to repositories like GitHub contributes greatly to a pre-print's potential reproducability.
+This gains importance as computational methods become increasingly popular in the rush to form predictions about emerging situations with limited data or laboratory research, which was the case for modelling studies in the early days of the COVID-19 pandemic (CITE).
+We also see growing concern over the quality and consequences of this sort of research, with bioRxiv barring purely computational work [@kwon2020].
 
-## Third discussion point - Type of Paper
-- A significantly higher proportion if
+Many concerns have arisen from the unprecedented rate at which COVID-19 research has been posted and consumed via pre-print servers, particularly in the early stages of the pandemic [@raynaud2021].
+Any rushed scientific research has potential to skip (or at least place less precedence on) quality open science practices, thus it may be reasonable to expect a decrease of open data or code markers in the pre-prints posted during times of increased overall posting to medRxiv.
+In our analysis, we found little relationship between time posted and likelihood of having open data or code markers with the proportion of papers containing these markers fluctuating greatly from month to month and no apparent decrease during periods of increased publication.
+This suggests that open science practices are more highly influenced by other factors, perhaps publication bias or the nature of the paper itself.
+On the other hand, we do not see an overall long-term increase in either open data or open code markers throughout our year of analysis which we may expect in the context of the aforementioned open science movements the pandemic has fostered.
+Although not pre-print specific, @else2020 found that overall research output has fluctuated between different fields and topics (namely modelling disease spread, public health, diagnostics and testing, mental health, and hospital mortality) throughout different stages of the pandemic which may account for some of the fluctuation and overall lack of linear trend over the course of the year.
+
+To emphasize the ongoing need for open data and code in modelling a pandemic, we consider two high profile epidemiological models that emerged in early 2020.
+modelling was conducted by Imperial College London (ICL) [@ferguson2020] and the Institute for Health Metrics and Evaluation (IHME) at the University of Washington [@murray2020], and both papers were initially posted to pre-print servers.
+The ICL model went on to become the most cited pre-print as of December 2020 [@else2020], and both had significant influence over policy and public health decisions worldwide [@adam2020].
+An independent review of these two models by @jin2020 found that while code and data were openly available for both, only the ICL model was reproducible due to limited transparency on the underlying methodology of the IHME model.
+The open source nature of these papers was fundamental to reproduction attempts and is a great example of the need for open data and code in reproducing COVID-19 research, particularly in evaluating pre-prints as they begin to influence public decision-making.
+
+In the context of the above factors, it was disheartening in our analysis to find that the proportion of modelling- and simulation-related pre-prints with open data or code increased only marginally from that of the entire sample.
+One might hope that modelling papers should universally be subject to the same analysis as conducted by @jin2020 as for the examples above, which is made possible by the availability of relevant code and data.
+Although our analysis was not particularly robust, this shows a need for future investigation and potential overall improvement in open science standards for these types of pre-prints (of course subject to the data and code considerations already discussed).
+This need is again emphasized by the new found speed at which pre-print articles may gain public, media, and political attention in the context of the pandemic.
+
+Beyond pre-prints, COVID-19 has had great influence over publication and peer review processes as well, with expedited review timelines for COVID-19 papers at the expense of longer waits for other scientific research [@else2020].
+Needless to say, it is important that open data and code standards be maintained in published work as well.
+Our findings in this regard were two fold: that open data or code markers do not appear to directly influence a pre-print's eventual publication, and that a lower proportion of published papers contain either open data or code markers than the general sample.
+Both of these raise concerns over publication bias, the potential that journals have favored novel yet less transparent or reproducible papers over those with null results but a high standard of open science practices.
+Concerns have already been raised through systemic reviews of COVID-19 publications [@raynaud2021], and oversights in data accessibility have lead to high profile retractions of publications in the past, for example two papers from The Lancet and the New England Journal of Medicine that were withdrawn due to concerns over the private nature of their underlying data set [@ledford2020].
+
+In all fields of science, increasing access to data and code used for pre-printed or published research is a step in the direction of more transparent, reproducible, and reliable research.
+The ongoing COVID-19 pandemic has created a novel, constantly changing scientific culture that should be navigated with the utmost care so as to uphold standards of scientific practice for both the research community and the safety of the general public.
+Our analysis shows that there is much improvement to be made in the areas of open data and code availability within COVID-19 pre-print papers on medRxiv.
 
@@
 
-- No open data/code was verified manually, all dependent on algorithm
-- Publication info has high rate of false negatives (i.e. medRxiv data seems to miss a lot of papers that go on to be published)
-- Want to look at geographic distribution and prevalence of open data/code - influence on open data policies and timing throughout pandemic
+In this paper we consider only pre-prints from medRxiv, but this analysis can and should be extended to other pre-print servers including bioRxiv and arXiv.
+The `medrxivr` package [@citemedrxivr] can be used with the bioRxiv API as well, and our code can be modified to conduct the same scraping and text mining procedure as was used for medRxiv data.
+
+We also wish to expand our analysis to consider the geographic distribution of research and the potential influence of different practices and policies concerning open science as pre-prints vary by location.
+This is pertinent to our current paper as the epicenter of the virus spread (and thus of scientific output) has shifted throughout the pandemic which has implications for our time-based analysis.
+
+An important weakness to note is the potential presence of false negatives in indicators of publication in our data set.
+@abdill2019 estimate that the false-negative rate may be as high as 37.5 percent for data pulled from the bioRxiv API, meaning analysis of published papers may represent only a fraction of those that have actually been published.
+It is unclear to what extent this is the case for medRxiv or what bias may exist in the subset of pre-prints for which publication was detected, as it is likely that this process relies on title-based text matching [@abdill2019].
+It is also likely that some of our more recent sampled pre-prints will be published in future which we could not account for at the time of our data collection.
+
+We also recognize that this analysis relies heavily on text-based analysis which was not verfied directly in most cases and may lead to higher levels of uncertainty.
+In future, we wish to take smaller sub-samples to validate factors like publication status or paper topic beyond simple keyword searches.
+or API output.
 
@@
 
-# Appendix {-}
+# Appendix 1
+Insert details on keyword search used for machine learning/modelling/simulation
 

### 2021-02-20 outputs/paper/paper.Rmd
First draft done!!!!!!

@@
 ---
-title: "Reproducibility of COVID-19 pre-prints on medRxiv"
-subtitle: "Markers of open code or data not identified in 81 per cent of pre-prints"
+title: "Reproducibility of COVID-19 pre-prints on medRxiv in 2020"
+subtitle: "Markers of open code or data not found in 81 per cent of pre-prints"
 author: "Annie Collins^[University of Toronto.]"
-thanks: "Paper presented at Toronto Workshop on Reproducibility, 26 Februrary 2021.
+thanks: "Paper presented at Toronto Workshop on Reproducibility, 26 February 2021.
 Collins thanks CANSSI Ontario for financial support.
@@
 date: "`r format(Sys.time(), '%d %B %Y')`"
-abstract: "We create a dataset of all the pre-prints published on medRxiv between between 28 January 2020 and 31 January 2021.
-We extract the text from these pre-prints and parse them looking for for keyword markers signalling the availability of the data and code underpinning the pre-print.
+abstract: "We create a dataset of all the pre-prints published on medRxiv between 28 January 2020 and 31 January 2021.
+We extract the text from these pre-prints and parse them looking for keyword markers signalling the availability of the data and code underpinning the pre-print.
 We are unable to find markers of either open data or open code for 81 per cent of the pre-prints in our sample.
@@
 library(tidyverse)
+library(stargazer)
 ```
@@
 med_open_data_results <- read_csv(here("outputs/data/med_open_data_results.csv"))
+
+med_results <- read_csv(here::here("outputs/data/med_results.csv")) # All COVID medRxiv papers (9,929)
 ```
@@
 
-Scientists use open repositories of papers to more quickly disseminate their research than is possible in traditional journals.
-These repositories, such as arxiv, bioRxiv, and medRxiv, are a critical component of science and many results build on the work published there, thus it is important that the results that are published are credible.
-Pre-print repositories, specifically medRxiv, have drawn unprecedented attention in the context of the 2019 novel coronavirus (COVID-19) pandemic and the changes it has thrust upon the scientific community [@else2020].
+Scientists use open repositories of papers to more quickly disseminate their research than is possible in traditional journals or conference proceedings.
+These repositories, such as arXiv, bioRxiv, medRxiv, and SocArXiv, are a critical component of science and many results build on the work published there.
+Thus it is important that the results that are published are credible.
+Pre-print repositories, specifically medRxiv, have drawn unprecedented attention in the context of the 2019 novel coronavirus (COVID-19) pandemic and the changes it has imposed on the scientific community [@else2020].
 These repositories are not peer-reviewed, and, in general, anyone with appropriate academic credentials can submit a paper.
@@
 While neither peer-review nor credentials are a panacea nor a guarantee of quality, given the importance of these repositories, it is important that scientists impose on themselves various standards for their results.
-Following @weissgerber2021automated we examine papers about COVID-19 published to medRxiv throughout 2020.
+Following @weissgerber2021automated we examine papers about COVID-19 published to medRxiv through to January 2021.
 We search for markers of open science as indicators of reproducibility, specifically open data and open code.
@@
 
-The remainder of this paper is structured as follows: first, we discuss the process of constructing our data set through retrieving pre-prints from the medRxiv repository and mining them for open data and open code markers.
-Then we will explore some key findings in this raw data and explore some logistic regression models that support these findings.
-Lastly we will discuss the implications of these findings in the broader context of reproducibility and science during the COVID-19 pandemic, as well as next steps to expand on our findings and questions raised in the research process.
+The remainder of this paper is structured as follows: in Section \@ref(data-and-methodology) we discuss the process of constructing our dataset through retrieving pre-prints from the medRxiv repository and mining them for open data and open code markers.
+In Sections \@ref(model) and \@ref(results) we explore some key findings in this raw data and explore some logistic regression models that support these findings.
+Finally, in Section \@ref(discussion) we discuss the implications of these findings in the broader context of reproducibility and science during the COVID-19 pandemic, as well as next steps to expand on our findings and questions raised in the research process.
 
-# Data & Methodology
+# Data and Methodology
 
-Our primary data set consists of information extracted from the medRxiv repository combined with output from running a sample of COVID-19-related pre-prints through the Open Data Detection in Publications (ODDPub) text mining algorithm [@citePDDPub], using the `oddpub` package [@citeODDPubpackage].
+## Overview
 
-We constructed this data set by first creating a local copy of the medRxiv repository via the medRxiv API and then filtering for papers related to the COVID-19 pandemic through several keyword searches to create our sampling frame (N = 9,929, including only the most recent version of any given pre-print).
-This data includes the following variables for each pre-print in the repository: title, abstract, author(s), date posted, research field, DOI, version number, corresponding author, corresponding author's institutional affiliation, and published DOI (if the paper has since been published in a peer reviewed journal).
+Our primary dataset consists of information extracted from the medRxiv repository combined with output from running a sample of COVID-19-related pre-prints through the Open Data Detection in Publications (ODDPub) text mining algorithm [@citePDDPub], using the `oddpub` package [@citeODDPubpackage].
+
+We constructed this dataset by first creating a local copy of the medRxiv repository via the medRxiv API.
+We identified papers related to the COVID-19 pandemic through several keyword searches to create our sampling frame (N = 9,929, including only the most recent version of any given pre-print).
+This data includes the following information about each pre-print in the repository: title, abstract, author(s), date posted, research field, DOI, version number, corresponding author, corresponding author's institutional affiliation, and published DOI (if the paper has since been published in a peer-reviewed journal).
 
 We then selected a random sample of these papers (N = 1,200) to check for open data and code markers using the ODDPub algorithm.
-This required downloading each paper as a PDF, converting the PDFs to text files, and conducting the open data and code detecting procedure to produce a results table indicating the presence of open data or open code markers in each paper (with a value of TRUE or FALSE for each marker and the relevant open data or open code statements when applicable).
-These PDFs were downloaded and converted to text files using the `medrxivr` package [@citemedrxivr].
+This required downloading each paper as a PDF and then converting the PDFs to text files, using the `medrxivr` package [@citemedrxivr].
+We then conducted the open data and open code detection procedure.
+This produced a results table indicating the presence of open data or open code markers in each paper (with a binary variable for each marker, and the relevant open data or open code statements when applicable).
 
-Our final data set was formed by joining these two tables together via DOI to form a data set including all original, qualitative information for each pre-print alongside its open data and open code status and markers.
+Our final dataset was formed by joining these two tables together via DOI to form a dataset including all original, qualitative information for each pre-print alongside its open data and open code status and markers.
 
-```{r monthly-papers-total, fig.cap = "Number of pre-prints related to COVID-19 posted to medRxiv"}
-# Number of COVID-related papers posted each month in total
-med_results <- read_csv(here::here("outputs/data/med_results.csv")) # All COVID medRxiv papers (9,929)
-
+```{r monthly-papers-total, fig.cap = "Number of pre-prints related to COVID-19 posted to medRxiv", out.width="90%", fig.align = "center"}
 med_results %>% 
@@
   geom_col() + 
-  labs(title = "Pre-prints Posted per Month",
+  labs(title = "Pre-prints posted per month",
        subtitle = "medRxiv, Total = 9,929",
        x = "Month",
-       y = "Number of Pre-prints") +
+       y = "Number of pre-prints") +
   theme_minimal()
 ```
+
+## Summary statistics
 
@@
 Broadly, we are unable to find markers of either open data or open code for around 81 per cent of the 1,200 sampled pre-prints.
-The remaining 19 per cent of pre-prints was comprised of 4 percent of the sample containing markers for open code, 8 percent of the sample with markers for open data, and 7 percent of the sample with markers for both open data and open code (Table \@ref(tab:summarycounts)).
+The remaining 19 per cent of pre-prints was comprised of 4 per cent of the sample containing markers for open code, 8 per cent of the sample with markers for open data, and 7 per cent of the sample with markers for both open data and open code (Table \@ref(tab:summarycounts)).
 
@@
          is_open_code = ifelse(is_open_code == 0, "No", "Yes")) %>% 
-  kable(col.names = c("Contains Open Data Markers", "Contains Open Code Markers", "Count", "Proportion of Total"),
+  kable(col.names = c("Open data markers", "Open code markers", "Count", "Proportion of total"),
         caption = "Counts and proportions of open data and code markers in our sample",
@@
 The distribution of total sampled pre-prints and sampled pre-prints with open data or code markers roughly follows that of COVID-19-related pre-prints posted in general (Figure \@ref(fig:monthly-papers-condition-stack)).
-The proportion of pre-prints with open data or code has fluctuated over time but shows no consistent overall increase or decrease throughout the course of the pandemic, nor in conjunction with increases or decreases in the total number of pre-prints posted to medRxiv (Figure \@ref(fig:monthly-proporiton-of-open).
-In our data set, only one pre-print was sampled for the month of January 2020.
-This pre-print contained neither open data nor open code markers, thus the 0 per cent rate of open data and code for this month should be treated as an outlier within the sample.
+The proportion of pre-prints with open data or code has fluctuated over time but shows no consistent overall increase or decrease throughout the course of the pandemic, nor in conjunction with increases or decreases in the total number of pre-prints posted to medRxiv (Figure \@ref(fig:monthly-proportion-of-open)).
+In our dataset, only one pre-print was sampled for the month of January 2020.
+This pre-print contained neither open data nor open code markers, thus the 0 per cent rate of open data and code for this month will be treated as an outlier, and removed modelling purposes.
 
-```{r monthly-papers-condition-stack, fig.cap = "Number of pre-prints related to COVID-19 sampled from medRxiv, distinguished by presence of open data or code markers"}
+```{r monthly-papers-condition-stack, fig.cap = "Number of pre-prints related to COVID-19 sampled from medRxiv, distinguished by presence of open data or code markers", out.width="90%", fig.align = "center"}
 # Number of papers for each open data/code status per month
@@
                position = "stack")) +
-  labs(fill = "Type of Marker") +
+  labs(fill = "Type of marker") +
   scale_x_discrete(breaks=c("2020-01-01","2020-04-01","2020-07-01", "2020-10-01", "2021-01-01"), 
                    labels=c("Jan 2020","Apr 2020","Jul 2020", "Oct 2020", "Jan 2021")) +
-  ylab("Number of Pre-prints") +
+  ylab("Number of pre-prints") +
   xlab("Month") +
-  labs(title="Sampled Pre-prints by Month", subtitle="medRxiv, Total = 1,200") +
+  labs(title="Sampled pre-prints by month", subtitle="medRxiv, Total = 1,200") +
   theme_minimal()
@@
 
-```{r proportion-of-open, fig.cap= "Proportion of pre-prints in sample with open data or open code markers by month"}
+```{r monthly-proportion-of-open, fig.cap= "Proportion of pre-prints in sample with open data or open code markers by month", out.width="90%", fig.align = "center"}
 # Proportion of papers posted with open data or open code each month
@@
   ggplot() +
-  geom_line(data = med_month_sum_cov, aes(month, prop_open_data, color = "Open Data")) +
-  geom_line(data = med_month_sum_cov, aes(month, prop_open_code, color = "Open Code")) +
-  ggtitle("Proportion of Sampled Pre-prints with Open Data or Code Markers") +
-  xlab("Month") +
-  ylab("Proportion of Pre-prints") +
-  labs(colour = "Type of Marker") + 
+  geom_line(data = med_month_sum_cov, aes(month, prop_open_data, color = "Open data")) +
+  geom_line(data = med_month_sum_cov, aes(month, prop_open_code, color = "Open code")) +
+  ggtitle("Proportion of sampled pre-prints with open data or code markers") +
+  labs(colour = "Type of marker",
+       x = "Month",
+       y = "Proportion of pre-prints") + 
   theme_minimal()
@@
 
-## Publication
+## Publication status
+
+In Table \@ref(tab:open-published-summary) we disaggregate pre-prints by whether there is an indication that it was published.
+We find that the proportion of pre-prints with open data or code markers among those that have been published is approximately five per cent lower compared with pre-prints that have not been published (Table \@ref(tab:open-published-summary)).
+
 ```{r open-published-summary}
@@
 published_open_status$condition[published_open_status$condition == 0] <- "Neither"
-published_open_status$condition[published_open_status$condition == 1 & published_open_status$is_open_code == 1] <- "Open Code"
-published_open_status$condition[published_open_status$condition == 1 & published_open_status$is_open_data == 1] <- "Open Data"
+published_open_status$condition[published_open_status$condition == 1 & published_open_status$is_open_code == 1] <- "Open code"
+published_open_status$condition[published_open_status$condition == 1 & published_open_status$is_open_data == 1] <- "Open data"
 
@@
   pivot_wider(names_from = condition, values_from = n) %>%
-  mutate(published = ifelse(published == 0, "No", "Yes"), `Proportion with Open Data and/or Code`= round((`Open Data` + `Open Code` + Both)/(`Open Data` + `Open Code` + Both + Neither), 2)) %>%
+  mutate(published = ifelse(published == 0, "No", "Yes"), `Proportion with either/both`= round((`Open data` + `Open code` + Both)/(`Open data` + `Open code` + Both + Neither), 2)) %>%
   rename(Published = published) %>%
@@
 
-```{r open-published-stack}
+There was a low number of papers that had markers of either open data or code in both those that were published and those that were not published (Figure \@ref(fig:open-published-stack)).
+
+```{r open-published-stack, fig.cap= "Number of pre-prints in sample with open data or open code markers by publication status", out.width="90%", fig.align = "center"}
 published_open_status$published[published_open_status$published == 0] <- "Published"
@@
   ggplot() + 
-  geom_bar(aes(x = published, fill=factor(condition, levels = c("Neither", "Open Code", "Open Data", "Both")), position = "stack")) +
-  labs(fill = "Type of Marker") +
-  ylab("Number of Pre-prints") +
-  ggtitle("Pre-prints by Publication Status") +
+  geom_bar(aes(x = published, fill=factor(condition, levels = c("Neither", "Open code", "Open data", "Both")), position = "stack")) +
+  labs(fill = "Type of marker",
+       y = "Number of pre-prints",
+       x = "Publication status") +
+  ggtitle("Pre-prints by publication status") +
   theme_minimal()
@@
 
-We see that the proportion of pre-prints with open data or code markers among those that have been published is approximately 5 per cent lower than that of pre-prints which have not been published (Table \@ref(tab:open-published-summary)).
-There was a low number of papers that had markers of either open data or code in both those that were published and those that were not published (Figure \@ref(fig:open-published-stack)).
-It is important to note here that our data set imperfectly characterizes publication.
-In particular, it does not have the publication details for some papers that were published, and even if it were a perfect record, there is a publication lag (estimated at an average of 60 days) that may skew the results [@kwon2020].
+It is important to note that our dataset imperfectly characterizes publication.
+In particular, it does not have the publication details for some papers that were published.
+And even if it were a perfect record, there is a publication lag (estimated at an average of around 60 days) that may skew the results [@kwon2020].
 
-## Type of Pre-print
+## Type of pre-print
 
-```{r stack-by-type}
+There are a variety of different types of pre-prints on medRxiv, including those focused on machine learning, modelling, and simulation.
+It may be that there are differences in open science practices between these.
+For instance, in papers related to simulation there is less likely to be issues around sharing code.
+
+To characterize the pre-prints by type, we performed keyword searches within the titles and abstracts of our dataset to examine potential differences in the prevalence of open data or code for specific types of papers.
+There were 21 sampled pre-prints that included the term 'machine learning'.
+Of those, the proportion of pre-prints with open data or code markers rose to 38 per cent, double that of the sample overall (Table \@ref(tab:summary-by-type)).
+Similarly, keywords relating to simulation appeared in 80 sampled pre-prints and keywords related to modelling appeared in over one-third of our sampled pre-prints.
+The latter two categories did not contain pre-prints with open data or code markers at a rate much higher than the general sample, with 22 and 24 per cent of each type of paper containing either open data or open code markers compared to 19 per cent overall.
+However, due to the significant role that modelling has played in the context of COVID-19, it is likely that a simple keyword search does not have the resolution needed to properly characterize this subset, it is it possible that it only contains pre-prints presenting their own, novel, models.
+
+```{r stack-by-type, fig.cap= "Number of pre-prints in sample with open data or open code markers by type", out.width="90%", fig.align = "center"}
+
 # Number of open data/code papers by keyword for different types
@@
 paper_type_keywords$condition[paper_type_keywords$condition == 0] <- "Neither"
-paper_type_keywords$condition[paper_type_keywords$condition == 1 & open_status$is_open_code == 1] <- "Open Code"
-paper_type_keywords$condition[paper_type_keywords$condition == 1 & open_status$is_open_data == 1] <- "Open Data"
+paper_type_keywords$condition[paper_type_keywords$condition == 1 & open_status$is_open_code == 1] <- "Open code"
+paper_type_keywords$condition[paper_type_keywords$condition == 1 & open_status$is_open_data == 1] <- "Open data"
 paper_type_keywords$`Machine Learning` <- str_detect( paper_type_keywords$title, "machine learning") | 
@@
   filter(Value == TRUE)
-# Plot
-paper_type_keywords %>% ggplot() + 
-  geom_bar(aes(x = Type, fill=factor(condition, levels = c("Neither", "Open Code", "Open Data", "Both")), position = "stack")) +
-  labs(fill = "Type of Marker") +
-  scale_x_discrete(labels=c("Machine Learning", "modelling", "Simulation")) +
-  ylab("Number of Pre-prints") +
-  xlab("Month") +
-  ggtitle("Sampled Pre-prints by Month") +
-  theme_minimal()
 
+# # Plot
+# paper_type_keywords %>% ggplot() + 
+#   geom_bar(aes(x = Type, fill=factor(condition, levels = c("Neither", "Open code", "Open data", "Both")), position = "stack")) +
+#   labs(fill = "Type of marker") +
+#   scale_x_discrete(labels=c("Machine learning", "Modelling", "Simulation")) +
+#   ylab("Number of pre-prints") +
+#   xlab("Month") +
+#   ggtitle("Sampled pre-prints by type") +
+#   theme_minimal()
 ```
@@
   pivot_wider(names_from = condition, values_from = n, values_fill = 0) %>% 
-  mutate(`Proportion with Open Data and/or Code`= round((`Open Data` + `Open Code` + Both)/(`Open Data` + `Open Code` + Both + Neither), 2)) %>%
-  kable(booktabs = TRUE)
+  mutate(Type = if_else(Type == "modelling", "Modelling", Type),
+         Type = if_else(Type == "Machine Learning", "Machine learning", Type),
+         ) %>% 
+  mutate(`Proportion with either/both`= round((`Open data` + `Open code` + Both)/(`Open data` + `Open code` + Both + Neither), 2)) %>%
+  kable(caption = "Counts and proportions of open data markers by the type of pre-print",
+        booktabs = TRUE)
 ```
-
-We performed some simple keyword searches within the titles and abstracts of our data set to examine potential differences in the prevalence of open data or code for specific types of papers.
-For pre-prints including the term "machine learning" (n = 21), the proportion of pre-prints with open data or code markers rose to 38 per cent, double that of the sample overall (Table \@ref(tab:summary-by-type)).
-Keywords relating to simulation appeared in 80 sampled pre-prints and keywords related to modelling appeared in over one third of our sampled pre-prints.
-The latter two categories did not contain pre-prints with open data or code markers at a rate much higher than the general sample, with 22 and 24 per cent of each type of paper containing either open data or open code markers compared to 19 per cent overall.
-Due to the significant role modelling has played in the context of COVID-19, it is likely that a simple keyword search is not exclusive enough for us to judge this subset as though it only contains pre-prints presenting their own, novel models.
 
@@
 
-We run our analysis in `R` [@citeR].
-We fit generalized linear models with open data and open code markers as binary variables (representing their presence or absence in a pre-print) as functions of the date at which a pre-print was posted.
+We are interested in understanding firstly whether open data and open code became more likely over time, and secondly whether the likelihood that at pre-print ends up published is related to provision of open data and open code.
+To examine these questions we estimate Equation \@ref(eq:first) by fitting two separate generalized linear models with open data and open code markers as binary variables (representing their presence or absence in a pre-print) that are explained as functions of the date at which a pre-print was posted.
 
-The models below display in greater clarity the negligible role time appears to play in the proportion of pre-prints with open data or open code posted to medRxiv.
+\begin{equation} 
+\mbox{Open data/code} = \beta_0 + \beta_1 \mbox{date} (\#eq:first)
+\end{equation}
+
+We then estimate Equation \@ref(eq:second), again by fitting separate generalized linear models, looking at whether a pre-print is published, based on whether it had open code/data.
+
+\begin{equation} 
+\mbox{Open data/code} = \beta_0 + \beta_1 \mbox{date} (\#eq:second)
+\end{equation}
+
+We estimate our models in the statistical programming language `R` [@citeR], using the function `glm()`.
+
+Our estimates (Table \@ref(tab:datatimemodel)) indicate, in greater clarity, the negligible role time appears to play in the proportion of pre-prints with open data or open code posted to medRxiv.
 Both models output negligibly small, non-significant coefficients on the date term, indicating limited influence of the date a pre-print was posted on its likelihood of containing open data or code markers.
 
-```{r data-time-model}
-glm(is_open_data ~ date, family = binomial, data = med_open_data_results) %>%
-  summary()
+```{r, echo=FALSE, warning=FALSE, message=FALSE, results = 'asis'}
+data_on_date <- glm(is_open_data ~ date, family = binomial, data = med_open_data_results)
+code_on_date <- glm(is_open_code ~ date, family = binomial, data = med_open_data_results)
+
+published_on_data <- glm(published ~ as.factor(is_open_data), family = binomial, data = med_open_data_results)
+published_on_code <- glm(published ~ as.factor(is_open_code), family = binomial, data = med_open_data_results)
+
+stargazer(data_on_date, code_on_date, published_on_data, published_on_code,
+          header = FALSE,
+          title = 'Estimation results',
+          dep.var.labels = c('Open data', 'Open code', 'Published'),
+          covariate.labels=c('Date', 'Has open data', 'Has open code', 'Constant'),
+          report=('vc*s'),
+          no.space = TRUE,
+          digits=2,
+          digits.extra=1,
+          notes.append = TRUE,
+          notes.align = "l",
+          ci = FALSE,
+          ci.level=0.95,
+          label = "tab:datatimemodel"
+          )
 ```
 
-```{r code-time-model}
-glm(is_open_code ~ date, family = binomial, data = med_open_data_results) %>%
-  summary()
-```
-
-We get similar results for publication status as a function of open data or open code presence, however we do see a significant (p < 0.05) coefficient indicating that the presence of open code markers may have a negative influence on a pre-print's likelihood of eventual publication.
+We get similar results for publication status as a function of open data or open code presence; however we do see a significant (p < 0.05) coefficient indicating that the presence of open code markers may have a negative influence on a pre-print's likelihood of eventual publication.
 It is unrealistic to assume that this means pre-prints with open code are less likely to be published on the basis of their code alone.
 There may be common cause factors involved, such as a disinclination of journals to publish purely computational work as has been the case with pre-print repositories like bioRxiv [@kwon2020].
-
-```{r data-published-model}
-glm(published ~ as.factor(is_open_data), family = binomial, data = med_open_data_results) %>%
-  summary()
-```
-```{r code-published-model}
-glm(published ~ as.factor(is_open_code), family = binomial, data = med_open_data_results) %>%
-  summary()
-```
 
@@
 Less than 20 per cent of sampled pre-prints indicated any open data or code markers.
-Of those that did contain markers, 4 per cent contained open code markers only, 8 percent contained open data markers only, and 7 per cent contained both open data and code markers.
+Of those that did contain markers, 4 per cent contained open code markers only, 8 per cent contained open data markers only, and 7 per cent contained both open data and code markers.
 
@@
 
-Transparency and reproducibility are two hallmarks of quality scientific research.
+## On the role of transparency and reproducibility
+
+Transparency and reproducibility are hallmarks of quality scientific research.
 Open data and open code contribute greatly to both in allowing the scientific community to more easily verify the authenticity of purported scientific discovery and its supporting evidence, which is especially important in cases where scientific research may quickly and directly impact clinical practice or policy such as during the COVID-19 pandemic.
-Among a myriad of other impacts on biomedical research, COVID-19 has dramatically increased in the popularity of pre-prints from both a production and consumption stand point.
+Among a myriad of other impacts on biomedical research, COVID-19 has dramatically increased the popularity of pre-prints from both a production and consumption stand-point.
 The number of COVID-19 pre-prints posted to medRxiv increased dramatically in the early stages of the pandemic while non-COVID-19 pre-print rates remained consistent.
@@
 This concern is slightly mitigated by recognition of challenges in working with biomedical data compared with data in other fields, notably privacy and ethics concerns when working with personal data [@Floca2014].
-The COVID-19 pandemic has seen an uptake in open science practices globally, as evidenced by the creation of open data repositories such as the dashboard maintained by the Center for Systems Science and Engineering at Johns Hopkins University [@citeCSSE] or the wave of publishers who have removed pay walls from published COVID-19 research [@gill2020].
+The COVID-19 pandemic has seen an uptake in open science practices globally, as evidenced by the creation of open data repositories such as the dashboard maintained by the Center for Systems Science and Engineering at Johns Hopkins University [@citeCSSE] or the large number of publishers who have removed paywalls from published COVID-19 research [@gill2020].
 An important next step may compare open data and code availability in COVID-19 pre-prints with those from other topics posted to medRxiv to examine whether the pandemic has increased transparency from the previous norm.
@@
 Open code as an open science marker is much more context and field-dependent, as not all biomedical research papers will rely on computational methods for their analyses.
-However in pre-prints where code comprises a large portion of the methodology or results, posting it openly to repositories like GitHub contributes greatly to a pre-print's potential reproducability.
+However, in pre-prints where code comprises a large portion of the methodology or results, posting it openly to repositories like GitHub contributes greatly to a pre-print's potential reproducibility.
 This gains importance as computational methods become increasingly popular in the rush to form predictions about emerging situations with limited data or laboratory research, which was the case for modelling studies in the early days of the COVID-19 pandemic (CITE).
-We also see growing concern over the quality and consequences of this sort of research, with bioRxiv barring purely computational work [@kwon2020].
+We also see growing concern over the quality and consequences of this sort of research, with bioRxiv not allowing purely computational work [@kwon2020].
 
-Many concerns have arisen from the unprecedented rate at which COVID-19 research has been posted and consumed via pre-print servers, particularly in the early stages of the pandemic [@raynaud2021].
+## The role of of pre-print repositories
+
+Many concerns have arisen from the unprecedented rate at which COVID-19 research has been posted and consumed via pre-print repositories, particularly in the early stages of the pandemic [@raynaud2021].
 Any rushed scientific research has potential to skip (or at least place less precedence on) quality open science practices, thus it may be reasonable to expect a decrease of open data or code markers in the pre-prints posted during times of increased overall posting to medRxiv.
 In our analysis, we found little relationship between time posted and likelihood of having open data or code markers with the proportion of papers containing these markers fluctuating greatly from month to month and no apparent decrease during periods of increased publication.
-This suggests that open science practices are more highly influenced by other factors, perhaps publication bias or the nature of the paper itself.
+This suggests that open science practices are more highly influenced by other factors, perhaps training, publication bias, or the nature of the paper itself.
 On the other hand, we do not see an overall long-term increase in either open data or open code markers throughout our year of analysis which we may expect in the context of the aforementioned open science movements the pandemic has fostered.
@@
 To emphasize the ongoing need for open data and code in modelling a pandemic, we consider two high profile epidemiological models that emerged in early 2020.
-modelling was conducted by Imperial College London (ICL) [@ferguson2020] and the Institute for Health Metrics and Evaluation (IHME) at the University of Washington [@murray2020], and both papers were initially posted to pre-print servers.
+Modelling was conducted by Imperial College London (ICL) [@ferguson2020] and the Institute for Health Metrics and Evaluation (IHME) at the University of Washington [@murray2020], and both papers were initially posted to pre-print repositories.
 The ICL model went on to become the most cited pre-print as of December 2020 [@else2020], and both had significant influence over policy and public health decisions worldwide [@adam2020].
 An independent review of these two models by @jin2020 found that while code and data were openly available for both, only the ICL model was reproducible due to limited transparency on the underlying methodology of the IHME model.
-The open source nature of these papers was fundamental to reproduction attempts and is a great example of the need for open data and code in reproducing COVID-19 research, particularly in evaluating pre-prints as they begin to influence public decision-making.
+The open-source nature of these papers was fundamental to reproduction attempts and is a great example of the need for open data and code in reproducing COVID-19 research, particularly in evaluating pre-prints as they begin to influence public decision-making.
 
@@
 Although our analysis was not particularly robust, this shows a need for future investigation and potential overall improvement in open science standards for these types of pre-prints (of course subject to the data and code considerations already discussed).
-This need is again emphasized by the new found speed at which pre-print articles may gain public, media, and political attention in the context of the pandemic.
+This need is again emphasized by the new-found speed at which pre-print articles may gain public, media, and political attention in the context of the pandemic.
+
+## The importance of open data and open code
 
@@
 Needless to say, it is important that open data and code standards be maintained in published work as well.
-Our findings in this regard were two fold: that open data or code markers do not appear to directly influence a pre-print's eventual publication, and that a lower proportion of published papers contain either open data or code markers than the general sample.
+Our findings in this regard were two-fold: that open data or code markers do not appear to directly influence a pre-print's eventual publication, and that a lower proportion of published papers contain either open data or code markers than the general sample.
 Both of these raise concerns over publication bias, the potential that journals have favored novel yet less transparent or reproducible papers over those with null results but a high standard of open science practices.
-Concerns have already been raised through systemic reviews of COVID-19 publications [@raynaud2021], and oversights in data accessibility have lead to high profile retractions of publications in the past, for example two papers from The Lancet and the New England Journal of Medicine that were withdrawn due to concerns over the private nature of their underlying data set [@ledford2020].
+Concerns have already been raised through systemic reviews of COVID-19 publications [@raynaud2021], and oversights in data accessibility have led to high profile retractions of publications in the past, for example two papers from The Lancet and the New England Journal of Medicine that were withdrawn due to concerns over the private nature of their underlying dataset [@ledford2020].
 
@@
 
+Demand for timely research / results in high frequency as epidemic is rapidly evolving.
+Preprints are more efficient at doing this because there is no time spent on peer review.
+However, they also allow lesser-known researchers to better disperse their research, because of the possibility that fast-tracked peer review may be biased towards established researchers.
+While there is a clear need for pre-prints, the point remains that they do not go through the peer review process.
+This question of quality and validity is particularly pertinent in the COVID-19 context because poorly validated results and false information may spread quickly, and have real effects.
+We are not saying that peer review implies that a paper is of a high-quality, we are instead saying that the provision of code and data alongside the preprint goes some way to allowing others to trust the findings of pre-prints even though they have not been peer-reviewed.
+One way this could be encouraged would be for pre-print repositories to have authors characterize the extent to which they have adopted open science practices as part of their submission.
+Although those papers that do not adopt these practices should not be rejected from pre-print repositories, greater clarity around this would be useful and might move the state-of-the-art forward.
+
 ## Weaknesses and next steps
 
-In this paper we consider only pre-prints from medRxiv, but this analysis can and should be extended to other pre-print servers including bioRxiv and arXiv.
+In this paper we consider only pre-prints from medRxiv, but this analysis can and should be extended to other pre-print repositories including bioRxiv and arXiv.
 The `medrxivr` package [@citemedrxivr] can be used with the bioRxiv API as well, and our code can be modified to conduct the same scraping and text mining procedure as was used for medRxiv data.
@@
 
-An important weakness to note is the potential presence of false negatives in indicators of publication in our data set.
-@abdill2019 estimate that the false-negative rate may be as high as 37.5 percent for data pulled from the bioRxiv API, meaning analysis of published papers may represent only a fraction of those that have actually been published.
+An important weakness to note is the potential presence of false negatives in indicators of publication in our dataset.
+@abdill2019 estimate that the false-negative rate may be as high as 37.5 per cent for data pulled from the bioRxiv API, meaning analysis of published papers may represent only a fraction of those that have actually been published.
 It is unclear to what extent this is the case for medRxiv or what bias may exist in the subset of pre-prints for which publication was detected, as it is likely that this process relies on title-based text matching [@abdill2019].
@@
 
-We also recognize that this analysis relies heavily on text-based analysis which was not verfied directly in most cases and may lead to higher levels of uncertainty.
-In future, we wish to take smaller sub-samples to validate factors like publication status or paper topic beyond simple keyword searches.
-or API output.
+We also recognize that this analysis relies heavily on text-based analysis which was not verified directly in most cases and may lead to higher levels of uncertainty.
+In future, we wish to take smaller sub-samples to validate factors like publication status or paper topic beyond simple keyword searches or API output.
 
@@
 
-# Appendix 1
+# (APPENDIX) Appendix {-}
+
+# Keywords
+
 Insert details on keyword search used for machine learning/modelling/simulation

### 2021-02-20 code_for_jeremy.R

@@ -1,0 +1,21 @@
+
+library(tidyverse)
+
+# Install the package to download arXiv
+# See: https://amfz.github.io/arxivdl/
+devtools::install_github("amfz/arxivdl")
+library(arxivdl)
+
+# Have a look at how many there are
+count <- get_record_count("econ.GN", "20200101 TO 20201231")
+
+# Get the information about them
+papers <- get_records("econ.GN", "20200101 TO 20201231", count)
+
+# Just get 10 to start
+papers <- 
+  papers %>% 
+  slice(1:10)
+
+# Do the actual download
+download_pdf(papers, dir="~/")

### 2021-02-20 scripts/01-data_gathering-arxiv.R
Get started with looking at arXiv

@@ -1,0 +1,128 @@
+#### Preamble ####
+# Purpose: Download papers from arxiv that are related to COVID-19.
+# Author: Annie Collins and Rohan Alexander
+# Data: 20 February 2021
+# Contact: rohan.alexander@utoronto.ca
+# License: MIT
+# Pre-requisites: 
+# - Need the following packages:
+#   - install.packages("aRxiv")
+
+
+#### Workspace setup ####
+library(aRxiv)
+library(tidyverse)
+# library(lubridate)
+# library(oddpub)
+citation('aRxiv')
+
+
+#### Get metadata ####
+# Get count of number of papers using the same terms as before
+arxiv_count('all:"COVID-19" all:"COVID 19" all:"covid-19" all:"covid 19" all:"SARS-CoV-2" all:"SARSCoV-2" all:"corona virus" all:"Corona Virus" all:"coronavirus" all:"2019-nCoV" all:"coronavirus-2"')
+# Result on 20 Feb is: 3434.
+
+arxiv_count('submittedDate:[20071018* TO 20210220*] AND (all:"COVID-19" all:"COVID 19" all:"covid-19" all:"covid 19" all:"SARS-CoV-2" all:"SARSCoV-2" all:"corona virus" all:"Corona Virus" all:"coronavirus" all:"2019-nCoV" all:"coronavirus-2")')
+# Result on 20 Feb is: 3434.
+
+arxiv_results <- arxiv_search(query = 'all:"COVID-19" all:"COVID 19" all:"covid-19" all:"covid 19" all:"SARS-CoV-2" all:"SARSCoV-2" all:"corona virus" all:"Corona Virus" all:"coronavirus" all:"2019-nCoV" all:"coronavirus-2"',
+                    limit = 3500,
+                    batchsize = 500)
+
+arxiv_count('submittedDate:[20071018* TO 20200331*] AND (all:"COVID-19" all:"COVID 19" all:"covid-19" all:"covid 19" all:"SARS-CoV-2" all:"SARSCoV-2" all:"corona virus" all:"Corona Virus" all:"coronavirus" all:"2019-nCoV" all:"coronavirus-2")')
+# There are 249 to get
+arxiv_result_to_march <- 
[…]

### 2021-03-04 code_for_jeremy.R
Update arXiv scraper to download PDFs and cleanup literature filesnames.

@@ -1,21 +1,0 @@
-
-library(tidyverse)
-
-# Install the package to download arXiv
-# See: https://amfz.github.io/arxivdl/
-devtools::install_github("amfz/arxivdl")
-library(arxivdl)
-
-# Have a look at how many there are
-count <- get_record_count("econ.GN", "20200101 TO 20201231")
-
-# Get the information about them
-papers <- get_records("econ.GN", "20200101 TO 20201231", count)
-
-# Just get 10 to start
-papers <- 
-  papers %>% 
-  slice(1:10)
-
-# Do the actual download
-download_pdf(papers, dir="~/")

### 2021-03-04 scripts/01-data_gathering-arxiv.R

@@ -1,7 +1,7 @@
 #### Preamble ####
-# Purpose: Download papers from arxiv that are related to COVID-19.
-# Author: Annie Collins and Rohan Alexander
-# Data: 20 February 2021
+# Purpose: Download papers from arXiv that are related to COVID-19.
+# Author: Rohan Alexander
+# Data: 4 March 2021
 # Contact: rohan.alexander@utoronto.ca
 # License: MIT
 # Pre-requisites: 
@@ -12,6 +12,9 @@
 #### Workspace setup ####
 library(aRxiv)
 library(tidyverse)
+library(lubridate)
+library(utils)
+library(purrr)
 # library(lubridate)
 # library(oddpub)
 citation('aRxiv')
@@ -41,7 +44,6 @@ arxiv_result_to_march_ii <-
                sort_by="submitted",
                limit = 3500,
                start = 100)
-
 
 arxiv_count('submittedDate:[20200401* TO 20200831*] AND (all:"COVID-19" all:"COVID 19" all:"covid-19" all:"covid 19" all:"SARS-CoV-2" all:"SARSCoV-2" all:"corona virus" all:"Corona Virus" all:"coronavirus" all:"2019-nCoV" all:"coronavirus-2")')
 # There are 1830 to get
@@ -84,7 +86,7 @@ all_arxiv_results <-
 write_csv(all_arxiv_results, "outputs/data/arxiv_results.csv")
 
 
-
+#### Have a quick look ####
 all_arxiv_results <- 
   read_csv("outputs/data/arxiv_results.csv")
 
@@ -99,6 +101,50 @@ all_arxiv_results %>%
   ggplot() + 
   geom_col(aes(x=submitted, y=n))
 
+
+#### Download PDFs ####
+all_arxiv_results <- 
+  read_csv("outputs/data/arxiv_results.csv")
+
+# Write a function
+download_pdfs <- 
+  function(link_to_pdf_of_interest, save_name){
+    utils::download.file(link_to_pdf_of_interest, save_name, mode = "wb")
+    message <- paste0("Done with ", link_to_pdf_of_interest, " at ", Sys.time())
+    print(message)
+    Sys.sleep(sample(x = c(5:10), size = 1))
+    }
+
+# Use the function
+get_all_arxiv_results <- 
+  all_arxiv_results %>% 
+  # slice(1:2) %>% # Uncomment when testing 
+  select(id, link_pdf) %>% 
[…]

### 2021-03-04 scripts/01-data_gathering-arxiv.R
Add arXiv txt files

@@ -141,34 +141,14 @@ purrr::walk2(get_all_arxiv_results$link_pdf,
 
 
 
+#### Convert to text ####
+
+# Set up folders for download and txt conversion
+arxiv_pdf_folder = "/Volumes/Hansard/arxiv/"
+arxiv_txt_folder = paste(getwd(), "/outputs/data/text-arXiv", sep = "")
+
+# Convert PDFs to text and saves in new folder
+oddpub::pdf_convert(arxiv_pdf_folder, arxiv_txt_folder)
+# install.packages('Rpoppler')
 
 
-
-# This is the old code for medarxiv - need to do equiv for arxiv:
-
-# 
-# # Sample from results
-# set.seed(100)
-# med_sample <- med_results[sample(nrow(med_results), 1200),]
-# med_sum <- med_sample %>% group_by(month=floor_date(date, "month")) %>% summarise(num=n())
-# write_csv(med_sample, "outputs/data/med_sample.csv")
-# 
-#   
-# #### Download relevant papers ####
-# # Set up folders for download and txt conversion
-# med_pdf_folder = paste(getwd(), "/outputs/data/pdf-medRxiv", sep = "")
-# med_txt_folder = paste(getwd(), "/outputs/data/text-medRxiv", sep = "")
-# 
-# # Download first 500 papers and latest 500 and save to computer
-# # head(med_results, 500) %>% mx_download(directory = med_pdf_folder, create = FALSE)
-# # tail(med_results, 500) %>% mx_download(directory = med_pdf_folder, create = FALSE)
-# 
-# # Download randomly sampled PDFs (will not)
-# med_sample %>% mx_download(directory = med_pdf_folder, create = FALSE)
-# 
-# # Convert PDFs to text and saves in new folder
-# pdf_convert(med_pdf_folder, med_txt_folder)
-# 
-# 
-# #### Clean up ####
-# rm()

### 2021-03-04 outputs/paper/paper.Rmd
Add open data results csv for arXiv

@@
 ---
-title: "Reproducibility of COVID-19 pre-prints on medRxiv in 2020"
+title: "Reproducibility of COVID-19 pre-prints in 2020"
 subtitle: "Markers of open code or data not found in 81 per cent of pre-prints"
-author: "Annie Collins^[University of Toronto.]"
-thanks: "Paper presented at Toronto Workshop on Reproducibility, 26 February 2021.
-Collins thanks CANSSI Ontario for financial support.
-Code and data are available at: https://github.com/anniecollins/reproducibility."
+author: 
+  - Annie Collins^[University of Toronto.]
+  - Rohan Alexander^[University of Toronto, rohan.alexander@utoronto.ca.]
+thanks: "Collins thanks CANSSI Ontario for financial support. Code and data are available at: https://github.com/anniecollins/reproducibility."
 date: "`r format(Sys.time(), '%d %B %Y')`"
-abstract: "We create a dataset of all the pre-prints published on medRxiv between 28 January 2020 and 31 January 2021.
+abstract: "We create a dataset of all the pre-prints published on arXiv and medRxiv between 28 January 2020 and 31 January 2021.
 We extract the text from these pre-prints and parse them looking for keyword markers signalling the availability of the data and code underpinning the pre-print.
-We are unable to find markers of either open data or open code for 81 per cent of the pre-prints in our sample.
-Our paper demonstrates the need to have authors categorize the degree of openness of their pre-print as part of the medRxiv submissions process, and more broadly, the need to better integrate open science training into a wide range of fields."
+We are unable to find markers of either open data or open code for 81 per cent of the pre-prints on medRxiv  in our sample, and X per cent of those on arXiv in our sample.
+Our paper demonstrates the need to have authors categorize the degree of openness of their pre-print as part of the pre-print submissions process, and more broadly, the need to better integrate open science training into a wide range of fields."
 output:

### 2021-03-04 scripts/01-data_gathering-medrxiv.R

@@ -1,6 +1,6 @@
 #### Preamble ####
 # Purpose: Download papers from medrxiv that are related to COVID-19.
-# Author: Annie Collins and Rohan Alexander
+# Author: Annie Collins
 # Data: 12 February 2021
 # Contact: rohan.alexander@utoronto.ca
 # License: MIT

### 2021-03-04 scripts/02-data_clean_and_prep-arXiv.R

@@ -1,0 +1,58 @@
+#### Preamble ####
+# Purpose: Parse the txt files created from the PDFs downloaded from arxiv in 01-data_gathering_arxiv.R
+# Author: Rohan Alexander
+# Data: 4 March 2021
+# Contact: rohan.alexander@utoronto.ca
+# License: MIT
+# Pre-requisites: 
+# - Need to have downloaded PDFs and converted them to txt files saved in outputs/data/
+
+
+#### Workspace setup ####
+# library(medrxivr)
+library(oddpub)
+library(tidyverse)
+
+# Read in the raw data. 
+# med_txt_folder = paste(getwd(), ", sep = "")
+# Load text files into list of string vectors for use in text mining algorithm.
+# Returns list of lists, with one list for each document (paper)
+arxiv_text_sentences <- 
+  oddpub::pdf_load(here::here("outputs/data/text-arXiv/")) # Requires closing backslash
+all_arxiv_results <- 
+  read_csv("outputs/data/arxiv_results.csv")
+
+
+#### Identify open data markers ####
+arxiv_open_data_results <- 
+  oddpub::open_data_search(arxiv_text_sentences)
+
+# Join med_sample to arxiv_open_data_results and save as arxiv_open_data_results
+arxiv_open_data_results <- 
+  arxiv_open_data_results %>% 
+  mutate(id = str_remove(article, "\\.txt"))
+
+arxiv_open_data_results <- 
+  arxiv_open_data_results %>% 
+  left_join(all_arxiv_results, by = "id")
+  
+
+# Convert TRUE/FALSE in ODDPub output to 1/0
+arxiv_open_data_results$is_open_code <- as.integer(arxiv_open_data_results$is_open_code)
+arxiv_open_data_results$is_open_data <- as.integer(arxiv_open_data_results$is_open_data)
+
+
+# Save it 
+write_csv(arxiv_open_data_results, 'outputs/data/arxiv_open_data_results.csv')
+
+
+#### Summary statistics ####
+# Read in data
+# TODO
+
+# Counts
+arxiv_open_data_results %>% 
+  count(is_open_data, is_open_code)
+
+
+

### 2021-03-04 scripts/02-data_clean_and_prep-medrxiv.R

@@ -1,6 +1,6 @@
 #### Preamble ####
 # Purpose: Download the txt files of the PDFs downloaded from medrxiv in 01-data_gathering_mexrxiv.R
-# Author: Annie Collins and Rohan Alexander
+# Author: Annie Collins
 # Data: 12 February 2021
 # Contact: rohan.alexander@utoronto.ca
 # License: MIT

### 2021-03-05 outputs/paper/paper.Rmd
Begin updating paper to include arXiv

@@
   - Annie Collins^[University of Toronto.]
-  - Rohan Alexander^[University of Toronto, rohan.alexander@utoronto.ca.]
 thanks: "Collins thanks CANSSI Ontario for financial support. Code and data are available at: https://github.com/anniecollins/reproducibility."
@@
 ```{r loaddata, include=FALSE}
-med_open_data_results <- read_csv(here("outputs/data/med_open_data_results.csv"))
+med_open_data_results <- 
+  read_csv(here::here("outputs/data/med_open_data_results.csv"))
+med_results <- 
+  read_csv(here::here("outputs/data/med_results.csv")) # All COVID medRxiv papers (9,929)
 
-med_results <- read_csv(here::here("outputs/data/med_results.csv")) # All COVID medRxiv papers (9,929)
+arxiv_open_data_results <- 
+  read_csv(here::here("outputs/data/arxiv_open_data_results.csv"))
+all_arxiv_results <- 
+  read_csv(here::here("outputs/data/arxiv_results.csv"))
+
+all_arxiv_results <- 
+  all_arxiv_results %>% 
+  mutate(submitted = as_date(submitted),
+         updated = as_date(updated))
 ```
@@
 
-```{r monthly-papers-total, fig.cap = "Number of pre-prints related to COVID-19 posted to medRxiv", out.width="90%", fig.align = "center"}
+```{r monthly-papers-total, fig.cap = "Number of pre-prints related to COVID-19 posted to arXiv and medRxiv", out.width="90%", fig.align = "center"}
+just_arxiv <- 
+  all_arxiv_results  %>% 
+  select(submitted) %>% 
+  mutate(type = "arXiv") %>% 
+  rename(date = submitted)
+
+just_medRxiv <- 
   med_results  %>% 
-  group_by(month = floor_date(date, "month")) %>% 
-  summarise(count=n()) %>% 
-  ggplot(aes(month, count)) + 
-  # geom_line(stat="identity") +
-  geom_col() + 
+  select(date) %>% 
+  mutate(type = "medRxiv")
+
+both <- rbind(just_arxiv, just_medRxiv)
+
+both %>% 
+  mutate(month = floor_date(date, "month")) %>% 
+  filter(year(date) >= 2020) %>% 
+  ggplot(aes(x = month)) + 
+  geom_histogram(aes(fill = type), stat="count", position = "dodge") + 
   labs(title = "Pre-prints posted per month",
-       subtitle = "medRxiv, Total = 9,929",
+       subtitle = "Total of 3,379 on arXiv and 9,929 on medRxiv",
        x = "Month",
-       y = "Number of pre-prints") +
+       y = "Number of pre-prints",
+       fill = "Repository") +
   theme_minimal()

### 2021-03-05 outputs/paper/paper.Rmd
Add txt for another 1000 arxiv papers

@@
 Thus it is important that the results that are published are credible.
-Pre-print repositories, specifically medRxiv, have drawn unprecedented attention in the context of the 2019 novel coronavirus (COVID-19) pandemic and the changes it has imposed on the scientific community [@else2020].
-These repositories are not peer-reviewed, and, in general, anyone with appropriate academic credentials can submit a paper.
+Pre-print repositories have drawn unprecedented attention in the context of the 2019 novel coronavirus (COVID-19) pandemic and the changes it has imposed on the scientific community [@else2020].
+These repositories are not peer-reviewed, and, in general, anyone with appropriate academic credentials can submit a pre-print
 
-While neither peer-review nor credentials are a panacea nor a guarantee of quality, given the importance of these repositories, it is important that scientists impose on themselves various standards for their results.
-Following @weissgerber2021automated we examine papers about COVID-19 published to medRxiv through to January 2021.
+Neither peer-review nor credentials are a panacea nor a guarantee of quality.
+And the gate-keeping and slow publication times of traditional journals mean pre-print repositories have an important role to play.
+But given the importance of these repositories, it is important that scientists impose on themselves various standards for their results.
+Following @weissgerber2021automated we examine papers about COVID-19 published to  arXiv, bioRxiv, medRxiv, and SocArXiv from January 2020, through to February 2021.
 We search for markers of open science as indicators of reproducibility, specifically open data and open code.
@@
 
-Our primary dataset consists of information extracted from the medRxiv repository combined with output from running a sample of COVID-19-related pre-prints through the Open Data Detection in Publications (ODDPub) text mining algorithm [@citePDDPub], using the `oddpub` package [@citeODDPubpackage].
+Our primary dataset consists of information extracted from the arXiv, bioRxiv, medRxiv, and SocArXiv pre-print repositories.
+We downloaded pre-prints that contained various keywords related to COVID-19 (a full list of these is available in Appendix \@ref(keywords)), and then identified the availability of open code and open data using the Open Data Detection in Publications (ODDPub) text mining algorithm [@citePDDPub] in the `oddpub` package [@citeODDPubpackage].
 
-We constructed this dataset by first creating a local copy of the medRxiv repository via the medRxiv API.
-We identified papers related to the COVID-19 pandemic through several keyword searches to create our sampling frame (N = 9,929, including only the most recent version of any given pre-print).
-This data includes the following information about each pre-print in the repository: title, abstract, author(s), date posted, research field, DOI, version number, corresponding author, corresponding author's institutional affiliation, and published DOI (if the paper has since been published in a peer-reviewed journal).
+We constructed this dataset by first creating a local copy of the repository using the repository API.
+We identified papers related to the COVID-19 pandemic through several keyword searches to create our dataset of papers and associated metadata.
+This metadata varies by repository, but generally includes the following information: title, abstract, author(s), date posted, research field, DOI, version number, corresponding author, corresponding author's institutional affiliation, and published DOI (if the pre-prints has since been published in a peer-reviewed journal).
+In the case of SocArXiv there are additionally fields that are self-reported by the submitting author about the availability of code and data.
 
-We then selected a random sample of these papers (N = 1,200) to check for open data and code markers using the ODDPub algorithm.
-This required downloading each paper as a PDF and then converting the PDFs to text files, using the `medrxivr` package [@citemedrxivr].
+We then checked these pre-prints for open data and code markers using the ODDPub algorithm.
+This required downloading each pre-print as a PDF and then converting the PDFs to text files.
 We then conducted the open data and open code detection procedure.
-This produced a results table indicating the presence of open data or open code markers in each paper (with a binary variable for each marker, and the relevant open data or open code statements when applicable).
+This involved searching for keywords and other markers of open data and open code such as references to GitHub repositories and similar.
+A full listing of these markers is included in Appendix \@ref(markers).
+This was conducted using the `open_data_search()` function from the `oddpub` package.
 
-Our final dataset was formed by joining these two tables together via DOI to form a dataset including all original, qualitative information for each pre-print alongside its open data and open code status and markers.
+The result of this process is a dataset indicating the presence of open data or open code markers in each pre-print (with a binary variable for each marker, and the relevant open data or open code statements when applicable).
+Our final analysis dataset was formed by joining these two datasets together, typically using the DOI or the unique filename, to form a dataset including all original, qualitative metadata information for each pre-print alongside its open data and open code status and markers.
 
-```{r monthly-papers-total, fig.cap = "Number of pre-prints related to COVID-19 posted to arXiv and medRxiv", out.width="90%", fig.align = "center"}
+```{r monthly-papers-total, fig.cap = "Number of pre-prints related to COVID-19", out.width="90%", fig.align = "center"}
 just_arxiv <- 
@@
   labs(title = "Pre-prints posted per month",
-       subtitle = "Total of 3,379 on arXiv and 9,929 on medRxiv",
+       subtitle = "Total of 3,379 relevant pre-prints on arXiv and 9,929 on medRxiv",
        x = "Month",
@@
 
+- Add reference somewhere to that paper about the numbers: https://link.springer.com/article/10.1007/s11192-020-03675-3
+- Add reference somewhere to that paper about keyword search and then analysis. Was it a Gary King one?
+
 ## On the role of transparency and reproducibility
@@
 
+Insert details on keyword search used to identify COVID-19 papers.
+
+# Markers
+
+Insert details on what markers the `oddpub::open_data_search()` uses. Include info here directly from package documentation (i.e. keywords/phrases used for text parsing)?
+
+# Classification
+
 Insert details on keyword search used for machine learning/modelling/simulation
-
-Include info here directly from package documentation (i.e. keywords/phrases used for text parsing)?
 

### 2021-03-05 scripts/01-data_gathering-arxiv.R

@@ -1,7 +1,7 @@
 #### Preamble ####
 # Purpose: Download papers from arXiv that are related to COVID-19.
 # Author: Rohan Alexander
-# Data: 4 March 2021
+# Data: 5 March 2021
 # Contact: rohan.alexander@utoronto.ca
 # License: MIT
 # Pre-requisites: 
@@ -131,13 +131,19 @@ get_all_arxiv_results <-
 
 safely_download_pdfs <- purrr::safely(download_pdfs)
 
+# Check what's already been downloaded
+already_got <- list.files(path = "/Volumes/Hansard/arxiv", full.names = TRUE)
+# Remove those rows
+get_all_arxiv_results <- 
+  get_all_arxiv_results %>% 
+  filter(!id %in% already_got)
+
 purrr::walk2(get_all_arxiv_results$link_pdf,
              get_all_arxiv_results$id,
              safely_download_pdfs)
 
-# Need to write a package that does this. Also that checks whether the file exists and then skips that.
-# Check if Annie has time - woudl be a nice companion package.
-
+# Need to write a package that does this.
+# Check if Annie has time - would be a nice companion package.
 
 
 

### 2021-03-05 scripts/02-data_clean_and_prep-arXiv.R

@@ -1,7 +1,7 @@
 #### Preamble ####
 # Purpose: Parse the txt files created from the PDFs downloaded from arxiv in 01-data_gathering_arxiv.R
 # Author: Rohan Alexander
-# Data: 4 March 2021
+# Data: 5 March 2021
 # Contact: rohan.alexander@utoronto.ca
 # License: MIT
 # Pre-requisites: 
@@ -27,7 +27,7 @@ all_arxiv_results <-
 arxiv_open_data_results <- 
   oddpub::open_data_search(arxiv_text_sentences)
 
-# Join med_sample to arxiv_open_data_results and save as arxiv_open_data_results
+# Join the dataset with the metadata with the dataset with the open markers
 arxiv_open_data_results <- 
   arxiv_open_data_results %>% 
   mutate(id = str_remove(article, "\\.txt"))
@@ -36,23 +36,15 @@ arxiv_open_data_results <-
   arxiv_open_data_results %>% 
   left_join(all_arxiv_results, by = "id")
   
-
 # Convert TRUE/FALSE in ODDPub output to 1/0
 arxiv_open_data_results$is_open_code <- as.integer(arxiv_open_data_results$is_open_code)
 arxiv_open_data_results$is_open_data <- as.integer(arxiv_open_data_results$is_open_data)
-
 
 # Save it 
 write_csv(arxiv_open_data_results, 'outputs/data/arxiv_open_data_results.csv')
 
 
-#### Summary statistics ####
-# Read in data
-# TODO
-
 # Counts
 arxiv_open_data_results %>% 
   count(is_open_data, is_open_code)
-
-
 

### 2021-03-06 outputs/paper/paper.Rmd
Add all arxiv papers as txt and also add socarxiv metadata csv

@@
 library(stargazer)
+library(wesanderson)
 ```
@@
        fill = "Repository") +
-  theme_minimal()
+  theme_minimal() +
+  scale_fill_manual(values = wes_palette("Darjeeling1"))
 ```

### 2021-03-06 scripts/01-data_gathering-socarxiv.R

@@ -1,0 +1,216 @@
+#### Preamble ####
+# Purpose: Download papers from socarxiv that are related to COVID-19.
+# Author: Rohan Alexander
+# Data: 5 March 2021
+# Contact: rohan.alexander@utoronto.ca
+# License: MIT
+# Pre-requisites: 
+# - 
+
+
+#### Workspace setup ####
+# library(aRxiv)
+library(httr)
+library(tidyverse)
+# library(lubridate)
+# library(utils)
+# library(purrr)
+# library(lubridate)
+# library(oddpub)
+
+
+#### Get metadata ####
+# Based on this: https://api.osf.io/v2/preprints/?filter[provider]=socarxiv
+# all_socarxiv_papers <- httr::GET('https://api.osf.io/v2/preprints/?filter[provider]=socarxiv') # This only gets 10 so we need pagination
+# socarxiv_papers_739 <- httr::GET('https://api.osf.io/v2/preprints/?filter%5Bprovider%5D=socarxiv&page=739')
+
+# Write a function that will take a page and a save location and will got an GET that data and save it as a CSV.
+get_meta_data_socarxiv <- 
+  function(number, location){
+    # number <- get_these$number[1] # Just for testing
+    # location <- get_these$location[1] # Just for testing
+    address <- paste0('https://api.osf.io/v2/preprints/?filter%5Bprovider%5D=socarxiv&page=', number)
+    socarxiv_data_on_papers <- httr::GET(address)
+    socarxiv_data_on_papers_as_dataset <- jsonlite::fromJSON(content(socarxiv_data_on_papers, "text"), flatten = TRUE)
+    socarxiv_data_on_papers_as_tibble <- 
+      socarxiv_data_on_papers_as_dataset$data %>% 
+      as_tibble()
+    socarxiv_data_on_papers_as_tibble <- 
+      socarxiv_data_on_papers_as_tibble %>% 
+      rowwise() %>% 
+      mutate_if(is.list, ~paste(unlist(.), collapse = '|'))
+    write_csv(socarxiv_data_on_papers_as_tibble, location)
+    message <- paste0("Done with ", number, " at ", Sys.time())
+    print(message)
+    Sys.sleep(sample(x = c(5:10), size = 1))
+  }
+
+# Set up the dataset that we're going to walk though
+get_these <- 
[…]

### 2021-03-06 scripts/01-data_gathering-socarxiv.R
Update arxiv and socarxiv

@@ -1,7 +1,7 @@
 #### Preamble ####
 # Purpose: Download papers from socarxiv that are related to COVID-19.
 # Author: Rohan Alexander
-# Data: 5 March 2021
+# Data: 6 March 2021
 # Contact: rohan.alexander@utoronto.ca
 # License: MIT
 # Pre-requisites: 
@@ -11,6 +11,7 @@
 #### Workspace setup ####
 # library(aRxiv)
 library(httr)
+library(lubridate)
 library(tidyverse)
 # library(lubridate)
 # library(utils)
@@ -64,82 +65,114 @@ purrr::walk2(get_these$number,
              get_these$location,
              safely_get_meta_data_socarxiv)
 
-
-
-
-# Need to map and read_csv
+# Gather them all into one CSV
 socarxiv_files <- list.files(path = "inputs/socarxiv", full.names = TRUE)
 
-all_socarxiv_metadata <- purrr::map_dfr(socarxiv_files, read_csv, col_types = cols(.default = "c"))
+all_socarxiv_metadata <- purrr::map_dfr(socarxiv_files, 
+                                        read_csv, 
+                                        col_types = cols(.default = "c"))
+
+#### Get COVID ones ####
+# Identify which ones have something to do with COVID.
+all_socarxiv_metadata <- 
+  all_socarxiv_metadata %>% 
+  rename(date_created = attributes.date_created,
+         date_modified = attributes.date_modified,
+         date_published = attributes.date_published,
+         date_last_transitioned = attributes.date_last_transitioned,
+         date_withdrawn = attributes.date_withdrawn,
+         title = attributes.title,
+         description = attributes.description,
+         tags = attributes.tags
+         ) %>% 
+  mutate(date_created = lubridate::as_date(date_created),
+         date_modified = lubridate::as_date(date_modified),
+         date_published = lubridate::as_date(date_published),
+         date_last_transitioned = lubridate::as_date(date_last_transitioned),
+         date_withdrawn = lubridate::as_date(date_withdrawn)
+         )
+
+all_socarxiv_metadata <- 
+  all_socarxiv_metadata %>% 
+  filter(year(date_created) >= 2020)
+
[…]

### 2021-05-25 outputs/paper/paper.Rmd
Expand time frame of data collection, updates to cleaning scripts/files structure

@@
 date: "`r format(Sys.time(), '%d %B %Y')`"
-abstract: "We create a dataset of all the pre-prints published on arXiv and medRxiv between 28 January 2020 and 31 January 2021.
+abstract: "We create a dataset of all the pre-prints published on arXiv, bioRxiv, and medRxiv between 28 January 2020 and 31 January 2021.
 We extract the text from these pre-prints and parse them looking for keyword markers signalling the availability of the data and code underpinning the pre-print.
@@
   read_csv(here::here("outputs/data/med_results.csv")) # All COVID medRxiv papers (9,929)
+
+bio_open_data_results <- 
+  read_csv(here::here("outputs/data/bio_open_data_results.csv"))
+bio_results <- 
+  read_csv(here::here("outputs/data/bio_results.csv")) # All COVID bioRxiv papers (3,031)
 
@@
 
-both <- rbind(just_arxiv, just_medRxiv)
+just_bioRxiv <- 
+  bio_results  %>% 
+  select(date) %>% 
+  mutate(type = "bioRxiv")
 
-both %>% 
+all <- rbind(just_arxiv, just_medRxiv, just_bioRxiv)
+
+all %>% 
   mutate(month = floor_date(date, "month")) %>% 
@@
   labs(title = "Pre-prints posted per month",
-       subtitle = "Total of 3,379 relevant pre-prints on arXiv and 9,929 on medRxiv",
+       subtitle = "Total of 3,379 relevant pre-prints on arXiv, 3,031 on bioRxiv, 9,929 on medRxiv",
        x = "Month",
@@
 Broadly, we are unable to find markers of either open data or open code for around 81 per cent of the 1,200 sampled pre-prints.
-The remaining 19 per cent of pre-prints was comprised of 4 per cent of the sample containing markers for open code, 8 per cent of the sample with markers for open data, and 7 per cent of the sample with markers for both open data and open code (Table \@ref(tab:summarycounts)).
+The remaining 19 per cent of pre-prints was comprised of 4 per cent of the sample containing markers for open code, 8 per cent of the sample with markers for open data, and 7 per cent of the sample with markers for both open data and open code (Table \@ref(tab:summarycounts-medRxiv)).
 
-```{r summarycounts}
+```{r summarycounts-medRxiv}
 # open data/open code count summary table
@@
   kable(col.names = c("Open data markers", "Open code markers", "Count", "Proportion of total"),
-        caption = "Counts and proportions of open data and code markers in our sample",
+        caption = "Counts and proportions of open data and code markers in medRxiv sample",
+        booktabs = TRUE,
+        digits = 2)
+```
+
+```{r summarycounts-bioRxiv}
+# open data/open code count summary table
+bio_open_data_results %>% 
+  count(is_open_data, is_open_code) %>%
+  mutate(prop_total = n / sum(n)) %>%
+  mutate(is_open_data = ifelse(is_open_data == 0, "No", "Yes"),
+         is_open_code = ifelse(is_open_code == 0, "No", "Yes")) %>% 
+  kable(col.names = c("Open data markers", "Open code markers", "Count", "Proportion of total"),
+        caption = "Counts and proportions of open data and code markers in bioRxiv sample",
         booktabs = TRUE,

### 2021-05-25 scripts/01-data_gathering-arxiv.R

@@ -19,21 +19,24 @@ library(purrr)
 # library(oddpub)
 citation('aRxiv')
 
+# As of 22 May, 2021, 4,164 COVID-19 pre-prints (website count)
+
 
 #### Get metadata ####
 # Get count of number of papers using the same terms as before
 arxiv_count('all:"COVID-19" all:"COVID 19" all:"covid-19" all:"covid 19" all:"SARS-CoV-2" all:"SARSCoV-2" all:"corona virus" all:"Corona Virus" all:"coronavirus" all:"2019-nCoV" all:"coronavirus-2"')
-# Result on 20 Feb is: 3434.
+# Result on 22 May is: 4,054
 
-arxiv_count('submittedDate:[20071018* TO 20210220*] AND (all:"COVID-19" all:"COVID 19" all:"covid-19" all:"covid 19" all:"SARS-CoV-2" all:"SARSCoV-2" all:"corona virus" all:"Corona Virus" all:"coronavirus" all:"2019-nCoV" all:"coronavirus-2")')
-# Result on 20 Feb is: 3434.
+# All records up to 1 May, 2021
+arxiv_count('submittedDate:[20071018* TO 20210501*] AND (all:"COVID-19" all:"COVID 19" all:"covid-19" all:"covid 19" all:"SARS-CoV-2" all:"SARSCoV-2" all:"corona virus" all:"Corona Virus" all:"coronavirus" all:"2019-nCoV" all:"coronavirus-2")')
+# Result on 22 May is: 3,947
 
-arxiv_results <- arxiv_search(query = 'all:"COVID-19" all:"COVID 19" all:"covid-19" all:"covid 19" all:"SARS-CoV-2" all:"SARSCoV-2" all:"corona virus" all:"Corona Virus" all:"coronavirus" all:"2019-nCoV" all:"coronavirus-2"',
-                    limit = 3500,
+arxiv_results <- arxiv_search(query = 'submittedDate:[20071018* TO 20210501*] AND (all:"COVID-19" all:"COVID 19" all:"covid-19" all:"covid 19" all:"SARS-CoV-2" all:"SARSCoV-2" all:"corona virus" all:"Corona Virus" all:"coronavirus" all:"2019-nCoV" all:"coronavirus-2)"',
+                    limit = 5000,
                     batchsize = 500)
 
[…]

### 2021-05-25 scripts/01-data_gathering-biorxiv.R

@@ -1,0 +1,132 @@
+#### Preamble ####
+# Purpose: Download papers from medrxiv that are related to COVID-19.
+# Author: Annie Collins and Rohan Alexander
+# Data: 12 February 2021
+# Contact: rohan.alexander@utoronto.ca
+# License: MIT
+# Pre-requisites: 
+# - Need the following packages:
+#   - devtools::install_github("mcguinlu/medrxivr")
+
+
+#### Workspace setup ####
+library(medrxivr)
+library(tidyverse)
+library(lubridate)
+library(oddpub)
+# citation('tidyverse')
+# citation('medrxivr')
+
+# Raw stats as of 22 May, 2021 (from medRxiv website)
+# 16,135 COVID articles total
+# 12,450 in medRxiv
+# 3,685 in bioRxiv
+
+#### Get metadata ####
+# Download copy of current database
+dates_2020 <- seq.Date(from = as.Date("2019-12-01"), to = as.Date("2020-12-31"), by = 2)
+dates_2021 <- seq.Date(from = as.Date("2021-01-01"), to = as.Date("2021-05-01"), by = "d")
+bio_data <- mx_api_content(from_date = as.character(dates_2020[1]), to_date = as.character(dates_2020[2]), server = "biorxiv")
+i <- 2
+j <- 1
+
+# Retrieve data from 2019-12-01 to 2020-12-31
+# n = 83,253 as of 23 May, 2021
+while (i < (length(dates_2020) - 1)) {
+  bio_data_next <- try(mx_api_content(from_date = as.character(dates_2020[i]), to_date = as.character(dates_2020[i+1]), server = "biorxiv"))
+  if("try-error" %in% class(bio_data_next)) {
+    bio_data_next <- mx_api_content(from_date = as.character(dates_2020[i]), to_date = as.character(dates_2020[i+2]), server = "biorxiv")
+    bio_data <- rbind(bio_data, bio_data_next)
+    i <- i + 2
+  } else {
+    bio_data <- rbind(bio_data, bio_data_next)
+    i <- i + 1
+  }
+}
+
+# Depending on i at end of loop may need to add in last few days of 2020 manually (if dates_2020[i] is 2020-12-29, run following)
+# n = 83,508 as of 23 May, 2021
+bio_data_next <- mx_api_content(from_date = as.character(dates_2020[i]), to_date = as.character(dates_2020[i+1]), server = "biorxiv")
+bio_data <- rbind(bio_data, bio_data_next)
+
[…]

### 2021-05-25 scripts/01-data_gathering-medrxiv.R

@@ -22,25 +22,29 @@ library(oddpub)
 # Download copy of current database
 med_data <- mx_snapshot()
 
-# Raw stats as of 31 Jan, 2021
-# 12,776 COVID articles total
-# 9,931 in medRxiv
-# 2,845 in bioRxiv
+# Raw stats as of 22 May, 2021 (from medRxiv website)
+# 16,135 COVID articles total
+# 12,450 in medRxiv
+# 3,685 in bioRxiv
 
 # Search database for COVID-19-related articles by keyword across title, abstract, and category. Sort results from oldest to newest.
 # Output exclude duplicate title, abstract, and DOI
-med_data <- med_data %>% filter(date >= "2019-12-01", date <= "2021-01-31")
+med_data <- med_data %>% filter(date >= "2019-12-01", date <= "2021-05-01")
 med_results <- mx_search(data = med_data, query = c("COVID-19",
                                                     "COVID 19",
                                                     "covid-19",
                                                     "covid 19",
+                                                    "novel coronavirus",
+                                                    "novel corona virus",
                                                     "SARS-CoV-2",
                                                     "SARSCoV-2",
+                                                    "sars-cov-2",
+                                                    "sars-CoV-2",
                                                     "corona virus",
                                                     "Corona Virus",
                                                     "coronavirus", 
                                                     "2019-nCoV",
-                                                    "coronavirus-2"), auto_caps = TRUE) # n = 9,9,929
+                                                    "coronavirus-2"), auto_caps = TRUE) # n = 12,060
 med_results <- med_results[order(med_results$date),]
 
 # Save results - this is sampling frame (info for all medRxiv COVID-19 papers)
@@ -57,7 +61,7 @@ med_plot
 
 # Sample from results
 set.seed(100)
-med_sample <- med_results[sample(nrow(med_results), 1200),]
+med_sample <- med_results[sample(nrow(med_results), 1500),]
 med_sum <- med_sample %>% group_by(month=floor_date(date, "month")) %>% summarise(num=n())
 write_csv(med_sample, "outputs/data/med_sample.csv")
 
@@ -72,7 +76,8 @@ med_txt_folder = paste(getwd(), "/outputs/data/text-medRxiv", sep = "")
 # tail(med_results, 500) %>% mx_download(directory = med_pdf_folder, create = FALSE)
 
 # Download randomly sampled PDFs (will not)
[…]

### 2021-05-25 scripts/02-data_clean_and_prep-arXiv.R

@@ -35,7 +35,7 @@ arxiv_open_data_results <-
 arxiv_open_data_results <- 
   arxiv_open_data_results %>% 
   left_join(all_arxiv_results, by = "id")
-  
+
 # Convert TRUE/FALSE in ODDPub output to 1/0
 arxiv_open_data_results$is_open_code <- as.integer(arxiv_open_data_results$is_open_code)
 arxiv_open_data_results$is_open_data <- as.integer(arxiv_open_data_results$is_open_data)

### 2021-05-25 scripts/02-data_clean_and_prep-medrxiv.R

@@ -15,7 +15,8 @@ library(oddpub)
 library(tidyverse)
 
 # Read in the raw data. 
-# med_txt_folder = paste(getwd(), ", sep = "")
+# med_txt_folder <- paste(getwd(), ", sep = "")
+
 # Load text files into list of string vectors for use in text mining algorithm.
 # Returns list of lists, with one list for each document (paper)
 med_text_sentences <- 

### 2021-05-25 scripts/03-data_gathering-biorxiv.R

@@ -1,120 +1,0 @@
-#### Preamble ####
-# Purpose: Download papers from medrxiv that are related to COVID-19.
-# Author: Annie Collins and Rohan Alexander
-# Data: 12 February 2021
-# Contact: rohan.alexander@utoronto.ca
-# License: MIT
-# Pre-requisites: 
-# - Need the following packages:
-#   - devtools::install_github("mcguinlu/medrxivr")
-
-
-#### Workspace setup ####
-library(medrxivr)
-library(tidyverse)
-library(lubridate)
-library(oddpub)
-# citation('tidyverse')
-# citation('medrxivr')
-
-
-#### Get metadata ####
-# Download copy of current database
-dates_2020 <- seq.Date(from = as.Date("2019-12-01"), to = as.Date("2020-12-31"), by = 2)
-dates_2021 <- seq.Date(from = as.Date("2021-01-01"), to = as.Date("2021-01-31"), by = "d")
-bio_data <- mx_api_content(from_date = as.character(dates_2020[1]), to_date = as.character(dates_2020[2]), server = "biorxiv")
-i <- 2
-j <- 1
-
-# Retrieve data from 2019-12-01 to 2020-12-31
-while (i < (length(dates_2020) - 1)) {
-  bio_data_next <- try(mx_api_content(from_date = as.character(dates_2020[i]), to_date = as.character(dates_2020[i+1]), server = "biorxiv"))
-  if("try-error" %in% class(bio_data_next)) {
-    bio_data_next <- mx_api_content(from_date = as.character(dates_2020[i]), to_date = as.character(dates_2020[i+2]), server = "biorxiv")
-    bio_data <- rbind(bio_data, bio_data_next)
-    i <- i + 2
-  } else {
-    bio_data <- rbind(bio_data, bio_data_next)
-    i <- i + 1
-  }
-}
-
-# Depending on i at end of loop may need to add in last few days of 2020 manually (if dates_2020[i] is 2020-12-29, run following)
-bio_data_next <- mx_api_content(from_date = as.character(dates_2020[i]), to_date = as.character(dates_2020[i+1]), server = "biorxiv")
-bio_data <- rbind(bio_data, bio_data_next)
-
-# Retrieve data from 2021-01-01 to 2021-01-31, skipping 2021-01-08 (j = 8)
-while (j < (length(dates_2021) - 1)) {
[…]

### 2021-05-28 scripts/01-data_gathering-socarxiv.R
Add SocArXiv data and files

@@ -13,6 +13,7 @@
 library(httr)
 library(lubridate)
 library(tidyverse)
+library(textreadr)
 # library(lubridate)
 # library(utils)
 # library(purrr)
@@ -47,8 +48,9 @@ get_meta_data_socarxiv <-
   }
 
 # Set up the dataset that we're going to walk though
+# Check how many pages of results exist at https://api.osf.io/v2/preprints/?filter%5Bprovider%5D=socarxiv&page= and adjust numeric range accordingly
 get_these <- 
-  tibble(number = c(1:739),
+  tibble(number = c(1:811),
          location  = paste0("inputs/socarxiv/", number, ".csv"))
 
 safely_get_meta_data_socarxiv <- purrr::safely(get_meta_data_socarxiv)
@@ -128,8 +130,8 @@ covid_socarxiv_metadata <-
   all_socarxiv_metadata %>% 
   filter(covid_flag == TRUE)
 
-utils::download.file("https://osf.io/preprints/socarxiv/fcqd9/download", 
-                     "test.pdf", 
+utils::download.file("https://osf.io/preprints/socarxiv/2p3xt/download", 
+                     "test.docx", 
                      mode = "wb")  
 
 # Write a function
@@ -141,7 +143,7 @@ download_pdfs <-
     Sys.sleep(sample(x = c(5:10), size = 1))
   }
 
-#
+
 # Use the function
 get_covid_socarxiv_results <- 
   covid_socarxiv_metadata %>%
@@ -149,31 +151,23 @@ get_covid_socarxiv_results <-
   select(id) %>% 
   mutate(
     link_pdf = paste0("https://osf.io/preprints/socarxiv/", id, "/download"),
-    save_name = paste0("/Volumes/Hansard/socarxiv/", id, ".pdf")
+    save_name = paste0("outputs/data/pdf-socarxiv/", id, ".pdf")
   )
 
 safely_download_pdfs <- purrr::safely(download_pdfs)
 
 # Check what's already been downloaded
-already_got <- list.files(path = "/Volumes/Hansard/socarxiv", full.names = TRUE)
+already_got <- list.files(path = "/outputs/data/pdf-socarxiv", full.names = TRUE)
 # Remove those rows
 get_covid_socarxiv_results <- 
   get_covid_socarxiv_results %>% 
   filter(!save_name %in% already_got)
 
+# Download pdfs
+# Warning: of sample, 65 papers are only available in .docx format. See below for continued download.
[…]

### 2021-05-28 scripts/02-data_clean_and_prep-socarxiv.R

@@ -1,0 +1,56 @@
+# Data Cleaning and Prep - SocArXiv
+
+# rbind open data results from docx and pdf files together
+# join all open data results to covid_socarxiv_metadata by `id`
+
+#### Preamble ####
+# Purpose: Download the txt files of the PDFs downloaded from socarxiv in 01-data_gathering_socarxiv.R
+# Author: Annie Collins, Rohan Alexander
+# Data: 12 February 2021
+# Contact: rohan.alexander@utoronto.ca
+# License: MIT
+# Pre-requisites: 
+# - Need to have downloaded PDFs and converted them to txt files saved in outputs/data/
+
+
+#### Workspace setup ####
+# Use R Projects, not setwd().
+library(oddpub)
+library(tidyverse)
+
+# Load text files into list of string vectors for use in text mining algorithm.
+# Returns list of lists, with one list for each document (paper)
+socarxiv_text_sentences <- 
+  oddpub::pdf_load(here::here("outputs/data/text-socarxiv/")) # Requires closing backslash
+
+#### Identify open data markers ####
+socarxiv_open_data_results <- 
+  oddpub::open_data_search(socarxiv_text_sentences)
+
+
+# DONE up to here, rest TODO
+
+# Join covid_socarxiv_metadata to socarxiv_open_data_results and save as socarxiv_open_data_results
+socarxiv_open_data_results <- socarxiv_open_data_results %>% mutate(id = str_sub(socarxiv_open_data_results$article, 1, 5)) %>% select(!article)
+socarxiv_open_data_results <- left_join(covid_socarxiv_metadata, socarxiv_open_data_results, by = c("id"))
+
+# Convert TRUE/FALSE in ODDPub output to 1/0
+socarxiv_open_data_results$is_open_code <- as.integer(socarxiv_open_data_results$is_open_code)
+socarxiv_open_data_results$is_open_data <- as.integer(socarxiv_open_data_results$is_open_data)
+
+# TODO: Add variable for type of paper - "machine learning", "model"/"modeling", "simulation", "simulate"?
+
+# Add variable 
+
+# Save it 
+class(socarxiv_open_data_results)
+write_csv(socarxiv_open_data_results, 'outputs/data/socarxiv_open_data_results.csv')
+
+
+#### Summary statistics ####
+# Read in data
+socarxiv_open_data_results <- read.csv('outputs/data/socarxiv_open_data_results.csv')
+
+# Counts
+socarxiv_open_data_results %>% 
+  count(is_open_data, is_open_code)

### 2021-06-09 outputs/paper/paper.Rmd
Updates to paper and socarxiv scripts

@@
 library(wesanderson)
+library(kableExtra)
 ```
@@
   read_csv(here::here("outputs/data/arxiv_results.csv"))
+
+socarxiv_open_data_results <- 
+  read_csv(here::here("outputs/data/socarxiv_open_data_results.csv"))
+socarxiv_results <- 
+  read_csv(here::here("outputs/data/socarxiv_results.csv")) # All COVID medRxiv papers (9,929)
 
@@
 This required downloading each pre-print as a PDF and then converting the PDFs to text files.
+Some papers from SocArxiv were only available in .docx format and were downloaded as such instead.
 We then conducted the open data and open code detection procedure.
@@
 
-all <- rbind(just_arxiv, just_medRxiv, just_bioRxiv)
+just_socarxiv <- 
+  socarxiv_results  %>% 
+  select(date_created) %>%
+  rename(date = "date_created") %>%
+  mutate(type = "socArXiv")
+
+all <- rbind(just_arxiv, just_medRxiv, just_bioRxiv, just_socarxiv)
 
@@
   geom_histogram(aes(fill = type), stat="count", position = "dodge") + 
-  labs(title = "Pre-prints posted per month",
-       subtitle = "Total of 3,379 relevant pre-prints on arXiv, 3,031 on bioRxiv, 9,929 on medRxiv",
+  labs(title = "COVID-19-related pre-prints posted per month",
+       subtitle = "Total of 3,812 relevant pre-prints on arXiv, 3,714 on bioRxiv, 12,060 on medRxiv, 444 on socArXiv",
        x = "Month",
@@
 
-```{r summarycounts-medRxiv}
+```{r summarycounts-medRxiv, }
 # open data/open code count summary table
+
+just_arxiv <-
+  arxiv_open_data_results  %>%
+  select(submitted, is_open_data, is_open_code) %>%
+  mutate(type = "arXiv") %>%
+  rename(date = submitted)
+
+just_medRxiv <-
   med_open_data_results  %>%
+  select(date, is_open_data, is_open_code) %>%
+  mutate(type = "medRxiv")
+
+just_bioRxiv <-
+  bio_open_data_results  %>%
+  select(date, is_open_data, is_open_code) %>%
+  mutate(type = "bioRxiv")
+
+just_socarxiv <-
+  socarxiv_open_data_results  %>%
+  select(date_created, is_open_data, is_open_code) %>%
+  rename(date = "date_created") %>%
+  mutate(type = "socArXiv")
+
+all <- rbind(just_arxiv, just_medRxiv, just_bioRxiv, just_socarxiv)
+
+all %>%
+  group_by(type) %>%
   count(is_open_data, is_open_code) %>%
@@
          is_open_code = ifelse(is_open_code == 0, "No", "Yes")) %>%
+  ungroup() %>%
+  select(is_open_data, is_open_code, n, prop_total) %>%
   kable(col.names = c("Open data markers", "Open code markers", "Count", "Proportion of total"),
@@
         booktabs = TRUE,
-        digits = 2)
-```
-
-```{r summarycounts-bioRxiv}
-# open data/open code count summary table
-bio_open_data_results %>% 
-  count(is_open_data, is_open_code) %>%
-  mutate(prop_total = n / sum(n)) %>%
-  mutate(is_open_data = ifelse(is_open_data == 0, "No", "Yes"),
-         is_open_code = ifelse(is_open_code == 0, "No", "Yes")) %>% 
-  kable(col.names = c("Open data markers", "Open code markers", "Count", "Proportion of total"),
-        caption = "Counts and proportions of open data and code markers in bioRxiv sample",
-        booktabs = TRUE,
-        digits = 2)
+        digits = 2) %>%
+  group_rows(index = c("arXiv" = 4, "bioRxiv" = 4, "medRxiv" = 4, "socArXiv" = 4))
 ```
@@
 # Number of papers for each open data/code status per month
-open_status <- 
+open_status_med <- 
   med_open_data_results %>% 
   select(title, date, is_open_code, is_open_data) %>% 
-  mutate(condition = is_open_data + is_open_code)
+  mutate(condition = is_open_data + is_open_code, repo = "medRxiv")
+
+open_status_bio <- 
+  bio_open_data_results %>% 
+  select(title, date, is_open_code, is_open_data) %>% 
+  mutate(condition = is_open_data + is_open_code, repo = "bioRxiv")
+
+open_status_arxiv <- 
+  arxiv_open_data_results %>% 
+  select(title, submitted, is_open_code, is_open_data) %>% 
+  mutate(condition = is_open_data + is_open_code, repo = "arXiv") %>%
+  rename(date = submitted)
+
+open_status_socarxiv <- 
+  socarxiv_open_data_results %>% 
+  select(title, date_created, is_open_code, is_open_data) %>% 
+  mutate(condition = is_open_data + is_open_code, repo = "socArXiv") %>%
+  rename(date = date_created)
+
+open_status <- rbind(open_status_med, open_status_bio, open_status_arxiv, open_status_socarxiv)
+
 open_status$condition[open_status$condition == 2] <- "Both"
@@
   labs(fill = "Type of marker") +
-  scale_x_discrete(breaks=c("2020-01-01","2020-04-01","2020-07-01", "2020-10-01", "2021-01-01"), 
-                   labels=c("Jan 2020","Apr 2020","Jul 2020", "Oct 2020", "Jan 2021")) +
+  scale_x_discrete(breaks=c("2020-01-01","2020-07-01", "2021-01-01"), 
+                   labels=c("Jan 2020", "Jul 2020", "Jan 2021")) +
   ylab("Number of pre-prints") +
@@
   labs(title="Sampled pre-prints by month", subtitle="medRxiv, Total = 1,200") +
-  theme_minimal()
+  theme_minimal() +
+  scale_fill_manual(values = wes_palette("Darjeeling1")) +
+  facet_wrap(~repo)
 ```
@@
 # Proportion of papers posted with open data or open code each month
-colors <- c("Open Data" = "blue", "Open Code" = "green")
 med_month_sum_cov <- 
@@
   group_by(month = floor_date(date, "month")) %>% 
-  summarise(count=n(), prop_open_code = sum(is_open_code)/n(), prop_open_data = sum(is_open_data)/n()) %>% 
-  mutate(num_days = days_in_month(month),
-         daily_rate = count/num_days)
-med_month_sum_cov %>%
+  summarise(count = n(), "Open Code" = mean(is_open_code), "Open Data" = mean(is_open_data)) %>% 
+  mutate(daily_rate = count/days_in_month(month), repo = "medRxiv")
+
+bio_month_sum_cov <- 
+  bio_open_data_results %>% 
+  group_by(month = floor_date(date, "month")) %>% 
+  summarise(count = n(), "Open Code" = mean(is_open_code), "Open Data" = mean(is_open_data)) %>% 
+  mutate(daily_rate = count/days_in_month(month), repo = "bioRxiv")
+
+arxiv_month_sum_cov <- 
+  arxiv_open_data_results %>% 
+  group_by(month = floor_date(submitted, "month")) %>% 
+  summarise(count = n(), "Open Code" = mean(is_open_code), "Open Data" = mean(is_open_data)) %>% 
+  mutate(daily_rate = count/days_in_month(month), repo = "arXiv")
+
+socarxiv_month_sum_cov <- 
+  socarxiv_open_data_results %>% 
+  group_by(month = floor_date(date_created, "month")) %>% 
+  summarise(count = n(), "Open Code" = mean(is_open_code), "Open Data" = mean(is_open_data)) %>% 
+  mutate(daily_rate = count/days_in_month(month), repo = "socArXiv")
+
+month_sum_cov <- rbind(med_month_sum_cov, bio_month_sum_cov, arxiv_month_sum_cov, socarxiv_month_sum_cov) %>%
+  pivot_longer(cols = c("Open Data", "Open Code")) %>%
+  filter(value != 1) # Removes outliers where small number of papers in a month was sampled and both had open data/code
+
+# TODO: Fix date labels, facet_wrap labels
+month_sum_cov %>%
   ggplot() +
-  geom_line(data = med_month_sum_cov, aes(month, prop_open_data, color = "Open data")) +
-  geom_line(data = med_month_sum_cov, aes(month, prop_open_code, color = "Open code")) +
+  geom_line(data = month_sum_cov, aes(month, value, color = repo)) +
   ggtitle("Proportion of sampled pre-prints with open data or code markers") +
-  labs(colour = "Type of marker",
+  labs(colour = "Repository",
        x = "Month",
        y = "Proportion of pre-prints") + 
-  theme_minimal()
+  theme_minimal() +
+  scale_color_manual(values = wes_palette("Darjeeling1")) +
+  facet_wrap(~name)
+
 ```
@@
 ```{r open-published-summary}
-published_open_status <- 
+# Maybe find a way to use the data frames constructed above instead of constructing new ones?
+med_published_open_status <- 
   med_open_data_results %>% 
   select(title, date, published, is_open_code, is_open_data) %>% 
-  mutate(condition = is_open_data + is_open_code)
+  mutate(condition = is_open_data + is_open_code, repo = "medRxiv")
+
+bio_published_open_status <- 
+  bio_open_data_results %>% 
+  select(title, date, published, is_open_code, is_open_data) %>% 
+  mutate(condition = is_open_data + is_open_code, repo = "bioRxiv")
+
+published_open_status <- rbind(med_published_open_status, bio_published_open_status)
+
 published_open_status$condition[published_open_status$condition == 2] <- "Both"
@@
 published_open_status %>%
-  count(published, condition) %>% 
+  count(repo, published, condition) %>% 
   pivot_wider(names_from = condition, values_from = n) %>%
-  mutate(published = ifelse(published == 0, "No", "Yes"), `Proportion with either/both`= round((`Open data` + `Open code` + Both)/(`Open data` + `Open code` + Both + Neither), 2)) %>%
-  rename(Published = published) %>%
+  mutate(Published = ifelse(published == 0, "No", "Yes"), `Proportion with either/both`= round((`Open data` + `Open code` + Both)/(`Open data` + `Open code` + Both + Neither), 2)) %>%
+  select(Published, Both, Neither, `Open code`, `Open data`, `Proportion with either/both`) %>%
   kable(caption = "Counts and proportions of open data markers by whether the pre-print was published",
-        booktabs = TRUE)
+        booktabs = TRUE) %>%
+  group_rows(index = c("bioRxiv" = 2, "medRxiv" = 2))
 ```
@@
 published_open_status %>% 
-  # mutate(published = ifelse(published == 0, "Unpublished", "Published")) +
+  mutate(published = ifelse(published == 0, "Unpublished", "Published")) %>%
   ggplot() + 
@@
   ggtitle("Pre-prints by publication status") +
-  theme_minimal()
+  theme_minimal() +
+  facet_wrap(~repo) + 
+  scale_fill_manual(values = wes_palette("Darjeeling1"))
+
 ```
@@
 # Number of open data/code papers by keyword for different types
-paper_type_keywords <- 
+med_paper_type_keywords <- 
   med_open_data_results %>% select(title, abstract, date, is_open_code, is_open_data) %>% 
-  mutate(condition = is_open_data + is_open_code)
+  mutate(condition = is_open_data + is_open_code, repo = "medRxiv")
+
+bio_paper_type_keywords <- 
+  bio_open_data_results %>% select(title, abstract, date, is_open_code, is_open_data) %>% 
+  mutate(condition = is_open_data + is_open_code, repo = "bioRxiv")
+
+arxiv_paper_type_keywords <- 
+  arxiv_open_data_results %>% select(title, abstract, submitted, is_open_code, is_open_data) %>% 
+  rename(date = submitted) %>%
+  mutate(condition = is_open_data + is_open_code, repo = "arXiv")
+
+socarxiv_paper_type_keywords <- 
+  socarxiv_open_data_results %>% select(title, description, date_created, is_open_code, is_open_data) %>% 
+  rename(date = date_created, abstract = description) %>%
+  mutate(condition = is_open_data + is_open_code, repo = "socArXiv")
+
+paper_type_keywords <- rbind(med_paper_type_keywords, bio_paper_type_keywords, arxiv_paper_type_keywords, socarxiv_paper_type_keywords)
+
 paper_type_keywords$condition[paper_type_keywords$condition == 2] <- "Both"
 paper_type_keywords$condition[paper_type_keywords$condition == 0] <- "Neither"
-paper_type_keywords$condition[paper_type_keywords$condition == 1 & open_status$is_open_code == 1] <- "Open code"
-paper_type_keywords$condition[paper_type_keywords$condition == 1 & open_status$is_open_data == 1] <- "Open data"
+paper_type_keywords$condition[paper_type_keywords$condition == 1 & paper_type_keywords$is_open_code == 1] <- "Open code"
+paper_type_keywords$condition[paper_type_keywords$condition == 1 & paper_type_keywords$is_open_data == 1] <- "Open data"
+
 paper_type_keywords$`Machine Learning` <- str_detect( paper_type_keywords$title, "machine learning") | 
@@
 # # Plot
-# paper_type_keywords %>% ggplot() + 
-#   geom_bar(aes(x = Type, fill=factor(condition, levels = c("Neither", "Open code", "Open data", "Both")), position = "stack")) +
-#   labs(fill = "Type of marker") +
-#   scale_x_discrete(labels=c("Machine learning", "Modelling", "Simulation")) +
-#   ylab("Number of pre-prints") +
-#   xlab("Month") +
-#   ggtitle("Sampled pre-prints by type") +
-#   theme_minimal()
+paper_type_keywords %>% ggplot() +
+  geom_bar(aes(x = Type, fill=factor(condition, levels = c("Neither", "Open code", "Open data", "Both")), position = "stack")) +
+  labs(fill = "Type of marker") +
+  scale_x_discrete(labels=c("Machine learning", "Modelling", "Simulation")) +
+  ylab("Number of pre-prints") +
+  xlab("Month") +
+  ggtitle("Sampled pre-prints by type") +
+  theme_minimal() +
+  scale_fill_manual(values = wes_palette("Darjeeling1")) +
+  facet_wrap(~repo)
+
 ```
@@
 paper_type_keywords %>% 
-  count(Type, condition) %>% 
+  count(repo, Type, condition) %>% 
   pivot_wider(names_from = condition, values_from = n, values_fill = 0) %>% 
@@
   mutate(`Proportion with either/both`= round((`Open data` + `Open code` + Both)/(`Open data` + `Open code` + Both + Neither), 2)) %>%
+  select(!repo) %>%
   kable(caption = "Counts and proportions of open data markers by the type of pre-print",
-        booktabs = TRUE)
+        booktabs = TRUE) %>%
+  group_rows(index = c("arxiv" = 3, "bioRxiv" = 3, "medRxiv" = 3, "socArXiv" = 3))
 ```
@@
 The COVID-19 pandemic has seen an uptake in open science practices globally, as evidenced by the creation of open data repositories such as the dashboard maintained by the Center for Systems Science and Engineering at Johns Hopkins University [@citeCSSE] or the large number of publishers who have removed paywalls from published COVID-19 research [@gill2020].
-An important next step may compare open data and code availability in COVID-19 pre-prints with those from other topics posted to medRxiv to examine whether the pandemic has increased transparency from the previous norm.
+(MENTION/REFERENCE https://wellcome.org/coronavirus-covid-19/open-data ?) An important next step may compare open data and code availability in COVID-19 pre-prints with those from other topics posted to medRxiv to examine whether the pandemic has increased transparency from the previous norm.
 
@@
 This gains importance as computational methods become increasingly popular in the rush to form predictions about emerging situations with limited data or laboratory research, which was the case for modelling studies in the early days of the COVID-19 pandemic (CITE).
-We also see growing concern over the quality and consequences of this sort of research, with bioRxiv not allowing purely computational work [@kwon2020].
+We also see growing concern over the quality and consequences of this sort of research, with bioRxiv no longer allowing purely computational work [@kwon2020].
 

### 2021-06-09 scripts/01-data_gathering-medrxiv.R

@@ -22,6 +22,9 @@ library(oddpub)
 # Download copy of current database
 med_data <- mx_snapshot()
 
+# Keep snapshot of pre-pandemic database (see 'Pre-Pandemic Data' below)
+med_data_2019 <- med_data %>% filter(date <= "2019-12-31")
+
 # Raw stats as of 22 May, 2021 (from medRxiv website)
 # 16,135 COVID articles total
 # 12,450 in medRxiv
@@ -50,10 +53,6 @@ med_results <- med_results[order(med_results$date),]
 # Save results - this is sampling frame (info for all medRxiv COVID-19 papers)
 write_csv(med_results, "outputs/data/med_results.csv")
 
-# Sometimes a paper has multiple versions - EXCLUDED IN PREVIOUS STEP, THIS IS MOOT
-# Filter to only uniques and keep latest version of the paper
-# med_results_unique <- med_results[!duplicated(med_results[c(2)]),]
-
 # Summarise and graph by date
 med_daily_sum <- med_results %>% group_by(date) %>% summarise(date = date, total = n())
 med_plot <- med_daily_sum %>% ggplot() + geom_line(aes(x=date, y=total)) + geom_smooth(aes(x=date, y=total))
@@ -81,6 +80,24 @@ med_sample %>% slice(1068:1500) %>% mx_download(directory = med_pdf_folder, crea
 
 # Convert PDFs to text and saves in new folder
 pdf_convert(med_pdf_folder, med_txt_folder)
+
+
+#### Pre-Pandemic Data
+View(med_data_2019)
+# Filter to only unique DOIs and keep latest version of the paper
+# First sort by descending version number so only most recent version is kept
+med_data_2019 <- med_data_2019[order(-med_data_2019$version),] %>% distinct(doi, .keep_all = TRUE)
+
+#### Download relevant papers ####
+# Set up folders for download and txt conversion
+med_pdf_folder_new <- paste0(getwd(), "/outputs/control-data/pdf-medRxiv")
+med_txt_folder_new <- paste0(getwd(), "/outputs/control-data/text-medRxiv")
+
+# Download all PDFs
+med_data_2019 %>% mx_download(directory = med_pdf_folder_new, create = FALSE)
+
+# Convert PDFs to text and saves in new folder
+pdf_convert(med_pdf_folder_new, med_txt_folder_new)
 
 
 #### Clean up ####

### 2021-06-09 scripts/01-data_gathering-socarxiv.R

@@ -124,11 +124,12 @@ all_socarxiv_metadata <-
 write_csv(all_socarxiv_metadata, "outputs/all_socarxiv_metadata.csv")
 
 
-
 #### Download PDFs ####
 covid_socarxiv_metadata <- 
   all_socarxiv_metadata %>% 
   filter(covid_flag == TRUE)
+
+write_csv(covid_socarxiv_metadata, "outputs/data/socarxiv_results.csv")
 
 utils::download.file("https://osf.io/preprints/socarxiv/2p3xt/download", 
                      "test.docx", 

### 2021-06-29 outputs/paper/paper-copy.Rmd
Updates to scripts, fixes to 2020/2021 data, paper updates

--- 2021-06-09 outputs/paper/paper.Rmd
@@
 author: 
+  - Rohan Alexander^[University of Toronto.]
   - Annie Collins^[University of Toronto.]
@@
 med_results <- 
-  read_csv(here::here("outputs/data/med_results.csv")) # All COVID medRxiv papers (9,929)
+  read_csv(here::here("outputs/data/med_results.csv")) # All COVID medRxiv papers (12,060)
+med_2019_open_data_results <- 
+  read_csv(here::here("outputs/control-data/med_2019_open_data_results.csv")) # All pre-prints posted to medRxiv in 2019
 
@@
 bio_results <- 
-  read_csv(here::here("outputs/data/bio_results.csv")) # All COVID bioRxiv papers (3,031)
+  read_csv(here::here("outputs/data/bio_results.csv")) # All COVID bioRxiv papers (3,714)
+bio_2019_open_data_results <- 
+  read_csv(here::here("outputs/control-data/bio_2019_open_data_results.csv"))
+bio_2019_results <- 
+  read_csv(here::here("outputs/control-data/bio_data_2019.csv"))
 
@@
 all_arxiv_results <- 
-  read_csv(here::here("outputs/data/arxiv_results.csv"))
+  read_csv(here::here("outputs/data/arxiv_results.csv")) # All COVID arXiv papers (3,812)
 
@@
 socarxiv_results <- 
-  read_csv(here::here("outputs/data/socarxiv_results.csv")) # All COVID medRxiv papers (9,929)
+  read_csv(here::here("outputs/data/socarxiv_results.csv")) # All COVID medRxiv papers (444). Same as socarxiv_sample.
 
@@
 Scientists use open repositories of papers to more quickly disseminate their research than is possible in traditional journals or conference proceedings.
-These repositories, such as arXiv, bioRxiv, medRxiv, and SocArXiv, are a critical component of science and many results build on the work published there.
+These repositories, such as arXiv, bioRxiv, medRxiv, and SocArXiv, are a critical component of scientific communication and many results build on the work published there.
 Thus it is important that the results that are published are credible.
@@
 But given the importance of these repositories, it is important that scientists impose on themselves various standards for their results.
-Following @weissgerber2021automated we examine papers about COVID-19 published to  arXiv, bioRxiv, medRxiv, and SocArXiv from January 2020, through to February 2021.
+Following @weissgerber2021automated we examine papers about COVID-19 published to  arXiv, bioRxiv, medRxiv, and SocArXiv from January 2020, through to May 1, 2021.
 We search for markers of open science as indicators of reproducibility, specifically open data and open code.
 
-We find that approximately 81 per cent of sampled papers contain neither open data nor open code markers.
+We find that approximately 76 per cent of papers sampled from arXiv, 68 percent of papers sampled from bioRxiv, 80 per cent of papers sampled from medRxiv, and 83 per cent of papers sampled from socArXiv contain neither open data nor open code markers.
 Examining trends over time, we find that the proportion of pre-prints containing open data or code markers has fluctuated but shown no obvious increasing or decreasing trend throughout the pandemic.
@@
 
-The remainder of this paper is structured as follows: in Section \@ref(data-and-methodology) we discuss the process of constructing our dataset through retrieving pre-prints from the medRxiv repository and mining them for open data and open code markers.
-In Sections \@ref(model) and \@ref(results) we explore some key findings in this raw data and explore some logistic regression models that support these findings.
+The remainder of this paper is structured as follows: in Section \@ref(methodology) we discuss the process of constructing our dataset through retrieving pre-prints from the arXiv, bioRxiv, medRxiv, and socArXiv repositories and mining them for open data and open code markers.
+In Section \@ref(results), we explore the results and key findings of this process.
 Finally, in Section \@ref(discussion) we discuss the implications of these findings in the broader context of reproducibility and science during the COVID-19 pandemic, as well as next steps to expand on our findings and questions raised in the research process.
 
-# Data and Methodology
+# Methodology
 
-## Overview
+## Pre-print metadata
+Our primary dataset consists of pre-print metadata extracted from the arXiv, bioRxiv, medRxiv, and socArXiv pre-print repositories via their respective Application Programming Interface (API).
+This metadata varies by repository, but generally includes the following information: title, abstract, author(s), date created, research field, DOI, version number, corresponding author, corresponding author's institutional affiliation, published DOI (if the pre-prints has since been published in a peer-reviewed journal), and download link.
+The data collection process was conducted separately for COVID-19 and pre-COVID-19 papers.
 
-Our primary dataset consists of information extracted from the arXiv, bioRxiv, medRxiv, and SocArXiv pre-print repositories.
-We downloaded pre-prints that contained various keywords related to COVID-19 (a full list of these is available in Appendix \@ref(keywords)), and then identified the availability of open code and open data using the Open Data Detection in Publications (ODDPub) text mining algorithm [@citePDDPub] in the `oddpub` package [@citeODDPubpackage].
+For COVID-19-related pre-prints, we first created a local copy of each repository containing all metadata for pre-prints registered between January 1, 2020 and May 1, 2021.
+In the case of socArXiv there are additionally fields that are self-reported by the submitting author about the availability of code and data.
+We classified individual pre-prints as "COVID-19-related" on the basis of containing one of more of the following terms in their title or abstract (case insensitive): "COVID-19", "COVID 19", "corona virus", "coronavirus", "coronavirus-2", "SARS-CoV-2", "SARSCoV-2", or "2019-nCoV".
+From each repository's dataset we randomly sampled pre-prints for further analysis, with the exception of socArXiv for which we analyzed all pre-prints that matched the above criteria due to their limited number (n = 410).
 
-We constructed this dataset by first creating a local copy of the repository using the repository API.
-We identified papers related to the COVID-19 pandemic through several keyword searches to create our dataset of papers and associated metadata.
-This metadata varies by repository, but generally includes the following information: title, abstract, author(s), date posted, research field, DOI, version number, corresponding author, corresponding author's institutional affiliation, and published DOI (if the pre-prints has since been published in a peer-reviewed journal).
-In the case of SocArXiv there are additionally fields that are self-reported by the submitting author about the availability of code and data.
+For pre-COVID-19 pre-prints, we created a local copy of each repository containing all metadata for pre-prints registered between January 1, 2019 and December 31, 2019.
+Since medRxiv was launched in June 2019, we used all pre-print data from the latter half of 2019.
+We then randomly sampled 1,200 pre-prints from each repository's dataset for analysis, with the exception of medRxiv for which only 913 pre-prints were available in total.
 
-We then checked these pre-prints for open data and code markers using the ODDPub algorithm.
+## Open data and code detection
+
+We checked our sampled pre-prints for open data and code markers using the Open Data Detection in Publications (ODDPub) text mining algorithm [@citePDDPub] within the `oddpub` R package [@citeODDPubpackage].
 This required downloading each pre-print as a PDF and then converting the PDFs to text files.
-Some papers from SocArxiv were only available in .docx format and were downloaded as such instead.
-We then conducted the open data and open code detection procedure.
-This involved searching for keywords and other markers of open data and open code such as references to GitHub repositories and similar.
+Some papers from socArXiv were only available in Word document format (.docx) and were downloaded as such and then converted to text format.
+We then conducted the open data and open code detection procedure which involved searching for keywords and other markers of open data and open code availability.
 A full listing of these markers is included in Appendix \@ref(markers).
@@
 
-The result of this process is a dataset indicating the presence of open data or open code markers in each pre-print (with a binary variable for each marker, and the relevant open data or open code statements when applicable).
-Our final analysis dataset was formed by joining these two datasets together, typically using the DOI or the unique filename, to form a dataset including all original, qualitative metadata information for each pre-print alongside its open data and open code status and markers.
+The result of this process is a dataset indicating the presence of open data or open code markers in each pre-print (with a logical vector for each marker, followed by the relevant open data or open code statements where applicable).
+Our final dataset was formed by joining this output with the original sample metadata, typically using the DOI or the unique file name, to form a dataset including all original, qualitative metadata for each pre-print alongside its open data and open code status and markers.
+
+Although socArXiv's metadata contained author-reported information concerning data and code availability for each pre-print, we elected to use the results of the ODDPub algorithm in our analysis to ensure comparability of results between pre-prints from all repositories.
+Notable discrepancies between the ODDPub algorithm and authors' self-reported data and code availability include...
 
@@
   labs(title = "COVID-19-related pre-prints posted per month",
-       subtitle = "Total of 3,812 relevant pre-prints on arXiv, 3,714 on bioRxiv, 12,060 on medRxiv, 444 on socArXiv",
+       subtitle = "Total of 3,896 relevant pre-prints on arXiv, 3,714 on bioRxiv, 12,060 on medRxiv, 410 on socArXiv",
        x = "Month",
@@
 
-## Summary statistics
+# Results
 
-The number of pre-prints posted per month increased dramatically between January and May 2020, reaching its maximum in May and subsequently decreasing.
-The number of pre-prints posted since August 2020 has remained reasonably steady at around 750 per month (Figure \@ref(fig:monthly-papers-total)).
+## All pre-prints
+The number of pre-prints posted per month increased dramatically in the first half of 2020 across all repositories, reaching its maximum sometime between April and June (depending on repository) and subsequently decreasing.
+The number of pre-prints posted monthly since August 2020 has remained reasonably steady, with the exception of medRxiv which experienced a spike up to nearly 1000 pre-prints posted in March 2021 (Figure \@ref(fig:monthly-papers-total)).
 For context, COVID-19 was declared a pandemic by the World Health Organization (WHO) on March 11, 2020, at which point the number of cases globally had just surpassed 118,000 (primarily in east Asia) and the virus had been reported in 114 countries [@citeWHOtimeline].
 
-Broadly, we are unable to find markers of either open data or open code for around 81 per cent of the 1,200 sampled pre-prints.
-The remaining 19 per cent of pre-prints was comprised of 4 per cent of the sample containing markers for open code, 8 per cent of the sample with markers for open data, and 7 per cent of the sample with markers for both open data and open code (Table \@ref(tab:summarycounts-medRxiv)).
+## Open data and code
+We analyzed a total of 3,910 COVID-19-related pre-prints.
+This sample is further broken down as follows: 1,500 from medRxiv, 1,000 from arXiv, 1,000 from bioRxiv, and 410 from socArXiv.
+Broadly, we are unable to find markers of either open data for open code for 2,987 or approximately 76 per cent of our sample (Table \@ref(tab:summarycounts-overall)).
+Of the remaining pre-prints, 6 per cent contained open code markers only, 10 per cent contained open data markers only, and 8 percent included markers of both open data and open code.
 
-```{r summarycounts-medRxiv, }
-# open data/open code count summary table
+Once differentiated by repository, we observe that open data and code markers were absent from 68 percent of the sampled bioRxiv pre-prints, 80 per cent of the sampled medRxiv pre-prints, 76 per cent of the sampled arXiv pre-prints, and 83 per cent of all COVID-19-related socArXiv pre-prints.
+The distribution of the remaining portion of pre-prints varies by repository (Table \@ref(tab:summarycounts-repositories)).
+Notably, 28 per cent of sampled pre-prints from bioRxiv contained open data markers and 20 per cent of sampled arXiv pre-prints contained markers of open code, the highest proportions of any repository for each type of marker.
 
+```{r, summarycounts-overall}
 just_arxiv <-
@@
   select(submitted, is_open_data, is_open_code) %>%
+  mutate(submitted = as.Date(submitted)) %>%
   mutate(type = "arXiv") %>%
@@
   med_open_data_results  %>%
+  mutate(date = as.Date(date))  %>%
   select(date, is_open_data, is_open_code) %>%
@@
   select(date, is_open_data, is_open_code) %>%
+  mutate(date = as.Date(date)) %>%
   mutate(type = "bioRxiv")
@@
 all %>%
+  count(is_open_data, is_open_code) %>%
+  mutate(prop_total = n / sum(n)) %>%
+  mutate(is_open_data = ifelse(is_open_data == 0, "No", "Yes"),
+         is_open_code = ifelse(is_open_code == 0, "No", "Yes")) %>%
+  select(is_open_data, is_open_code, n, prop_total) %>%
+  kable(col.names = c("Open data markers", "Open code markers", "Count", "Proportion of total"),
+        caption = "Counts and proportions of open data and code markers in sample",
+        booktabs = TRUE,
+        digits = 2)
+```
+
+```{r summarycounts-repositories}
+# open data/open code count summary table
+
+all %>%
   group_by(type) %>%
@@
   kable(col.names = c("Open data markers", "Open code markers", "Count", "Proportion of total"),
-        caption = "Counts and proportions of open data and code markers in medRxiv sample",
+        caption = "Counts and proportions of open data and code markers by pre-print repository",
         booktabs = TRUE,
@@
 The distribution of total sampled pre-prints and sampled pre-prints with open data or code markers roughly follows that of COVID-19-related pre-prints posted in general (Figure \@ref(fig:monthly-papers-condition-stack)).
-The proportion of pre-prints with open data or code has fluctuated over time but shows no consistent overall increase or decrease throughout the course of the pandemic, nor in conjunction with increases or decreases in the total number of pre-prints posted to medRxiv (Figure \@ref(fig:monthly-proportion-of-open)).
-In our dataset, only one pre-print was sampled for the month of January 2020.
-This pre-print contained neither open data nor open code markers, thus the 0 per cent rate of open data and code for this month will be treated as an outlier, and removed modelling purposes.
+The proportion of pre-prints with open data or code has fluctuated over time but shows no consistent overall increase or decrease throughout the course of the pandemic, nor in conjunction with increases or decreases in the total number of pre-prints posted to any given repository (Figure \@ref(fig:monthly-proportion-of-open)).
+In our datasets, very few (if any) pre-prints were sampled for the month of January 2020.
+None of these pre-prints contained open data or open code markers, thus the 0 per cent rate of open data and code for this month across all repositories should be considered an outlier.
 
@@
   select(title, date, is_open_code, is_open_data) %>% 
-  mutate(condition = is_open_data + is_open_code, repo = "bioRxiv")
+  mutate(condition = is_open_data + is_open_code, repo = "bioRxiv", date = as.character(date))
 
@@
   select(title, submitted, is_open_code, is_open_data) %>% 
-  mutate(condition = is_open_data + is_open_code, repo = "arXiv") %>%
-  rename(date = submitted)
+  mutate(condition = is_open_data + is_open_code, repo = "arXiv", date = as.character(submitted) %>% str_sub(end = 10)) %>%
+  select(title, date, is_open_code, is_open_data, condition, repo)
 
@@
   select(title, date_created, is_open_code, is_open_data) %>% 
-  mutate(condition = is_open_data + is_open_code, repo = "socArXiv") %>%
-  rename(date = date_created)
+  mutate(condition = is_open_data + is_open_code, repo = "socArXiv", date = as.character(date_created)) %>%
+  select(title, date, is_open_code, is_open_data, condition, repo)
 
@@
 
+open_status$date <- as.Date(open_status$date)
 open_status$condition[open_status$condition == 2] <- "Both"
@@
   med_open_data_results %>% 
+  mutate(date = as.Date(date)) %>%
   group_by(month = floor_date(date, "month")) %>% 
@@
   bio_open_data_results %>% 
+  mutate(date = as.Date(date)) %>%
   group_by(month = floor_date(date, "month")) %>% 
@@
 
-In Table \@ref(tab:open-published-summary) we disaggregate pre-prints by whether there is an indication that it was published.
-We find that the proportion of pre-prints with open data or code markers among those that have been published is approximately five per cent lower compared with pre-prints that have not been published (Table \@ref(tab:open-published-summary)).
+Our metadata also contains an indication of whether or not a pre-print has been published in the form of a DOI linking to the corresponding published paper.
+The proportion of pre-prints that have been published varies by repository (Table \@ref(tab:published-sample-summary)).
+Notably, of all COVID-19-related pre-prints created during 2020 and 2021, approximately one third of those posted to bioRxiv and nearly 30 percent of those posted to medRxiv were eventually published in peer reviewed journals.
+This is high in comparison to the proportions from arXiv and socArXiv, which may be a reflection of the unprecedented attention pre-print servers showcasing research from the biomedical and life sciences have received throughout the pandemic.
+
+```{r published-sample-summary}
+med_published <- 
+  med_results %>% 
+  select(title, date, published) %>% 
+  mutate(repo = "medRxiv", published = as.numeric(!is.na(published)))
+
+bio_published <- 
+  bio_results %>% 
+  select(title, date, published) %>% 
+  mutate(repo = "bioRxiv", published = as.numeric(!is.na(published)))
+
+arxiv_published <- 
+  all_arxiv_results %>% 
+  select(title, submitted, doi) %>%
+  mutate(doi = as.numeric(!is.na(doi)), repo = "arXiv") %>%
+  rename(published = doi, date = submitted)
+
+socarxiv_published <- 
+  socarxiv_results %>% 
+  select(title, date_created, links.doi) %>%
+  mutate(links.doi = as.numeric(!is.na(links.doi)), repo = "socArXiv") %>%
+  rename(published = links.doi, date = date_created)
+
+published <- rbind(med_published, bio_published, arxiv_published, socarxiv_published)
+
+published %>% 
+  group_by(repo) %>% 
+  summarise(`Published pre-prints` = sum(published), `Proportion published` = mean(published) %>% round(2)) %>%
+  kable(caption = "Counts and proportion of published COVID-19 pre-prints in each repository",
+        col.names = c("Repositiory", "Published pre-prints", "Proportion published"))
+```
+
+In Table \@ref(tab:open-published-summary) we disaggregate sampled pre-prints by whether or not there is an indication of publication.
+We find that the proportion of pre-prints with open data or code markers among those that have been published is approximately the same as pre-prints that have not been published, differing by one percent only within the bioRxiv and arXiv samples, and three percent in the socArxiv sample.
 
@@
 # Maybe find a way to use the data frames constructed above instead of constructing new ones?
+
+# ArXiv variables: doi
+# SocArXiv variables: links.doi
+
 med_published_open_status <- 
@@
 
-published_open_status <- rbind(med_published_open_status, bio_published_open_status)
+arxiv_published_open_status <- 
+  arxiv_open_data_results %>% 
+  select(title, submitted, doi, is_open_code, is_open_data) %>%
+  mutate(doi = as.numeric(!is.na(doi)), condition = is_open_data + is_open_code, repo = "arXiv") %>%
+  rename(published = doi, date = submitted)
+
+socarxiv_published_open_status <- 
+  socarxiv_open_data_results %>% 
+  select(title, date_created, links.doi, is_open_code, is_open_data) %>%
+  mutate(links.doi = as.numeric(!is.na(links.doi)), condition = is_open_data + is_open_code, repo = "socArXiv") %>%
+  rename(published = links.doi, date = date_created)
+
+published_open_status <- rbind(med_published_open_status, bio_published_open_status, arxiv_published_open_status, socarxiv_published_open_status)
 
@@
   count(repo, published, condition) %>% 
-  pivot_wider(names_from = condition, values_from = n) %>%
-  mutate(Published = ifelse(published == 0, "No", "Yes"), `Proportion with either/both`= round((`Open data` + `Open code` + Both)/(`Open data` + `Open code` + Both + Neither), 2)) %>%
-  select(Published, Both, Neither, `Open code`, `Open data`, `Proportion with either/both`) %>%
+  pivot_wider(names_from = condition, values_from = n, values_fill = 0) %>%
+  mutate(Published = ifelse(published == 0, "No", "Yes"), `Proportion with neither`= round((`Neither`)/(`Open data` + `Open code` + Both + Neither), 2)) %>%
+  select(Published, Both, Neither, `Open code`, `Open data`, `Proportion with neither`) %>%
   kable(caption = "Counts and proportions of open data markers by whether the pre-print was published",
         booktabs = TRUE) %>%
-  group_rows(index = c("bioRxiv" = 2, "medRxiv" = 2))
+  group_rows(index = c("bioRxiv" = 2, "medRxiv" = 2, "arXiv" = 2, "socArXiv" = 2))
 ```
 
-There was a low number of papers that had markers of either open data or code in both those that were published and those that were not published (Figure \@ref(fig:open-published-stack)).
+```{r open-published-stack, fig.cap= "Number of pre-prints in sample with open data or open code markers by publication status", out.width="90%", fig.align = "center"}
 
-```{r open-published-stack, fig.cap= "Number of pre-prints in sample with open data or open code markers by publication status", out.width="90%", fig.align = "center"}
-published_open_status$published[published_open_status$published == 0] <- "Published"
-published_open_status$published[published_open_status$published == 1] <- "Unpublished"
+# TODO: are these graphs even necessary?
+
+# published_open_status$published[published_open_status$published == 0] <- "Published"
+# published_open_status$published[published_open_status$published == 1] <- "Unpublished"
 
@@
 It is important to note that our dataset imperfectly characterizes publication.
-In particular, it does not have the publication details for some papers that were published.
-And even if it were a perfect record, there is a publication lag (estimated at an average of around 60 days) that may skew the results [@kwon2020].
+In particular, it likely does not have the publication details for some papers that were published.
+And even if it were a perfect record, there is a publication lag (estimated at an average of around 60 days for COVID-19-related pre-prints) that may skew the results for the papers in the latter portion of our sample [@kwon2020].
 
-## Type of pre-print
+## Pre-pandemic Pre-prints
 
-There are a variety of different types of pre-prints on medRxiv, including those focused on machine learning, modelling, and simulation.
-It may be that there are differences in open science practices between these.
-For instance, in papers related to simulation there is less likely to be issues around sharing code.
+In order to examine the influence of the COVID-19 pandemic on open science practices in during the pandemic, we analyzed pre-prints posted between January and December 2019 from each of the four repositories using the same process as was done for the COVID-19-related pre-prints.
+Since medRxiv was founded in June 2019, all pre-prints unrelated to COVID-19 posted from the latter half of 2019 were analyzed (a total of 913).
+For bioRxiv, a random sample of 1,200 was taken from all non-COVID-19-related pre-prints posted in the relevant date range.
 
-To characterize the pre-prints by type, we performed keyword searches within the titles and abstracts of our dataset to examine potential differences in the prevalence of open data or code for specific types of papers.
-There were 21 sampled pre-prints that included the term 'machine learning'.
-Of those, the proportion of pre-prints with open data or code markers rose to 38 per cent, double that of the sample overall (Table \@ref(tab:summary-by-type)).
-Similarly, keywords relating to simulation appeared in 80 sampled pre-prints and keywords related to modelling appeared in over one-third of our sampled pre-prints.
-The latter two categories did not contain pre-prints with open data or code markers at a rate much higher than the general sample, with 22 and 24 per cent of each type of paper containing either open data or open code markers compared to 19 per cent overall.
-However, due to the significant role that modelling has played in the context of COVID-19, it is likely that a simple keyword search does not have the resolution needed to properly characterize this subset, it is it possible that it only contains pre-prints presenting their own, novel, models.
+```{r 2019-results}
+bio_2019 <- bio_2019_results %>%
+  select(date) %>%
+  mutate(type = "bioRxiv")
 
-```{r stack-by-type, fig.cap= "Number of pre-prints in sample with open data or open code markers by type", out.width="90%", fig.align = "center"}
+med_2019 <- med_2019_open_data_results %>%
+  select(date) %>%
+  mutate(type = "medRxiv")
 
-# Number of open data/code papers by keyword for different types
-med_paper_type_keywords <- 
-  med_open_data_results %>% select(title, abstract, date, is_open_code, is_open_data) %>% 
+all_2019 <- rbind(bio_2019, med_2019)
+
+# TODO: position = "dodge" not working
+all_2019 %>% 
+  mutate(month = floor_date(date, "month")) %>% 
+  # filter(year(date) >= 2020) %>% 
+  ggplot(aes(x = month, fill = type)) + 
+  geom_histogram(stat="count", position = "dodge2") +
+  labs(title = "Pre-prints posted per month, 2019",
+       subtitle = "Total of 31,752 pre-prints on bioRxiv, 913 on medRxiv",
+       x = "Month",
+       y = "Number of pre-prints",
+       fill = "Repository") +
+  theme_minimal() +
+  scale_fill_manual(values = wes_palette("Darjeeling1"))
+```
+
+```{r 2019-open-results}
+just_2019_medRxiv <-
+  med_2019_open_data_results  %>%
+  mutate(date = as.Date(date))  %>%
+  select(date, is_open_data, is_open_code) %>%
+  mutate(type = "medRxiv")
+
+just_2019_bioRxiv <-
+  bio_2019_open_data_results  %>%
+  select(date, is_open_data, is_open_code) %>%
+  mutate(date = as.Date(date)) %>%
+  mutate(type = "bioRxiv")
+
+all_2019 <- rbind(just_2019_medRxiv, just_2019_bioRxiv)
+
+all_2019 %>%
+  group_by(type) %>%
+  count(is_open_data, is_open_code) %>%
+  mutate(prop_total = n / sum(n)) %>%
+  mutate(is_open_data = ifelse(is_open_data == 0, "No", "Yes"),
+         is_open_code = ifelse(is_open_code == 0, "No", "Yes")) %>%
+  ungroup() %>%
+  select(is_open_data, is_open_code, n, prop_total) %>%
+  kable(col.names = c("Open data markers", "Open code markers", "Count", "Proportion of total"),
+        caption = "Counts and proportions of open data and code markers in 2019 medRxiv and bioRxiv samples",
+        booktabs = TRUE,
+        digits = 2) %>%
+  group_rows(index = c("bioRxiv" = 4, "medRxiv" = 4))
+```
+
+Between June and December 2019, the number of pre-prints posted to medRxiv monthly saw an overall increase which may be expected as the repository gained recognition and popularity in the medical research community.
+The number of papers posted monthly to bioRxiv also saw an overall increase throughout 2019.
+It is important to note here that due to its relative immaturity at the beginning of the COVID-19 pandemic, a significant portion of medRxiv's overall usage has been dedicated to COVID-19-related research.
+In total, 19,638 pre-prints have been posted to medRxiv since June 2019, 12,060 (approximately 61 per cent) of which relate to COVID-19.
+
+Of the analyzed pre-prints from 2019, 63 percent of those posted to bioRxiv and 75 per cent of those posted to medRxiv showed no indication of open data or open code (Table \@ref(tab:2019-published)).
+Both of these rates are approximately five per cent lower than the corresponding proportions of COVID-19-related pre-prints, suggesting that the analyzed pre-prints from 2019 contained an overall higher prevalence of open data and code markers than pre-prints concerning COVID-19.
+Specifically, we found that open data availability in medRxiv pre-prints was significantly associated with a pre-pandemic registration date (chi-squared = 8.225, p < 0.005), as was open code availability for bioRxiv pre-prints (chi-squared = 15.028, p < 0.005).
+This would suggest that open data and code practices have suffered in the context of COVID-19.
+
+```{r 2019-published}
+med_published_2019 <- 
+  med_2019_open_data_results %>% 
+  select(title, date, published) %>% 
+  mutate(repo = "medRxiv", published = as.numeric(published))
+
+bio_published_2019 <- 
+  bio_2019_results %>% 
+  select(title, date, published) %>% 
+  mutate(repo = "bioRxiv", published = as.numeric(!is.na(published)))
+
+published_2019 <- rbind(med_published_2019, bio_published_2019)
+
+published_2019 %>% 
+  group_by(repo) %>% 
+  summarise(`Published pre-prints` = sum(published), `Proportion published` = mean(published) %>% round(2)) %>%
+  kable(caption = "Counts and proportion of published COVID-19 pre-prints in each repository, 2019",
+        col.names = c("Repositiory", "Published pre-prints", "Proportion published"))
+```
+
+```{r, 2019-open-publishing}
+med_2019_published_open_status <- 
+  med_2019_open_data_results %>% 
+  select(title, date, published, is_open_code, is_open_data) %>% 
   mutate(condition = is_open_data + is_open_code, repo = "medRxiv")
 
-bio_paper_type_keywords <- 
-  bio_open_data_results %>% select(title, abstract, date, is_open_code, is_open_data) %>% 
+bio_2019_published_open_status <- 
+  bio_2019_open_data_results %>% 
+  select(title, date, published, is_open_code, is_open_data) %>% 
   mutate(condition = is_open_data + is_open_code, repo = "bioRxiv")
 
-arxiv_paper_type_keywords <- 
-  arxiv_open_data_results %>% select(title, abstract, submitted, is_open_code, is_open_data) %>% 
-  rename(date = submitted) %>%
-  mutate(condition = is_open_data + is_open_code, repo = "arXiv")
+published_2019_open_status <- rbind(med_2019_published_open_status, bio_2019_published_open_status)
 
-socarxiv_paper_type_keywords <- 
-  socarxiv_open_data_results %>% select(title, description, date_created, is_open_code, is_open_data) %>% 
-  rename(date = date_created, abstract = description) %>%
-  mutate(condition = is_open_data + is_open_code, repo = "socArXiv")
+published_2019_open_status$condition[published_2019_open_status$condition == 2] <- "Both"
+published_2019_open_status$condition[published_2019_open_status$condition == 0] <- "Neither"
+published_2019_open_status$condition[published_2019_open_status$condition == 1 & published_2019_open_status$is_open_code == 1] <- "Open code"
+published_2019_open_status$condition[published_2019_open_status$condition == 1 & published_2019_open_status$is_open_data == 1] <- "Open data"
 
-paper_type_keywords <- rbind(med_paper_type_keywords, bio_paper_type_keywords, arxiv_paper_type_keywords, socarxiv_paper_type_keywords)
-
-paper_type_keywords$condition[paper_type_keywords$condition == 2] <- "Both"
-paper_type_keywords$condition[paper_type_keywords$condition == 0] <- "Neither"
-paper_type_keywords$condition[paper_type_keywords$condition == 1 & paper_type_keywords$is_open_code == 1] <- "Open code"
-paper_type_keywords$condition[paper_type_keywords$condition == 1 & paper_type_keywords$is_open_data == 1] <- "Open data"
-
-paper_type_keywords$`Machine Learning` <- str_detect( paper_type_keywords$title, "machine learning") | 
-                                          str_detect( paper_type_keywords$abstract, "machine learning")
-paper_type_keywords$Simulation <- str_detect( paper_type_keywords$title, "simulate|simulation|simulating") | 
-                                    str_detect( paper_type_keywords$abstract, "simulate|simulation|simulating|simulated")
-paper_type_keywords$modelling <- str_detect( paper_type_keywords$title, "modelling|model|models|modeling") | 
-                                str_detect( paper_type_keywords$abstract, "modelling|model|models|modeling")
-paper_type_keywords <- paper_type_keywords %>% 
-  pivot_longer(cols = c("Machine Learning", "Simulation", "modelling"), names_to = "Type", values_to = "Value") %>%
-  filter(Value == TRUE)
-
-# # Plot
-paper_type_keywords %>% ggplot() +
-  geom_bar(aes(x = Type, fill=factor(condition, levels = c("Neither", "Open code", "Open data", "Both")), position = "stack")) +
-  labs(fill = "Type of marker") +
-  scale_x_discrete(labels=c("Machine learning", "Modelling", "Simulation")) +
-  ylab("Number of pre-prints") +
-  xlab("Month") +
-  ggtitle("Sampled pre-prints by type") +
-  theme_minimal() +
-  scale_fill_manual(values = wes_palette("Darjeeling1")) +
-  facet_wrap(~repo)
-
+published_2019_open_status %>%
+  count(repo, published, condition) %>% 
+  pivot_wider(names_from = condition, values_from = n, values_fill = 0) %>%
+  mutate(Published = ifelse(published == 0, "No", "Yes"), `Proportion with neither`= round((`Neither`)/(`Open data` + `Open code` + Both + Neither), 2)) %>%
+  select(Published, Both, Neither, `Open code`, `Open data`, `Proportion with neither`) %>%
+  kable(caption = "Counts and proportions of open data markers by whether the pre-print was published, 2019",
+        booktabs = TRUE) %>%
+  group_rows(index = c("bioRxiv" = 2, "medRxiv" = 2))
 ```
 
-```{r summary-by-type}
-paper_type_keywords %>% 
-  count(repo, Type, condition) %>% 
-  pivot_wider(names_from = condition, values_from = n, values_fill = 0) %>% 
-  mutate(Type = if_else(Type == "modelling", "Modelling", Type),
-         Type = if_else(Type == "Machine Learning", "Machine learning", Type),
-         ) %>% 
-  mutate(`Proportion with either/both`= round((`Open data` + `Open code` + Both)/(`Open data` + `Open code` + Both + Neither), 2)) %>%
-  select(!repo) %>%
-  kable(caption = "Counts and proportions of open data markers by the type of pre-print",
-        booktabs = TRUE) %>%
-  group_rows(index = c("arxiv" = 3, "bioRxiv" = 3, "medRxiv" = 3, "socArXiv" = 3))
-```
-
-# Model
-
-We are interested in understanding firstly whether open data and open code became more likely over time, and secondly whether the likelihood that at pre-print ends up published is related to provision of open data and open code.
-To examine these questions we estimate Equation \@ref(eq:first) by fitting two separate generalized linear models with open data and open code markers as binary variables (representing their presence or absence in a pre-print) that are explained as functions of the date at which a pre-print was posted.
-
-\begin{equation} 
-\mbox{Open data/code} = \beta_0 + \beta_1 \mbox{date} (\#eq:first)
-\end{equation}
-
-We then estimate Equation \@ref(eq:second), again by fitting separate generalized linear models, looking at whether a pre-print is published, based on whether it had open code/data.
-
-\begin{equation} 
-\mbox{Open data/code} = \beta_0 + \beta_1 \mbox{date} (\#eq:second)
-\end{equation}
-
-We estimate our models in the statistical programming language `R` [@citeR], using the function `glm()`.
-
-Our estimates (Table \@ref(tab:datatimemodel)) indicate, in greater clarity, the negligible role time appears to play in the proportion of pre-prints with open data or open code posted to medRxiv.
-Both models output negligibly small, non-significant coefficients on the date term, indicating limited influence of the date a pre-print was posted on its likelihood of containing open data or code markers.
-
-```{r, echo=FALSE, warning=FALSE, message=FALSE, results = 'asis'}
-data_on_date <- glm(is_open_data ~ date, family = binomial, data = med_open_data_results)
-code_on_date <- glm(is_open_code ~ date, family = binomial, data = med_open_data_results)
-
-published_on_data <- glm(published ~ as.factor(is_open_data), family = binomial, data = med_open_data_results)
-published_on_code <- glm(published ~ as.factor(is_open_code), family = binomial, data = med_open_data_results)
-
-stargazer(data_on_date, code_on_date, published_on_data, published_on_code,
-          header = FALSE,
-          title = 'Estimation results',
-          dep.var.labels = c('Open data', 'Open code', 'Published'),
-          covariate.labels=c('Date', 'Has open data', 'Has open code', 'Constant'),
-          report=('vc*s'),
-          no.space = TRUE,
-          digits=2,
-          digits.extra=1,
-          notes.append = TRUE,
-          notes.align = "l",
-          ci = FALSE,
-          ci.level=0.95,
-          label = "tab:datatimemodel"
-          )
-```
-
-We get similar results for publication status as a function of open data or open code presence; however we do see a significant (p < 0.05) coefficient indicating that the presence of open code markers may have a negative influence on a pre-print's likelihood of eventual publication.
-It is unrealistic to assume that this means pre-prints with open code are less likely to be published on the basis of their code alone.
-There may be common cause factors involved, such as a disinclination of journals to publish purely computational work as has been the case with pre-print repositories like bioRxiv [@kwon2020].
-
-# Results
-
-Less than 20 per cent of sampled pre-prints indicated any open data or code markers.
-Of those that did contain markers, 4 per cent contained open code markers only, 8 per cent contained open data markers only, and 7 per cent contained both open data and code markers.
-
-We find that time has little influence over the likelihood of a pre-print to have open data or code markers.
-In the context of the COVID-19 pandemic, this means that the prevalence of open data and code markers has not consistently increased nor decreased over the course of the pandemic, and also appears to be unimpacted by the monthly rate of pre-prints posted to medRxiv (which increased dramatically between January and May 2020 and has fluctuated since).
-On one hand, it is encouraging to note that open data and code does not appear to have suffered in times of high publication rates, namely April through July 2020.
-On the other hand, one might hope that more data has become openly available throughout the course of the pandemic, or that the rate of availability of open data or code has improved as the scientific community has recognized the importance of global collaboration in combating the pandemic, neither of which appear to be the case.
-
-The presence of open data or code markers does not appear to have significant influence over whether or not a pre-print posted to medRxiv has subsequently been published in a peer reviewed journal, however the proportion of published pre-prints with open data or code markers appears to be slightly lower than those that have not been published (15 per cent versus 20 per cent).
-This is not necessarily a significant result given the size of our sample and the potential inaccuracies in the medRxiv API's attempts to identify publication, however it does provide a potential area of further study.
-
-The proportion of pre-prints with open data or code markers is significantly higher among pre-prints with keywords indicating machine learning-based research.
-This is a somewhat anticipated result, as machine learning tends to rely more heavily on computational and code-focused methodology, however the subset of sampled pre-prints with keywords relating to simulation is very small.
-On the other hand, the prevalence of pre-prints with open data or code markers only saw a slight increase in the subset of pre-prints with either modelling or simulation keywords.
-Since the pandemic has seen a rise in scientific and public focus on epidemiological modelling, it is likely that not all papers showing keywords for modelling actually propose their own models which would account for the minimal increase of open data and code markers in this context.
+Examining publication rates for pre-pandemic papers, we observe that 64 per cent of pre-prints posted to bioRxiv and 61 per cent of pre-prints posted to medRxiv during 2019 were eventually peer reviewed and published (Table \@ref(tab:2019-published)).
+These rates are approximately double those of the COVID-19-related pre-prints posted to servers during 2020 and 2021 (33 per cent and 31 per cent from bioRxiv and medRxiv respectively).
+When disaggregated by open data and code status, we find that published and unpublished pre-prints contain open data and code markers in similar proportions (Table \@ref(tab:2019-open-publishing)).
+This mimics the behaviour of published and unpublished COVID-19-related pre-prints.
 
@@
 
-Open data is generally accepted to be beneficial to the scientific process, and to a paper's reproducibility potential, hence it is concerning that over 80 per cent of pre-prints in our sample contained no open data markers.
+Open data is generally accepted to be beneficial to the scientific process, and to a paper's reproducibility potential, hence it is concerning that over 75 per cent of pre-prints in our sample contained no open data markers.
 This concern is slightly mitigated by recognition of challenges in working with biomedical data compared with data in other fields, notably privacy and ethics concerns when working with personal data [@Floca2014].
 The COVID-19 pandemic has seen an uptake in open science practices globally, as evidenced by the creation of open data repositories such as the dashboard maintained by the Center for Systems Science and Engineering at Johns Hopkins University [@citeCSSE] or the large number of publishers who have removed paywalls from published COVID-19 research [@gill2020].
-(MENTION/REFERENCE https://wellcome.org/coronavirus-covid-19/open-data ?) An important next step may compare open data and code availability in COVID-19 pre-prints with those from other topics posted to medRxiv to examine whether the pandemic has increased transparency from the previous norm.
+(MENTION/REFERENCE https://wellcome.org/coronavirus-covid-19/open-data ?)
+- Insert discussion on difference from 2019 data
 
@@
 On the other hand, we do not see an overall long-term increase in either open data or open code markers throughout our year of analysis which we may expect in the context of the aforementioned open science movements the pandemic has fostered.
-Although not pre-print specific, @else2020 found that overall research output has fluctuated between different fields and topics (namely modelling disease spread, public health, diagnostics and testing, mental health, and hospital mortality) throughout different stages of the pandemic which may account for some of the fluctuation and overall lack of linear trend over the course of the year.
+Although not pre-print specific, @else2020 found that overall research output has fluctuated between different fields and topics (namely modelling disease spread, public health, diagnostics and testing, mental health, and hospital mortality) throughout different stages of the pandemic which may account for some of the fluctuation and overall lack of noticeable trend over the course of the year.
 
@@
 Needless to say, it is important that open data and code standards be maintained in published work as well.
-Our findings in this regard were two-fold: that open data or code markers do not appear to directly influence a pre-print's eventual publication, and that a lower proportion of published papers contain either open data or code markers than the general sample.
+Our findings in this regard were two-fold: that open data or code markers do not appear to directly influence a pre-print's eventual publication, and that a lower proportion of published papers contain either open data or code markers than the general sample (TODO: no longer valid; cite new McGuinness/SHephard paper).
 Both of these raise concerns over publication bias, the potential that journals have favored novel yet less transparent or reproducible papers over those with null results but a high standard of open science practices.
@@
 The ongoing COVID-19 pandemic has created a novel, constantly changing scientific culture that should be navigated with the utmost care so as to uphold standards of scientific practice for both the research community and the safety of the general public.
-Our analysis shows that there is much improvement to be made in the areas of open data and code availability within COVID-19 pre-print papers on medRxiv.
+Our analysis shows that there is much improvement to be made in the areas of open data and code availability within COVID-19 pre-print papers on arXiv, bioRxiv, medRxiv, and socArXiv.
 
@@
 
-# Keywords
-
-Insert details on keyword search used to identify COVID-19 papers.
-
 # Markers

### 2021-06-29 outputs/paper/paper.Rmd
Updates to scripts, fixes to 2020/2021 data, paper updates

@@
 But given the importance of these repositories, it is important that scientists impose on themselves various standards for their results.
-Following @weissgerber2021automated we examine papers about COVID-19 published to  arXiv, bioRxiv, medRxiv, and SocArXiv from January 2020, through to February 2021.
+Following @weissgerber2021automated we examine papers about COVID-19 published to  arXiv, bioRxiv, medRxiv, and SocArXiv from January 2020, through to May 1, 2021.
 We search for markers of open science as indicators of reproducibility, specifically open data and open code.
 
-We find that approximately 81 per cent of sampled papers contain neither open data nor open code markers.
+We find that approximately 75 per cent of papers sampled from arXiv, 68 percent of papers sampled from bioRxiv, 80 per cent of papers sampled from medRxiv, and 84 per cent of papers sampled from socArXiv contain neither open data nor open code markers.
 Examining trends over time, we find that the proportion of pre-prints containing open data or code markers has fluctuated but shown no obvious increasing or decreasing trend throughout the pandemic.
@@
 
-The remainder of this paper is structured as follows: in Section \@ref(data-and-methodology) we discuss the process of constructing our dataset through retrieving pre-prints from the medRxiv repository and mining them for open data and open code markers.
+The remainder of this paper is structured as follows: in Section \@ref(data-and-methodology) we discuss the process of constructing our dataset through retrieving pre-prints from the arXiv, bioRxiv, medRxiv, and socArXiv repositories and mining them for open data and open code markers.
 In Sections \@ref(model) and \@ref(results) we explore some key findings in this raw data and explore some logistic regression models that support these findings.
@@
 
-We constructed this dataset by first creating a local copy of the repository using the repository API.
+We constructed this dataset by first creating a local copy of each repository using the repository API.
 We identified papers related to the COVID-19 pandemic through several keyword searches to create our dataset of papers and associated metadata.
@@
 This required downloading each pre-print as a PDF and then converting the PDFs to text files.
-Some papers from SocArxiv were only available in .docx format and were downloaded as such instead.
+Some papers from SocArxiv were only available in .docx format and were downloaded as such and then converted to text format.
 We then conducted the open data and open code detection procedure.
@@
 
-The result of this process is a dataset indicating the presence of open data or open code markers in each pre-print (with a binary variable for each marker, and the relevant open data or open code statements when applicable).
-Our final analysis dataset was formed by joining these two datasets together, typically using the DOI or the unique filename, to form a dataset including all original, qualitative metadata information for each pre-print alongside its open data and open code status and markers.
+The result of this process is a dataset indicating the presence of open data or open code markers in each pre-print (with a logical vector for each marker, followed by the relevant open data or open code statements when applicable).
+Our final dataset was formed by joining this dataframe with the original sample dataframe, typically using the DOI or the unique filename, to form a dataset including all original, qualitative metadata for each pre-print alongside its open data and open code status and markers.
 
@@
 
-The number of pre-prints posted per month increased dramatically between January and May 2020, reaching its maximum in May and subsequently decreasing.
-The number of pre-prints posted since August 2020 has remained reasonably steady at around 750 per month (Figure \@ref(fig:monthly-papers-total)).
+The number of pre-prints posted per month increased dramatically in the first half of 2020 across all repositories, reaching its maximum sometime between April and June (depending on repository) and subsequently decreasing.
+The number of pre-prints posted monthly since August 2020 has remained reasonably steady, with the exception of medRxiv which experienced a spike up to nearly 1000 pre-prints posted in March 2021 (Figure \@ref(fig:monthly-papers-total)).
 For context, COVID-19 was declared a pandemic by the World Health Organization (WHO) on March 11, 2020, at which point the number of cases globally had just surpassed 118,000 (primarily in east Asia) and the virus had been reported in 114 countries [@citeWHOtimeline].
 
-Broadly, we are unable to find markers of either open data or open code for around 81 per cent of the 1,200 sampled pre-prints.
-The remaining 19 per cent of pre-prints was comprised of 4 per cent of the sample containing markers for open code, 8 per cent of the sample with markers for open data, and 7 per cent of the sample with markers for both open data and open code (Table \@ref(tab:summarycounts-medRxiv)).
+Broadly, we are unable to find markers of either open data or open code for around 68 percent of the sampled bioRxiv pre-prints, 80 per cent of the sampled medRxiv pre-prints, 76 per cent of the sampled arXiv pre-prints, and 84 per cent of all COVID-19 related socArXiv pre-prints.
+The distribution of the remaining portion of pre-prints varies by repository (Table \@ref(tab:summarycounts-medRxiv)).
+Notably, 28 per cent of sampled pre-prints from bioRxiv contained open data markers, the highest of proportion of any repository.
+Similarly, 20 per cent of sampled arXiv pre-prints contained markers of open code, the highest of any of the repositories in question.
 
@@
 
-In Table \@ref(tab:open-published-summary) we disaggregate pre-prints by whether there is an indication that it was published.
-We find that the proportion of pre-prints with open data or code markers among those that have been published is approximately five per cent lower compared with pre-prints that have not been published (Table \@ref(tab:open-published-summary)).
+Our metadata also contains an indication of whether or not a pre-print has been published in the form of a DOI linking to the corresponding published paper.
+The proportion of pre-prints that have been published varies by repository (Table \@ref(tab:published-sample-summary)).
+Notably, of all COVID-19-related pre-prints created during 2020 and 2021, approximately one third of those posted to bioRxiv and nearly 30 percent of those posted to medRxiv were eventually published in peer reviewed journals.
+This is high in comparison to the proportions from arXiv and socArXiv, which may be indication of a bias towards pre-print servers showcasing research from the biomedical and life sciences.
+
+```{r published-sample-summary}
+med_published <- 
+  med_results %>% 
+  select(title, date, published) %>% 
+  mutate(repo = "medRxiv", published = as.numeric(!is.na(published)))
+
+bio_published <- 
+  bio_results %>% 
+  select(title, date, published) %>% 
+  mutate(repo = "bioRxiv", published = as.numeric(!is.na(published)))
+
+arxiv_published <- 
+  all_arxiv_results %>% 
+  select(title, submitted, doi) %>%
+  mutate(doi = as.numeric(!is.na(doi)), repo = "arXiv") %>%
+  rename(published = doi, date = submitted)
+
+socarxiv_published <- 
+  socarxiv_results %>% 
+  select(title, date_created, links.doi) %>%
+  mutate(links.doi = as.numeric(!is.na(links.doi)), repo = "socArXiv") %>%
+  rename(published = links.doi, date = date_created)
+
+published <- rbind(med_published, bio_published, arxiv_published, socarxiv_published)
+
+published %>% 
+  group_by(repo) %>% 
+  summarise(`Published pre-prints` = sum(published), `Proportion published` = mean(published) %>% round(2)) %>%
+  kable(caption = "Counts and proportion of published COVID-19 pre-prints in each repository",
+        col.names = c("Repositiory", "Published pre-prints", "Proportion published"))
+```
+
+In Table \@ref(tab:open-published-summary) we disaggregate sampled pre-prints by whether there is an indication that it was published.
+We find that the proportion of pre-prints with open data or code markers among those that have been published is approximately the same as pre-prints that have not been published, differing by one percent only within the bioRxiv and arXiv samples, and three percent in the socArxiv sample (Table \@ref(tab:open-published-summary)).
 
@@
 # Maybe find a way to use the data frames constructed above instead of constructing new ones?
+# TODO: rethink this section, the proportions are nearly identical between those that are published and those that aren't
+
+# ArXiv variables: doi (looks like best); link_doi, journal_ref seem to offer supplenmentary information
+# SocArXiv variables: links.doi
+
 med_published_open_status <- 
@@
 It is important to note that our dataset imperfectly characterizes publication.
-In particular, it does not have the publication details for some papers that were published.
-And even if it were a perfect record, there is a publication lag (estimated at an average of around 60 days) that may skew the results [@kwon2020].
-
+In particular, it likely does not have the publication details for some papers that were published.
+And even if it were a perfect record, there is a publication lag (estimated at an average of around 60 days) that may skew the results for the papers in the latter portion of our sample [@kwon2020].
 ## Type of pre-print
@@
 
+## Pre-pandemic Pre-prints
+
+In order to examine the influence of the COVID-19 pandemic on open science practices in during the pandemic, we analyzed pre-prints posted between January and December 2019 from each of the four repositories using the same process as was done for the COVID-19-related pre-prints.
+Since medRxiv was founded in June 2019, all pre-prints unrelated to COVID-19 posted from the latter half of 2019 were analyzed (a total of 913).
+For bioRxiv, a random sample of 1,200 was taken from all non-COVID-19-related pre-prints posted in the relevant date range.
+
+```{r 2019-results}
+bio_2019 <- bio_2019_results %>%
+  select(date) %>%
+  mutate(type = "bioRxiv")
+
+med_2019 <- med_2019_open_data_results %>%
+  select(date) %>%
+  mutate(type = "medRxiv")
+
+all_2019 <- rbind(bio_2019, med_2019)
+
+# TODO: position = "dodge" not working
+all_2019 %>% 
+  mutate(month = floor_date(date, "month")) %>% 
+  # filter(year(date) >= 2020) %>% 
+  ggplot(aes(x = month, fill = type)) + 
+  geom_histogram(stat="count", position = "dodge") +
+  labs(title = "Pre-prints posted per month, 2019",
+       subtitle = "Total of 31,752 pre-prints on bioRxiv, 913 on medRxiv",
+       x = "Month",
+       y = "Number of pre-prints",
+       fill = "Repository") +
+  theme_minimal() +
+  scale_fill_manual(values = wes_palette("Darjeeling1"))
+```
+
+```{r 2019-open-results}
+just_2019_medRxiv <-
+  med_2019_open_data_results  %>%
+  mutate(date = as.Date(date))  %>%
+  select(date, is_open_data, is_open_code) %>%
+  mutate(type = "medRxiv")
+
+just_2019_bioRxiv <-
+  bio_2019_open_data_results  %>%
+  select(date, is_open_data, is_open_code) %>%
+  mutate(date = as.Date(date)) %>%
+  mutate(type = "bioRxiv")
+
+all_2019 <- rbind(just_2019_medRxiv, just_2019_bioRxiv)
+
+all_2019 %>%
+  group_by(type) %>%
+  count(is_open_data, is_open_code) %>%
+  mutate(prop_total = n / sum(n)) %>%
+  mutate(is_open_data = ifelse(is_open_data == 0, "No", "Yes"),
+         is_open_code = ifelse(is_open_code == 0, "No", "Yes")) %>%
+  ungroup() %>%
+  select(is_open_data, is_open_code, n, prop_total) %>%
+  kable(col.names = c("Open data markers", "Open code markers", "Count", "Proportion of total"),
+        caption = "Counts and proportions of open data and code markers in 2019 medRxiv and bioRxiv samples",
+        booktabs = TRUE,
+        digits = 2) %>%
+  group_rows(index = c("bioRxiv" = 4, "medRxiv" = 4))
+```
+
+Between June and December 2019, the number of pre-prints posted to medRxiv monthly saw an overall increase which may be expected as the repository gained recognition and popularity in the medical research community.
+The number of papers posted monthly to bioRxiv also saw an overall increase throughout 2019.
+It is important to note here that due to its relative immaturity at the beginning of the COVID-19 pandemic, a significant portion of medRxiv's overall usage has been dedicated to COVID-19-related research.
+In total, 19,638 pre-prints have been posted to medRxiv since June 2019, 12,060 (approximately 61 per cent) of which relate to COVID-19.
+
+Of the analyzed pre-prints from 2019, 63 percent of those posted to bioRxiv and 75 per cent of those posted to medRxiv showed no indication of open data or open code.
+Both of these proportions are approximately five per cent lower than the corresponding proportion of COVID-19-related pre-prints, meaning that the analyzed pre-prints from 2019 contained an overall higher prevalence of open data or code markers than pre-prints concerning COVID-19.
+
+```{r 2019-published}
+med_published_2019 <- 
+  med_2019_open_data_results %>% 
+  select(title, date, published) %>% 
+  mutate(repo = "medRxiv", published = as.numeric(published))
+
+bio_published_2019 <- 
+  bio_2019_results %>% 
+  select(title, date, published) %>% 
+  mutate(repo = "bioRxiv", published = as.numeric(!is.na(published)))
+
+published_2019 <- rbind(med_published_2019, bio_published_2019)
+
+published_2019 %>% 
+  group_by(repo) %>% 
+  summarise(`Published pre-prints` = sum(published), `Proportion published` = mean(published) %>% round(2)) %>%
+  kable(caption = "Counts and proportion of published COVID-19 pre-prints in each repository, 2019",
+        col.names = c("Repositiory", "Published pre-prints", "Proportion published"))
+```
+
+```{r, 2019-open-publishing}
+med_2019_published_open_status <- 
+  med_2019_open_data_results %>% 
+  select(title, date, published, is_open_code, is_open_data) %>% 
+  mutate(condition = is_open_data + is_open_code, repo = "medRxiv")
+
+bio_2019_published_open_status <- 
+  bio_2019_open_data_results %>% 
+  select(title, date, published, is_open_code, is_open_data) %>% 
+  mutate(condition = is_open_data + is_open_code, repo = "bioRxiv")
+
+published_2019_open_status <- rbind(med_2019_published_open_status, bio_2019_published_open_status)
+
+published_2019_open_status$condition[published_2019_open_status$condition == 2] <- "Both"
+published_2019_open_status$condition[published_2019_open_status$condition == 0] <- "Neither"
+published_2019_open_status$condition[published_2019_open_status$condition == 1 & published_2019_open_status$is_open_code == 1] <- "Open code"
+published_2019_open_status$condition[published_2019_open_status$condition == 1 & published_2019_open_status$is_open_data == 1] <- "Open data"
+
+published_2019_open_status %>%
+  count(repo, published, condition) %>% 
+  pivot_wider(names_from = condition, values_from = n, values_fill = 0) %>%
+  mutate(Published = ifelse(published == 0, "No", "Yes"), `Proportion with neither`= round((`Neither`)/(`Open data` + `Open code` + Both + Neither), 2)) %>%
+  select(Published, Both, Neither, `Open code`, `Open data`, `Proportion with neither`) %>%
+  kable(caption = "Counts and proportions of open data markers by whether the pre-print was published, 2019",
+        booktabs = TRUE) %>%
+  group_rows(index = c("bioRxiv" = 2, "medRxiv" = 2))
+```
+
+Examining publication rates for pre-pandemic papers, we observe that 64 per cent of pre-prints posted to bioRxiv and 61 per cent of pre-prints posted to medRxiv during 2019 were eventually peer reviewed and published (Table \@ref(tab:2019-published).
+These rates are approximately double those of the COVID-19-related pre-prints posted to servers during 2020 and 2021 (33 per cent and 31 per cent from bioRxiv and medRxiv respectively).
+When disaggregated by open data and code status, we find that published and unpublished pre-prints contain open data and code markers with similar prevelance (Table \@ref(tab:2019-open-publishing)).
+This mimics the behaviour of published and unpublished COVID-19-related pre-prints.
+
 # Model
@@
 
-Less than 20 per cent of sampled pre-prints indicated any open data or code markers.
-Of those that did contain markers, 4 per cent contained open code markers only, 8 per cent contained open data markers only, and 7 per cent contained both open data and code markers.
+## Summary of all papers, then differences by repository + reasons
+- Overall, 76 percent of sampled papers did not have open data or code
+- Of repositories, bioRxiv had least with no open data/code (68%) and socArXiv had the
+Overall, approximately 76 percent of pre-prints analyzed across all four repositories (arXiv, bioRxiv, medRxiv, and socArXiv) contained no markers of open data or code.
+Of the repositories in question, bioRxiv had the lowest proportion of pre-prints with neither open data nor code markers at 68 per cent.
+BioRxiv also had the highest proportion of pre-prints with open data markers at 28 per cent (TODO: why?).
+83 per cent of all socArXiv pre-prints related to COVID-19 contained no open data or code markers, the lowest proportion of any of the repositories.
+This may be expected given the nature of pre-prints posted to socArXiv (social sciences and humanities papers which may less reliant on computational results requiring code).
+
+## Time and posting rate influence on open data/code - pre-pandemic and during pandemic as well
+- Open data or code does not appear to have increased in availability throughout the pandemic
+- Open data or code availability does not appear to have suffered in times of high publication like April through June 2020
+- On medRxiv, open data became less available during the pandemic than prior to the pandemic
+  - Could have something to do with how popular medRxiv was during the pandemic and how new it was during 2019
+- On bioRxiv, there was not significant evidence to suggest that the pandemic has decreased the availability of open data or code, although there was a noticable difference in the rates
 
@@
 
+## Publication - why is there little to no difference between published vs non published pre-prints? Publication bias? Insert chi-test results
+- We find little to no difference between the availability of data and code in published versus unpublished pre-prints
+- Good to know that, as a whole, data and code are not becoming less available as results are published (although we do not endeavor to make direct comparisons between the published and pre-print versions of individual papers)
+
 The presence of open data or code markers does not appear to have significant influence over whether or not a pre-print posted to medRxiv has subsequently been published in a peer reviewed journal, however the proportion of published pre-prints with open data or code markers appears to be slightly lower than those that have not been published (15 per cent versus 20 per cent).
@@
 
+## Type of paper - leave for now? Incorporate some into first paragraph
 The proportion of pre-prints with open data or code markers is significantly higher among pre-prints with keywords indicating machine learning-based research.
@@
 Since the pandemic has seen a rise in scientific and public focus on epidemiological modelling, it is likely that not all papers showing keywords for modelling actually propose their own models which would account for the minimal increase of open data and code markers in this context.
+
+## Pre-pandemic vs during pandemic - chi tests, publication
 

### 2021-06-29 scripts/01-data_gathering-arxiv.R

@@ -28,22 +28,22 @@ arxiv_count('all:"COVID-19" all:"COVID 19" all:"covid-19" all:"covid 19" all:"SA
 # Result on 22 May is: 4,054
 
 # All records up to 1 May, 2021
-arxiv_count('submittedDate:[20071018* TO 20210501*] AND (all:"COVID-19" all:"COVID 19" all:"covid-19" all:"covid 19" all:"SARS-CoV-2" all:"SARSCoV-2" all:"corona virus" all:"Corona Virus" all:"coronavirus" all:"2019-nCoV" all:"coronavirus-2")')
-# Result on 22 May is: 3,947
+arxiv_count('submittedDate:[20200101* TO 20210501*] AND (all:"COVID-19" all:"COVID 19" all:"covid-19" all:"covid 19" all:"SARS-CoV-2" all:"SARSCoV-2" all:"corona virus" all:"Corona Virus" all:"coronavirus" all:"2019-nCoV" all:"coronavirus-2")')
+# Result on 22 May is: 3,932
 
-arxiv_results <- arxiv_search(query = 'submittedDate:[20071018* TO 20210501*] AND (all:"COVID-19" all:"COVID 19" all:"covid-19" all:"covid 19" all:"SARS-CoV-2" all:"SARSCoV-2" all:"corona virus" all:"Corona Virus" all:"coronavirus" all:"2019-nCoV" all:"coronavirus-2)"',
+arxiv_results <- arxiv_search(query = 'submittedDate:[20200101* TO 20210501*] AND (all:"COVID-19" all:"COVID 19" all:"covid-19" all:"covid 19" all:"SARS-CoV-2" all:"SARSCoV-2" all:"corona virus" all:"Corona Virus" all:"coronavirus" all:"2019-nCoV" all:"coronavirus-2)"',
                     limit = 5000,
                     batchsize = 500)
 
-arxiv_count('submittedDate:[20071018* TO 20200331*] AND (all:"COVID-19" all:"COVID 19" all:"covid-19" all:"covid 19" all:"SARS-CoV-2" all:"SARSCoV-2" all:"corona virus" all:"Corona Virus" all:"coronavirus" all:"2019-nCoV" all:"coronavirus-2")')
-# There are 251 to get
[…]

### 2021-06-29 scripts/01-data_gathering-medrxiv.R

@@ -67,8 +67,8 @@ write_csv(med_sample, "outputs/data/med_sample.csv")
   
 #### Download relevant papers ####
 # Set up folders for download and txt conversion
-med_pdf_folder = paste(getwd(), "/outputs/data/pdf-medRxiv", sep = "")
-med_txt_folder = paste(getwd(), "/outputs/data/text-medRxiv", sep = "")
+med_pdf_folder = paste0(getwd(), "/outputs/data/pdf-medRxiv")
+med_txt_folder = paste0(getwd(), "/outputs/data/text-medRxiv")
 
 # Download first 500 papers and latest 500 and save to computer
 # head(med_results, 500) %>% mx_download(directory = med_pdf_folder, create = FALSE)
@@ -79,6 +79,33 @@ med_txt_folder = paste(getwd(), "/outputs/data/text-medRxiv", sep = "")
 med_sample %>% slice(1068:1500) %>% mx_download(directory = med_pdf_folder, create = FALSE)
 
 # Convert PDFs to text and saves in new folder
+pdf_convert(med_pdf_folder, med_txt_folder)
+
+# PROBLEM: some PDFs won't convert to text
+downloaded_pdf <- list.files("outputs/data/pdf-medRxiv")
+downloaded_txt <- list.files("outputs/data/text-medRxiv")
+not_working <- med_sample %>% filter(!paste0(ID, "_10.1101_", str_sub(doi, start=9), ".txt") %in% downloaded_txt)
+# Remove file that isn't working
+pdf_file <- paste0(getwd(), "/outputs/data/pdf-medRxiv/", not_working$ID, "_10.1101_", str_sub(not_working$doi, start=9), ".pdf")
+file.remove(pdf_file)
+med_sample <- med_sample %>% filter(!doi %in% not_working$doi)
+
+# Sample new papers (may need to change seed if this step is repeated)
+set.seed(50)
+medrxiv_sample_new <- med_results[sample(nrow(med_results), nrow(not_working)),]
+# Check that new papers are not currently in the sample
+# If line 99 returns any true values, repeat sample with different seed and check again
+downloaded_pdf <- list.files("outputs/data/pdf-medRxiv")
+paste0(medrxiv_sample_new$ID, "_10.1101_", str_sub(medrxiv_sample_new$doi, start=9), ".pdf") %in% downloaded_pdf
[…]

### 2021-06-29 scripts/01-data_gathering-socarxiv.R

@@ -127,7 +127,7 @@ write_csv(all_socarxiv_metadata, "outputs/all_socarxiv_metadata.csv")
 #### Download PDFs ####
 covid_socarxiv_metadata <- 
   all_socarxiv_metadata %>% 
-  filter(covid_flag == TRUE)
+  filter(covid_flag == TRUE, date_created <= as.Date("2021-05-01")) # Take up to May 1, 2021
 
 write_csv(covid_socarxiv_metadata, "outputs/data/socarxiv_results.csv")
 

### 2021-06-29 scripts/02-data_clean_and_prep-arXiv.R

@@ -19,8 +19,8 @@ library(tidyverse)
 # Returns list of lists, with one list for each document (paper)
 arxiv_text_sentences <- 
   oddpub::pdf_load(here::here("outputs/data/text-arXiv/")) # Requires closing backslash
-all_arxiv_results <- 
-  read_csv("outputs/data/arxiv_results.csv")
+arxiv_sample <- 
+  read_csv("outputs/data/arxiv_sample.csv")
 
 
 #### Identify open data markers ####
@@ -32,9 +32,7 @@ arxiv_open_data_results <-
   arxiv_open_data_results %>% 
   mutate(id = str_remove(article, "\\.txt"))
 
-arxiv_open_data_results <- 
-  arxiv_open_data_results %>% 
-  left_join(all_arxiv_results, by = "id")
+arxiv_open_data_results <- left_join(arxiv_sample, arxiv_open_data_results, by = "id")
 
 # Convert TRUE/FALSE in ODDPub output to 1/0
 arxiv_open_data_results$is_open_code <- as.integer(arxiv_open_data_results$is_open_code)

### 2021-06-29 scripts/02-data_clean_and_prep-biorxiv.R

@@ -82,8 +82,8 @@ bio_sample_2019$join_id <- str_sub(bio_sample_2019$doi, start = 9)
 bio_2019_open_data_results <- merge(bio_sample_2019, bio_2019_open_data_results, by = "join_id")
 
 # Reassign published values to 0 or 1 based on presence of publication
-bio_2019_open_data_results$published[!is.na(bio_2019_open_data_results$published)] <- 1
-bio_2019_open_data_results$published[is.na(bio_2019_open_data_results$published)] <- 0
+bio_2019_open_data_results$published[!bio_2019_open_data_results$published == "NA"] <- 1
+bio_2019_open_data_results$published[bio_2019_open_data_results$published == "NA"] <- 0
 
 # Convert TRUE/FALSE in ODDPub output to 1/0
 bio_2019_open_data_results$is_open_code <- as.integer(bio_2019_open_data_results$is_open_code)

### 2021-06-29 scripts/02-data_clean_and_prep-medrxiv.R

@@ -75,6 +75,8 @@ med_2019_text_sentences <-
 med_2019_open_data_results <- 
   oddpub::open_data_search(med_2019_text_sentences)
 
+med_2019_open_data_results <- med_2019_open_data_results %>% select(article, is_open_data, open_data_category, is_open_code, open_data_statements, open_code_statements)
+
 # Join med_data_2019 to med_2019_open_data_results and save as med_2019_open_data_results
 # TODO: Double check join_id
 med_2019_open_data_results$join_id <- med_2019_open_data_results$article %>% str_remove(".txt") %>% str_replace_all("_", "/") %>% substr(start=2, stop=50)
@@ -82,8 +84,8 @@ med_2019_open_data_results$join_id <- med_2019_open_data_results$article %>% str
 med_2019_open_data_results <- left_join(med_data_2019, med_2019_open_data_results, by = c("doi" = "join_id"))
 
 # Reassign published values to 0 or 1 based on presence of publication
-med_2019_open_data_results$published[!is.na(med_2019_open_data_results$published)] <- 1
-med_2019_open_data_results$published[is.na(med_2019_open_data_results$published)] <- 0
+med_2019_open_data_results$published[!med_2019_open_data_results$published == "NA"] <- 1
+med_2019_open_data_results$published[med_2019_open_data_results$published == "NA"] <- 0
 
 # Convert TRUE/FALSE in ODDPub output to 1/0
 med_2019_open_data_results$is_open_code <- as.integer(med_2019_open_data_results$is_open_code)

### 2021-06-29 scripts/02-data_clean_and_prep-socarxiv.R

@@ -40,8 +40,6 @@ socarxiv_open_data_results$is_open_data <- as.integer(socarxiv_open_data_results
 
 # TODO: Add variable for type of paper - "machine learning", "model"/"modeling", "simulation", "simulate"?
 
-# Add variable 
-
 # Save it 
 class(socarxiv_open_data_results)
 write_csv(socarxiv_open_data_results, 'outputs/data/socarxiv_open_data_results.csv')

### 2021-06-29 scripts/03-tests-biorxiv-medrxiv.R

@@ -1,0 +1,202 @@
+#### Load data
+bio_open_data_results <- read.csv("outputs/data/bio_open_data_results.csv")
+bio_2019_open_data_results <- read.csv("outputs/control-data/bio_2019_open_data_results.csv")
+
+med_open_data_results <- read.csv("outputs/data/med_open_data_results.csv")
+med_2019_open_data_results <- read.csv("outputs/control-data/med_2019_open_data_results.csv")
+
+arxiv_open_data_results <- read.csv("outputs/data/arxiv_open_data_results.csv")
+
+socarxiv_open_data_results <- read.csv("outputs/data/socarxiv_open_data_results.csv")
+
+#### Construct contingency tables
+# TODO: simplify
+
+# BioRxiv data before/during pandemic
+bio_data_status <- bio_open_data_results %>% 
+  count(is_open_data) %>% 
+  mutate(status="During COVID-19", .before=is_open_data) %>% 
+  pivot_wider(names_from = is_open_data, values_from=n)
+bio_data_status <- bio_2019_open_data_results %>% 
+  count(is_open_data) %>% 
+  mutate(status="Pre-COVID-19", .before=is_open_data) %>% 
+  pivot_wider(names_from = is_open_data, values_from=n) %>%
+  rbind(bio_data_status)
+
+bio_ContTable <- as.table(cbind(bio_data_status$`0`, bio_data_status$`1`))
+dimnames(bio_ContTable) <- list(status = c("Pre-COVID-19", "During COVID-19"), data = c("NoOpenData", "OpenData"))
+
+# BioRxiv code before/during pandemic
+bio_code_status <- bio_open_data_results %>% 
+  count(is_open_code) %>% 
+  mutate(status="During COVID-19", .before=is_open_code) %>% 
+  pivot_wider(names_from = is_open_code, values_from=n)
+bio_code_status <- bio_2019_open_data_results %>% 
+  count(is_open_code) %>% 
+  mutate(status="Pre-COVID-19", .before=is_open_code) %>% 
+  pivot_wider(names_from = is_open_code, values_from=n) %>%
+  rbind(bio_code_status)
+
+bio_code_ContTable <- as.table(cbind(bio_code_status$`0`, bio_code_status$`1`))
+dimnames(bio_code_ContTable) <- list(status = c("Pre-COVID-19", "During COVID-19"), code = c("NoOpenCode", "OpenCode"))
+
[…]

### 2021-07-09 outputs/paper/paper-copy.Rmd

@@
 ---
-title: "Reproducibility of COVID-19 pre-prints in 2020"
-subtitle: "Markers of open code or data not found in 81 per cent of pre-prints"
+title: "Reproducibility of COVID-19 pre-prints"
 author: 
-  - Rohan Alexander^[University of Toronto.]
   - Annie Collins^[University of Toronto.]
+  - Rohan Alexander^[University of Toronto, rohan.alexander@utoronto.ca.]
 thanks: "Collins thanks CANSSI Ontario for financial support. Code and data are available at: https://github.com/anniecollins/reproducibility."
 date: "`r format(Sys.time(), '%d %B %Y')`"
-abstract: "We create a dataset of all the pre-prints published on arXiv, bioRxiv, and medRxiv between 28 January 2020 and 31 January 2021.
+abstract: "We create a dataset of pre-prints posted to arXiv, bioRxiv, medRxiv, and SocArXiv between 28 January 2020 and 1 May 2021 that are related to COVID-19.
 We extract the text from these pre-prints and parse them looking for keyword markers signalling the availability of the data and code underpinning the pre-print.
-We are unable to find markers of either open data or open code for 81 per cent of the pre-prints on medRxiv  in our sample, and X per cent of those on arXiv in our sample.
-Our paper demonstrates the need to have authors categorize the degree of openness of their pre-print as part of the pre-print submissions process, and more broadly, the need to better integrate open science training into a wide range of fields."
+For the pre-prints that are in our sample, we are unable to find markers of either open data or open code for 76 per cent of those on arXiv, 68 per cent of those on bioRxiv, 80 per cent of those on medRxiv, and 83 per cent of those on SocArXiv.
+We conclude that there may be value in having authors categorize the degree of openness of their pre-print as part of the pre-print submissions process, and more broadly, the need to better integrate open science training into a wide range of fields."
 output:
@@
 
-Scientists use open repositories of papers to more quickly disseminate their research than is possible in traditional journals or conference proceedings.
-These repositories, such as arXiv, bioRxiv, medRxiv, and SocArXiv, are a critical component of scientific communication and many results build on the work published there.
-Thus it is important that the results that are published are credible.
-Pre-print repositories have drawn unprecedented attention in the context of the 2019 novel coronavirus (COVID-19) pandemic and the changes it has imposed on the scientific community [@else2020].
-These repositories are not peer-reviewed, and, in general, anyone with appropriate academic credentials can submit a pre-print
+Scientists use open repositories of papers to disseminate their research more quickly than is possible in traditional journals or conference proceedings.
+These repositories, such as arXiv, bioRxiv, medRxiv, and SocArXiv, are a critical component of scientific communication and many results build on the pre-prints posted there.
+Pre-print repositories have been especially important during the 2019 novel coronavirus (COVID-19) pandemic and the changes it has imposed on the scientific community [@else2020].
+The centrality of pre-prints to science means that it is important that the results that are posted are credible.
+These repositories are not peer-reviewed, and, in general, anyone with appropriate academic credentials can submit a pre-print.
 
@@
 And the gate-keeping and slow publication times of traditional journals mean pre-print repositories have an important role to play.
-But given the importance of these repositories, it is important that scientists impose on themselves various standards for their results.
-Following @weissgerber2021automated we examine papers about COVID-19 published to  arXiv, bioRxiv, medRxiv, and SocArXiv from January 2020, through to May 1, 2021.
+But it is important that scientists impose standards on themselves, and arguably repositories have a role to play here.
+Following @weissgerber2021automated we examine pre-prints about COVID-19 posted to arXiv, bioRxiv, medRxiv, and SocArXiv from 28 January 2020 through to 1 May 2021.
 We search for markers of open science as indicators of reproducibility, specifically open data and open code.
 
-We find that approximately 76 per cent of papers sampled from arXiv, 68 percent of papers sampled from bioRxiv, 80 per cent of papers sampled from medRxiv, and 83 per cent of papers sampled from socArXiv contain neither open data nor open code markers.
-Examining trends over time, we find that the proportion of pre-prints containing open data or code markers has fluctuated but shown no obvious increasing or decreasing trend throughout the pandemic.
-We also find that the presence of open data or open code markers has little influence on a pre-print's future publication, while the subset of sampled pre-prints that has been published contains an overall lower proportion of papers with these markers.
-Finally, we briefly examine the presence of open data and code markers in specific types of pre-prints, namely modelling, simulation, and machine learning research.
+We find that of the papers sampled, approximately 76 per cent of papers from arXiv, 68 per cent of papers from bioRxiv, 80 per cent of papers from medRxiv, and 83 per cent of papers from SocArXiv contain neither open data nor open code markers.
+A summary of our main results is contained in Figure \@ref(fig:flowchart).
+Examining trends over time, we find that the proportion of pre-prints containing open data or code markers has fluctuated but shown no obvious trend throughout the pandemic.
+We also find that the presence of open data or open code markers seems to have little association with a pre-print's subsequent publication, and the subset of sampled pre-prints that have been published contains an overall lower proportion of papers with these markers.
+<!-- Finally, we briefly examine the presence of open data and code markers in specific types of pre-prints, namely modelling, simulation, and machine learning research. -->
 
-The remainder of this paper is structured as follows: in Section \@ref(methodology) we discuss the process of constructing our dataset through retrieving pre-prints from the arXiv, bioRxiv, medRxiv, and socArXiv repositories and mining them for open data and open code markers.
-In Section \@ref(results), we explore the results and key findings of this process.
+```{r flowchart, fig.cap = "Summary of process and main results", out.width="90%", fig.align = "center"}
+library(DiagrammeR)
+
+DiagrammeR::grViz("digraph {
+
+graph [layout = dot, rankdir = TB]
+
+# define the global styles of the nodes. We can override these in box if we wish
+node [shape = rectangle]
+
+all [label =  'All pre-prints posted between 28 January 2020 and 1 May 2021']
+onlycovid [label =  'Those about COVID-19']
+arxivcovidcount [label =  'arXiv: 3,896 pre-prints']
+biorxivcovidcount [label =  'bioRxiv: 3,714 pre-prints']
+medrxivcovidcount [label =  'medRxiv: 12,060 pre-prints']
+socarxivcovidcount [label =  'SocArXiv: 410 pre-prints']
+randomsample [label =  'Random sampling stratified by repository']
+arxivsamplecount [label =  'arXiv: 1,000 pre-prints']
+biorxivsamplecount [label =  'bioRxiv: 1,000 pre-prints']
+medrxivsamplecount [label =  'medRxiv: 1,500 pre-prints']
+socarxivsamplecount [label =  'SocArXiv: 410 pre-prints']
+opencodeanddata [label =  'Those with markers of open code and open data']
+arxivopencount [label =  'arXiv: 104 pre-prints']
+biorxivopencount [label =  'bioRxiv: 78 pre-prints']
+medrxivopencount [label =  'medRxiv: 101 pre-prints']
+socarxivopencount [label =  'SocArXiv: 17 pre-prints']
+
+# edge definitions with the node IDs
+all -> onlycovid -> {arxivcovidcount biorxivcovidcount medrxivcovidcount socarxivcovidcount} -> randomsample -> {arxivsamplecount biorxivsamplecount medrxivsamplecount socarxivsamplecount} -> opencodeanddata -> {arxivopencount biorxivopencount medrxivopencount socarxivopencount}
+}")
+```
+
+The remainder of this paper is structured as follows: in Section \@ref(methodology) we discuss the process of constructing our dataset through retrieving pre-prints from the arXiv, bioRxiv, medRxiv, and SocArXiv repositories and mining them for open data and open code markers.
+In Section \@ref(results), we present the results and key findings of this process.
 Finally, in Section \@ref(discussion) we discuss the implications of these findings in the broader context of reproducibility and science during the COVID-19 pandemic, as well as next steps to expand on our findings and questions raised in the research process.
@@
 ## Pre-print metadata
-Our primary dataset consists of pre-print metadata extracted from the arXiv, bioRxiv, medRxiv, and socArXiv pre-print repositories via their respective Application Programming Interface (API).
-This metadata varies by repository, but generally includes the following information: title, abstract, author(s), date created, research field, DOI, version number, corresponding author, corresponding author's institutional affiliation, published DOI (if the pre-prints has since been published in a peer-reviewed journal), and download link.
+
+Our primary dataset consists of pre-print metadata extracted from the arXiv, bioRxiv, medRxiv, and SocArXiv pre-print repositories via their respective Application Programming Interfaces (APIs).
+This metadata varies by repository, but generally includes the following information: title, abstract, author(s), date created, research field, DOI, version number, corresponding author, corresponding author's institutional affiliation, published DOI (if the pre-print has since been published in a peer-reviewed journal), and download link.
 The data collection process was conducted separately for COVID-19 and pre-COVID-19 papers.
 
-For COVID-19-related pre-prints, we first created a local copy of each repository containing all metadata for pre-prints registered between January 1, 2020 and May 1, 2021.
-In the case of socArXiv there are additionally fields that are self-reported by the submitting author about the availability of code and data.
-We classified individual pre-prints as "COVID-19-related" on the basis of containing one of more of the following terms in their title or abstract (case insensitive): "COVID-19", "COVID 19", "corona virus", "coronavirus", "coronavirus-2", "SARS-CoV-2", "SARSCoV-2", or "2019-nCoV".
-From each repository's dataset we randomly sampled pre-prints for further analysis, with the exception of socArXiv for which we analyzed all pre-prints that matched the above criteria due to their limited number (n = 410).
+For COVID-19-related pre-prints, we first created a local copy of each repository containing all metadata for pre-prints posted between January 1, 2020, and May 1, 2021.
+In the case of SocArXiv there are fields that are self-reported by the submitting author about the availability of code and data.
+We classified individual pre-prints as "COVID-19-related" based on whether they contained one or more of the following terms in their title or abstract (case insensitive): "COVID-19", "COVID 19", "corona virus", "coronavirus", "coronavirus-2", "SARS-CoV-2", "SARSCoV-2", or "2019-nCoV".
+Future work could make this keyword approach more systematic, for instance following @king2017computer.
+We then randomly sampled pre-prints for further analysis, except for SocArXiv for which we analyzed all pre-prints that matched the above criteria as there were only 410.
 
-For pre-COVID-19 pre-prints, we created a local copy of each repository containing all metadata for pre-prints registered between January 1, 2019 and December 31, 2019.
+For pre-COVID-19 pre-prints, we created a local copy of each repository containing all metadata for pre-prints posted between January 1, 2019, and December 31, 2019.
 Since medRxiv was launched in June 2019, we used all pre-print data from the latter half of 2019.
-We then randomly sampled 1,200 pre-prints from each repository's dataset for analysis, with the exception of medRxiv for which only 913 pre-prints were available in total.
+We then randomly sampled 1,200 pre-prints from each repository's dataset for analysis, with the exception of medRxiv for which only 913 pre-prints were available over this time.
 
@@
 We checked our sampled pre-prints for open data and code markers using the Open Data Detection in Publications (ODDPub) text mining algorithm [@citePDDPub] within the `oddpub` R package [@citeODDPubpackage].
-This required downloading each pre-print as a PDF and then converting the PDFs to text files.
-Some papers from socArXiv were only available in Word document format (.docx) and were downloaded as such and then converted to text format.
+This required downloading each pre-print as a PDF, which we did using `heapsofpapers` [@citealexandermafouz], and then converting the PDFs to text files.
+Some papers from SocArXiv were only available in Word document format (.docx) and were downloaded as such and then converted to text format.
 We then conducted the open data and open code detection procedure which involved searching for keywords and other markers of open data and open code availability.
@@
 This was conducted using the `open_data_search()` function from the `oddpub` package.
+All of our workflow as conducted in the statistical programming language R [@citeR].
 
@@
 
-Although socArXiv's metadata contained author-reported information concerning data and code availability for each pre-print, we elected to use the results of the ODDPub algorithm in our analysis to ensure comparability of results between pre-prints from all repositories.
-Notable discrepancies between the ODDPub algorithm and authors' self-reported data and code availability include...
+Although SocArXiv's metadata contained author-reported information concerning data and code availability for each pre-print, we elected to use the results of the ODDPub algorithm in our analysis to ensure comparability of results between pre-prints from all repositories.
+Notable discrepancies between the ODDPub algorithm and authors' self-reported data and code availability are documented in Appendix \@ref(socarxivissues).
 
@@
   rename(date = "date_created") %>%
-  mutate(type = "socArXiv")
+  mutate(type = "SocArXiv")
 
@@
   filter(year(date) >= 2020) %>%
+  filter(date < "2021-05-01") %>% 
   ggplot(aes(x = month)) + 
@@
   labs(title = "COVID-19-related pre-prints posted per month",
-       subtitle = "Total of 3,896 relevant pre-prints on arXiv, 3,714 on bioRxiv, 12,060 on medRxiv, 410 on socArXiv",
+       subtitle = "Total of 3,896 relevant pre-prints on arXiv, 3,714 on bioRxiv, 12,060 on medRxiv, and \n410 on SocArXiv.",
        x = "Month",
@@
 ## All pre-prints
-The number of pre-prints posted per month increased dramatically in the first half of 2020 across all repositories, reaching its maximum sometime between April and June (depending on repository) and subsequently decreasing.
-The number of pre-prints posted monthly since August 2020 has remained reasonably steady, with the exception of medRxiv which experienced a spike up to nearly 1000 pre-prints posted in March 2021 (Figure \@ref(fig:monthly-papers-total)).
+
+The number of pre-prints posted per month increased in the first half of 2020 across all repositories, reaching a maximum sometime between April and June (depending on repository) and subsequently decreasing.
+The number of pre-prints posted monthly since August 2020 has remained reasonably steady, with the exception of medRxiv which experienced an increase to nearly 1,000 pre-prints posted in March 2021 (Figure \@ref(fig:monthly-papers-total)).
 For context, COVID-19 was declared a pandemic by the World Health Organization (WHO) on March 11, 2020, at which point the number of cases globally had just surpassed 118,000 (primarily in east Asia) and the virus had been reported in 114 countries [@citeWHOtimeline].
@@
 ## Open data and code
-We analyzed a total of 3,910 COVID-19-related pre-prints.
-This sample is further broken down as follows: 1,500 from medRxiv, 1,000 from arXiv, 1,000 from bioRxiv, and 410 from socArXiv.
-Broadly, we are unable to find markers of either open data for open code for 2,987 or approximately 76 per cent of our sample (Table \@ref(tab:summarycounts-overall)).
-Of the remaining pre-prints, 6 per cent contained open code markers only, 10 per cent contained open data markers only, and 8 percent included markers of both open data and open code.
 
-Once differentiated by repository, we observe that open data and code markers were absent from 68 percent of the sampled bioRxiv pre-prints, 80 per cent of the sampled medRxiv pre-prints, 76 per cent of the sampled arXiv pre-prints, and 83 per cent of all COVID-19-related socArXiv pre-prints.
-The distribution of the remaining portion of pre-prints varies by repository (Table \@ref(tab:summarycounts-repositories)).
+From that collection of all pre-prints related to COVID019 we randomly sampled 3,910 pre-prints to analyze, stratified by repository.
+This sample is broken down as follows: 1,500 from medRxiv, 1,000 from arXiv, 1,000 from bioRxiv, and 410 from SocArXiv.
+Broadly, we are unable to find markers of either open data for open code for 2,987 pre-prints or approximately 76 per cent of our sample (Table \@ref(tab:summarycounts-repositories)).
+Of the remaining pre-prints, 6 per cent contained open code markers only, 10 per cent contained open data markers only, and 8 per cent included markers of both open data and open code.
+
+Once differentiated by repository, we observe that open data and code markers were absent from 68 per cent of the sampled bioRxiv pre-prints, 80 per cent of the sampled medRxiv pre-prints, 76 per cent of the sampled arXiv pre-prints, and 83 per cent of all COVID-19-related SocArXiv pre-prints.
+The distribution of the remaining portion of pre-prints also varies by repository (Table \@ref(tab:summarycounts-repositories)).
 Notably, 28 per cent of sampled pre-prints from bioRxiv contained open data markers and 20 per cent of sampled arXiv pre-prints contained markers of open code, the highest proportions of any repository for each type of marker.
+Our results are broadly similar to @@mcguinness2021descriptive, who focus on medRxiv and find that 23 per cent describe open data.
 
@@
 
+all_total <- 
   all %>%
@@
          is_open_code = ifelse(is_open_code == 0, "No", "Yes")) %>%
-  select(is_open_data, is_open_code, n, prop_total) %>%
-  kable(col.names = c("Open data markers", "Open code markers", "Count", "Proportion of total"),
-        caption = "Counts and proportions of open data and code markers in sample",
-        booktabs = TRUE,
-        digits = 2)
+  select(is_open_data, is_open_code, n, prop_total)
 ```
@@
 
+all_by_type <- 
   all %>%
@@
   ungroup() %>%
-  select(is_open_data, is_open_code, n, prop_total) %>%
+  select(is_open_data, is_open_code, n, prop_total)
+
+rbind(all_total, all_by_type) %>% 
   kable(col.names = c("Open data markers", "Open code markers", "Count", "Proportion of total"),
@@
         booktabs = TRUE,
-        digits = 2) %>%
-  group_rows(index = c("arXiv" = 4, "bioRxiv" = 4, "medRxiv" = 4, "socArXiv" = 4))
+        digits = 2,
+        format.args = list(big.mark = ",")) %>%
+  group_rows(index = c("Total" = 4, "arXiv" = 4, "bioRxiv" = 4, "medRxiv" = 4, "SocArXiv" = 4))
 ```
@@
 The distribution of total sampled pre-prints and sampled pre-prints with open data or code markers roughly follows that of COVID-19-related pre-prints posted in general (Figure \@ref(fig:monthly-papers-condition-stack)).
-The proportion of pre-prints with open data or code has fluctuated over time but shows no consistent overall increase or decrease throughout the course of the pandemic, nor in conjunction with increases or decreases in the total number of pre-prints posted to any given repository (Figure \@ref(fig:monthly-proportion-of-open)).
+The proportion of pre-prints with open data or code has fluctuated over time but shows no consistent overall increase or decrease throughout the course of the pandemic, nor in conjunction with increases or decreases in the total number of pre-prints posted to any given repository.
 In our datasets, very few (if any) pre-prints were sampled for the month of January 2020.
@@
 
-```{r monthly-papers-condition-stack, fig.cap = "Number of pre-prints related to COVID-19 sampled from medRxiv, distinguished by presence of open data or code markers", out.width="90%", fig.align = "center"}
+```{r monthly-papers-condition-stack, fig.cap = "Number of sampled pre-prints related to COVID-19, distinguished by presence of open data or code markers", out.width="90%", fig.align = "center"}
 # Number of papers for each open data/code status per month
@@
   select(title, date_created, is_open_code, is_open_data) %>% 
-  mutate(condition = is_open_data + is_open_code, repo = "socArXiv", date = as.character(date_created)) %>%
+  mutate(condition = is_open_data + is_open_code, repo = "SocArXiv", date = as.character(date_created)) %>%
   select(title, date, is_open_code, is_open_data, condition, repo)
@@
   xlab("Month") +
-  labs(title="Sampled pre-prints by month", subtitle="medRxiv, Total = 1,200") +
+  labs(title="Sampled pre-prints by month", subtitle="Sample size from arXiv is 1,000, from bioRxiv is 1,000, from medRxiv is 1,500, and from \nSocArXiv is 410.") +
   theme_minimal() +
@@
   summarise(count = n(), "Open Code" = mean(is_open_code), "Open Data" = mean(is_open_data)) %>% 
-  mutate(daily_rate = count/days_in_month(month), repo = "socArXiv")
+  mutate(daily_rate = count/days_in_month(month), repo = "SocArXiv")
 
@@
 # TODO: Fix date labels, facet_wrap labels
-month_sum_cov %>%
-  ggplot() +
-  geom_line(data = month_sum_cov, aes(month, value, color = repo)) +
-  ggtitle("Proportion of sampled pre-prints with open data or code markers") +
-  labs(colour = "Repository",
-       x = "Month",
-       y = "Proportion of pre-prints") + 
-  theme_minimal() +
-  scale_color_manual(values = wes_palette("Darjeeling1")) +
-  facet_wrap(~name)
-
+# month_sum_cov %>%
+#   ggplot() +
+#   geom_line(data = month_sum_cov, aes(month, value, color = repo)) +
+#   ggtitle("Proportion of sampled pre-prints with open data or code markers") +
+#   labs(colour = "Repository",
+#        x = "Month",
+#        y = "Proportion of pre-prints") + 
+#   theme_minimal() +
+#   scale_color_manual(values = wes_palette("Darjeeling1")) +
+#   facet_wrap(~name)
 ```
@@
 
-Our metadata also contains an indication of whether or not a pre-print has been published in the form of a DOI linking to the corresponding published paper.
+Our metadata also contains an indication of whether a pre-print has been published, in the form of a DOI linking to the corresponding published paper.
 The proportion of pre-prints that have been published varies by repository (Table \@ref(tab:published-sample-summary)).
-Notably, of all COVID-19-related pre-prints created during 2020 and 2021, approximately one third of those posted to bioRxiv and nearly 30 percent of those posted to medRxiv were eventually published in peer reviewed journals.
-This is high in comparison to the proportions from arXiv and socArXiv, which may be a reflection of the unprecedented attention pre-print servers showcasing research from the biomedical and life sciences have received throughout the pandemic.
+Notably, of all COVID-19-related pre-prints in our dataset, approximately one third of those posted to bioRxiv, and nearly 30 per cent of those posted to medRxiv, were published in peer-reviewed journals.
+This is high in comparison to the proportions from arXiv and SocArXiv and may reflect the attention that pre-prints of research from the biomedical and life sciences have received throughout the pandemic.
 
@@
   select(title, date_created, links.doi) %>%
-  mutate(links.doi = as.numeric(!is.na(links.doi)), repo = "socArXiv") %>%
+  mutate(links.doi = as.numeric(!is.na(links.doi)), repo = "SocArXiv") %>%
   rename(published = links.doi, date = date_created)
@@
   group_by(repo) %>% 
-  summarise(`Published pre-prints` = sum(published), `Proportion published` = mean(published) %>% round(2)) %>%
+  summarise(`Published pre-prints` = sum(published), 
+            `Proportion published` = mean(published) %>% round(2)) %>%
   kable(caption = "Counts and proportion of published COVID-19 pre-prints in each repository",
-        col.names = c("Repositiory", "Published pre-prints", "Proportion published"))
+        col.names = c("Repositiory", "Published pre-prints", "Proportion published"),
+        format.args = list(big.mark = ","))
 ```
 
-In Table \@ref(tab:open-published-summary) we disaggregate sampled pre-prints by whether or not there is an indication of publication.
-We find that the proportion of pre-prints with open data or code markers among those that have been published is approximately the same as pre-prints that have not been published, differing by one percent only within the bioRxiv and arXiv samples, and three percent in the socArxiv sample.
+In Table \@ref(tab:open-published-summary) we disaggregate sampled pre-prints by whether there is an indication of publication.
+We find that the proportion of pre-prints with open data or code markers among those that have been published is roughly the same as pre-prints that have not been published, differing by one per cent only within the bioRxiv and arXiv samples, and three per cent in the SocArXiv sample.
 
@@
   select(title, date_created, links.doi, is_open_code, is_open_data) %>%
-  mutate(links.doi = as.numeric(!is.na(links.doi)), condition = is_open_data + is_open_code, repo = "socArXiv") %>%
+  mutate(links.doi = as.numeric(!is.na(links.doi)), condition = is_open_data + is_open_code, repo = "SocArXiv") %>%
   rename(published = links.doi, date = date_created)
@@
   kable(caption = "Counts and proportions of open data markers by whether the pre-print was published",
-        booktabs = TRUE) %>%
-  group_rows(index = c("bioRxiv" = 2, "medRxiv" = 2, "arXiv" = 2, "socArXiv" = 2))
+        booktabs = TRUE,
+        format.args = list(big.mark = ",")) %>%
+  group_rows(index = c("bioRxiv" = 2, "medRxiv" = 2, "arXiv" = 2, "SocArXiv" = 2))
 ```
 
-```{r open-published-stack, fig.cap= "Number of pre-prints in sample with open data or open code markers by publication status", out.width="90%", fig.align = "center"}
+```{r open-published-stack, fig.cap= "Number of pre-prints in sample with open data or open code markers \nby publication status", out.width="90%", fig.align = "center"}
 
@@
 
-It is important to note that our dataset imperfectly characterizes publication.
+It is important to note that our dataset likely imperfectly characterizes publication.
 In particular, it likely does not have the publication details for some papers that were published.
-And even if it were a perfect record, there is a publication lag (estimated at an average of around 60 days for COVID-19-related pre-prints) that may skew the results for the papers in the latter portion of our sample [@kwon2020].
+And even if it were a perfect record, there is a publication lag (estimated at an average of around 60 days for COVID-19-related pre-prints, although that varies by discipline) that may especially skew the results for pre-prints in the latter portion of our sample [@kwon2020].
 
-## Pre-pandemic Pre-prints
+## Pre-pandemic pre-prints
 
 In order to examine the influence of the COVID-19 pandemic on open science practices in during the pandemic, we analyzed pre-prints posted between January and December 2019 from each of the four repositories using the same process as was done for the COVID-19-related pre-prints.
-Since medRxiv was founded in June 2019, all pre-prints unrelated to COVID-19 posted from the latter half of 2019 were analyzed (a total of 913).
+Since medRxiv was founded in June 2019, all pre-prints posted in the latter half of 2019 were analyzed (a total of 913).
 For bioRxiv, a random sample of 1,200 was taken from all non-COVID-19-related pre-prints posted in the relevant date range.
@@
         booktabs = TRUE,
-        digits = 2) %>%
+        digits = 2,
+        format.args = list(big.mark = ",")) %>%
   group_rows(index = c("bioRxiv" = 4, "medRxiv" = 4))
@@
 
-Of the analyzed pre-prints from 2019, 63 percent of those posted to bioRxiv and 75 per cent of those posted to medRxiv showed no indication of open data or open code (Table \@ref(tab:2019-published)).
-Both of these rates are approximately five per cent lower than the corresponding proportions of COVID-19-related pre-prints, suggesting that the analyzed pre-prints from 2019 contained an overall higher prevalence of open data and code markers than pre-prints concerning COVID-19.
+Of the analyzed pre-prints from 2019, 63 per cent of those posted to bioRxiv and 75 per cent of those posted to medRxiv showed no indication of open data or open code (Table \@ref(tab:2019-published)).
+Both rates are approximately five per cent lower than the corresponding proportions of COVID-19-related pre-prints, suggesting that the analyzed pre-prints from 2019 may contain an overall higher prevalence of open data and code markers than pre-prints concerning COVID-19.
 Specifically, we found that open data availability in medRxiv pre-prints was significantly associated with a pre-pandemic registration date (chi-squared = 8.225, p < 0.005), as was open code availability for bioRxiv pre-prints (chi-squared = 15.028, p < 0.005).
-This would suggest that open data and code practices have suffered in the context of COVID-19.
+This would suggest that open data and code practices may have suffered in the context of COVID-19.
 
@@
   kable(caption = "Counts and proportion of published COVID-19 pre-prints in each repository, 2019",
-        col.names = c("Repositiory", "Published pre-prints", "Proportion published"))
+        col.names = c("Repositiory", "Published pre-prints", "Proportion published"),
+        format.args = list(big.mark = ","))
 ```
@@
   kable(caption = "Counts and proportions of open data markers by whether the pre-print was published, 2019",
-        booktabs = TRUE) %>%
+        booktabs = TRUE,
+        format.args = list(big.mark = ",")) %>%
   group_rows(index = c("bioRxiv" = 2, "medRxiv" = 2))
@@
 Examining publication rates for pre-pandemic papers, we observe that 64 per cent of pre-prints posted to bioRxiv and 61 per cent of pre-prints posted to medRxiv during 2019 were eventually peer reviewed and published (Table \@ref(tab:2019-published)).
-These rates are approximately double those of the COVID-19-related pre-prints posted to servers during 2020 and 2021 (33 per cent and 31 per cent from bioRxiv and medRxiv respectively).
+These rates are approximately double those of the COVID-19-related pre-prints posted during 2020 and 2021 (33 per cent and 31 per cent from bioRxiv and medRxiv respectively).
 When disaggregated by open data and code status, we find that published and unpublished pre-prints contain open data and code markers in similar proportions (Table \@ref(tab:2019-open-publishing)).
@@
 
-- Add reference somewhere to that paper about the numbers: https://link.springer.com/article/10.1007/s11192-020-03675-3
-- Add reference somewhere to that paper about keyword search and then analysis. Was it a Gary King one?
-
 ## On the role of transparency and reproducibility
@@
 Transparency and reproducibility are hallmarks of quality scientific research.
-Open data and open code contribute greatly to both in allowing the scientific community to more easily verify the authenticity of purported scientific discovery and its supporting evidence, which is especially important in cases where scientific research may quickly and directly impact clinical practice or policy such as during the COVID-19 pandemic.
-Among a myriad of other impacts on biomedical research, COVID-19 has dramatically increased the popularity of pre-prints from both a production and consumption stand-point.
-The number of COVID-19 pre-prints posted to medRxiv increased dramatically in the early stages of the pandemic while non-COVID-19 pre-print rates remained consistent.
-The same trends were apparent in abstracts accessed by medRxiv users, where COVID-19 pre-print abstracts were viewed over 15 times the rate of non-COVID-19 pre-print abstracts [@citeFraser].
-For these reasons, it is more important now than ever to examine open science standards and reproducibility within pre-print repositories.
+Open data and open code contribute to both by allowing the scientific community to more easily verify the authenticity of purported scientific discovery and its supporting evidence.
+This is especially important in cases where scientific research may quickly and directly impact clinical practice or public policy such as during the COVID-19 pandemic.
+Among many other impacts on biomedical research, COVID-19 has dramatically increased the popularity of pre-prints from both a production and consumption standpoint.
+The number of COVID-19 pre-prints posted to medRxiv increased dramatically in the early stages of the pandemic while non-COVID-19 pre-print numbers were largely as expected.
+The same trends were apparent in abstracts accessed by medRxiv users, where COVID-19 pre-print abstracts were viewed over 15 times more than non-COVID-19 pre-print abstracts [@citeFraser].
+For these reasons, it is important to examine open science standards and reproducibility within pre-print repositories.
 
@@
 The COVID-19 pandemic has seen an uptake in open science practices globally, as evidenced by the creation of open data repositories such as the dashboard maintained by the Center for Systems Science and Engineering at Johns Hopkins University [@citeCSSE] or the large number of publishers who have removed paywalls from published COVID-19 research [@gill2020].
-(MENTION/REFERENCE https://wellcome.org/coronavirus-covid-19/open-data ?)
-- Insert discussion on difference from 2019 data
+While the intention at the start of the pandemic was that there would be 'clear statements regarding the availability of underlying data' [@citeWellcome] some retractions of work have been based on 'unreliable or nonexistent data' [@da2021optimizing].
+SocArXiv asks submitters to make explicit the degree of openness in the data and this is something that could be easily adopted by other pre-print repositories.
 
@@
 However, in pre-prints where code comprises a large portion of the methodology or results, posting it openly to repositories like GitHub contributes greatly to a pre-print's potential reproducibility.
-This gains importance as computational methods become increasingly popular in the rush to form predictions about emerging situations with limited data or laboratory research, which was the case for modelling studies in the early days of the COVID-19 pandemic (CITE).
+This gains importance as computational methods become increasingly popular in the rush to form predictions about emerging situations with limited data or laboratory research, which was the case for modelling studies in the early days of the COVID-19 pandemic.
 We also see growing concern over the quality and consequences of this sort of research, with bioRxiv no longer allowing purely computational work [@kwon2020].
 
-## The role of of pre-print repositories
+The other concern is the adverse selection issue caused by meeting the open science aims of sharing code and data.
+Authors that share their data and code open themselves up to criticism of their work because of this.
+If authors who make their data and code available make similar mistakes to authors who choose to not publish their data and code, it is more likely that the mistake would not be noticed in the case where data and code were not published.
+The current system is biased against those who follow best practice.
+Indeed @mcguinness2021descriptive advocate that '(s)trict editorial policies that mandate data sharing'.
 
+## The role of pre-print repositories
+
+There has been an enormous amount of research on COVID-19 [@da2021publishing].
 Many concerns have arisen from the unprecedented rate at which COVID-19 research has been posted and consumed via pre-print repositories, particularly in the early stages of the pandemic [@raynaud2021].
-Any rushed scientific research has potential to skip (or at least place less precedence on) quality open science practices, thus it may be reasonable to expect a decrease of open data or code markers in the pre-prints posted during times of increased overall posting to medRxiv.
-In our analysis, we found little relationship between time posted and likelihood of having open data or code markers with the proportion of papers containing these markers fluctuating greatly from month to month and no apparent decrease during periods of increased publication.
-This suggests that open science practices are more highly influenced by other factors, perhaps training, publication bias, or the nature of the paper itself.
-On the other hand, we do not see an overall long-term increase in either open data or open code markers throughout our year of analysis which we may expect in the context of the aforementioned open science movements the pandemic has fostered.
+Any rushed scientific research has potential to skip (or at least place less precedence on) open science practices, thus it may be reasonable to expect a decrease in open data or code markers in the pre-prints posted during times of increased overall posting to medRxiv.
+In our analysis, we found little relationship between date posted and likelihood of having open data or code markers with the proportion of pre-prints containing these markers fluctuating greatly from month to month and no apparent decrease during periods of increased publication.
+This suggests that open science practices are more influenced by other factors, perhaps training, publication bias, or the nature of the pre-print itself.
+On the other hand, we do not see an overall long-term increase in either open data or open code markers throughout our period of analysis which we may have expected in the context of the aforementioned open science movements the pandemic has fostered.
 Although not pre-print specific, @else2020 found that overall research output has fluctuated between different fields and topics (namely modelling disease spread, public health, diagnostics and testing, mental health, and hospital mortality) throughout different stages of the pandemic which may account for some of the fluctuation and overall lack of noticeable trend over the course of the year.
@@
 To emphasize the ongoing need for open data and code in modelling a pandemic, we consider two high profile epidemiological models that emerged in early 2020.
-Modelling was conducted by Imperial College London (ICL) [@ferguson2020] and the Institute for Health Metrics and Evaluation (IHME) at the University of Washington [@murray2020], and both papers were initially posted to pre-print repositories.
+Modelling was conducted by Imperial College London (ICL) [@ferguson2020] and the Institute for Health Metrics and Evaluation (IHME) at the University of Washington [@murray2020], and both were initially posted to pre-print repositories.
 The ICL model went on to become the most cited pre-print as of December 2020 [@else2020], and both had significant influence over policy and public health decisions worldwide [@adam2020].
 An independent review of these two models by @jin2020 found that while code and data were openly available for both, only the ICL model was reproducible due to limited transparency on the underlying methodology of the IHME model.
-The open-source nature of these papers was fundamental to reproduction attempts and is a great example of the need for open data and code in reproducing COVID-19 research, particularly in evaluating pre-prints as they begin to influence public decision-making.
-
-In the context of the above factors, it was disheartening in our analysis to find that the proportion of modelling- and simulation-related pre-prints with open data or code increased only marginally from that of the entire sample.
+The open-source nature of these models was fundamental to reproduction attempts and is a great example of the need for open data and code in reproducing COVID-19 research, particularly in evaluating pre-prints as they begin to influence public decision-making.
+<!-- In the context of the above factors, it was disheartening in our analysis to find that the proportion of modelling- and simulation-related pre-prints with open data or code increased only marginally from that of the entire sample.
 One might hope that modelling papers should universally be subject to the same analysis as conducted by @jin2020 as for the examples above, which is made possible by the availability of relevant code and data.
+-->
 Although our analysis was not particularly robust, this shows a need for future investigation and potential overall improvement in open science standards for these types of pre-prints (of course subject to the data and code considerations already discussed).
-This need is again emphasized by the new-found speed at which pre-print articles may gain public, media, and political attention in the context of the pandemic.
+This need is again emphasized by the new-found speed at which pre-prints may gain public, media, and political attention in the context of the pandemic.
 
@@
 Needless to say, it is important that open data and code standards be maintained in published work as well.
-Our findings in this regard were two-fold: that open data or code markers do not appear to directly influence a pre-print's eventual publication, and that a lower proportion of published papers contain either open data or code markers than the general sample (TODO: no longer valid; cite new McGuinness/SHephard paper).
+Our findings in this regard were two-fold: that open data or code markers may not directly influence a pre-print's eventual publication, and that a lower proportion of published papers contain either open data or code markers than the general sample.
 Both of these raise concerns over publication bias, the potential that journals have favored novel yet less transparent or reproducible papers over those with null results but a high standard of open science practices.
@@
 The ongoing COVID-19 pandemic has created a novel, constantly changing scientific culture that should be navigated with the utmost care so as to uphold standards of scientific practice for both the research community and the safety of the general public.
-Our analysis shows that there is much improvement to be made in the areas of open data and code availability within COVID-19 pre-print papers on arXiv, bioRxiv, medRxiv, and socArXiv.
+Our analysis shows that there is much improvement to be made in the areas of open data and code availability within COVID-19 pre-print papers on arXiv, bioRxiv, medRxiv, and SocArXiv.
 
@@
 
-In this paper we consider only pre-prints from medRxiv, but this analysis can and should be extended to other pre-print repositories including bioRxiv and arXiv.
+<!-- In this paper we consider only pre-prints from medRxiv, but this analysis can and should be extended to other pre-print repositories including bioRxiv and arXiv.
 The `medrxivr` package [@citemedrxivr] can be used with the bioRxiv API as well, and our code can be modified to conduct the same scraping and text mining procedure as was used for medRxiv data.
+-->
 
-We also wish to expand our analysis to consider the geographic distribution of research and the potential influence of different practices and policies concerning open science as pre-prints vary by location.
-This is pertinent to our current paper as the epicenter of the virus spread (and thus of scientific output) has shifted throughout the pandemic which has implications for our time-based analysis.
+We wish to expand our analysis to consider the geographic distribution of research and the potential influence of different practices and policies concerning open science as pre-prints vary by location.
+This is important as the epicenter of the virus spread (and thus of scientific output) has shifted throughout the pandemic which has implications for our time-based analysis.
 
@@
 
+# SocArXiv differences {#socarxivissues}
+
+Insert details...
+
 # Classification

### 2021-07-14 outputs/paper/paper-copy.Rmd
Add 2019 arXiv and socArXiv data

@@
 library(kableExtra)
+library(DiagrammeR)
 ```
@@
   read_csv(here::here("outputs/data/arxiv_results.csv")) # All COVID arXiv papers (3,812)
+arxiv_2019_open_data_results <- 
+  read_csv(here::here("outputs/control-data/arxiv_2019_open_data_results.csv"))
+all_arxiv_2019_results <- 
+  read_csv(here::here("outputs/control-data/arxiv_data_2019.csv"))
 
@@
 socarxiv_results <- 
-  read_csv(here::here("outputs/data/socarxiv_results.csv")) # All COVID medRxiv papers (444). Same as socarxiv_sample.
+  read_csv(here::here("outputs/data/socarxiv_results.csv")) # All COVID medRxiv papers (410). Same as socarxiv_sample.  
+socarxiv_2019_open_data_results <- 
+  read_csv(here::here("outputs/control-data/socarxiv_2019_open_data_results.csv"))
+socarxiv_metadata_2019 <- 
+  read_csv(here::here("outputs/control-data/socarxiv_metadata_2019.csv"))
 
@@
 Examining trends over time, we find that the proportion of pre-prints containing open data or code markers has fluctuated but shown no obvious trend throughout the pandemic.
-We also find that the presence of open data or open code markers seems to have little association with a pre-print's subsequent publication, and the subset of sampled pre-prints that have been published contains an overall lower proportion of papers with these markers.
+We also find that the presence of open data or open code markers seems to have little association with a pre-print's subsequent publication, and the subset of sampled pre-prints that have been published contains approximately the same proportion of papers with these markers.
 <!-- Finally, we briefly examine the presence of open data and code markers in specific types of pre-prints, namely modelling, simulation, and machine learning research. -->
@@
 ```{r flowchart, fig.cap = "Summary of process and main results", out.width="90%", fig.align = "center"}
-library(DiagrammeR)
-
 DiagrammeR::grViz("digraph {
@@
 
-From that collection of all pre-prints related to COVID019 we randomly sampled 3,910 pre-prints to analyze, stratified by repository.
+From that collection of all pre-prints related to COVID-19 we randomly sampled 3,910 pre-prints to analyze, stratified by repository.
 This sample is broken down as follows: 1,500 from medRxiv, 1,000 from arXiv, 1,000 from bioRxiv, and 410 from SocArXiv.
@@
 Notably, 28 per cent of sampled pre-prints from bioRxiv contained open data markers and 20 per cent of sampled arXiv pre-prints contained markers of open code, the highest proportions of any repository for each type of marker.
-Our results are broadly similar to @@mcguinness2021descriptive, who focus on medRxiv and find that 23 per cent describe open data.
+Our results are broadly similar to @mcguinness2021descriptive, who focus on medRxiv and find that 23 per cent describe open data.
 
@@
 Notably, of all COVID-19-related pre-prints in our dataset, approximately one third of those posted to bioRxiv, and nearly 30 per cent of those posted to medRxiv, were published in peer-reviewed journals.
-This is high in comparison to the proportions from arXiv and SocArXiv and may reflect the attention that pre-prints of research from the biomedical and life sciences have received throughout the pandemic.
+This is high in comparison to the proportions from arXiv and SocArXiv and may reflect the attention that pre-prints concerning research from the biomedical and life sciences have received throughout the pandemic.
 
@@
 
-all_2019 <- rbind(bio_2019, med_2019)
+socarxiv_2019 <- socarxiv_metadata_2019 %>%
+  select(date_created) %>%
+  mutate(type = "socArXiv") %>%
+  rename(date = date_created)
+
+arxiv_2019 <- all_arxiv_2019_results %>%
+  select(submitted) %>%
+  mutate(type = "arXiv") %>%
+  rename(date = submitted)
+
+all_2019 <- rbind(bio_2019, med_2019, socarxiv_2019, arxiv_2019)
 
@@
   labs(title = "Pre-prints posted per month, 2019",
-       subtitle = "Total of 31,752 pre-prints on bioRxiv, 913 on medRxiv",
+       subtitle = "Total of 150,018 pre-prints on arXiv, 31,752 on bioRxiv, 913 on medRxiv, 1,614 on socArXiv",
        x = "Month",
@@
   med_2019_open_data_results  %>%
-  mutate(date = as.Date(date))  %>%
-  select(date, is_open_data, is_open_code) %>%
-  mutate(type = "medRxiv")
+  mutate(date = as.Date(date), type = "medRxiv")  %>%
+  select(date, is_open_data, is_open_code, type)
 
@@
   select(date, is_open_data, is_open_code) %>%
-  mutate(date = as.Date(date)) %>%
-  mutate(type = "bioRxiv")
+  mutate(date = as.Date(date), type = "bioRxiv")
 
-all_2019 <- rbind(just_2019_medRxiv, just_2019_bioRxiv)
+just_2019_socarxiv <- 
+  socarxiv_2019_open_data_results %>%
+  select(date_created, is_open_data, is_open_code) %>%
+  mutate(date = as.Date(date_created), type = "socArXiv") %>%
+  select(date, is_open_data, is_open_code, type)
+
+just_2019_arxiv <-
+  arxiv_2019_open_data_results %>%
+  select(submitted, is_open_data, is_open_code) %>%
+  mutate(date = as.Date(submitted), type = "arXiv") %>%
+  select(date, is_open_data, is_open_code, type)
+
+all_2019 <- rbind(just_2019_medRxiv, just_2019_bioRxiv, just_2019_socarxiv, just_2019_arxiv)
 
@@
   kable(col.names = c("Open data markers", "Open code markers", "Count", "Proportion of total"),
-        caption = "Counts and proportions of open data and code markers in 2019 medRxiv and bioRxiv samples",
+        caption = "Counts and proportions of open data and code markers in 2019 sample",
         booktabs = TRUE,
@@
         format.args = list(big.mark = ",")) %>%
-  group_rows(index = c("bioRxiv" = 4, "medRxiv" = 4))
+  group_rows(index = c("arXiv" = 4, "bioRxiv" = 4, "medRxiv" = 4, "socArXiv" = 4))
 ```
@@
 It is important to note here that due to its relative immaturity at the beginning of the COVID-19 pandemic, a significant portion of medRxiv's overall usage has been dedicated to COVID-19-related research.
-In total, 19,638 pre-prints have been posted to medRxiv since June 2019, 12,060 (approximately 61 per cent) of which relate to COVID-19.
+In total, 19,280 pre-prints were been posted to medRxiv between June 2019 and May 1, 2021, 12,060 (approximately 63 per cent) of which relate to COVID-19.
 
@@
 
-published_2019 <- rbind(med_published_2019, bio_published_2019)
+socarxiv_published_2019 <- 
+  socarxiv_metadata_2019 %>% 
+  select(title, date_created, links.doi) %>% 
+  mutate(repo = "socArXiv", published = as.numeric(!is.na(links.doi))) %>%
+  rename(date = date_created) %>%
+  select(title, date, published, repo)
+
+arxiv_published_2019 <-
+  all_arxiv_2019_results %>%
+  select(title, submitted, doi) %>%
+  mutate(repo = "arXiv", published = as.numeric(!is.na(doi))) %>%
+  rename(date = submitted) %>%
+  select(title, date, published, repo)
+
+published_2019 <- rbind(med_published_2019, bio_published_2019, socarxiv_published_2019, arxiv_published_2019)
 
@@
 
-published_2019_open_status <- rbind(med_2019_published_open_status, bio_2019_published_open_status)
+socarxiv_2019_published_open_status <- 
+  socarxiv_2019_open_data_results %>%
+  mutate(published = !is.na(links.doi) %>% as.numeric()) %>%
+  select(title, date_created, published, is_open_code, is_open_data) %>%
+  rename(date = date_created) %>%
+  mutate(condition = is_open_data + is_open_code, repo = "socArXiv")
+
+arxiv_2019_published_open_status <- 
+  arxiv_2019_open_data_results %>%
+  mutate(published = !is.na(doi) %>% as.numeric()) %>%
+  select(title, submitted, published, is_open_code, is_open_data) %>%
+  rename(date = submitted) %>%
+  mutate(condition = is_open_data + is_open_code, repo = "arXiv")
+
+published_2019_open_status <- rbind(med_2019_published_open_status, bio_2019_published_open_status, socarxiv_2019_published_open_status, arxiv_2019_published_open_status)
 
@@
         format.args = list(big.mark = ",")) %>%
-  group_rows(index = c("bioRxiv" = 2, "medRxiv" = 2))
+  group_rows(index = c("arXiv" = 2, "bioRxiv" = 2, "medRxiv" = 2, "socArXiv" = 2))
 ```
@@
 This is especially important in cases where scientific research may quickly and directly impact clinical practice or public policy such as during the COVID-19 pandemic.
-Among many other impacts on biomedical research, COVID-19 has dramatically increased the popularity of pre-prints from both a production and consumption standpoint.
+Among many other impacts on the research landscape, COVID-19 has dramatically increased the popularity of pre-prints from both a production and consumption standpoint.
 The number of COVID-19 pre-prints posted to medRxiv increased dramatically in the early stages of the pandemic while non-COVID-19 pre-print numbers were largely as expected.
@@
 @abdill2019 estimate that the false-negative rate may be as high as 37.5 per cent for data pulled from the bioRxiv API, meaning analysis of published papers may represent only a fraction of those that have actually been published.
-It is unclear to what extent this is the case for medRxiv or what bias may exist in the subset of pre-prints for which publication was detected, as it is likely that this process relies on title-based text matching [@abdill2019].
+It is unclear to what extent this is the case for other repositories or what bias may exist in the subset of pre-prints for which publication was detected, as it is likely that this process relies on title-based text matching [@abdill2019].
 It is also likely that some of our more recent sampled pre-prints will be published in future which we could not account for at the time of our data collection.
@@
 
-# Classification
-
-Insert details on keyword search used for machine learning/modelling/simulation
-
 \newpage

### 2021-07-14 scripts/01-data_gathering-arxiv.R

@@ -249,49 +249,585 @@ oddpub::pdf_convert(arxiv_pdf_folder, arxiv_txt_folder)
 arxiv_count('submittedDate:[20190101* TO 20191231*]')
 # Result on 22 May is: 155,455
 
-arxiv_results_2019 <- arxiv_search(query = 'submittedDate:[20190101* TO 20190331*]',
-                              limit = 1000,
+arxiv_results <- arxiv_search(query = 'submittedDate:[20190101* TO 20210501*]',
+                              limit = 5000,
                               batchsize = 500)
 
-nums <- seq(from = 500, to = 42000, by = 500)
 
-# Q1
-for (num in nums) {
-  arxiv_count('submittedDate:[20190101* TO 20190331*]')
-  arxiv_results_2019_new <- arxiv_search(query = 'submittedDate:[20190101* TO 20190331*]',
-                                         limit = 1000,
-                                         batchsize = 500,
-                                         start = num)
-  arxiv_results_2019 <- rbind(arxiv_results_2019, arxiv_results_2019_new)
-}
+# January
+arxiv_count('submittedDate:[20190101* TO 20190131*]') # 11,039
+arxiv_result_to_jan_i <- 
+  arxiv_search(query = 'submittedDate:[20190101* TO 20190131*]',
+               sort_by="submitted",
+               limit = 3500,
+               start = 0)
+arxiv_result_to_jan_ii <- 
+  arxiv_search(query = 'submittedDate:[20190101* TO 20190131*]',
+               sort_by="submitted",
+               limit = 3500,
+               start = 2300)
+arxiv_result_to_jan_iii <- 
+  arxiv_search(query = 'submittedDate:[20190101* TO 20190131*]',
+               sort_by="submitted",
+               limit = 3500,
+               start = 4100)
+arxiv_result_to_jan_iv <- 
+  arxiv_search(query = 'submittedDate:[20190101* TO 20190228*]',
+               sort_by="submitted",
+               limit = 3500,
+               start = 5900)
+arxiv_result_to_jan_v <- 
+  arxiv_search(query = 'submittedDate:[20190101* TO 20190228*]',
+               sort_by="submitted",
+               limit = 3500,
+               start = 7400)
+arxiv_result_to_jan_vi <- 
+  arxiv_search(query = 'submittedDate:[20190101* TO 20190228*]',
+               sort_by="submitted",
+               limit = 3500,
[…]

### 2021-07-14 scripts/02-data_clean_and_prep-arXiv.R

@@ -46,3 +46,35 @@ write_csv(arxiv_open_data_results, 'outputs/data/arxiv_open_data_results.csv')
 arxiv_open_data_results %>% 
   count(is_open_data, is_open_code)
 
+
+#### Pre-pandemic data ####
+
+# Read in the raw data. 
+arxiv_2019_text_sentences <- 
+  oddpub::pdf_load(here::here("outputs/control-data/text-arXiv/")) # Requires closing backslash
+arxiv_2019_sample <- 
+  read_csv("outputs/control-data/arxiv_2019_sample.csv")
+
+
+#### Identify open data markers ####
+arxiv_2019_open_data_results <- 
+  oddpub::open_data_search(arxiv_2019_text_sentences)
+
+# Join the dataset with the metadata with the dataset with the open markers
+arxiv_2019_open_data_results <- 
+  arxiv_2019_open_data_results %>% 
+  mutate(id = str_remove(article, "\\.txt"))
+
+arxiv_2019_open_data_results <- left_join(arxiv_2019_sample, arxiv_2019_open_data_results, by = "id")
+
+# Convert TRUE/FALSE in ODDPub output to 1/0
+arxiv_2019_open_data_results$is_open_code <- as.integer(arxiv_2019_open_data_results$is_open_code)
+arxiv_2019_open_data_results$is_open_data <- as.integer(arxiv_2019_open_data_results$is_open_data)
+
+# Save it 
+write_csv(arxiv_2019_open_data_results, 'outputs/control-data/arxiv_2019_open_data_results.csv')
+
+
+# Counts
+arxiv_2019_open_data_results %>% 
+  count(is_open_data, is_open_code)

### 2021-07-14 scripts/01-data_gathering-arxiv.R
Update socArXiv and medRxiv COVID-19 data

@@ -25,13 +25,13 @@ citation('aRxiv')
 #### Get metadata ####
 # Get count of number of papers using the same terms as before
 arxiv_count('all:"COVID-19" all:"COVID 19" all:"covid-19" all:"covid 19" all:"SARS-CoV-2" all:"SARSCoV-2" all:"corona virus" all:"Corona Virus" all:"coronavirus" all:"2019-nCoV" all:"coronavirus-2"')
-# Result on 22 May is: 4,054
+# Result on 22 May is: 4,352
 
 # All records up to 1 May, 2021
-arxiv_count('submittedDate:[20200101* TO 20210501*] AND (all:"COVID-19" all:"COVID 19" all:"covid-19" all:"covid 19" all:"SARS-CoV-2" all:"SARSCoV-2" all:"corona virus" all:"Corona Virus" all:"coronavirus" all:"2019-nCoV" all:"coronavirus-2")')
-# Result on 22 May is: 3,932
+arxiv_count('submittedDate:[20200101* TO 20210630*] AND (all:"COVID-19" all:"COVID 19" all:"covid-19" all:"covid 19" all:"SARS-CoV-2" all:"SARSCoV-2" all:"corona virus" all:"Corona Virus" all:"coronavirus" all:"2019-nCoV" all:"coronavirus-2")')
+# Result on 22 May is: 4281
 
-arxiv_results <- arxiv_search(query = 'submittedDate:[20200101* TO 20210501*] AND (all:"COVID-19" all:"COVID 19" all:"covid-19" all:"covid 19" all:"SARS-CoV-2" all:"SARSCoV-2" all:"corona virus" all:"Corona Virus" all:"coronavirus" all:"2019-nCoV" all:"coronavirus-2)"',
+arxiv_results <- arxiv_search(query = 'submittedDate:[20200101* TO 20210630*] AND (all:"COVID-19" all:"COVID 19" all:"covid-19" all:"covid 19" all:"SARS-CoV-2" all:"SARSCoV-2" all:"corona virus" all:"Corona Virus" all:"coronavirus" all:"2019-nCoV" all:"coronavirus-2)"',
                     limit = 5000,
                     batchsize = 500)
 
@@ -72,14 +72,14 @@ arxiv_result_april_to_aug_iiii <-
                start = 1700)
 
 # Spetember 2020 to May 2021 (present)
[…]

### 2021-07-14 scripts/01-data_gathering-medrxiv.R

@@ -32,7 +32,7 @@ med_data_2019 <- med_data %>% filter(date <= "2019-12-31")
 
 # Search database for COVID-19-related articles by keyword across title, abstract, and category. Sort results from oldest to newest.
 # Output exclude duplicate title, abstract, and DOI
-med_data <- med_data %>% filter(date >= "2019-12-01", date <= "2021-05-01")
+med_data <- med_data %>% filter(date >= "2019-12-01", date <= "2021-06-30")
 med_results <- mx_search(data = med_data, query = c("COVID-19",
                                                     "COVID 19",
                                                     "covid-19",
@@ -47,7 +47,7 @@ med_results <- mx_search(data = med_data, query = c("COVID-19",
                                                     "Corona Virus",
                                                     "coronavirus", 
                                                     "2019-nCoV",
-                                                    "coronavirus-2"), auto_caps = TRUE) # n = 12,060
+                                                    "coronavirus-2"), auto_caps = TRUE) # n = 13,194
 med_results <- med_results[order(med_results$date),]
 
 # Save results - this is sampling frame (info for all medRxiv COVID-19 papers)
@@ -70,13 +70,20 @@ write_csv(med_sample, "outputs/data/med_sample.csv")
 med_pdf_folder = paste0(getwd(), "/outputs/data/pdf-medRxiv")
 med_txt_folder = paste0(getwd(), "/outputs/data/text-medRxiv")
 
-# Download first 500 papers and latest 500 and save to computer
-# head(med_results, 500) %>% mx_download(directory = med_pdf_folder, create = FALSE)
-# tail(med_results, 500) %>% mx_download(directory = med_pdf_folder, create = FALSE)
+downloaded_pdf <- list.files("outputs/data/pdf-medRxiv")
+downloaded_txt <- list.files("outputs/data/text-medRxiv")
+# Remove files not in sample
+pdf_file <- downloaded_pdf[!str_sub(downloaded_pdf, start = -23, end = -5) %in% str_sub(med_sample$doi, start=9)]
+txt_file <- downloaded_txt[!str_sub(downloaded_txt, start = 15) %in% paste0(str_sub(med_sample$doi, start=9), ".txt")]
[…]

### 2021-07-14 scripts/01-data_gathering-socarxiv.R

@@ -50,8 +50,8 @@ get_meta_data_socarxiv <-
 # Set up the dataset that we're going to walk though
 # Check how many pages of results exist at https://api.osf.io/v2/preprints/?filter%5Bprovider%5D=socarxiv&page= and adjust numeric range accordingly
 get_these <- 
-  tibble(number = c(1:811),
-         location  = paste0("inputs/socarxiv/", number, ".csv"))
+  tibble(number = c(1:39),   # Only the new stuff as July 13
+         location  = paste0("inputs/socarxiv/", number, "-July.csv"))
 
 safely_get_meta_data_socarxiv <- purrr::safely(get_meta_data_socarxiv)
 
@@ -127,7 +127,7 @@ write_csv(all_socarxiv_metadata, "outputs/all_socarxiv_metadata.csv")
 #### Download PDFs ####
 covid_socarxiv_metadata <- 
   all_socarxiv_metadata %>% 
-  filter(covid_flag == TRUE, date_created <= as.Date("2021-05-01")) # Take up to May 1, 2021
+  filter(covid_flag == TRUE, date_created <= as.Date("2021-06-30")) # Take up to May 1, 2021
 
 write_csv(covid_socarxiv_metadata, "outputs/data/socarxiv_results.csv")
 
@@ -158,7 +158,7 @@ get_covid_socarxiv_results <-
 safely_download_pdfs <- purrr::safely(download_pdfs)
 
 # Check what's already been downloaded
-already_got <- list.files(path = "/outputs/data/pdf-socarxiv", full.names = TRUE)
+already_got <- list.files(path = "outputs/data/pdf-socarxiv", full.names = TRUE)
 # Remove those rows
 get_covid_socarxiv_results <- 
   get_covid_socarxiv_results %>% 
@@ -205,19 +205,7 @@ downloaded_pdf <- list.files("outputs/data/pdf-socarxiv")
 downloaded_txt <- list.files("outputs/data/text-socarxiv")
 
 # for each pdf, cycle through all txt files, and if there is no key from sample that corresponds to the pdf, remove it
-docx_files <- data.frame()
-for (pdf in downloaded_pdf) {
-  x <- FALSE
-  for (txt in downloaded_txt) {
-    if(grepl(substr(txt, 1, 5), pdf)) {   # if there is a txt that matches the pdf, x is true
-      x <- TRUE     # doi in downloads
-    }
-  } 
-  if (!x) {  # if there is no txt that matches the pdf, remove it
[…]

### 2021-07-14 scripts/02-data_clean_and_prep-socarxiv.R

@@ -18,16 +18,20 @@
 library(oddpub)
 library(tidyverse)
 
+downloaded_txt <- list.files(path = paste0(getwd(), "/outputs/data/text-socarxiv"), full.names = TRUE) %>% as.data.frame()
+not_analyzed <- downloaded_txt %>% filter(!str_sub(downloaded_txt$., -9, -5) %in% socarxiv_open_data_results$id)
+walk2(not_analyzed, rep("/Users/AnniesMac/reproducibility-new/outputs/data/text-socarxiv2/", nrow(not_analyzed)), file.copy)
+
 # Load text files into list of string vectors for use in text mining algorithm.
 # Returns list of lists, with one list for each document (paper)
-socarxiv_text_sentences <- 
+socarxiv_open_data_results <- 
   oddpub::pdf_load(here::here("outputs/data/text-socarxiv/")) # Requires closing backslash
 
 #### Identify open data markers ####
 socarxiv_open_data_results <- 
-  oddpub::open_data_search(socarxiv_text_sentences)
+  oddpub::open_data_search(socarxiv_open_data_results)
 
-
+covid_socarxiv_metadata <- covid_socarxiv_metadata %>% filter(id %in% socarxiv_open_data_results$id)
 # DONE up to here, rest TODO
 
 # Join covid_socarxiv_metadata to socarxiv_open_data_results and save as socarxiv_open_data_results
@@ -39,11 +43,9 @@ socarxiv_open_data_results$is_open_code <- as.integer(socarxiv_open_data_results
 socarxiv_open_data_results$is_open_data <- as.integer(socarxiv_open_data_results$is_open_data)
 
 # TODO: Add variable for type of paper - "machine learning", "model"/"modeling", "simulation", "simulate"?
-
 # Save it 
 class(socarxiv_open_data_results)
 write_csv(socarxiv_open_data_results, 'outputs/data/socarxiv_open_data_results.csv')
-
 
 #### Summary statistics ####
 # Read in data

### 2021-07-16 scripts/01-data_gathering-arxiv.R
Update arXiv and bioRxiv data

@@ -25,18 +25,18 @@ citation('aRxiv')
 #### Get metadata ####
 # Get count of number of papers using the same terms as before
 arxiv_count('all:"COVID-19" all:"COVID 19" all:"covid-19" all:"covid 19" all:"SARS-CoV-2" all:"SARSCoV-2" all:"corona virus" all:"Corona Virus" all:"coronavirus" all:"2019-nCoV" all:"coronavirus-2"')
-# Result on 22 May is: 4,352
+# Result on 15 July is: 4,352
 
-# All records up to 1 May, 2021
+# All records up to 30 June, 2021
 arxiv_count('submittedDate:[20200101* TO 20210630*] AND (all:"COVID-19" all:"COVID 19" all:"covid-19" all:"covid 19" all:"SARS-CoV-2" all:"SARSCoV-2" all:"corona virus" all:"Corona Virus" all:"coronavirus" all:"2019-nCoV" all:"coronavirus-2")')
-# Result on 22 May is: 4281
+# Result on 15 July is: 4280
 
 arxiv_results <- arxiv_search(query = 'submittedDate:[20200101* TO 20210630*] AND (all:"COVID-19" all:"COVID 19" all:"covid-19" all:"covid 19" all:"SARS-CoV-2" all:"SARSCoV-2" all:"corona virus" all:"Corona Virus" all:"coronavirus" all:"2019-nCoV" all:"coronavirus-2)"',
                     limit = 5000,
                     batchsize = 500)
 
 arxiv_count('submittedDate:[20200101* TO 20200331*] AND (all:"COVID-19" all:"COVID 19" all:"covid-19" all:"covid 19" all:"SARS-CoV-2" all:"SARSCoV-2" all:"corona virus" all:"Corona Virus" all:"coronavirus" all:"2019-nCoV" all:"coronavirus-2")')
-# There are 235 to get
+# There are 232 to get
 arxiv_result_to_march <- 
   arxiv_search(query = 'submittedDate:[20200101* TO 20200331*] AND (all:"COVID-19" all:"COVID 19" all:"covid-19" all:"covid 19" all:"SARS-CoV-2" all:"SARSCoV-2" all:"corona virus" all:"Corona Virus" all:"coronavirus" all:"2019-nCoV" all:"coronavirus-2")',
                sort_by="submitted",
@@ -64,7 +64,7 @@ arxiv_result_april_to_aug_iii <-
[…]

### 2021-07-16 scripts/01-data_gathering-biorxiv.R

@@ -24,8 +24,8 @@ library(oddpub)
 
 #### Get metadata ####
 # Download copy of current database
-dates_2020 <- seq.Date(from = as.Date("2019-12-01"), to = as.Date("2020-12-31"), by = 2)
-dates_2021 <- seq.Date(from = as.Date("2021-01-01"), to = as.Date("2021-05-01"), by = "d")
+dates_2020 <- seq.Date(from = as.Date("2020-01-01"), to = as.Date("2020-12-31"), by = 2)
+dates_2021 <- seq.Date(from = as.Date("2021-05-01"), to = as.Date("2021-06-30"), by = "d")
 bio_data <- mx_api_content(from_date = as.character(dates_2020[1]), to_date = as.character(dates_2020[2]), server = "biorxiv")
 i <- 2
 j <- 1
@@ -62,10 +62,15 @@ while (j < (length(dates_2021) - 1)) {
     j <- j + 1
   }
 }
+# TO HERE
+bio_data_original <- read_csv("outputs/data/bio_results.csv")
+bio_data <- rbind(bio_data_original, bio_data)
+bio_data <- bio_data %>% distinct(doi, .keep_all = TRUE)
+bio_data <- bio_data %>% filter(date < "2021-07-01" & year(date) > "2019")
 
 # Depending on j at end of loop may need to add in last few days of 2021 range manually (if dates_2020[j] is 2021-04-30, run following)
 # n = 101,654 (total) as of 23 May, 2021
-bio_data_next <- mx_api_content(from_date = as.character(dates_2021[j]), to_date = as.character(dates_2021[j+1]), server = "biorxiv")
+bio_data_next <- mx_api_content(from_date = as.character(dates_2021[j]), to_date = "2021-07-01", server = "biorxiv")
 bio_data <- rbind(bio_data, bio_data_next)
 
 # Raw stats as of 31 Jan, 2021
@@ -77,7 +82,7 @@ bio_results <- bio_data %>% filter(grepl("COVID-19|COVID 19|SARS-CoV-2|SARSCoV-2
                                      grepl("COVID-19|COVID 19|SARS-CoV-2|SARSCoV-2|novel corona virus|novel coronavirus|2019-nCoV|coronavirus-2", abstract, ignore.case = TRUE))
 
 # Sometimes a paper has multiple versions
-# Filter to only uniques and keep latest version of the paper (n = 3,714)
+# Filter to only uniques and keep latest version of the paper (n = 4,146)
[…]

### 2021-07-16 scripts/02-data_clean_and_prep-biorxiv.R

@@ -20,8 +20,6 @@ library(tidyverse)
 # Returns list of lists, with one list for each document (paper)
 bio_text_sentences <- 
   oddpub::pdf_load(here::here("outputs/data/text-bioRxiv/")) # Requires closing backslash
-
-
 # TODO: Maybe want to change this to something else more mainstream.
 # Example starts here
 # install.packages("readtext")

### 2021-07-20 outputs/paper/paper-copy.Rmd
Update figures/results to match new data

@@
 date: "`r format(Sys.time(), '%d %B %Y')`"
-abstract: "We create a dataset of pre-prints posted to arXiv, bioRxiv, medRxiv, and SocArXiv between 28 January 2020 and 1 May 2021 that are related to COVID-19.
+abstract: "We create a dataset of pre-prints posted to arXiv, bioRxiv, medRxiv, and SocArXiv between 28 January 2020 and 30 June 2021 that are related to COVID-19.
 We extract the text from these pre-prints and parse them looking for keyword markers signalling the availability of the data and code underpinning the pre-print.
@@
   read_csv(here::here("outputs/data/socarxiv_open_data_results.csv"))
-socarxiv_results <- 
-  read_csv(here::here("outputs/data/socarxiv_results.csv")) # All COVID medRxiv papers (410). Same as socarxiv_sample.  
 socarxiv_2019_open_data_results <- 
@@
 But it is important that scientists impose standards on themselves, and arguably repositories have a role to play here.
-Following @weissgerber2021automated we examine pre-prints about COVID-19 posted to arXiv, bioRxiv, medRxiv, and SocArXiv from 28 January 2020 through to 1 May 2021.
+Following @weissgerber2021automated we examine pre-prints about COVID-19 posted to arXiv, bioRxiv, medRxiv, and SocArXiv from 28 January 2020 through to 30 June 2021.
 We search for markers of open science as indicators of reproducibility, specifically open data and open code.
@@
 
-all [label =  'All pre-prints posted between 28 January 2020 and 1 May 2021']
+all [label =  'All pre-prints posted between 28 January 2020 and 30 June 2021']
 onlycovid [label =  'Those about COVID-19']
-arxivcovidcount [label =  'arXiv: 3,896 pre-prints']
-biorxivcovidcount [label =  'bioRxiv: 3,714 pre-prints']
-medrxivcovidcount [label =  'medRxiv: 12,060 pre-prints']
-socarxivcovidcount [label =  'SocArXiv: 410 pre-prints']
+arxivcovidcount [label =  'arXiv: 4,250 pre-prints']
+biorxivcovidcount [label =  'bioRxiv: 4,146 pre-prints']
+medrxivcovidcount [label =  'medRxiv: 13,194 pre-prints']
+socarxivcovidcount [label =  'SocArXiv: 478 pre-prints']
 randomsample [label =  'Random sampling stratified by repository']
@@
 medrxivsamplecount [label =  'medRxiv: 1,500 pre-prints']
-socarxivsamplecount [label =  'SocArXiv: 410 pre-prints']
+socarxivsamplecount [label =  'SocArXiv: 478 pre-prints']
 opencodeanddata [label =  'Those with markers of open code and open data']
-arxivopencount [label =  'arXiv: 104 pre-prints']
-biorxivopencount [label =  'bioRxiv: 78 pre-prints']
-medrxivopencount [label =  'medRxiv: 101 pre-prints']
-socarxivopencount [label =  'SocArXiv: 17 pre-prints']
+arxivopencount [label =  'arXiv: 248 pre-prints']
+biorxivopencount [label =  'bioRxiv: 326 pre-prints']
+medrxivopencount [label =  'medRxiv: 320 pre-prints']
+socarxivopencount [label =  'SocArXiv: 73 pre-prints']
 
@@
 
-For COVID-19-related pre-prints, we first created a local copy of each repository containing all metadata for pre-prints posted between January 1, 2020, and May 1, 2021.
+For COVID-19-related pre-prints, we first created a local copy of each repository containing all metadata for pre-prints posted between 1 January, 2020, and 30 June, 2021.
 In the case of SocArXiv there are fields that are self-reported by the submitting author about the availability of code and data.
@@
 
-For pre-COVID-19 pre-prints, we created a local copy of each repository containing all metadata for pre-prints posted between January 1, 2019, and December 31, 2019.
+For pre-COVID-19 pre-prints, we created a local copy of each repository containing all metadata for pre-prints posted between 1 January, 2019, and December 31, 2019.
 Since medRxiv was launched in June 2019, we used all pre-print data from the latter half of 2019.
@@
 just_socarxiv <- 
-  socarxiv_results  %>% 
+  socarxiv_open_data_results  %>% 
   select(date_created) %>%
   rename(date = "date_created") %>%
-  mutate(type = "SocArXiv")
+  mutate(date = as.Date(date), type = "SocArXiv")
 
@@
   filter(year(date) >= 2020) %>%
-  filter(date < "2021-05-01") %>% 
+  filter(date < "2021-06-30") %>% 
   ggplot(aes(x = month)) + 
@@
   labs(title = "COVID-19-related pre-prints posted per month",
-       subtitle = "Total of 3,896 relevant pre-prints on arXiv, 3,714 on bioRxiv, 12,060 on medRxiv, and \n410 on SocArXiv.",
+       subtitle = "Total of 4,250 relevant pre-prints on arXiv, 4,146 on bioRxiv, 13,194 on medRxiv, and \n478 on SocArXiv.",
        x = "Month",
@@
        fill = "Repository") +
+  scale_x_date(breaks=as.Date(c("2020-01-01","2020-07-01", "2021-01-01", "2021-07-01")), 
+                   labels=c("Jan 2020", "Jul 2020", "Jan 2021", "Jul 2021")) +
   theme_minimal() +
@@
 
-From that collection of all pre-prints related to COVID-19 we randomly sampled 3,910 pre-prints to analyze, stratified by repository.
-This sample is broken down as follows: 1,500 from medRxiv, 1,000 from arXiv, 1,000 from bioRxiv, and 410 from SocArXiv.
-Broadly, we are unable to find markers of either open data for open code for 2,987 pre-prints or approximately 76 per cent of our sample (Table \@ref(tab:summarycounts-repositories)).
-Of the remaining pre-prints, 6 per cent contained open code markers only, 10 per cent contained open data markers only, and 8 per cent included markers of both open data and open code.
+From the collection of all pre-prints related to COVID-19 we randomly sampled 3,910 pre-prints to analyze, stratified by repository.
+This sample is broken down as follows: 1,500 from medRxiv, 1,000 from arXiv, 1,000 from bioRxiv, and 410 from socArXiv.
+Broadly, we are unable to find markers of either open data for open code for 3,011 pre-prints or approximately 76 per cent of our sample (Table \@ref(tab:summarycounts-repositories)).
+Of the remaining pre-prints, 7 per cent contained open code markers only, 10 per cent contained open data markers only, and 8 per cent included markers of both open data and open code.
 
-Once differentiated by repository, we observe that open data and code markers were absent from 68 per cent of the sampled bioRxiv pre-prints, 80 per cent of the sampled medRxiv pre-prints, 76 per cent of the sampled arXiv pre-prints, and 83 per cent of all COVID-19-related SocArXiv pre-prints.
+Once differentiated by repository, we observe that open data and code markers were absent from 67 per cent of the sampled bioRxiv pre-prints, 79 per cent of the sampled medRxiv pre-prints, 75 per cent of the sampled arXiv pre-prints, and 85 per cent of all COVID-19-related SocArXiv pre-prints.
 The distribution of the remaining portion of pre-prints also varies by repository (Table \@ref(tab:summarycounts-repositories)).
-Notably, 28 per cent of sampled pre-prints from bioRxiv contained open data markers and 20 per cent of sampled arXiv pre-prints contained markers of open code, the highest proportions of any repository for each type of marker.
+Notably, 28 per cent of sampled pre-prints from bioRxiv contained open data markers and 22 per cent of sampled arXiv pre-prints contained markers of open code, the highest proportions of any repository for each type of marker.
 Our results are broadly similar to @mcguinness2021descriptive, who focus on medRxiv and find that 23 per cent describe open data.
@@
   socarxiv_open_data_results %>% 
-  group_by(month = floor_date(date_created, "month")) %>% 
+  group_by(month = floor_date(as.Date(date_created), "month")) %>% 
   summarise(count = n(), "Open Code" = mean(is_open_code), "Open Data" = mean(is_open_data)) %>% 
@@
 The proportion of pre-prints that have been published varies by repository (Table \@ref(tab:published-sample-summary)).
-Notably, of all COVID-19-related pre-prints in our dataset, approximately one third of those posted to bioRxiv, and nearly 30 per cent of those posted to medRxiv, were published in peer-reviewed journals.
-This is high in comparison to the proportions from arXiv and SocArXiv and may reflect the attention that pre-prints concerning research from the biomedical and life sciences have received throughout the pandemic.
+Notably, of all COVID-19-related pre-prints in our dataset, approximately 30 per cent of those posted to bioRxiv, and nearly one third of those posted to medRxiv, were published in peer-reviewed journals.
+This is high in comparison to the proportions from arXiv and SocArXiv, and although this might suggest that COVID-19-related pre-prints have received greater attention overall than pre-prints from other fields, our results in Section \@ref(pre-pandemic pre-prints) suggest that this pattern pre-dates the pandemic.
 
@@
 socarxiv_published <- 
-  socarxiv_results %>% 
+  socarxiv_open_data_results %>% 
   select(title, date_created, links.doi) %>%
@@
 In Table \@ref(tab:open-published-summary) we disaggregate sampled pre-prints by whether there is an indication of publication.
-We find that the proportion of pre-prints with open data or code markers among those that have been published is roughly the same as pre-prints that have not been published, differing by one per cent only within the bioRxiv and arXiv samples, and three per cent in the SocArXiv sample.
+We find that the proportion of pre-prints with open data or code markers among those that have been published is roughly the same as pre-prints that have not been published, differing by one per cent only within the bioRxiv and medRxiv samples, and three per cent in the arXiv sample.
 
@@
 
-published_open_status %>% 
-  mutate(published = ifelse(published == 0, "Unpublished", "Published")) %>%
-  ggplot() + 
-  geom_bar(aes(x = published, fill=factor(condition, levels = c("Neither", "Open code", "Open data", "Both")), position = "stack")) +
-  labs(fill = "Type of marker",
-       y = "Number of pre-prints",
-       x = "Publication status") +
-  ggtitle("Pre-prints by publication status") +
-  theme_minimal() +
-  facet_wrap(~repo) + 
-  scale_fill_manual(values = wes_palette("Darjeeling1"))
+# published_open_status %>% 
+#   mutate(published = ifelse(published == 0, "Unpublished", "Published")) %>%
+#   ggplot() + 
+#   geom_bar(aes(x = published, fill=factor(condition, levels = c("Neither", "Open code", "Open data", "Both")), position = "stack")) +
+#   labs(fill = "Type of marker",
+#        y = "Number of pre-prints",
+#        x = "Publication status") +
+#   ggtitle("Pre-prints by publication status") +
+#   theme_minimal() +
+#   facet_wrap(~repo) + 
+#   scale_fill_manual(values = wes_palette("Darjeeling1"))
 
@@
 Since medRxiv was founded in June 2019, all pre-prints posted in the latter half of 2019 were analyzed (a total of 913).
-For bioRxiv, a random sample of 1,200 was taken from all non-COVID-19-related pre-prints posted in the relevant date range.
+For all other repositories, a random sample of 1,200 was taken from all non-COVID-19-related pre-prints posted in the relevant date range.
 
@@
 It is important to note here that due to its relative immaturity at the beginning of the COVID-19 pandemic, a significant portion of medRxiv's overall usage has been dedicated to COVID-19-related research.
-In total, 19,280 pre-prints were been posted to medRxiv between June 2019 and May 1, 2021, 12,060 (approximately 63 per cent) of which relate to COVID-19.
+In total, 21,647 pre-prints were been posted to medRxiv between June 2019 and 30 June, 2021, 13,194 (approximately 61 per cent) of which relate to COVID-19.
 
-Of the analyzed pre-prints from 2019, 63 per cent of those posted to bioRxiv and 75 per cent of those posted to medRxiv showed no indication of open data or open code (Table \@ref(tab:2019-published)).
-Both rates are approximately five per cent lower than the corresponding proportions of COVID-19-related pre-prints, suggesting that the analyzed pre-prints from 2019 may contain an overall higher prevalence of open data and code markers than pre-prints concerning COVID-19.
-Specifically, we found that open data availability in medRxiv pre-prints was significantly associated with a pre-pandemic registration date (chi-squared = 8.225, p < 0.005), as was open code availability for bioRxiv pre-prints (chi-squared = 15.028, p < 0.005).
+Of the analyzed pre-prints from 2019, 93 per cent of those posted to arXiv, 63 per cent of those posted to bioRxiv, 75 per cent of those posted to medRxiv, 92 per cent of those posted to SocArXiv showed no indication of open data or open code (Table \@ref(tab:2019-published)).
+Both the bioRxiv and medRxiv rates are approximately four per cent lower than the corresponding proportions of COVID-19-related pre-prints, suggesting that the analyzed pre-prints from 2019 may contain an overall higher prevalence of open data and code markers than pre-prints concerning COVID-19.
+Specifically, we found that open data availability in medRxiv pre-prints was significantly associated with a pre-pandemic registration date ($\chi$^2^ = 4.8508, p < 0.005), as was open code availability for bioRxiv pre-prints ($\chi$^2^ = 14.491, p < 0.005).
 This would suggest that open data and code practices may have suffered in the context of COVID-19.
+
+On the other hand, the analyzed arXiv and socArXiv pre-prints from 2019 contain a lower proportion of open data and code markers overall than their COVID-19-related counterparts, with a decrease of seven per cent in sampled SocArXiv pre-prints and 18 per cent in sampled arXiv papers.
+For these repositories, the presence of both open data and open code markers was significantly associated with registration *during* the pandemic, suggesting that pre-prints related to COVID-19 in arXiv and socArXiv more consistently adhered to open science practices than their pre-pandemic counterparts ($\chi$^2^ = 93.124, arXiv open data;  $\chi$^2^ = 106.88, arXiv open code; $\chi$^2^ = 12.303, socArXiv open data; $\chi$^2^ = 8.1598, socArXiv open code; p < 0.005).
 
@@
 
-Examining publication rates for pre-pandemic papers, we observe that 64 per cent of pre-prints posted to bioRxiv and 61 per cent of pre-prints posted to medRxiv during 2019 were eventually peer reviewed and published (Table \@ref(tab:2019-published)).
-These rates are approximately double those of the COVID-19-related pre-prints posted during 2020 and 2021 (33 per cent and 31 per cent from bioRxiv and medRxiv respectively).
+Examining publication rates for pre-pandemic papers, we observe that 41 per cent of pre-prints posted to arXiv, 64 per cent of pre-prints posted to bioRxiv, 61 per cent of pre-prints posted to medRxiv, and 37 per cent of pre-prints posted to SocArXiv during 2019 were eventually peer reviewed and published (Table \@ref(tab:2019-published)).
+These rates are at least double those of the COVID-19-related pre-prints posted in each repository during 2020 and 2021 (33 per cent and 31 per cent from bioRxiv and medRxiv respectively).
 When disaggregated by open data and code status, we find that published and unpublished pre-prints contain open data and code markers in similar proportions (Table \@ref(tab:2019-open-publishing)).

### 2021-07-20 scripts/01-data_gathering-socarxiv.R

@@ -170,22 +170,6 @@ purrr::walk2(get_covid_socarxiv_results$link_pdf,
              get_covid_socarxiv_results$save_name,
              safely_download_pdfs)
 
-#### Have a quick look ####
-all_arxiv_results <- 
-  read_csv("outputs/data/arxiv_results.csv")
-
-all_arxiv_results <- 
-  all_arxiv_results %>% 
-  mutate(submitted = lubridate::as_date(submitted))
-
-# Summarise and graph by date
-all_arxiv_results %>% 
-  filter(lubridate::year(submitted) >= 2020) %>% 
-  count(submitted) %>% 
-  ggplot() + 
-  geom_col(aes(x=submitted, y=n))
-
-
 
 
 #### Convert to text ####

### 2021-07-20 scripts/02-data_clean_and_prep-socarxiv.R

@@ -32,7 +32,7 @@ socarxiv_open_data_results <-
   oddpub::open_data_search(socarxiv_open_data_results)
 
 covid_socarxiv_metadata <- covid_socarxiv_metadata %>% filter(id %in% socarxiv_open_data_results$id)
-# DONE up to here, rest TODO
+covid_socarxiv_metadata <- covid_socarxiv_metadata %>% distinct(id, .keep_all = TRUE)
 
 # Join covid_socarxiv_metadata to socarxiv_open_data_results and save as socarxiv_open_data_results
 socarxiv_open_data_results <- socarxiv_open_data_results %>% mutate(id = str_sub(socarxiv_open_data_results$article, 1, 5)) %>% select(!article)

### 2021-07-20 scripts/03-tests-biorxiv-medrxiv.R

@@ -69,6 +69,64 @@ med_code_ContTable <- as.table(cbind(med_code_status$`0`, med_code_status$`1`))
 dimnames(med_code_ContTable) <- list(status = c("Pre-COVID-19", "During COVID-19"), code = c("NoOpenCode", "OpenCode"))
 
 
+# ArXiv before/during pandemic
+arxiv_code_status <- arxiv_open_data_results %>% 
+  count(is_open_code) %>% 
+  mutate(status="During COVID-19", .before=is_open_code) %>% 
+  pivot_wider(names_from = is_open_code, values_from=n)
+arxiv_code_status <- arxiv_2019_open_data_results %>% 
+  count(is_open_code) %>% 
+  mutate(status="Pre-COVID-19", .before=is_open_code) %>% 
+  pivot_wider(names_from = is_open_code, values_from=n) %>%
+  rbind(arxiv_code_status)
+
+arxiv_code_ContTable <- as.table(cbind(arxiv_code_status$`0`, arxiv_code_status$`1`))
+dimnames(arxiv_code_ContTable) <- list(status = c("Pre-COVID-19", "During COVID-19"), data = c("NoOpenData", "OpenData"))
+
+# ArXiv before/during pandemic
+arxiv_data_status <- arxiv_open_data_results %>% 
+  count(is_open_data) %>% 
+  mutate(status="During COVID-19", .before=is_open_data) %>% 
+  pivot_wider(names_from = is_open_data, values_from=n)
+arxiv_data_status <- arxiv_2019_open_data_results %>% 
+  count(is_open_data) %>% 
+  mutate(status="Pre-COVID-19", .before=is_open_data) %>% 
+  pivot_wider(names_from = is_open_data, values_from=n) %>%
+  rbind(arxiv_data_status)
+
+arxiv_ContTable <- as.table(cbind(arxiv_data_status$`0`, arxiv_data_status$`1`))
+dimnames(arxiv_ContTable) <- list(status = c("Pre-COVID-19", "During COVID-19"), data = c("NoOpenData", "OpenData"))
+
+# SocArXiv before/during pandemic
+socarxiv_data_status <- socarxiv_open_data_results %>% 
+  count(is_open_data) %>% 
+  mutate(status="During COVID-19", .before=is_open_data) %>% 
+  pivot_wider(names_from = is_open_data, values_from=n)
+socarxiv_data_status <- socarxiv_2019_open_data_results %>% 
[…]

### 2021-07-20 outputs/paper/paper-copy.Rmd
Minor tweaks to words

@@
 We classified individual pre-prints as "COVID-19-related" based on whether they contained one or more of the following terms in their title or abstract (case insensitive): "COVID-19", "COVID 19", "corona virus", "coronavirus", "coronavirus-2", "SARS-CoV-2", "SARSCoV-2", or "2019-nCoV".
-Future work could make this keyword approach more systematic, for instance following @king2017computer.
 We then randomly sampled pre-prints for further analysis, except for SocArXiv for which we analyzed all pre-prints that matched the above criteria as there were only 410.
@@
 Since medRxiv was launched in June 2019, we used all pre-print data from the latter half of 2019.
-We then randomly sampled 1,200 pre-prints from each repository's dataset for analysis, with the exception of medRxiv for which only 913 pre-prints were available over this time.
+We then randomly sampled 1,200 pre-prints from each repository's dataset for analysis, except for medRxiv for which only 913 pre-prints were available over this time.
 
@@
 We then conducted the open data and open code detection procedure which involved searching for keywords and other markers of open data and open code availability.
-A full listing of these markers is included in Appendix \@ref(markers).
 This was conducted using the `open_data_search()` function from the `oddpub` package.
-All of our workflow as conducted in the statistical programming language R [@citeR].
+What constitutes open code or open data is complicated and discipline specific.
+The details of the `oddpub` approach are available in @riedel2020oddpub.
+The general criteria are that specific mention should be made of where the data and code are located, and that data should be as close to raw as possible.
+Our work was conducted using the statistical programming language R [@citeR].
 
@@
 Although SocArXiv's metadata contained author-reported information concerning data and code availability for each pre-print, we elected to use the results of the ODDPub algorithm in our analysis to ensure comparability of results between pre-prints from all repositories.
-Notable discrepancies between the ODDPub algorithm and authors' self-reported data and code availability are documented in Appendix \@ref(socarxivissues).
+<!-- Notable discrepancies between the ODDPub algorithm and authors' self-reported data and code availability are documented in Appendix \@ref(socarxivissues). -->
 
@@
 From the collection of all pre-prints related to COVID-19 we randomly sampled 3,910 pre-prints to analyze, stratified by repository.
-This sample is broken down as follows: 1,500 from medRxiv, 1,000 from arXiv, 1,000 from bioRxiv, and 410 from socArXiv.
+This sample is broken down as follows: 1,500 from medRxiv, 1,000 from arXiv, 1,000 from bioRxiv, and 410 from SocArXiv.
 Broadly, we are unable to find markers of either open data for open code for 3,011 pre-prints or approximately 76 per cent of our sample (Table \@ref(tab:summarycounts-repositories)).
@@
 It is important to note that our dataset likely imperfectly characterizes publication.
-In particular, it likely does not have the publication details for some papers that were published.
+It likely does not have the publication details for some papers that were published.
 And even if it were a perfect record, there is a publication lag (estimated at an average of around 60 days for COVID-19-related pre-prints, although that varies by discipline) that may especially skew the results for pre-prints in the latter portion of our sample [@kwon2020].
@@
 
-In order to examine the influence of the COVID-19 pandemic on open science practices in during the pandemic, we analyzed pre-prints posted between January and December 2019 from each of the four repositories using the same process as was done for the COVID-19-related pre-prints.
+To examine the influence of the COVID-19 pandemic on open science practices in during the pandemic, we analyzed pre-prints posted between January and December 2019 from each of the four repositories using the same process as was done for the COVID-19-related pre-prints.
 Since medRxiv was founded in June 2019, all pre-prints posted in the latter half of 2019 were analyzed (a total of 913).
@@
   labs(title = "Pre-prints posted per month, 2019",
-       subtitle = "Total of 150,018 pre-prints on arXiv, 31,752 on bioRxiv, 913 on medRxiv, 1,614 on socArXiv",
+       subtitle = "Total of 150,018 pre-prints on arXiv, 31,752 on bioRxiv, 913 on medRxiv, and \n1,614 on socArXiv",
        x = "Month",
@@
 It is important to note here that due to its relative immaturity at the beginning of the COVID-19 pandemic, a significant portion of medRxiv's overall usage has been dedicated to COVID-19-related research.
-In total, 21,647 pre-prints were been posted to medRxiv between June 2019 and 30 June, 2021, 13,194 (approximately 61 per cent) of which relate to COVID-19.
+In total, 21,647 pre-prints were posted to medRxiv between June 2019 and 30 June, 2021, 13,194 (approximately 61 per cent) of which relate to COVID-19.
 
@@
 
-On the other hand, the analyzed arXiv and socArXiv pre-prints from 2019 contain a lower proportion of open data and code markers overall than their COVID-19-related counterparts, with a decrease of seven per cent in sampled SocArXiv pre-prints and 18 per cent in sampled arXiv papers.
-For these repositories, the presence of both open data and open code markers was significantly associated with registration *during* the pandemic, suggesting that pre-prints related to COVID-19 in arXiv and socArXiv more consistently adhered to open science practices than their pre-pandemic counterparts ($\chi$^2^ = 93.124, arXiv open data;  $\chi$^2^ = 106.88, arXiv open code; $\chi$^2^ = 12.303, socArXiv open data; $\chi$^2^ = 8.1598, socArXiv open code; p < 0.005).
+On the other hand, the analyzed arXiv and SocArXiv pre-prints from 2019 contain a lower proportion of open data and code markers overall than their COVID-19-related counterparts, with a decrease of seven per cent in sampled SocArXiv pre-prints and 18 per cent in sampled arXiv papers.
+For these repositories, the presence of both open data and open code markers was significantly associated with registration *during* the pandemic, suggesting that pre-prints related to COVID-19 in arXiv and SocArXiv more consistently adhered to open science practices than their pre-pandemic counterparts ($\chi$^2^ = 93.124, arXiv open data;  $\chi$^2^ = 106.88, arXiv open code; $\chi$^2^ = 12.303, SocArXiv open data; $\chi$^2^ = 8.1598, SocArXiv open code; p < 0.005).
 
@@
 The current system is biased against those who follow best practice.
-Indeed @mcguinness2021descriptive advocate that '(s)trict editorial policies that mandate data sharing'.
+Indeed @mcguinness2021descriptive advocate '(s)trict editorial policies that mandate data sharing'.
 
@@
 
-There has been an enormous amount of research on COVID-19 [@da2021publishing].
-Many concerns have arisen from the unprecedented rate at which COVID-19 research has been posted and consumed via pre-print repositories, particularly in the early stages of the pandemic [@raynaud2021].
+There has been a large amount of research on COVID-19 [@da2021publishing].
+Many concerns have arisen from the rate at which COVID-19 research has been posted and consumed via pre-print repositories, particularly in the early stages of the pandemic [@raynaud2021].
 Any rushed scientific research has potential to skip (or at least place less precedence on) open science practices, thus it may be reasonable to expect a decrease in open data or code markers in the pre-prints posted during times of increased overall posting to medRxiv.
@@
 -->
-Although our analysis was not particularly robust, this shows a need for future investigation and potential overall improvement in open science standards for these types of pre-prints (of course subject to the data and code considerations already discussed).
+Our analysis suggests a need for future investigation and potential overall improvement in open science standards for these types of pre-prints (of course subject to the data and code considerations already discussed).
 This need is again emphasized by the new-found speed at which pre-prints may gain public, media, and political attention in the context of the pandemic.
@@
 Beyond pre-prints, COVID-19 has had great influence over publication and peer review processes as well, with expedited review timelines for COVID-19 papers at the expense of longer waits for other scientific research [@else2020].
-Needless to say, it is important that open data and code standards be maintained in published work as well.
+It is important that open data and code standards be maintained in published work as well.
 Our findings in this regard were two-fold: that open data or code markers may not directly influence a pre-print's eventual publication, and that a lower proportion of published papers contain either open data or code markers than the general sample.
-Both of these raise concerns over publication bias, the potential that journals have favored novel yet less transparent or reproducible papers over those with null results but a high standard of open science practices.
-Concerns have already been raised through systemic reviews of COVID-19 publications [@raynaud2021], and oversights in data accessibility have led to high profile retractions of publications in the past, for example two papers from The Lancet and the New England Journal of Medicine that were withdrawn due to concerns over the private nature of their underlying dataset [@ledford2020].
+Both raise concerns over publication bias, the potential that journals have favored novel yet less transparent or reproducible papers over those with null results but a high standard of open science practices.
+Concerns have already been raised through systemic reviews of COVID-19 publications [@raynaud2021], and oversights in data accessibility have led to high profile retractions of publications in the past, for example papers from *The Lancet* and the *New England Journal of Medicine* were withdrawn due to concerns over the private nature of their underlying dataset [@ledford2020].
 
 In all fields of science, increasing access to data and code used for pre-printed or published research is a step in the direction of more transparent, reproducible, and reliable research.
-The ongoing COVID-19 pandemic has created a novel, constantly changing scientific culture that should be navigated with the utmost care so as to uphold standards of scientific practice for both the research community and the safety of the general public.
-Our analysis shows that there is much improvement to be made in the areas of open data and code availability within COVID-19 pre-print papers on arXiv, bioRxiv, medRxiv, and SocArXiv.
+The ongoing COVID-19 pandemic has created a novel, constantly changing scientific culture that should be navigated with care to uphold standards of scientific practice for both the research community and the safety of the general public.
+Our analysis shows that there is room for improvement in the areas of open data and code availability within COVID-19 pre-print papers on arXiv, bioRxiv, medRxiv, and SocArXiv.
 
-Demand for timely research / results in high frequency as epidemic is rapidly evolving.
-Preprints are more efficient at doing this because there is no time spent on peer review.
-However, they also allow lesser-known researchers to better disperse their research, because of the possibility that fast-tracked peer review may be biased towards established researchers.
+There is demand for timely research and high frequency results because the pandemic rapidly evolved.
+Preprints are efficient in this role because there is no time spent on peer review.
+They also allow lesser-known researchers to better disperse their research, because of the possibility that fast-tracked peer review may be biased towards established researchers.
 While there is a clear need for pre-prints, the point remains that they do not go through the peer review process.
 This question of quality and validity is particularly pertinent in the COVID-19 context because poorly validated results and false information may spread quickly, and have real effects.
-We are not saying that peer review implies that a paper is of a high-quality, we are instead saying that the provision of code and data alongside the preprint goes some way to allowing others to trust the findings of pre-prints even though they have not been peer-reviewed.
-One way this could be encouraged would be for pre-print repositories to have authors characterize the extent to which they have adopted open science practices as part of their submission.
-Although those papers that do not adopt these practices should not be rejected from pre-print repositories, greater clarity around this would be useful and might move the state-of-the-art forward.
+We are not saying that peer review implies that a paper is of a high-quality, we are instead saying that the provision of code and data alongside the pre-print goes some way to allowing others to trust the findings of pre-prints even though they have not been peer-reviewed.
+One way this could be encouraged would be for pre-print repositories to have authors characterize the extent to which they have adopted open science practices as part of their submission, in the same way that is done in SocArXiv.
+Although those pre-prints that do not adopt these practices should not be rejected from pre-print repositories, greater clarity around this would be useful and might move the state-of-the-art forward.
 
@@
 We wish to expand our analysis to consider the geographic distribution of research and the potential influence of different practices and policies concerning open science as pre-prints vary by location.
-This is important as the epicenter of the virus spread (and thus of scientific output) has shifted throughout the pandemic which has implications for our time-based analysis.
+This is important as the epicenter of the pandemic changed throughout the pandemic which has implications for our time-based analysis.
 
@@
 We also recognize that this analysis relies heavily on text-based analysis which was not verified directly in most cases and may lead to higher levels of uncertainty.
-In future, we wish to take smaller sub-samples to validate factors like publication status or paper topic beyond simple keyword searches or API output.
+The `oddpub` package was built to analyze biomedical publications and it may be that some of the differences that we find between repositories are due to this.
+In future, we wish to take smaller sub-samples to validate factors like publication status, paper topic, and open code and data status, beyond the approaches that we used here.
 
@@
 
-# (APPENDIX) Appendix {-}
+<!-- # (APPENDIX) Appendix {-}  -->
 
-# Markers
+<!-- # Markers -->
 
-Insert details on what markers the `oddpub::open_data_search()` uses. Include info here directly from package documentation (i.e. keywords/phrases used for text parsing)?
+<!-- Insert details on what markers the `oddpub::open_data_search()` uses. Include info here directly from package documentation (i.e. keywords/phrases used for text parsing)? -->
 
-# SocArXiv differences {#socarxivissues}
+<!-- # SocArXiv differences {#socarxivissues} -->
 
-Insert details...
+<!-- Insert details... -->
 
-\newpage
+<!-- \newpage -->
 

### 2021-07-21 outputs/paper/paper-copy.Rmd
Paper updates

@@
 We extract the text from these pre-prints and parse them looking for keyword markers signalling the availability of the data and code underpinning the pre-print.
-For the pre-prints that are in our sample, we are unable to find markers of either open data or open code for 76 per cent of those on arXiv, 68 per cent of those on bioRxiv, 80 per cent of those on medRxiv, and 83 per cent of those on SocArXiv.
+For the pre-prints that are in our sample, we are unable to find markers of either open data or open code for 75 per cent of those on arXiv, 67 per cent of those on bioRxiv, 79 per cent of those on medRxiv, and 85 per cent of those on SocArXiv.
 We conclude that there may be value in having authors categorize the degree of openness of their pre-print as part of the pre-print submissions process, and more broadly, the need to better integrate open science training into a wide range of fields."
@@
 We classified individual pre-prints as "COVID-19-related" based on whether they contained one or more of the following terms in their title or abstract (case insensitive): "COVID-19", "COVID 19", "corona virus", "coronavirus", "coronavirus-2", "SARS-CoV-2", "SARSCoV-2", or "2019-nCoV".
-We then randomly sampled pre-prints for further analysis, except for SocArXiv for which we analyzed all pre-prints that matched the above criteria as there were only 410.
+We then randomly sampled pre-prints for further analysis, except for SocArXiv for which we analyzed all pre-prints that matched the above criteria as there were only 478.
 
@@
 Since medRxiv was launched in June 2019, we used all pre-print data from the latter half of 2019.
-We then randomly sampled 1,200 pre-prints from each repository's dataset for analysis, except for medRxiv for which only 913 pre-prints were available over this time.
+We then randomly sampled 1,200 pre-prints from each repository's dataset for analysis, with the exception of medRxiv for which only 913 pre-prints were available over this time.
 
@@
 From the collection of all pre-prints related to COVID-19 we randomly sampled 3,910 pre-prints to analyze, stratified by repository.
-This sample is broken down as follows: 1,500 from medRxiv, 1,000 from arXiv, 1,000 from bioRxiv, and 410 from SocArXiv.
-Broadly, we are unable to find markers of either open data for open code for 3,011 pre-prints or approximately 76 per cent of our sample (Table \@ref(tab:summarycounts-repositories)).
+This sample is broken down as follows: 1,500 from medRxiv, 1,000 from arXiv, 1,000 from bioRxiv, and 478 from SocArXiv.
+Broadly, we are unable to find markers of either open data or open code for 3,011 pre-prints or approximately 76 per cent of our sample (Table \@ref(tab:summarycounts-repositories)).
 Of the remaining pre-prints, 7 per cent contained open code markers only, 10 per cent contained open data markers only, and 8 per cent included markers of both open data and open code.
 
-Once differentiated by repository, we observe that open data and code markers were absent from 67 per cent of the sampled bioRxiv pre-prints, 79 per cent of the sampled medRxiv pre-prints, 75 per cent of the sampled arXiv pre-prints, and 85 per cent of all COVID-19-related SocArXiv pre-prints.
+Once differentiated by repository, we observe that open data and code markers were absent from 75 per cent of the sampled arXiv pre-prints, 67 per cent of the sampled bioRxiv pre-prints, 79 per cent of the sampled medRxiv pre-prints, and 85 per cent of all COVID-19-related SocArXiv pre-prints.
 The distribution of the remaining portion of pre-prints also varies by repository (Table \@ref(tab:summarycounts-repositories)).
@@
   kable(col.names = c("Open data markers", "Open code markers", "Count", "Proportion of total"),
-        caption = "Counts and proportions of open data and code markers by pre-print repository",
+        caption = "Count and proportions of open data and code markers by pre-print repository",
         booktabs = TRUE,
@@
 Notably, of all COVID-19-related pre-prints in our dataset, approximately 30 per cent of those posted to bioRxiv, and nearly one third of those posted to medRxiv, were published in peer-reviewed journals.
-This is high in comparison to the proportions from arXiv and SocArXiv, and although this might suggest that COVID-19-related pre-prints have received greater attention overall than pre-prints from other fields, our results in Section \@ref(pre-pandemic pre-prints) suggest that this pattern pre-dates the pandemic.
+This is high in comparison to the proportions from arXiv and SocArXiv, and although this might suggest that COVID-19-related pre-prints have received greater attention overall than pre-prints from other fields, our results in Section \@ref(pre-pandemic-pre-prints) suggest that this pattern pre-dates the pandemic.
 
@@
 
-```{r 2019-results}
+```{r 2019-results-med-arxiv, out.width="75%", fig.align='center', fig.cap = "Number of pre-prints posted per month to arXiv and bioRxiv in 2019"}
 bio_2019 <- bio_2019_results %>%
@@
 
-all_2019 <- rbind(bio_2019, med_2019, socarxiv_2019, arxiv_2019)
+bio_arxiv_2019 <- rbind(bio_2019, arxiv_2019)
 
 # TODO: position = "dodge" not working
-all_2019 %>% 
+bio_arxiv_2019 %>% 
   mutate(month = floor_date(date, "month")) %>% 
@@
   labs(title = "Pre-prints posted per month, 2019",
-       subtitle = "Total of 150,018 pre-prints on arXiv, 31,752 on bioRxiv, 913 on medRxiv, and \n1,614 on socArXiv",
+       subtitle = "Total of 150,018 pre-prints on arXiv and 31,752 on bioRxiv",
+       x = "Month",
+       y = "Number of pre-prints",
+       fill = "Repository") +
+  theme_minimal() +
+  scale_fill_manual(values = wes_palette("Darjeeling1"))
+```
+
+```{r 2019-results-med-sociarxiv, out.width="75%", fig.align='center', fig.cap = "Number of pre-prints posted per month to medRxiv and socArXiv in 2019"}
+med_socarxiv_2019 <- rbind(med_2019, socarxiv_2019)
+
+med_socarxiv_2019 %>% 
+  mutate(month = floor_date(date, "month")) %>% 
+  # filter(year(date) >= 2020) %>% 
+  ggplot(aes(x = month, fill = type)) + 
+  geom_histogram(stat="count", position = "dodge2") +
+  labs(title = "Pre-prints posted per month, 2019",
+       subtitle = "Total of 913 pre-prints on medRxiv and 1,614 on socArXiv",
        x = "Month",
@@
 
+all_2019_total <- 
+  all_2019 %>%
+  count(is_open_data, is_open_code) %>%
+  mutate(prop_total = n / sum(n)) %>%
+  mutate(is_open_data = ifelse(is_open_data == 0, "No", "Yes"),
+         is_open_code = ifelse(is_open_code == 0, "No", "Yes")) %>%
+  select(is_open_data, is_open_code, n, prop_total)
+
+all_2019_by_type <- 
   all_2019 %>%
@@
   ungroup() %>%
-  select(is_open_data, is_open_code, n, prop_total) %>%
+  select(is_open_data, is_open_code, n, prop_total)
+
+rbind(all_2019_total, all_2019_by_type) %>% 
   kable(col.names = c("Open data markers", "Open code markers", "Count", "Proportion of total"),
-        caption = "Counts and proportions of open data and code markers in 2019 sample",
+        caption = "Count and proportions of open data and code markers by pre-print repository in 2019 sample",
         booktabs = TRUE,
@@
         format.args = list(big.mark = ",")) %>%
-  group_rows(index = c("arXiv" = 4, "bioRxiv" = 4, "medRxiv" = 4, "socArXiv" = 4))
+  group_rows(index = c("Total" = 4, "arXiv" = 4, "bioRxiv" = 4, "medRxiv" = 4, "SocArXiv" = 4))
+
 ```
 
-Between June and December 2019, the number of pre-prints posted to medRxiv monthly saw an overall increase which may be expected as the repository gained recognition and popularity in the medical research community.
-The number of papers posted monthly to bioRxiv also saw an overall increase throughout 2019.
+Between June and December 2019, the number of pre-prints posted to medRxiv monthly saw an overall increase which may be expected as the repository gained recognition and popularity in the medical research community (Figure \@ref(fig:2019-results-med-sociarxiv)).
+The number of pre-prints posted monthly to bioRxiv also saw a slight overall increase throughout 2019, while the number of those posted to arXiv and SocArXiv fluctuated throughout the year (Figures \@ref(fig:2019-results-med-arxiv) and \@ref(fig:2019-results-med-sociarxiv)).
 It is important to note here that due to its relative immaturity at the beginning of the COVID-19 pandemic, a significant portion of medRxiv's overall usage has been dedicated to COVID-19-related research.
-In total, 21,647 pre-prints were posted to medRxiv between June 2019 and 30 June, 2021, 13,194 (approximately 61 per cent) of which relate to COVID-19.
+In total, 21,647 pre-prints were posted to medRxiv between June 2019 and 30 June, 2021, 13,194 of which (approximately 61 per cent) relate to COVID-19.
 
@@
 Examining publication rates for pre-pandemic papers, we observe that 41 per cent of pre-prints posted to arXiv, 64 per cent of pre-prints posted to bioRxiv, 61 per cent of pre-prints posted to medRxiv, and 37 per cent of pre-prints posted to SocArXiv during 2019 were eventually peer reviewed and published (Table \@ref(tab:2019-published)).
-These rates are at least double those of the COVID-19-related pre-prints posted in each repository during 2020 and 2021 (33 per cent and 31 per cent from bioRxiv and medRxiv respectively).
+These rates are at least double those of the COVID-19-related pre-prints posted in each repository during 2020 and 2021.
 When disaggregated by open data and code status, we find that published and unpublished pre-prints contain open data and code markers in similar proportions (Table \@ref(tab:2019-open-publishing)).
@@
 Transparency and reproducibility are hallmarks of quality scientific research.
-Open data and open code contribute to both by allowing the scientific community to more easily verify the authenticity of purported scientific discovery and its supporting evidence.
+Open data and open code contribute to both by allowing the scientific community to more easily verify the authenticity of purported scientific discoveries and their supporting evidence.
 This is especially important in cases where scientific research may quickly and directly impact clinical practice or public policy such as during the COVID-19 pandemic.
@@
 Any rushed scientific research has potential to skip (or at least place less precedence on) open science practices, thus it may be reasonable to expect a decrease in open data or code markers in the pre-prints posted during times of increased overall posting to medRxiv.
-In our analysis, we found little relationship between date posted and likelihood of having open data or code markers with the proportion of pre-prints containing these markers fluctuating greatly from month to month and no apparent decrease during periods of increased publication.
-This suggests that open science practices are more influenced by other factors, perhaps training, publication bias, or the nature of the pre-print itself.
+In our analysis, we found little relationship between date posted and likelihood of having open data or code markers with the proportion of pre-prints containing these markers fluctuating greatly from month to month and no apparent decrease during periods of increased registration This suggests that open science practices are more influenced by other factors, perhaps training, publication bias, or the nature of the pre-print itself.
 On the other hand, we do not see an overall long-term increase in either open data or open code markers throughout our period of analysis which we may have expected in the context of the aforementioned open science movements the pandemic has fostered.
@@
 The open-source nature of these models was fundamental to reproduction attempts and is a great example of the need for open data and code in reproducing COVID-19 research, particularly in evaluating pre-prints as they begin to influence public decision-making.
-<!-- In the context of the above factors, it was disheartening in our analysis to find that the proportion of modelling- and simulation-related pre-prints with open data or code increased only marginally from that of the entire sample.
-One might hope that modelling papers should universally be subject to the same analysis as conducted by @jin2020 as for the examples above, which is made possible by the availability of relevant code and data.
--->
-Our analysis suggests a need for future investigation and potential overall improvement in open science standards for these types of pre-prints (of course subject to the data and code considerations already discussed).
-This need is again emphasized by the new-found speed at which pre-prints may gain public, media, and political attention in the context of the pandemic.
+
+In the context of the above factors, it was encouraging in our analysis to find that the proportion of pre-prints with open data or code posted to arXiv --- a pre-print server dedicated to computational and quantitative work such as modelling and simulation studies --- increased from seven per cent pre-pandemic to 25 per cent for COVID-19-related pre-prints.
+This pattern, however, was not observed among the analyzed bioRxiv and medRxiv pre-prints.
+With many pre-prints from these repositories still pertaining to epidemiological modelling, one might hope that they should universally be subject to the same analysis as conducted by @jin2020 as for the examples above, which is made possible by the availability of relevant code and data.
+Our analysis suggests a need for future investigation and potential overall improvement in open science standards for these types of pre-prints (subject to the data and code considerations already discussed).
+This need is again emphasized by the new-found speed at which pre-prints may gain public, media, and political attention in the context of the pandemic, particularly those from medRxiv and bioRxiv.
 
@@
 It is important that open data and code standards be maintained in published work as well.
-Our findings in this regard were two-fold: that open data or code markers may not directly influence a pre-print's eventual publication, and that a lower proportion of published papers contain either open data or code markers than the general sample.
-Both raise concerns over publication bias, the potential that journals have favored novel yet less transparent or reproducible papers over those with null results but a high standard of open science practices.
-Concerns have already been raised through systemic reviews of COVID-19 publications [@raynaud2021], and oversights in data accessibility have led to high profile retractions of publications in the past, for example papers from *The Lancet* and the *New England Journal of Medicine* were withdrawn due to concerns over the private nature of their underlying dataset [@ledford2020].
+In our sample, published pre-prints contain open data or code markers in similar proportions to their unpublished counterparts, a pattern that was present for pre-prints related to COVID-19 as well as those posted in 2019.
+This appears initially to alleviate some concerns over the relationship between open data and publication bias, the potential that journals have favoured novel yet less transparent or reproducible papers over those with null results but a high standard of open science practices.
+However, publication bias is complex and this result should be approached with caution.
+Concerns have already been raised through systemic reviews of COVID-19 publications [@raynaud2021], and oversights in data accessibility have led to high profile retractions of publications in the past, for example papers from *The Lancet* and the *New England Journal of Medicine* which were withdrawn due to concerns over the private nature of their underlying dataset [@ledford2020].
 
@@
 There is demand for timely research and high frequency results because the pandemic rapidly evolved.
-Preprints are efficient in this role because there is no time spent on peer review.
+Pre-prints are efficient in this role because there is no time spent on peer review.
 They also allow lesser-known researchers to better disperse their research, because of the possibility that fast-tracked peer review may be biased towards established researchers.

### 2021-07-21 outputs/paper/paper-copy.Rmd
Paper updates

@@
 socarxivsamplecount [label =  'SocArXiv: 478 pre-prints']
-opencodeanddata [label =  'Those with markers of open code and open data']
+opencodeanddata [label =  'Those with markers of open code or open data']
 arxivopencount [label =  'arXiv: 248 pre-prints']

### 2021-07-21 outputs/paper/paper-copy.Rmd
Minor tweaks to the paper throughout

@@
   - Rohan Alexander^[University of Toronto, rohan.alexander@utoronto.ca.]
-thanks: "Collins thanks CANSSI Ontario for financial support. Code and data are available at: https://github.com/anniecollins/reproducibility."
+thanks: "We thank Amy Farrow, Jessica Gronsbell, Monica Alexander, and Thomas William Rosenthal for helpful comments.
+Collins thanks CANSSI Ontario and Monica Alexander for financial support.
+Code and data are available at: https://github.com/anniecollins/reproducibility."
 date: "`r format(Sys.time(), '%d %B %Y')`"
-abstract: "We create a dataset of pre-prints posted to arXiv, bioRxiv, medRxiv, and SocArXiv between 28 January 2020 and 30 June 2021 that are related to COVID-19.
+abstract: "To examine the reproducibility of COVID-19 research, we create a dataset of pre-prints posted to arXiv, bioRxiv, medRxiv, and SocArXiv between 28 January 2020 and 30 June 2021 that are related to COVID-19.
 We extract the text from these pre-prints and parse them looking for keyword markers signalling the availability of the data and code underpinning the pre-print.
 For the pre-prints that are in our sample, we are unable to find markers of either open data or open code for 75 per cent of those on arXiv, 67 per cent of those on bioRxiv, 79 per cent of those on medRxiv, and 85 per cent of those on SocArXiv.
-We conclude that there may be value in having authors categorize the degree of openness of their pre-print as part of the pre-print submissions process, and more broadly, the need to better integrate open science training into a wide range of fields."
+We conclude that there may be value in having authors categorize the degree of openness of their pre-print as part of the pre-print submissions process, and more broadly, there is a need to better integrate open science training into a wide range of fields."
 output:
@@
 Scientists use open repositories of papers to disseminate their research more quickly than is possible in traditional journals or conference proceedings.
-These repositories, such as arXiv, bioRxiv, medRxiv, and SocArXiv, are a critical component of scientific communication and many results build on the pre-prints posted there.
+These repositories, such as arXiv, bioRxiv, medRxiv, and SocArXiv, are a critical component of scientific communication and many  results, in the overall world of research, build on the pre-prints posted there.
 Pre-print repositories have been especially important during the 2019 novel coronavirus (COVID-19) pandemic and the changes it has imposed on the scientific community [@else2020].
@@
 Neither peer-review nor credentials are a panacea nor a guarantee of quality.
-And the gate-keeping and slow publication times of traditional journals mean pre-print repositories have an important role to play.
+And the gate-keeping and slow publication times of traditional journals mean pre-print repositories are important when speed is essential.
 But it is important that scientists impose standards on themselves, and arguably repositories have a role to play here.
-Following @weissgerber2021automated we examine pre-prints about COVID-19 posted to arXiv, bioRxiv, medRxiv, and SocArXiv from 28 January 2020 through to 30 June 2021.
+Following @weissgerber2021automated, we examine pre-prints about COVID-19 posted to arXiv, bioRxiv, medRxiv, and SocArXiv from 28 January 2020 through to 30 June 2021.
+By way of background, each of these four repositories has a different focus: arXiv is general, bioRxiv focuses on biological sciences, medRxiv focuses on health sciences, and SocArXiv focuses on social sciences.
 We search for markers of open science as indicators of reproducibility, specifically open data and open code.
@@
 In the case of SocArXiv there are fields that are self-reported by the submitting author about the availability of code and data.
-We classified individual pre-prints as "COVID-19-related" based on whether they contained one or more of the following terms in their title or abstract (case insensitive): "COVID-19", "COVID 19", "corona virus", "coronavirus", "coronavirus-2", "SARS-CoV-2", "SARSCoV-2", or "2019-nCoV".
-We then randomly sampled pre-prints for further analysis, except for SocArXiv for which we analyzed all pre-prints that matched the above criteria as there were only 478.
+We classified individual pre-prints as "COVID-19-related" based on whether they contained one or more of the following terms in their title or abstract (case insensitive): "COVID-19", "COVID 19", "corona virus", "coronavirus", "coronavirus-2", "SARS-CoV-2", "SARSCoV-2", and "2019-nCoV".
+We then randomly sampled pre-prints for further analysis, except for SocArXiv, for which we analyzed all pre-prints that matched the above criteria, because there were only 478.
 
@@
 We checked our sampled pre-prints for open data and code markers using the Open Data Detection in Publications (ODDPub) text mining algorithm [@citePDDPub] within the `oddpub` R package [@citeODDPubpackage].
-This required downloading each pre-print as a PDF, which we did using `heapsofpapers` [@citealexandermafouz], and then converting the PDFs to text files.
+This required downloading each pre-print as a PDF, which we did using `heapsofpapers` [@citealexandermafouz] and then converting the PDFs to text files.
 Some papers from SocArXiv were only available in Word document format (.docx) and were downloaded as such and then converted to text format.
-We then conducted the open data and open code detection procedure which involved searching for keywords and other markers of open data and open code availability.
+We then conducted the open data and open code detection procedure, which involved searching for keywords and other markers of open data and open code availability.
 This was conducted using the `open_data_search()` function from the `oddpub` package.
 What constitutes open code or open data is complicated and discipline specific.
-The details of the `oddpub` approach are available in @riedel2020oddpub.
+The details of the `oddpub` approach are available in @citePDDPub.
 The general criteria are that specific mention should be made of where the data and code are located, and that data should be as close to raw as possible.
@@
 The result of this process is a dataset indicating the presence of open data or open code markers in each pre-print (with a logical vector for each marker, followed by the relevant open data or open code statements where applicable).
-Our final dataset was formed by joining this output with the original sample metadata, typically using the DOI or the unique file name, to form a dataset including all original, qualitative metadata for each pre-print alongside its open data and open code status and markers.
+Our final dataset was formed by joining this output with the original sample metadata, typically using the DOI or the unique file name, to form a dataset including all original metadata for each pre-print alongside its open data and open code status and markers.
 
@@
 The number of pre-prints posted per month increased in the first half of 2020 across all repositories, reaching a maximum sometime between April and June (depending on repository) and subsequently decreasing.
-The number of pre-prints posted monthly since August 2020 has remained reasonably steady, with the exception of medRxiv which experienced an increase to nearly 1,000 pre-prints posted in March 2021 (Figure \@ref(fig:monthly-papers-total)).
+The number of pre-prints posted monthly since August 2020 has remained reasonably steady, with the exception of medRxiv, which experienced an increase to nearly 1,000 pre-prints posted in March 2021 (Figure \@ref(fig:monthly-papers-total)).
 For context, COVID-19 was declared a pandemic by the World Health Organization (WHO) on March 11, 2020, at which point the number of cases globally had just surpassed 118,000 (primarily in east Asia) and the virus had been reported in 114 countries [@citeWHOtimeline].
@@
 
-From the collection of all pre-prints related to COVID-19 we randomly sampled 3,910 pre-prints to analyze, stratified by repository.
+From the collection of all pre-prints related to COVID-19, we randomly sampled 3,910 pre-prints to analyze, stratified by repository.
 This sample is broken down as follows: 1,500 from medRxiv, 1,000 from arXiv, 1,000 from bioRxiv, and 478 from SocArXiv.
@@
   xlab("Month") +
-  labs(title="Sampled pre-prints by month", subtitle="Sample size from arXiv is 1,000, from bioRxiv is 1,000, from medRxiv is 1,500, and from \nSocArXiv is 410.") +
+  labs(title="Sampled pre-prints by month", subtitle="Sample size from arXiv is 1,000, from bioRxiv is 1,000, from medRxiv is 1,500, and from \nSocArXiv is 410. Note the differing y-axes.") +
   theme_minimal() +
   scale_fill_manual(values = wes_palette("Darjeeling1")) +
-  facet_wrap(~repo)
+  facet_wrap(~repo,
+             scales = "free_y")
 ```
@@
 The proportion of pre-prints that have been published varies by repository (Table \@ref(tab:published-sample-summary)).
-Notably, of all COVID-19-related pre-prints in our dataset, approximately 30 per cent of those posted to bioRxiv, and nearly one third of those posted to medRxiv, were published in peer-reviewed journals.
-This is high in comparison to the proportions from arXiv and SocArXiv, and although this might suggest that COVID-19-related pre-prints have received greater attention overall than pre-prints from other fields, our results in Section \@ref(pre-pandemic-pre-prints) suggest that this pattern pre-dates the pandemic.
+Notably, of all COVID-19-related pre-prints in our dataset, approximately 30 per cent of those posted to bioRxiv and nearly one third of those posted to medRxiv were published in peer-reviewed journals.
+This is high in comparison to the proportions from arXiv and SocArXiv, and although this might suggest that COVID-19-related pre-prints in biomedical fields have received greater attention overall than pre-prints from other fields, our results in Section \@ref(pre-pandemic-pre-prints) suggest that this pattern pre-dates the pandemic.
 
@@
   kable(caption = "Counts and proportion of published COVID-19 pre-prints in each repository",
-        col.names = c("Repositiory", "Published pre-prints", "Proportion published"),
+        col.names = c("Repository", "Published pre-prints", "Proportion published"),
         format.args = list(big.mark = ","))
@@
 In Table \@ref(tab:open-published-summary) we disaggregate sampled pre-prints by whether there is an indication of publication.
-We find that the proportion of pre-prints with open data or code markers among those that have been published is roughly the same as pre-prints that have not been published, differing by one per cent only within the bioRxiv and medRxiv samples, and three per cent in the arXiv sample.
+We find that the proportion of pre-prints with open data or code markers among those that have been published is roughly the same as pre-prints that have not been published, differing by one per cent only within the bioRxiv and medRxiv samples and three per cent in the arXiv sample.
 
@@
 
-```{r 2019-results-med-arxiv, out.width="75%", fig.align='center', fig.cap = "Number of pre-prints posted per month to arXiv and bioRxiv in 2019"}
+```{r 2019-results-med-arxiv, out.width="90%", fig.align='center', fig.cap = "Number of pre-prints posted per month to arXiv, bioRxiv, medRxiv, and SocArXiv in 2019"}
 bio_2019 <- bio_2019_results %>%
@@
 
-bio_arxiv_2019 <- rbind(bio_2019, arxiv_2019)
+all_2019 <- rbind(arxiv_2019, bio_2019, med_2019, socarxiv_2019)
 
 # TODO: position = "dodge" not working
-bio_arxiv_2019 %>% 
+all_2019 %>% 
   mutate(month = floor_date(date, "month")) %>% 
@@
   labs(title = "Pre-prints posted per month, 2019",
-       subtitle = "Total of 150,018 pre-prints on arXiv and 31,752 on bioRxiv",
+       subtitle = "Total of 150,018 pre-prints on arXiv and 31,752 on bioRxiv, 913 pre-prints on \n medRxiv and 1,614 on SocArXiv",
        x = "Month",
@@
   theme_minimal() +
-  scale_fill_manual(values = wes_palette("Darjeeling1"))
-```
-
-```{r 2019-results-med-sociarxiv, out.width="75%", fig.align='center', fig.cap = "Number of pre-prints posted per month to medRxiv and socArXiv in 2019"}
-med_socarxiv_2019 <- rbind(med_2019, socarxiv_2019)
-
-med_socarxiv_2019 %>% 
-  mutate(month = floor_date(date, "month")) %>% 
-  # filter(year(date) >= 2020) %>% 
-  ggplot(aes(x = month, fill = type)) + 
-  geom_histogram(stat="count", position = "dodge2") +
-  labs(title = "Pre-prints posted per month, 2019",
-       subtitle = "Total of 913 pre-prints on medRxiv and 1,614 on socArXiv",
-       x = "Month",
-       y = "Number of pre-prints",
-       fill = "Repository") +
-  theme_minimal() +
-  scale_fill_manual(values = wes_palette("Darjeeling1"))
+  scale_fill_manual(values = wes_palette("Darjeeling1")) +
+  facet_wrap(~type,
+             scales = "free_y")
 ```
@@
 
-Between June and December 2019, the number of pre-prints posted to medRxiv monthly saw an overall increase which may be expected as the repository gained recognition and popularity in the medical research community (Figure \@ref(fig:2019-results-med-sociarxiv)).
-The number of pre-prints posted monthly to bioRxiv also saw a slight overall increase throughout 2019, while the number of those posted to arXiv and SocArXiv fluctuated throughout the year (Figures \@ref(fig:2019-results-med-arxiv) and \@ref(fig:2019-results-med-sociarxiv)).
+Between June and December 2019, the number of pre-prints posted to medRxiv monthly saw an overall increase, which may be expected as the repository gained recognition and popularity in the medical research community (Figure \@ref(fig:2019-results-med-arxiv)).
+The number of pre-prints posted monthly to bioRxiv also saw a slight overall increase throughout 2019, while the number of those posted to arXiv and SocArXiv fluctuated throughout the year (Figure \@ref(fig:2019-results-med-arxiv)).
 It is important to note here that due to its relative immaturity at the beginning of the COVID-19 pandemic, a significant portion of medRxiv's overall usage has been dedicated to COVID-19-related research.
@@
 Open data and open code contribute to both by allowing the scientific community to more easily verify the authenticity of purported scientific discoveries and their supporting evidence.
-This is especially important in cases where scientific research may quickly and directly impact clinical practice or public policy such as during the COVID-19 pandemic.
+This is especially important in cases where scientific research may quickly and directly impact clinical practice or public policy, such as research on the COVID-19 pandemic.
 Among many other impacts on the research landscape, COVID-19 has dramatically increased the popularity of pre-prints from both a production and consumption standpoint.
-The number of COVID-19 pre-prints posted to medRxiv increased dramatically in the early stages of the pandemic while non-COVID-19 pre-print numbers were largely as expected.
+The number of COVID-19 pre-prints posted to medRxiv increased dramatically in the early stages of the pandemic, while non-COVID-19 pre-print numbers were largely as expected.
 The same trends were apparent in abstracts accessed by medRxiv users, where COVID-19 pre-print abstracts were viewed over 15 times more than non-COVID-19 pre-print abstracts [@citeFraser].
@@
 
-Open data is generally accepted to be beneficial to the scientific process, and to a paper's reproducibility potential, hence it is concerning that over 75 per cent of pre-prints in our sample contained no open data markers.
+Open data is generally accepted to be beneficial to the scientific process and to a paper's reproducibility potential, hence it is concerning that over 75 per cent of pre-prints in our sample contained no open data markers.
 This concern is slightly mitigated by recognition of challenges in working with biomedical data compared with data in other fields, notably privacy and ethics concerns when working with personal data [@Floca2014].
@@
 While the intention at the start of the pandemic was that there would be 'clear statements regarding the availability of underlying data' [@citeWellcome] some retractions of work have been based on 'unreliable or nonexistent data' [@da2021optimizing].
-SocArXiv asks submitters to make explicit the degree of openness in the data and this is something that could be easily adopted by other pre-print repositories.
+SocArXiv asks submitters to make explicit the degree of openness in the data, and this is something that could be easily adopted by other pre-print repositories.
 
@@
 The other concern is the adverse selection issue caused by meeting the open science aims of sharing code and data.
-Authors that share their data and code open themselves up to criticism of their work because of this.
+Authors that share their data and code open their work up to criticism.
 If authors who make their data and code available make similar mistakes to authors who choose to not publish their data and code, it is more likely that the mistake would not be noticed in the case where data and code were not published.
 The current system is biased against those who follow best practice.
-Indeed @mcguinness2021descriptive advocate '(s)trict editorial policies that mandate data sharing'.
+Indeed, @mcguinness2021descriptive advocate '(s)trict editorial policies that mandate data sharing'.
 
@@
 Any rushed scientific research has potential to skip (or at least place less precedence on) open science practices, thus it may be reasonable to expect a decrease in open data or code markers in the pre-prints posted during times of increased overall posting to medRxiv.
-In our analysis, we found little relationship between date posted and likelihood of having open data or code markers with the proportion of pre-prints containing these markers fluctuating greatly from month to month and no apparent decrease during periods of increased registration This suggests that open science practices are more influenced by other factors, perhaps training, publication bias, or the nature of the pre-print itself.
-On the other hand, we do not see an overall long-term increase in either open data or open code markers throughout our period of analysis which we may have expected in the context of the aforementioned open science movements the pandemic has fostered.
-Although not pre-print specific, @else2020 found that overall research output has fluctuated between different fields and topics (namely modelling disease spread, public health, diagnostics and testing, mental health, and hospital mortality) throughout different stages of the pandemic which may account for some of the fluctuation and overall lack of noticeable trend over the course of the year.
+In our analysis, we found little relationship between date posted and likelihood of having open data or code markers, with the proportion of pre-prints containing these markers fluctuating greatly from month to month and no apparent decrease during periods of increased registration.
+This suggests that open science practices are more influenced by other factors, perhaps including training, publication bias, or the nature of the pre-print itself.
+On the other hand, we do not see an overall long-term increase in either open data or open code markers throughout our period of analysis, which we may have expected in the context of the open science movements the pandemic has fostered.
+Although not pre-print specific, @else2020 found that overall research output has fluctuated between different fields and topics (namely modelling disease spread, public health, diagnostics and testing, mental health, and hospital mortality) throughout different stages of the pandemic, which may account for some of the fluctuation and overall lack of noticeable trend over the course of the year.
 
@@
 
-In the context of the above factors, it was encouraging in our analysis to find that the proportion of pre-prints with open data or code posted to arXiv --- a pre-print server dedicated to computational and quantitative work such as modelling and simulation studies --- increased from seven per cent pre-pandemic to 25 per cent for COVID-19-related pre-prints.
+In the context of the above factors, it was encouraging to find in our analysis that the proportion of pre-prints with open data or code posted to arXiv increased from seven per cent pre-pandemic to 25 per cent for COVID-19-related pre-prints.
 This pattern, however, was not observed among the analyzed bioRxiv and medRxiv pre-prints.
@@
 
-Beyond pre-prints, COVID-19 has had great influence over publication and peer review processes as well, with expedited review timelines for COVID-19 papers at the expense of longer waits for other scientific research [@else2020].
+Beyond pre-prints, COVID-19 has had great influence over publication and peer review processes, with timelines for COVID-19 papers being expedited at the expense of longer waits for other scientific research [@else2020].
 It is important that open data and code standards be maintained in published work as well.
-In our sample, published pre-prints contain open data or code markers in similar proportions to their unpublished counterparts, a pattern that was present for pre-prints related to COVID-19 as well as those posted in 2019.
-This appears initially to alleviate some concerns over the relationship between open data and publication bias, the potential that journals have favoured novel yet less transparent or reproducible papers over those with null results but a high standard of open science practices.
+In our sample, published pre-prints contain open data or code markers in similar proportions to their unpublished counterparts, a pattern that was present for pre-prints related to COVID-19 and those posted in 2019.
+This appears initially to alleviate some concerns over the relationship between open data and publication bias, that is, the potential that journals have favoured novel yet less transparent or reproducible papers over those with null results but a high standard of open science practices.
 However, publication bias is complex and this result should be approached with caution.
-Concerns have already been raised through systemic reviews of COVID-19 publications [@raynaud2021], and oversights in data accessibility have led to high profile retractions of publications in the past, for example papers from *The Lancet* and the *New England Journal of Medicine* which were withdrawn due to concerns over the private nature of their underlying dataset [@ledford2020].
+Concerns have already been raised through systemic reviews of COVID-19 publications [@raynaud2021], and oversights in data accessibility have led to high profile retractions of publications in the past; for example, papers from *The Lancet* and the *New England Journal of Medicine* which were withdrawn due to concerns over the private nature of their underlying dataset [@ledford2020].
 
 In all fields of science, increasing access to data and code used for pre-printed or published research is a step in the direction of more transparent, reproducible, and reliable research.
-The ongoing COVID-19 pandemic has created a novel, constantly changing scientific culture that should be navigated with care to uphold standards of scientific practice for both the research community and the safety of the general public.
+The ongoing COVID-19 pandemic has created a novel, constantly changing scientific culture that should be navigated with care to uphold standards of scientific practice for both the research community and the safety of the public.
 Our analysis shows that there is room for improvement in the areas of open data and code availability within COVID-19 pre-print papers on arXiv, bioRxiv, medRxiv, and SocArXiv.
 
-There is demand for timely research and high frequency results because the pandemic rapidly evolved.
+There is demand for timely research and high frequency results because the pandemic rapidly evolves.
 Pre-prints are efficient in this role because there is no time spent on peer review.
-They also allow lesser-known researchers to better disperse their research, because of the possibility that fast-tracked peer review may be biased towards established researchers.
+They also allow lesser-known researchers to better disperse their research because of the possibility that fast-tracked peer review may be biased towards established researchers.
 While there is a clear need for pre-prints, the point remains that they do not go through the peer review process.
-This question of quality and validity is particularly pertinent in the COVID-19 context because poorly validated results and false information may spread quickly, and have real effects.
-We are not saying that peer review implies that a paper is of a high-quality, we are instead saying that the provision of code and data alongside the pre-print goes some way to allowing others to trust the findings of pre-prints even though they have not been peer-reviewed.
-One way this could be encouraged would be for pre-print repositories to have authors characterize the extent to which they have adopted open science practices as part of their submission, in the same way that is done in SocArXiv.
+This question of quality and validity is particularly pertinent in the COVID-19 context because poorly validated results and false information may spread quickly and have real effects.
+We are not saying that peer review implies that a paper is of a high-quality; we are instead saying that the provision of code and data alongside the pre-print goes some way to allowing others to trust the findings of pre-prints, even though they have not been peer-reviewed.
+One way this could be encouraged would be for all pre-print repositories to have authors characterize the extent to which they have adopted open science practices as part of their submission, in the same way that is done in SocArXiv.
 Although those pre-prints that do not adopt these practices should not be rejected from pre-print repositories, greater clarity around this would be useful and might move the state-of-the-art forward.
@@
 We wish to expand our analysis to consider the geographic distribution of research and the potential influence of different practices and policies concerning open science as pre-prints vary by location.
-This is important as the epicenter of the pandemic changed throughout the pandemic which has implications for our time-based analysis.
+This is important because the epicenter of the pandemic changed throughout the pandemic, which has implications for our time-based analysis.
 
 An important weakness to note is the potential presence of false negatives in indicators of publication in our dataset.
-@abdill2019 estimate that the false-negative rate may be as high as 37.5 per cent for data pulled from the bioRxiv API, meaning analysis of published papers may represent only a fraction of those that have actually been published.
-It is unclear to what extent this is the case for other repositories or what bias may exist in the subset of pre-prints for which publication was detected, as it is likely that this process relies on title-based text matching [@abdill2019].
-It is also likely that some of our more recent sampled pre-prints will be published in future which we could not account for at the time of our data collection.
+@abdill2019 estimate that the false-negative rate may be as high as 37.5 per cent for data pulled from the bioRxiv API, meaning analysis of published papers may represent only a fraction of those that have been published.
+It is unclear to what extent this is the case for other repositories or what bias may exist in the subset of pre-prints for which publication was detected, because it is likely that this process relies on title-based text matching [@abdill2019].
+It is also likely that some of our more recent sampled pre-prints will be published in the future which we could not account for at the time of our data collection.
+
+Our paper depends on search responses from the various repositories, which are based on our selection of keywords.
+Our selection of keywords is not exhaustive, for instance, perhaps 'the pandemic' could result in additional papers.
+Future work could make this keyword approach more systematic, for instance following @king2017computer.
 

### 2021-07-22 outputs/paper/paper-copy.Rmd
Minor updates to paper, update slides to match paper

@@
 author: 
+  - Rohan Alexander^[University of Toronto, rohan.alexander@utoronto.ca.]
   - Annie Collins^[University of Toronto.]
-  - Rohan Alexander^[University of Toronto, rohan.alexander@utoronto.ca.]
 thanks: "We thank Amy Farrow, Jessica Gronsbell, Monica Alexander, and Thomas William Rosenthal for helpful comments.
 Collins thanks CANSSI Ontario and Monica Alexander for financial support.
-Code and data are available at: https://github.com/anniecollins/reproducibility."
+Code and data are available at: https://github.com/anniecollins/reproducibility_markers_in_covid19_preprints."
 date: "`r format(Sys.time(), '%d %B %Y')`"
@@
         format.args = list(big.mark = ",")) %>%
-  group_rows(index = c("bioRxiv" = 2, "medRxiv" = 2, "arXiv" = 2, "SocArXiv" = 2))
+  group_rows(index = c("arXiv" = 2, "bioRxiv" = 2, "medRxiv" = 2, "SocArXiv" = 2))
 ```
@@
 
-To examine the influence of the COVID-19 pandemic on open science practices in during the pandemic, we analyzed pre-prints posted between January and December 2019 from each of the four repositories using the same process as was done for the COVID-19-related pre-prints.
+To examine the influence of the COVID-19 pandemic on open science practices during the pandemic, we analyzed pre-prints posted between January and December 2019 from each of the four repositories using the same process as was done for the COVID-19-related pre-prints.
 Since medRxiv was founded in June 2019, all pre-prints posted in the latter half of 2019 were analyzed (a total of 913).
@@
 
-# TODO: position = "dodge" not working
 all_2019 %>% 
@@
   facet_wrap(~type,
-             scales = "free_y")
+             scales = "free_y") +
+  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
 ```
@@
 The current system is biased against those who follow best practice.
-Indeed, @mcguinness2021descriptive advocate '(s)trict editorial policies that mandate data sharing'.
+Indeed, @mcguinness2021descriptive advocate for "(s)trict editorial policies that mandate data sharing."
 

### 2021-07-22 outputs/paper/paper.Rmd
As submitted to arXiv

--- 2021-05-25 outputs/paper/paper.Rmd
@@
 ---
-title: "Reproducibility of COVID-19 pre-prints in 2020"
-subtitle: "Markers of open code or data not found in 81 per cent of pre-prints"
+title: "Reproducibility of COVID-19 pre-prints"
 author: 
   - Annie Collins^[University of Toronto.]
-thanks: "Collins thanks CANSSI Ontario for financial support. Code and data are available at: https://github.com/anniecollins/reproducibility."
+  - Rohan Alexander^[University of Toronto, rohan.alexander@utoronto.ca.]
+thanks: "We thank Amy Farrow, Jessica Gronsbell, Monica Alexander, and Thomas William Rosenthal for helpful comments.
+Collins thanks CANSSI Ontario and Monica Alexander for financial support.
+Code and data are available at: https://github.com/anniecollins/reproducibility_markers_in_covid19_preprints."
 date: "`r format(Sys.time(), '%d %B %Y')`"
-abstract: "We create a dataset of all the pre-prints published on arXiv, bioRxiv, and medRxiv between 28 January 2020 and 31 January 2021.
+abstract: "To examine the reproducibility of COVID-19 research, we create a dataset of pre-prints posted to arXiv, bioRxiv, medRxiv, and SocArXiv between 28 January 2020 and 30 June 2021 that are related to COVID-19.
 We extract the text from these pre-prints and parse them looking for keyword markers signalling the availability of the data and code underpinning the pre-print.
-We are unable to find markers of either open data or open code for 81 per cent of the pre-prints on medRxiv  in our sample, and X per cent of those on arXiv in our sample.
-Our paper demonstrates the need to have authors categorize the degree of openness of their pre-print as part of the pre-print submissions process, and more broadly, the need to better integrate open science training into a wide range of fields."
+For the pre-prints that are in our sample, we are unable to find markers of either open data or open code for 75 per cent of those on arXiv, 67 per cent of those on bioRxiv, 79 per cent of those on medRxiv, and 85 per cent of those on SocArXiv.
+We conclude that there may be value in having authors categorize the degree of openness of their pre-print as part of the pre-print submissions process, and more broadly, there is a need to better integrate open science training into a wide range of fields."
 output:
   bookdown::pdf_document2:
+    keep_tex:  true
 toc: FALSE
@@
 library(wesanderson)
+library(kableExtra)
+library(DiagrammeR)
 ```
@@
 all_arxiv_results <- 
-  read_csv(here::here("outputs/data/arxiv_results.csv"))
+  read_csv(here::here("outputs/data/arxiv_results.csv")) # All COVID arXiv papers (3,812)
+arxiv_2019_open_data_results <- 
+  read_csv(here::here("outputs/control-data/arxiv_2019_open_data_results.csv"))
+all_arxiv_2019_results <- 
+  read_csv(here::here("outputs/control-data/arxiv_data_2019.csv"))
+
+socarxiv_open_data_results <- 
+  read_csv(here::here("outputs/data/socarxiv_open_data_results.csv"))
+socarxiv_2019_open_data_results <- 
+  read_csv(here::here("outputs/control-data/socarxiv_2019_open_data_results.csv"))
+socarxiv_metadata_2019 <- 
+  read_csv(here::here("outputs/control-data/socarxiv_metadata_2019.csv"))
 
@@
 
-Scientists use open repositories of papers to more quickly disseminate their research than is possible in traditional journals or conference proceedings.
-These repositories, such as arXiv, bioRxiv, medRxiv, and SocArXiv, are a critical component of science and many results build on the work published there.
-Thus it is important that the results that are published are credible.
-Pre-print repositories have drawn unprecedented attention in the context of the 2019 novel coronavirus (COVID-19) pandemic and the changes it has imposed on the scientific community [@else2020].
-These repositories are not peer-reviewed, and, in general, anyone with appropriate academic credentials can submit a pre-print
+Scientists use open repositories of papers to disseminate their research more quickly than is possible in traditional journals or conference proceedings.
+These repositories, such as arXiv, bioRxiv, medRxiv, and SocArXiv, are a critical component of scientific communication and a lot of research builds on the pre-prints posted there.
+Pre-print repositories have been especially important during the 2019 novel coronavirus (COVID-19) pandemic and the changes it has imposed on the scientific community [@else2020].
+The centrality of pre-prints to science means that it is important that the results that are posted are credible.
+These repositories are not peer-reviewed, and, in general, anyone with appropriate academic credentials can submit a pre-print.
 
 Neither peer-review nor credentials are a panacea nor a guarantee of quality.
-And the gate-keeping and slow publication times of traditional journals mean pre-print repositories have an important role to play.
-But given the importance of these repositories, it is important that scientists impose on themselves various standards for their results.
-Following @weissgerber2021automated we examine papers about COVID-19 published to  arXiv, bioRxiv, medRxiv, and SocArXiv from January 2020, through to February 2021.
+And the gate-keeping and slow publication times of traditional journals mean pre-print repositories are important.
+But it is important that scientists impose standards on themselves, and arguably repositories have a role to play here.
+Following @weissgerber2021automated, we examine pre-prints about COVID-19 posted to arXiv, bioRxiv, medRxiv, and SocArXiv from 28 January 2020 through to 30 June 2021.
+By way of background, each of these four repositories has a different focus: arXiv is general, bioRxiv focuses on biological sciences, medRxiv focuses on health sciences, and SocArXiv focuses on social sciences.
 We search for markers of open science as indicators of reproducibility, specifically open data and open code.
 
-We find that approximately 81 per cent of sampled papers contain neither open data nor open code markers.
-Examining trends over time, we find that the proportion of pre-prints containing open data or code markers has fluctuated but shown no obvious increasing or decreasing trend throughout the pandemic.
-We also find that the presence of open data or open code markers has little influence on a pre-print's future publication, while the subset of sampled pre-prints that has been published contains an overall lower proportion of papers with these markers.
-Finally, we briefly examine the presence of open data and code markers in specific types of pre-prints, namely modelling, simulation, and machine learning research.
+We find that of the papers sampled, approximately 75 per cent of papers from arXiv, 67 per cent of papers from bioRxiv, 79 per cent of papers from medRxiv, and 85 per cent of papers from SocArXiv contain neither open data nor open code markers.
+A summary of our main results is contained in Figure \@ref(fig:flowchart).
+Examining trends over time, we find that the proportion of pre-prints containing open data or code markers has fluctuated but shown no obvious trend throughout the pandemic.
+We also find that the presence of open data or open code markers seems to have little association with a pre-print's subsequent publication, and the subset of sampled pre-prints that have been published contains approximately the same proportion of papers with these markers.
+<!-- Finally, we briefly examine the presence of open data and code markers in specific types of pre-prints, namely modelling, simulation, and machine learning research. -->
 
-The remainder of this paper is structured as follows: in Section \@ref(data-and-methodology) we discuss the process of constructing our dataset through retrieving pre-prints from the medRxiv repository and mining them for open data and open code markers.
-In Sections \@ref(model) and \@ref(results) we explore some key findings in this raw data and explore some logistic regression models that support these findings.
+```{r flowchart, fig.cap = "Summary of process and main results", out.width="90%", fig.align = "center"}
+DiagrammeR::grViz("digraph {
+
+graph [layout = dot, rankdir = TB]
+
+# define the global styles of the nodes. We can override these in box if we wish
+node [shape = rectangle]
+
+all [label =  'All pre-prints posted between 28 January 2020 and 30 June 2021']
+onlycovid [label =  'Those about COVID-19']
+arxivcovidcount [label =  'arXiv: 4,250 pre-prints']
+biorxivcovidcount [label =  'bioRxiv: 4,146 pre-prints']
+medrxivcovidcount [label =  'medRxiv: 13,194 pre-prints']
+socarxivcovidcount [label =  'SocArXiv: 478 pre-prints']
+randomsample [label =  'Random sampling stratified by repository']
+arxivsamplecount [label =  'arXiv: 1,000 pre-prints']
+biorxivsamplecount [label =  'bioRxiv: 1,000 pre-prints']
+medrxivsamplecount [label =  'medRxiv: 1,500 pre-prints']
+socarxivsamplecount [label =  'SocArXiv: 478 pre-prints']
+opencodeanddata [label =  'Those with markers of open code or open data']
+arxivopencount [label =  'arXiv: 248 pre-prints']
+biorxivopencount [label =  'bioRxiv: 326 pre-prints']
+medrxivopencount [label =  'medRxiv: 320 pre-prints']
+socarxivopencount [label =  'SocArXiv: 73 pre-prints']
+
+# edge definitions with the node IDs
+all -> onlycovid -> {arxivcovidcount biorxivcovidcount medrxivcovidcount socarxivcovidcount} -> randomsample -> {arxivsamplecount biorxivsamplecount medrxivsamplecount socarxivsamplecount} -> opencodeanddata -> {arxivopencount biorxivopencount medrxivopencount socarxivopencount}
+}")
+```
+
+The remainder of this paper is structured as follows: in Section \@ref(methodology) we discuss the process of constructing our dataset through retrieving pre-prints from the arXiv, bioRxiv, medRxiv, and SocArXiv repositories and mining them for open data and open code markers.
+In Section \@ref(results), we present the results and key findings of this process.
 Finally, in Section \@ref(discussion) we discuss the implications of these findings in the broader context of reproducibility and science during the COVID-19 pandemic, as well as next steps to expand on our findings and questions raised in the research process.
 
-# Data and Methodology
+# Methodology
 
-## Overview
+## Pre-print metadata
 
-Our primary dataset consists of information extracted from the arXiv, bioRxiv, medRxiv, and SocArXiv pre-print repositories.
-We downloaded pre-prints that contained various keywords related to COVID-19 (a full list of these is available in Appendix \@ref(keywords)), and then identified the availability of open code and open data using the Open Data Detection in Publications (ODDPub) text mining algorithm [@citePDDPub] in the `oddpub` package [@citeODDPubpackage].
+Our primary dataset consists of pre-print metadata extracted from the arXiv, bioRxiv, medRxiv, and SocArXiv pre-print repositories via their respective Application Programming Interfaces (APIs).
+This metadata varies by repository, but generally includes the following information: title, abstract, author(s), date created, research field, DOI, version number, corresponding author, corresponding author's institutional affiliation, published DOI (if the pre-print has since been published in a peer-reviewed journal), and download link.
+The data collection process was conducted separately for COVID-19 and pre-COVID-19 papers.
 
-We constructed this dataset by first creating a local copy of the repository using the repository API.
-We identified papers related to the COVID-19 pandemic through several keyword searches to create our dataset of papers and associated metadata.
-This metadata varies by repository, but generally includes the following information: title, abstract, author(s), date posted, research field, DOI, version number, corresponding author, corresponding author's institutional affiliation, and published DOI (if the pre-prints has since been published in a peer-reviewed journal).
-In the case of SocArXiv there are additionally fields that are self-reported by the submitting author about the availability of code and data.
+For COVID-19-related pre-prints, we first created a local copy of each repository containing all metadata for pre-prints posted between 1 January, 2020, and 30 June, 2021.
+In the case of SocArXiv there are fields that are self-reported by the submitting author about the availability of code and data.
+We classified individual pre-prints as "COVID-19-related" based on whether they contained one or more of the following terms in their title or abstract (case insensitive): "COVID-19", "COVID 19", "corona virus", "coronavirus", "coronavirus-2", "SARS-CoV-2", "SARSCoV-2", and "2019-nCoV".
+We then randomly sampled pre-prints for further analysis, except for SocArXiv, for which we analyzed all pre-prints that matched the above criteria, because there were only 478.
 
-We then checked these pre-prints for open data and code markers using the ODDPub algorithm.
-This required downloading each pre-print as a PDF and then converting the PDFs to text files.
-We then conducted the open data and open code detection procedure.
-This involved searching for keywords and other markers of open data and open code such as references to GitHub repositories and similar.
-A full listing of these markers is included in Appendix \@ref(markers).
+For pre-COVID-19 pre-prints, we created a local copy of each repository containing all metadata for pre-prints posted between 1 January, 2019, and December 31, 2019.
+Since medRxiv was launched in June 2019, we used all pre-print data from the latter half of 2019.
+We then randomly sampled 1,200 pre-prints from each repository's dataset for analysis, except for medRxiv for which only 913 pre-prints were available over this time.
+
+## Open data and code detection
+
+We checked our sampled pre-prints for open data and code markers using the Open Data Detection in Publications (ODDPub) text mining algorithm [@citePDDPub] within the `oddpub` R package [@citeODDPubpackage].
+This required downloading each pre-print as a PDF, which we did using `heapsofpapers` [@citealexandermafouz] and then converting the PDFs to text files.
+Some papers from SocArXiv were only available in Word document format (.docx) and were downloaded as such and then converted to text format.
+We then conducted the open data and open code detection procedure, which involved searching for keywords and other markers of open data and open code availability.
 This was conducted using the `open_data_search()` function from the `oddpub` package.
+What constitutes open code or open data is complicated and discipline specific.
+The details of the `oddpub` approach are available in @citePDDPub.
+The general criteria are that specific mention should be made of where the data and code are located, and that data should be as close to raw as possible.
+Our work was conducted using the statistical programming language R [@citeR].
 
-The result of this process is a dataset indicating the presence of open data or open code markers in each pre-print (with a binary variable for each marker, and the relevant open data or open code statements when applicable).
-Our final analysis dataset was formed by joining these two datasets together, typically using the DOI or the unique filename, to form a dataset including all original, qualitative metadata information for each pre-print alongside its open data and open code status and markers.
+The result of this process is a dataset indicating the presence of open data or open code markers in each pre-print (with a logical vector for each marker, followed by the relevant open data or open code statements where applicable).
+Our final dataset was formed by joining this output with the original sample metadata, typically using the DOI or the unique file name, to form a dataset including all original metadata for each pre-print alongside its open data and open code status and markers.
+
+Although SocArXiv's metadata contained author-reported information concerning data and code availability for each pre-print, we elected to use the results of the ODDPub algorithm in our analysis to ensure comparability of results between pre-prints from all repositories.
+<!-- Notable discrepancies between the ODDPub algorithm and authors' self-reported data and code availability are documented in Appendix \@ref(socarxivissues). -->
 
@@
 
-all <- rbind(just_arxiv, just_medRxiv, just_bioRxiv)
+just_socarxiv <- 
+  socarxiv_open_data_results  %>% 
+  select(date_created) %>%
+  rename(date = "date_created") %>%
+  mutate(date = as.Date(date), type = "SocArXiv")
+
+all <- rbind(just_arxiv, just_medRxiv, just_bioRxiv, just_socarxiv)
 
@@
   filter(year(date) >= 2020) %>%
+  filter(date < "2021-06-30") %>% 
   ggplot(aes(x = month)) + 
   geom_histogram(aes(fill = type), stat="count", position = "dodge") + 
-  labs(title = "Pre-prints posted per month",
-       subtitle = "Total of 3,379 relevant pre-prints on arXiv, 3,031 on bioRxiv, 9,929 on medRxiv",
+  labs(title = "COVID-19-related pre-prints posted per month",
+       subtitle = "Total of 4,250 relevant pre-prints on arXiv, 4,146 on bioRxiv, 13,194 on medRxiv, and \n478 on SocArXiv.",
        x = "Month",
@@
        fill = "Repository") +
+  scale_x_date(breaks=as.Date(c("2020-01-01","2020-07-01", "2021-01-01")),
+                   labels=c("Jan 2020", "Jul 2020", "Jan 2021")) +
   theme_minimal() +
-  scale_fill_manual(values = wes_palette("Darjeeling1"))
+  scale_fill_manual(values = wes_palette("Darjeeling1")) +
+  facet_wrap(~type,
+             scales = "free_y")
 ```
 
-## Summary statistics
+# Results
 
-The number of pre-prints posted per month increased dramatically between January and May 2020, reaching its maximum in May and subsequently decreasing.
-The number of pre-prints posted since August 2020 has remained reasonably steady at around 750 per month (Figure \@ref(fig:monthly-papers-total)).
+## All pre-prints related to COVID-19
+
+The number of pre-prints posted per month increased in the first half of 2020 across all repositories, reaching a maximum sometime between April and June (depending on repository) and subsequently decreasing.
+The number of pre-prints posted monthly since August 2020 has remained reasonably steady, with the exception of medRxiv, which experienced an increase to nearly 1,000 pre-prints posted in March 2021 (Figure \@ref(fig:monthly-papers-total)).
 For context, COVID-19 was declared a pandemic by the World Health Organization (WHO) on March 11, 2020, at which point the number of cases globally had just surpassed 118,000 (primarily in east Asia) and the virus had been reported in 114 countries [@citeWHOtimeline].
 
-Broadly, we are unable to find markers of either open data or open code for around 81 per cent of the 1,200 sampled pre-prints.
-The remaining 19 per cent of pre-prints was comprised of 4 per cent of the sample containing markers for open code, 8 per cent of the sample with markers for open data, and 7 per cent of the sample with markers for both open data and open code (Table \@ref(tab:summarycounts-medRxiv)).
+## Open data and code
 
-```{r summarycounts-medRxiv}
-# open data/open code count summary table
+From the collection of all pre-prints related to COVID-19, we randomly sampled 3,910 pre-prints to analyze, stratified by repository.
+This sample is broken down as follows: 1,500 from medRxiv, 1,000 from arXiv, 1,000 from bioRxiv, and 478 from SocArXiv.
+Broadly, we are unable to find markers of either open data or open code for 3,011 pre-prints or approximately 76 per cent of our sample (Table \@ref(tab:summarycounts-repositories)).
+Of the remaining pre-prints, 7 per cent contained open code markers only, 10 per cent contained open data markers only, and 8 per cent included markers of both open data and open code.
+
+When differentiated by repository, we observe that open data and code markers were absent from 75 per cent of the sampled arXiv pre-prints, 67 per cent of the sampled bioRxiv pre-prints, 79 per cent of the sampled medRxiv pre-prints, and 85 per cent of all COVID-19-related SocArXiv pre-prints.
+The distribution of the remaining portion of pre-prints also varies by repository (Table \@ref(tab:summarycounts-repositories)).
+Notably, 28 per cent of sampled pre-prints from bioRxiv contained open data markers and 22 per cent of sampled arXiv pre-prints contained markers of open code, the highest proportions of any repository for each type of marker.
+Our results are similar to @mcguinness2021descriptive, who focus on medRxiv and find that 23 per cent describe open data.
+
+```{r, summarycounts-overall}
+just_arxiv <-
+  arxiv_open_data_results  %>%
+  select(submitted, is_open_data, is_open_code) %>%
+  mutate(submitted = as.Date(submitted)) %>%
+  mutate(type = "arXiv") %>%
+  rename(date = submitted)
+
+just_medRxiv <-
   med_open_data_results  %>%
+  mutate(date = as.Date(date))  %>%
+  select(date, is_open_data, is_open_code) %>%
+  mutate(type = "medRxiv")
+
+just_bioRxiv <-
+  bio_open_data_results  %>%
+  select(date, is_open_data, is_open_code) %>%
+  mutate(date = as.Date(date)) %>%
+  mutate(type = "bioRxiv")
+
+just_socarxiv <-
+  socarxiv_open_data_results  %>%
+  select(date_created, is_open_data, is_open_code) %>%
+  rename(date = "date_created") %>%
+  mutate(type = "SocArXiv")
+
+all <- rbind(just_arxiv, just_medRxiv, just_bioRxiv, just_socarxiv)
+
+all_total <- 
+  all %>%
   count(is_open_data, is_open_code) %>%
@@
          is_open_code = ifelse(is_open_code == 0, "No", "Yes")) %>%
-  kable(col.names = c("Open data markers", "Open code markers", "Count", "Proportion of total"),
-        caption = "Counts and proportions of open data and code markers in medRxiv sample",
-        booktabs = TRUE,
-        digits = 2)
+  select(is_open_data, is_open_code, n, prop_total)
 ```
 
-```{r summarycounts-bioRxiv}
+```{r summarycounts-repositories}
 # open data/open code count summary table
-bio_open_data_results %>% 
+
+all_by_type <- 
+  all %>%
+  group_by(type) %>%
   count(is_open_data, is_open_code) %>%
@@
          is_open_code = ifelse(is_open_code == 0, "No", "Yes")) %>%
+  ungroup() %>%
+  select(is_open_data, is_open_code, n, prop_total)
+
+rbind(all_total, all_by_type) %>% 
   kable(col.names = c("Open data markers", "Open code markers", "Count", "Proportion of total"),
-        caption = "Counts and proportions of open data and code markers in bioRxiv sample",
+        caption = "Count and proportions of open data and code markers by pre-print repository",
         booktabs = TRUE,
-        digits = 2)
+        digits = 2,
+        format.args = list(big.mark = ",")) %>%
+  group_rows(index = c("Total" = 4, "arXiv" = 4, "bioRxiv" = 4, "medRxiv" = 4, "SocArXiv" = 4))
 ```
@@
 The distribution of total sampled pre-prints and sampled pre-prints with open data or code markers roughly follows that of COVID-19-related pre-prints posted in general (Figure \@ref(fig:monthly-papers-condition-stack)).
-The proportion of pre-prints with open data or code has fluctuated over time but shows no consistent overall increase or decrease throughout the course of the pandemic, nor in conjunction with increases or decreases in the total number of pre-prints posted to medRxiv (Figure \@ref(fig:monthly-proportion-of-open)).
-In our dataset, only one pre-print was sampled for the month of January 2020.
-This pre-print contained neither open data nor open code markers, thus the 0 per cent rate of open data and code for this month will be treated as an outlier, and removed modelling purposes.
+The proportion of pre-prints with open data or code has fluctuated over time but shows no consistent overall increase or decrease throughout the course of the pandemic, nor in conjunction with increases or decreases in the total number of pre-prints posted to any given repository.
+In our datasets, very few (if any) pre-prints were sampled for the month of January 2020.
+None of these pre-prints contained open data or open code markers, thus the 0 per cent rate of open data and code for this month across all repositories should be considered an outlier.
 
-```{r monthly-papers-condition-stack, fig.cap = "Number of pre-prints related to COVID-19 sampled from medRxiv, distinguished by presence of open data or code markers", out.width="90%", fig.align = "center"}
+```{r monthly-papers-condition-stack, fig.cap = "Number of sampled pre-prints related to COVID-19, distinguished by presence of open data or code markers", out.width="90%", fig.align = "center"}
 # Number of papers for each open data/code status per month
-open_status <- 
+open_status_med <- 
   med_open_data_results %>% 
   select(title, date, is_open_code, is_open_data) %>% 
-  mutate(condition = is_open_data + is_open_code)
+  mutate(condition = is_open_data + is_open_code, repo = "medRxiv")
+
+open_status_bio <- 
+  bio_open_data_results %>% 
+  select(title, date, is_open_code, is_open_data) %>% 
+  mutate(condition = is_open_data + is_open_code, repo = "bioRxiv", date = as.character(date))
+
+open_status_arxiv <- 
+  arxiv_open_data_results %>% 
+  select(title, submitted, is_open_code, is_open_data) %>% 
+  mutate(condition = is_open_data + is_open_code, repo = "arXiv", date = as.character(submitted) %>% str_sub(end = 10)) %>%
+  select(title, date, is_open_code, is_open_data, condition, repo)
+
+open_status_socarxiv <- 
+  socarxiv_open_data_results %>% 
+  select(title, date_created, is_open_code, is_open_data) %>% 
+  mutate(condition = is_open_data + is_open_code, repo = "SocArXiv", date = as.character(date_created)) %>%
+  select(title, date, is_open_code, is_open_data, condition, repo)
+
+open_status <- rbind(open_status_med, open_status_bio, open_status_arxiv, open_status_socarxiv)
+
+open_status$date <- as.Date(open_status$date)
 open_status$condition[open_status$condition == 2] <- "Both"
@@
   labs(fill = "Type of marker") +
-  scale_x_discrete(breaks=c("2020-01-01","2020-04-01","2020-07-01", "2020-10-01", "2021-01-01"), 
-                   labels=c("Jan 2020","Apr 2020","Jul 2020", "Oct 2020", "Jan 2021")) +
+  scale_x_discrete(breaks=c("2020-01-01","2020-07-01", "2021-01-01"), 
+                   labels=c("Jan 2020", "Jul 2020", "Jan 2021")) +
   ylab("Number of pre-prints") +
   xlab("Month") +
-  labs(title="Sampled pre-prints by month", subtitle="medRxiv, Total = 1,200") +
-  theme_minimal()
+  labs(title="Sampled pre-prints by month", subtitle="Sample size from arXiv is 1,000, from bioRxiv is 1,000, from medRxiv is 1,500, and from \nSocArXiv is 410. Note the different y-axes.") +
+  theme_minimal() +
+  scale_fill_manual(values = wes_palette("Darjeeling1")) +
+  facet_wrap(~repo,
+             scales = "free_y")
 ```
@@
 # Proportion of papers posted with open data or open code each month
-colors <- c("Open Data" = "blue", "Open Code" = "green")
 med_month_sum_cov <- 
   med_open_data_results %>% 
+  mutate(date = as.Date(date)) %>%
   group_by(month = floor_date(date, "month")) %>% 
-  summarise(count=n(), prop_open_code = sum(is_open_code)/n(), prop_open_data = sum(is_open_data)/n()) %>% 
-  mutate(num_days = days_in_month(month),
-         daily_rate = count/num_days)
-med_month_sum_cov %>%
-  ggplot() +
-  geom_line(data = med_month_sum_cov, aes(month, prop_open_data, color = "Open data")) +
-  geom_line(data = med_month_sum_cov, aes(month, prop_open_code, color = "Open code")) +
-  ggtitle("Proportion of sampled pre-prints with open data or code markers") +
-  labs(colour = "Type of marker",
-       x = "Month",
-       y = "Proportion of pre-prints") + 
-  theme_minimal()
+  summarise(count = n(), "Open Code" = mean(is_open_code), "Open Data" = mean(is_open_data)) %>% 
+  mutate(daily_rate = count/days_in_month(month), repo = "medRxiv")
+
+bio_month_sum_cov <- 
+  bio_open_data_results %>% 
+  mutate(date = as.Date(date)) %>%
+  group_by(month = floor_date(date, "month")) %>% 
+  summarise(count = n(), "Open Code" = mean(is_open_code), "Open Data" = mean(is_open_data)) %>% 
+  mutate(daily_rate = count/days_in_month(month), repo = "bioRxiv")
+
+arxiv_month_sum_cov <- 
+  arxiv_open_data_results %>% 
+  group_by(month = floor_date(submitted, "month")) %>% 
+  summarise(count = n(), "Open Code" = mean(is_open_code), "Open Data" = mean(is_open_data)) %>% 
+  mutate(daily_rate = count/days_in_month(month), repo = "arXiv")
+
+socarxiv_month_sum_cov <- 
+  socarxiv_open_data_results %>% 
+  group_by(month = floor_date(as.Date(date_created), "month")) %>% 
+  summarise(count = n(), "Open Code" = mean(is_open_code), "Open Data" = mean(is_open_data)) %>% 
+  mutate(daily_rate = count/days_in_month(month), repo = "SocArXiv")
+
+month_sum_cov <- rbind(med_month_sum_cov, bio_month_sum_cov, arxiv_month_sum_cov, socarxiv_month_sum_cov) %>%
+  pivot_longer(cols = c("Open Data", "Open Code")) %>%
+  filter(value != 1) # Removes outliers where small number of papers in a month was sampled and both had open data/code
+
+# TODO: Fix date labels, facet_wrap labels
+# month_sum_cov %>%
+#   ggplot() +
+#   geom_line(data = month_sum_cov, aes(month, value, color = repo)) +
+#   ggtitle("Proportion of sampled pre-prints with open data or code markers") +
+#   labs(colour = "Repository",
+#        x = "Month",
+#        y = "Proportion of pre-prints") + 
+#   theme_minimal() +
+#   scale_color_manual(values = wes_palette("Darjeeling1")) +
+#   facet_wrap(~name)
 ```
@@
 
-In Table \@ref(tab:open-published-summary) we disaggregate pre-prints by whether there is an indication that it was published.
-We find that the proportion of pre-prints with open data or code markers among those that have been published is approximately five per cent lower compared with pre-prints that have not been published (Table \@ref(tab:open-published-summary)).
+Our metadata also contains an indication of whether a pre-print has been published, in the form of a DOI linking to the corresponding published paper.
+The proportion of pre-prints that have been published varies by repository (Table \@ref(tab:published-sample-summary)).
+Notably, of all COVID-19-related pre-prints in our dataset, approximately 30 per cent of those posted to bioRxiv and nearly one third of those posted to medRxiv were published.
+This is high in comparison to the proportions from arXiv and SocArXiv, and although this might suggest that COVID-19-related pre-prints in biomedical fields have received greater attention overall than pre-prints from other fields, our results in Section \@ref(pre-pandemic-pre-prints) suggest that this pattern pre-dates the pandemic.
+
+```{r published-sample-summary}
+med_published <- 
+  med_results %>% 
+  select(title, date, published) %>% 
+  mutate(repo = "medRxiv", published = as.numeric(!is.na(published)))
+
+bio_published <- 
+  bio_results %>% 
+  select(title, date, published) %>% 
+  mutate(repo = "bioRxiv", published = as.numeric(!is.na(published)))
+
+arxiv_published <- 
+  all_arxiv_results %>% 
+  select(title, submitted, doi) %>%
+  mutate(doi = as.numeric(!is.na(doi)), repo = "arXiv") %>%
+  rename(published = doi, date = submitted)
+
+socarxiv_published <- 
+  socarxiv_open_data_results %>% 
+  select(title, date_created, links.doi) %>%
+  mutate(links.doi = as.numeric(!is.na(links.doi)), repo = "SocArXiv") %>%
+  rename(published = links.doi, date = date_created)
+
+published <- rbind(med_published, bio_published, arxiv_published, socarxiv_published)
+
+published %>% 
+  group_by(repo) %>% 
+  summarise(`Published pre-prints` = sum(published), 
+            `Proportion published` = mean(published) %>% round(2)) %>%
+  kable(caption = "Counts and proportion of published COVID-19 pre-prints in each repository",
+        col.names = c("Repository", "Published pre-prints", "Proportion published"),
+        format.args = list(big.mark = ","))
+```
+
+In Table \@ref(tab:open-published-summary) we disaggregate sampled pre-prints by whether there is an indication of publication.
+We find that the proportion of pre-prints with open data or code markers among those that have been published is roughly the same as pre-prints that have not been published, differing by only a few percentage points.
 
 ```{r open-published-summary}
-published_open_status <- 
+# Maybe find a way to use the data frames constructed above instead of constructing new ones?
+
+# ArXiv variables: doi
+# SocArXiv variables: links.doi
+
+med_published_open_status <- 
   med_open_data_results %>% 
   select(title, date, published, is_open_code, is_open_data) %>% 
-  mutate(condition = is_open_data + is_open_code)
+  mutate(condition = is_open_data + is_open_code, repo = "medRxiv")
+
+bio_published_open_status <- 
+  bio_open_data_results %>% 
+  select(title, date, published, is_open_code, is_open_data) %>% 
+  mutate(condition = is_open_data + is_open_code, repo = "bioRxiv")
+
+arxiv_published_open_status <- 
+  arxiv_open_data_results %>% 
+  select(title, submitted, doi, is_open_code, is_open_data) %>%
+  mutate(doi = as.numeric(!is.na(doi)), condition = is_open_data + is_open_code, repo = "arXiv") %>%
+  rename(published = doi, date = submitted)
+
+socarxiv_published_open_status <- 
+  socarxiv_open_data_results %>% 
+  select(title, date_created, links.doi, is_open_code, is_open_data) %>%
+  mutate(links.doi = as.numeric(!is.na(links.doi)), condition = is_open_data + is_open_code, repo = "SocArXiv") %>%
+  rename(published = links.doi, date = date_created)
+
+published_open_status <- rbind(med_published_open_status, bio_published_open_status, arxiv_published_open_status, socarxiv_published_open_status)
+
 published_open_status$condition[published_open_status$condition == 2] <- "Both"
@@
 published_open_status %>%
-  count(published, condition) %>% 
-  pivot_wider(names_from = condition, values_from = n) %>%
-  mutate(published = ifelse(published == 0, "No", "Yes"), `Proportion with either/both`= round((`Open data` + `Open code` + Both)/(`Open data` + `Open code` + Both + Neither), 2)) %>%
-  rename(Published = published) %>%
+  count(repo, published, condition) %>% 
+  pivot_wider(names_from = condition, values_from = n, values_fill = 0) %>%
+  mutate(Published = ifelse(published == 0, "No", "Yes"), `Proportion with neither`= round((`Neither`)/(`Open data` + `Open code` + Both + Neither), 2)) %>%
+  select(Published, Both, Neither, `Open code`, `Open data`, `Proportion with neither`) %>%
   kable(caption = "Counts and proportions of open data markers by whether the pre-print was published",
-        booktabs = TRUE)
+        booktabs = TRUE,
+        format.args = list(big.mark = ",")) %>%
+  group_rows(index = c("arXiv" = 2, "bioRxiv" = 2, "medRxiv" = 2, "SocArXiv" = 2))
 ```
 
-There was a low number of papers that had markers of either open data or code in both those that were published and those that were not published (Figure \@ref(fig:open-published-stack)).
+```{r open-published-stack, fig.cap= "Number of pre-prints in sample with open data or open code markers \nby publication status", out.width="90%", fig.align = "center"}
 
-```{r open-published-stack, fig.cap= "Number of pre-prints in sample with open data or open code markers by publication status", out.width="90%", fig.align = "center"}
-published_open_status$published[published_open_status$published == 0] <- "Published"
-published_open_status$published[published_open_status$published == 1] <- "Unpublished"
+# TODO: are these graphs even necessary?
 
-published_open_status %>% 
-  # mutate(published = ifelse(published == 0, "Unpublished", "Published")) +
-  ggplot() + 
-  geom_bar(aes(x = published, fill=factor(condition, levels = c("Neither", "Open code", "Open data", "Both")), position = "stack")) +
-  labs(fill = "Type of marker",
-       y = "Number of pre-prints",
-       x = "Publication status") +
-  ggtitle("Pre-prints by publication status") +
-  theme_minimal()
+# published_open_status$published[published_open_status$published == 0] <- "Published"
+# published_open_status$published[published_open_status$published == 1] <- "Unpublished"
+
+# published_open_status %>% 
+#   mutate(published = ifelse(published == 0, "Unpublished", "Published")) %>%
+#   ggplot() + 
+#   geom_bar(aes(x = published, fill=factor(condition, levels = c("Neither", "Open code", "Open data", "Both")), position = "stack")) +
+#   labs(fill = "Type of marker",
+#        y = "Number of pre-prints",
+#        x = "Publication status") +
+#   ggtitle("Pre-prints by publication status") +
+#   theme_minimal() +
+#   facet_wrap(~repo) + 
+#   scale_fill_manual(values = wes_palette("Darjeeling1"))
+
 ```
 
-It is important to note that our dataset imperfectly characterizes publication.
-In particular, it does not have the publication details for some papers that were published.
-And even if it were a perfect record, there is a publication lag (estimated at an average of around 60 days) that may skew the results [@kwon2020].
+Our dataset likely imperfectly characterizes publication and does not have the publication details for some papers that were published.
+And even if it were a perfect record, there is a publication lag (estimated at an average of around 60 days for COVID-19-related pre-prints, although that varies by discipline) that may especially skew the results for pre-prints in the latter portion of our sample [@kwon2020].
 
-## Type of pre-print
+## Pre-pandemic pre-prints
 
-There are a variety of different types of pre-prints on medRxiv, including those focused on machine learning, modelling, and simulation.
-It may be that there are differences in open science practices between these.
-For instance, in papers related to simulation there is less likely to be issues around sharing code.
+To examine the influence of the COVID-19 pandemic on open science practices during the pandemic, we analyzed pre-prints posted between January and December 2019 from each of the four repositories using the same process as was done for the COVID-19-related pre-prints.
+Since medRxiv was founded in June 2019, all pre-prints posted in the latter half of 2019 were analyzed (a total of 913).
+For all other repositories, a random sample of 1,200 was taken from all non-COVID-19-related pre-prints posted in the relevant date range.
 
-To characterize the pre-prints by type, we performed keyword searches within the titles and abstracts of our dataset to examine potential differences in the prevalence of open data or code for specific types of papers.
-There were 21 sampled pre-prints that included the term 'machine learning'.
-Of those, the proportion of pre-prints with open data or code markers rose to 38 per cent, double that of the sample overall (Table \@ref(tab:summary-by-type)).
-Similarly, keywords relating to simulation appeared in 80 sampled pre-prints and keywords related to modelling appeared in over one-third of our sampled pre-prints.
-The latter two categories did not contain pre-prints with open data or code markers at a rate much higher than the general sample, with 22 and 24 per cent of each type of paper containing either open data or open code markers compared to 19 per cent overall.
-However, due to the significant role that modelling has played in the context of COVID-19, it is likely that a simple keyword search does not have the resolution needed to properly characterize this subset, it is it possible that it only contains pre-prints presenting their own, novel, models.
+```{r 2019-results-med-arxiv, out.width="90%", fig.align='center', fig.cap = "Number of pre-prints posted per month to arXiv, bioRxiv, medRxiv, and SocArXiv in 2019"}
+bio_2019 <- bio_2019_results %>%
+  select(date) %>%
+  mutate(type = "bioRxiv")
 
-```{r stack-by-type, fig.cap= "Number of pre-prints in sample with open data or open code markers by type", out.width="90%", fig.align = "center"}
+med_2019 <- med_2019_open_data_results %>%
+  select(date) %>%
+  mutate(type = "medRxiv")
 
-# Number of open data/code papers by keyword for different types
-paper_type_keywords <- 
-  med_open_data_results %>% select(title, abstract, date, is_open_code, is_open_data) %>% 
-  mutate(condition = is_open_data + is_open_code)
-paper_type_keywords$condition[paper_type_keywords$condition == 2] <- "Both"
-paper_type_keywords$condition[paper_type_keywords$condition == 0] <- "Neither"
-paper_type_keywords$condition[paper_type_keywords$condition == 1 & open_status$is_open_code == 1] <- "Open code"
-paper_type_keywords$condition[paper_type_keywords$condition == 1 & open_status$is_open_data == 1] <- "Open data"
-paper_type_keywords$`Machine Learning` <- str_detect( paper_type_keywords$title, "machine learning") | 
-                                          str_detect( paper_type_keywords$abstract, "machine learning")
-paper_type_keywords$Simulation <- str_detect( paper_type_keywords$title, "simulate|simulation|simulating") | 
-                                    str_detect( paper_type_keywords$abstract, "simulate|simulation|simulating|simulated")
-paper_type_keywords$modelling <- str_detect( paper_type_keywords$title, "modelling|model|models|modeling") | 
-                                str_detect( paper_type_keywords$abstract, "modelling|model|models|modeling")
-paper_type_keywords <- paper_type_keywords %>% 
-  pivot_longer(cols = c("Machine Learning", "Simulation", "modelling"), names_to = "Type", values_to = "Value") %>%
-  filter(Value == TRUE)
+socarxiv_2019 <- socarxiv_metadata_2019 %>%
+  select(date_created) %>%
+  mutate(type = "socArXiv") %>%
+  rename(date = date_created)
 
-# # Plot
-# paper_type_keywords %>% ggplot() + 
-#   geom_bar(aes(x = Type, fill=factor(condition, levels = c("Neither", "Open code", "Open data", "Both")), position = "stack")) +
-#   labs(fill = "Type of marker") +
-#   scale_x_discrete(labels=c("Machine learning", "Modelling", "Simulation")) +
-#   ylab("Number of pre-prints") +
-#   xlab("Month") +
-#   ggtitle("Sampled pre-prints by type") +
-#   theme_minimal()
+arxiv_2019 <- all_arxiv_2019_results %>%
+  select(submitted) %>%
+  mutate(type = "arXiv") %>%
+  rename(date = submitted)
+
+all_2019 <- rbind(arxiv_2019, bio_2019, med_2019, socarxiv_2019)
+
+all_2019 %>% 
+  mutate(month = floor_date(date, "month")) %>% 
+  # filter(year(date) >= 2020) %>% 
+  ggplot(aes(x = month, fill = type)) + 
+  geom_histogram(stat="count", position = "dodge2") +
+  labs(title = "Pre-prints posted per month, 2019",
+       subtitle = "Total of 150,018 pre-prints on arXiv and 31,752 on bioRxiv, 913 pre-prints on \n medRxiv and 1,614 on SocArXiv",
+       x = "Month",
+       y = "Number of pre-prints",
+       fill = "Repository") +
+  theme_minimal() +
+  scale_fill_manual(values = wes_palette("Darjeeling1")) +
+  facet_wrap(~type,
+             scales = "free_y") +
+  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
 ```
 
-```{r summary-by-type}
-paper_type_keywords %>% 
-  count(Type, condition) %>% 
-  pivot_wider(names_from = condition, values_from = n, values_fill = 0) %>% 
-  mutate(Type = if_else(Type == "modelling", "Modelling", Type),
-         Type = if_else(Type == "Machine Learning", "Machine learning", Type),
-         ) %>% 
-  mutate(`Proportion with either/both`= round((`Open data` + `Open code` + Both)/(`Open data` + `Open code` + Both + Neither), 2)) %>%
-  kable(caption = "Counts and proportions of open data markers by the type of pre-print",
-        booktabs = TRUE)
+```{r 2019-open-results}
+just_2019_medRxiv <-
+  med_2019_open_data_results  %>%
+  mutate(date = as.Date(date), type = "medRxiv")  %>%
+  select(date, is_open_data, is_open_code, type)
+
+just_2019_bioRxiv <-
+  bio_2019_open_data_results  %>%
+  select(date, is_open_data, is_open_code) %>%
+  mutate(date = as.Date(date), type = "bioRxiv")
+
+just_2019_socarxiv <- 
+  socarxiv_2019_open_data_results %>%
+  select(date_created, is_open_data, is_open_code) %>%
+  mutate(date = as.Date(date_created), type = "socArXiv") %>%
+  select(date, is_open_data, is_open_code, type)
+
+just_2019_arxiv <-
+  arxiv_2019_open_data_results %>%
+  select(submitted, is_open_data, is_open_code) %>%
+  mutate(date = as.Date(submitted), type = "arXiv") %>%
+  select(date, is_open_data, is_open_code, type)
+
+all_2019 <- rbind(just_2019_medRxiv, just_2019_bioRxiv, just_2019_socarxiv, just_2019_arxiv)
+
+all_2019_total <- 
+  all_2019 %>%
+  count(is_open_data, is_open_code) %>%
+  mutate(prop_total = n / sum(n)) %>%
+  mutate(is_open_data = ifelse(is_open_data == 0, "No", "Yes"),
+         is_open_code = ifelse(is_open_code == 0, "No", "Yes")) %>%
+  select(is_open_data, is_open_code, n, prop_total)
+
+all_2019_by_type <- 
+  all_2019 %>%
+  group_by(type) %>%
+  count(is_open_data, is_open_code) %>%
+  mutate(prop_total = n / sum(n)) %>%
+  mutate(is_open_data = ifelse(is_open_data == 0, "No", "Yes"),
+         is_open_code = ifelse(is_open_code == 0, "No", "Yes")) %>%
+  ungroup() %>%
+  select(is_open_data, is_open_code, n, prop_total)
+
+rbind(all_2019_total, all_2019_by_type) %>% 
+  kable(col.names = c("Open data markers", "Open code markers", "Count", "Proportion of total"),
+        caption = "Count and proportions of open data and code markers by pre-print repository in 2019 sample",
+        booktabs = TRUE,
+        digits = 2,
+        format.args = list(big.mark = ",")) %>%
+  group_rows(index = c("Total" = 4, "arXiv" = 4, "bioRxiv" = 4, "medRxiv" = 4, "SocArXiv" = 4))
+
 ```
 
-# Model
+Between June and December 2019, the number of pre-prints posted to medRxiv monthly saw an overall increase, which may be expected as the repository gained recognition and popularity in the medical research community (Figure \@ref(fig:2019-results-med-arxiv)).
+The number of pre-prints posted monthly to bioRxiv also saw a slight overall increase throughout 2019, while the number of those posted to arXiv and SocArXiv fluctuated throughout the year (Figure \@ref(fig:2019-results-med-arxiv)).
+Due to its relative immaturity at the beginning of the COVID-19 pandemic, a significant portion of medRxiv's overall usage has been dedicated to COVID-19-related research.
+In total, 21,647 pre-prints were posted to medRxiv between June 2019 and 30 June, 2021, 13,194 of which (approximately 61 per cent) relate to COVID-19.
 
-We are interested in understanding firstly whether open data and open code became more likely over time, and secondly whether the likelihood that at pre-print ends up published is related to provision of open data and open code.
-To examine these questions we estimate Equation \@ref(eq:first) by fitting two separate generalized linear models with open data and open code markers as binary variables (representing their presence or absence in a pre-print) that are explained as functions of the date at which a pre-print was posted.
+Of the analyzed pre-prints from 2019, 93 per cent of those posted to arXiv, 63 per cent of those posted to bioRxiv, 75 per cent of those posted to medRxiv, 92 per cent of those posted to SocArXiv showed no indication of open data or open code (Table \@ref(tab:2019-published)).
+Both the bioRxiv and medRxiv rates are approximately four per cent lower than the corresponding proportions of COVID-19-related pre-prints, suggesting that the analyzed pre-prints from 2019 may contain an overall higher prevalence of open data and code markers than pre-prints concerning COVID-19.
+Specifically, we found that open data availability in medRxiv pre-prints was significantly associated with a pre-pandemic registration date ($\chi$^2^ = 4.8508, p < 0.005), as was open code availability for bioRxiv pre-prints ($\chi$^2^ = 14.491, p < 0.005).
+This would suggest that open data and code practices may have suffered in the context of COVID-19.
+Or it may be something that is backfilled after posting.
 
-\begin{equation} 
-\mbox{Open data/code} = \beta_0 + \beta_1 \mbox{date} (\#eq:first)
-\end{equation}
+On the other hand, the analyzed arXiv and SocArXiv pre-prints from 2019 contain a lower proportion of open data and code markers overall than their COVID-19-related counterparts, with a decrease of seven per cent in sampled SocArXiv pre-prints and 18 per cent in sampled arXiv papers.
+For these repositories, the presence of both open data and open code markers was significantly associated with registration during the pandemic, suggesting that pre-prints related to COVID-19 in arXiv and SocArXiv may have more consistently adhered to open science practices than their pre-pandemic counterparts ($\chi$^2^ = 93.124, arXiv open data;  $\chi$^2^ = 106.88, arXiv open code; $\chi$^2^ = 12.303, SocArXiv open data; $\chi$^2^ = 8.1598, SocArXiv open code; p < 0.005).
 
-We then estimate Equation \@ref(eq:second), again by fitting separate generalized linear models, looking at whether a pre-print is published, based on whether it had open code/data.
+```{r 2019-published}
+med_published_2019 <- 
+  med_2019_open_data_results %>% 
+  select(title, date, published) %>% 
+  mutate(repo = "medRxiv", published = as.numeric(published))
 
-\begin{equation} 
-\mbox{Open data/code} = \beta_0 + \beta_1 \mbox{date} (\#eq:second)
-\end{equation}
+bio_published_2019 <- 
+  bio_2019_results %>% 
+  select(title, date, published) %>% 
+  mutate(repo = "bioRxiv", published = as.numeric(!is.na(published)))
 
-We estimate our models in the statistical programming language `R` [@citeR], using the function `glm()`.
+socarxiv_published_2019 <- 
+  socarxiv_metadata_2019 %>% 
+  select(title, date_created, links.doi) %>% 
+  mutate(repo = "socArXiv", published = as.numeric(!is.na(links.doi))) %>%
+  rename(date = date_created) %>%
+  select(title, date, published, repo)
 
-Our estimates (Table \@ref(tab:datatimemodel)) indicate, in greater clarity, the negligible role time appears to play in the proportion of pre-prints with open data or open code posted to medRxiv.
-Both models output negligibly small, non-significant coefficients on the date term, indicating limited influence of the date a pre-print was posted on its likelihood of containing open data or code markers.
+arxiv_published_2019 <-
+  all_arxiv_2019_results %>%
+  select(title, submitted, doi) %>%
+  mutate(repo = "arXiv", published = as.numeric(!is.na(doi))) %>%
+  rename(date = submitted) %>%
+  select(title, date, published, repo)
 
-```{r, echo=FALSE, warning=FALSE, message=FALSE, results = 'asis'}
-data_on_date <- glm(is_open_data ~ date, family = binomial, data = med_open_data_results)
-code_on_date <- glm(is_open_code ~ date, family = binomial, data = med_open_data_results)
+published_2019 <- rbind(med_published_2019, bio_published_2019, socarxiv_published_2019, arxiv_published_2019)
 
-published_on_data <- glm(published ~ as.factor(is_open_data), family = binomial, data = med_open_data_results)
-published_on_code <- glm(published ~ as.factor(is_open_code), family = binomial, data = med_open_data_results)
-
-stargazer(data_on_date, code_on_date, published_on_data, published_on_code,
-          header = FALSE,
-          title = 'Estimation results',
-          dep.var.labels = c('Open data', 'Open code', 'Published'),
-          covariate.labels=c('Date', 'Has open data', 'Has open code', 'Constant'),
-          report=('vc*s'),
-          no.space = TRUE,
-          digits=2,
-          digits.extra=1,
-          notes.append = TRUE,
-          notes.align = "l",
-          ci = FALSE,
-          ci.level=0.95,
-          label = "tab:datatimemodel"
-          )
+published_2019 %>% 
+  group_by(repo) %>% 
+  summarise(`Published pre-prints` = sum(published), `Proportion published` = mean(published) %>% round(2)) %>%
+  kable(caption = "Counts and proportion of published COVID-19 pre-prints in each repository, 2019",
+        col.names = c("Repositiory", "Published pre-prints", "Proportion published"),
+        format.args = list(big.mark = ","))
 ```
 
-We get similar results for publication status as a function of open data or open code presence; however we do see a significant (p < 0.05) coefficient indicating that the presence of open code markers may have a negative influence on a pre-print's likelihood of eventual publication.
-It is unrealistic to assume that this means pre-prints with open code are less likely to be published on the basis of their code alone.
-There may be common cause factors involved, such as a disinclination of journals to publish purely computational work as has been the case with pre-print repositories like bioRxiv [@kwon2020].
+```{r, 2019-open-publishing}
+med_2019_published_open_status <- 
+  med_2019_open_data_results %>% 
+  select(title, date, published, is_open_code, is_open_data) %>% 
+  mutate(condition = is_open_data + is_open_code, repo = "medRxiv")
 
-# Results
+bio_2019_published_open_status <- 
+  bio_2019_open_data_results %>% 
+  select(title, date, published, is_open_code, is_open_data) %>% 
+  mutate(condition = is_open_data + is_open_code, repo = "bioRxiv")
 
-Less than 20 per cent of sampled pre-prints indicated any open data or code markers.
-Of those that did contain markers, 4 per cent contained open code markers only, 8 per cent contained open data markers only, and 7 per cent contained both open data and code markers.
+socarxiv_2019_published_open_status <- 
+  socarxiv_2019_open_data_results %>%
+  mutate(published = !is.na(links.doi) %>% as.numeric()) %>%
+  select(title, date_created, published, is_open_code, is_open_data) %>%
+  rename(date = date_created) %>%
+  mutate(condition = is_open_data + is_open_code, repo = "socArXiv")
 
-We find that time has little influence over the likelihood of a pre-print to have open data or code markers.
-In the context of the COVID-19 pandemic, this means that the prevalence of open data and code markers has not consistently increased nor decreased over the course of the pandemic, and also appears to be unimpacted by the monthly rate of pre-prints posted to medRxiv (which increased dramatically between January and May 2020 and has fluctuated since).
-On one hand, it is encouraging to note that open data and code does not appear to have suffered in times of high publication rates, namely April through July 2020.
-On the other hand, one might hope that more data has become openly available throughout the course of the pandemic, or that the rate of availability of open data or code has improved as the scientific community has recognized the importance of global collaboration in combating the pandemic, neither of which appear to be the case.
+arxiv_2019_published_open_status <- 
+  arxiv_2019_open_data_results %>%
+  mutate(published = !is.na(doi) %>% as.numeric()) %>%
+  select(title, submitted, published, is_open_code, is_open_data) %>%
+  rename(date = submitted) %>%
+  mutate(condition = is_open_data + is_open_code, repo = "arXiv")
 
-The presence of open data or code markers does not appear to have significant influence over whether or not a pre-print posted to medRxiv has subsequently been published in a peer reviewed journal, however the proportion of published pre-prints with open data or code markers appears to be slightly lower than those that have not been published (15 per cent versus 20 per cent).
-This is not necessarily a significant result given the size of our sample and the potential inaccuracies in the medRxiv API's attempts to identify publication, however it does provide a potential area of further study.
+published_2019_open_status <- rbind(med_2019_published_open_status, bio_2019_published_open_status, socarxiv_2019_published_open_status, arxiv_2019_published_open_status)
 
-The proportion of pre-prints with open data or code markers is significantly higher among pre-prints with keywords indicating machine learning-based research.
-This is a somewhat anticipated result, as machine learning tends to rely more heavily on computational and code-focused methodology, however the subset of sampled pre-prints with keywords relating to simulation is very small.
-On the other hand, the prevalence of pre-prints with open data or code markers only saw a slight increase in the subset of pre-prints with either modelling or simulation keywords.
-Since the pandemic has seen a rise in scientific and public focus on epidemiological modelling, it is likely that not all papers showing keywords for modelling actually propose their own models which would account for the minimal increase of open data and code markers in this context.
+published_2019_open_status$condition[published_2019_open_status$condition == 2] <- "Both"
+published_2019_open_status$condition[published_2019_open_status$condition == 0] <- "Neither"
+published_2019_open_status$condition[published_2019_open_status$condition == 1 & published_2019_open_status$is_open_code == 1] <- "Open code"
+published_2019_open_status$condition[published_2019_open_status$condition == 1 & published_2019_open_status$is_open_data == 1] <- "Open data"
+
+published_2019_open_status %>%
+  count(repo, published, condition) %>% 
+  pivot_wider(names_from = condition, values_from = n, values_fill = 0) %>%
+  mutate(Published = ifelse(published == 0, "No", "Yes"), `Proportion with neither`= round((`Neither`)/(`Open data` + `Open code` + Both + Neither), 2)) %>%
+  select(Published, Both, Neither, `Open code`, `Open data`, `Proportion with neither`) %>%
+  kable(caption = "Counts and proportions of open data markers by whether the pre-print was published, 2019",
+        booktabs = TRUE,
+        format.args = list(big.mark = ",")) %>%
+  group_rows(index = c("arXiv" = 2, "bioRxiv" = 2, "medRxiv" = 2, "socArXiv" = 2))
+```
+
+Examining publication rates for pre-pandemic papers, we observe that 41 per cent of pre-prints posted to arXiv, 64 per cent of pre-prints posted to bioRxiv, 61 per cent of pre-prints posted to medRxiv, and 37 per cent of pre-prints posted to SocArXiv during 2019 were eventually peer reviewed and published (Table \@ref(tab:2019-published)).
+These rates are at least double those of the COVID-19-related pre-prints posted in each repository during 2020 and 2021.
+When disaggregated by open data and code status, we find that published and unpublished pre-prints contain open data and code markers in similar proportions (Table \@ref(tab:2019-open-publishing)).
+This mimics the behaviour of published and unpublished COVID-19-related pre-prints.
 
@@
 
-- Add reference somewhere to that paper about the numbers: https://link.springer.com/article/10.1007/s11192-020-03675-3
-- Add reference somewhere to that paper about keyword search and then analysis. Was it a Gary King one?
-
 ## On the role of transparency and reproducibility
 
-Transparency and reproducibility are hallmarks of quality scientific research.
-Open data and open code contribute greatly to both in allowing the scientific community to more easily verify the authenticity of purported scientific discovery and its supporting evidence, which is especially important in cases where scientific research may quickly and directly impact clinical practice or policy such as during the COVID-19 pandemic.
-Among a myriad of other impacts on biomedical research, COVID-19 has dramatically increased the popularity of pre-prints from both a production and consumption stand-point.
-The number of COVID-19 pre-prints posted to medRxiv increased dramatically in the early stages of the pandemic while non-COVID-19 pre-print rates remained consistent.
-The same trends were apparent in abstracts accessed by medRxiv users, where COVID-19 pre-print abstracts were viewed over 15 times the rate of non-COVID-19 pre-print abstracts [@citeFraser].
-For these reasons, it is more important now than ever to examine open science standards and reproducibility within pre-print repositories.
+Transparency and reproducibility are hallmarks of quality scientific research due to their relationship with independent verification [@Stodden2020Theme].
+Open data and open code contribute to both by allowing the scientific community to more easily verify the authenticity of purported scientific discoveries and their supporting evidence.
+This is especially important in cases where scientific research may quickly and directly impact clinical practice or public policy, such as research on the COVID-19 pandemic.
+Among many other impacts on the research landscape, COVID-19 has increased the popularity of pre-prints from both a production and consumption standpoint.
+The number of COVID-19 pre-prints posted to medRxiv increased in the early stages of the pandemic, while non-COVID-19 pre-print numbers were largely as expected.
+The same trends were apparent in abstracts accessed by medRxiv users, where COVID-19 pre-print abstracts were viewed over 15 times more than non-COVID-19 pre-print abstracts [@citeFraser].
+For these reasons, it is important to examine open science standards and reproducibility within pre-print repositories.
 
-Open data is generally accepted to be beneficial to the scientific process, and to a paper's reproducibility potential, hence it is concerning that over 80 per cent of pre-prints in our sample contained no open data markers.
+Open data is generally accepted to be beneficial to the scientific process and to a paper's reproducibility potential, hence it is concerning that around 75 per cent of pre-prints in our sample contained no open data markers.
 This concern is slightly mitigated by recognition of challenges in working with biomedical data compared with data in other fields, notably privacy and ethics concerns when working with personal data [@Floca2014].
-The COVID-19 pandemic has seen an uptake in open science practices globally, as evidenced by the creation of open data repositories such as the dashboard maintained by the Center for Systems Science and Engineering at Johns Hopkins University [@citeCSSE] or the large number of publishers who have removed paywalls from published COVID-19 research [@gill2020].
-An important next step may compare open data and code availability in COVID-19 pre-prints with those from other topics posted to medRxiv to examine whether the pandemic has increased transparency from the previous norm.
+The COVID-19 pandemic has seen open science initiatives, as evidenced by the creation of open data repositories such as the dashboard maintained by the Center for Systems Science and Engineering at Johns Hopkins University [@citeCSSE] or the large number of publishers who have removed paywalls from published COVID-19 research [@gill2020].
+While the intention at the start of the pandemic was that there would be 'clear statements regarding the availability of underlying data' [@citeWellcome] some retractions of work have been based on 'unreliable or nonexistent data' [@da2021optimizing].
+SocArXiv asks submitters to make explicit the degree of openness in the data, and this is something that could be easily adopted by other pre-print repositories.
 
-Open code as an open science marker is much more context and field-dependent, as not all biomedical research papers will rely on computational methods for their analyses.
-However, in pre-prints where code comprises a large portion of the methodology or results, posting it openly to repositories like GitHub contributes greatly to a pre-print's potential reproducibility.
-This gains importance as computational methods become increasingly popular in the rush to form predictions about emerging situations with limited data or laboratory research, which was the case for modelling studies in the early days of the COVID-19 pandemic (CITE).
-We also see growing concern over the quality and consequences of this sort of research, with bioRxiv not allowing purely computational work [@kwon2020].
+Open code as an open science marker is context and field-dependent, as not all biomedical research papers will rely on computational methods for their analyses.
+However, in pre-prints where code comprises a large portion of the methodology or results, posting it openly to repositories like GitHub contributes to a pre-print's potential reproducibility.
+This is important when computational methods are used to form predictions about emerging situations with limited data or laboratory research, which was the case for modelling studies in the early days of the COVID-19 pandemic.
+We also see growing concern over the quality and consequences of this sort of research, with bioRxiv no longer allowing purely computational work [@kwon2020].
 
-## The role of of pre-print repositories
+The other concern is the adverse selection issue caused by meeting the open science aims of sharing code and data.
+Authors that share their data and code open their work up to criticism.
+If authors who make their data and code available make similar mistakes to authors who choose to not publish their data and code, it is more likely that the mistake would not be noticed in the case where data and code were not published.
+The current system is biased against those who follow best practice.
+@mcguinness2021descriptive advocate for '(s)trict editorial policies that mandate data sharing', and other changed norms are needed.
 
-Many concerns have arisen from the unprecedented rate at which COVID-19 research has been posted and consumed via pre-print repositories, particularly in the early stages of the pandemic [@raynaud2021].
-Any rushed scientific research has potential to skip (or at least place less precedence on) quality open science practices, thus it may be reasonable to expect a decrease of open data or code markers in the pre-prints posted during times of increased overall posting to medRxiv.
-In our analysis, we found little relationship between time posted and likelihood of having open data or code markers with the proportion of papers containing these markers fluctuating greatly from month to month and no apparent decrease during periods of increased publication.
-This suggests that open science practices are more highly influenced by other factors, perhaps training, publication bias, or the nature of the paper itself.
-On the other hand, we do not see an overall long-term increase in either open data or open code markers throughout our year of analysis which we may expect in the context of the aforementioned open science movements the pandemic has fostered.
-Although not pre-print specific, @else2020 found that overall research output has fluctuated between different fields and topics (namely modelling disease spread, public health, diagnostics and testing, mental health, and hospital mortality) throughout different stages of the pandemic which may account for some of the fluctuation and overall lack of linear trend over the course of the year.
+## The role of pre-print repositories
+
+There has been a large amount of research on COVID-19 [@da2021publishing].
+Many concerns have arisen from the rate at which COVID-19 research has been posted and consumed via pre-print repositories, particularly in the early stages of the pandemic [@raynaud2021].
+Rushed scientific research has potential to skip (or at least place less precedence on) open science practices, thus it may be reasonable to expect a decrease in open data or code markers in the initial few months of the pandemic.
+We found little relationship between date posted and likelihood of having open data or code markers, with the proportion of pre-prints containing these markers fluctuating from month to month.
+This suggests that open science practices are more influenced by other factors, perhaps including training, publication bias, or the nature of the pre-print itself.
+On the other hand, we do not see an overall long-term increase in either open data or open code markers throughout our period of analysis, which we may have expected in the context of the open science movements the pandemic has fostered.
+Although not pre-print specific, @else2020 found that overall research output has fluctuated between different fields and topics (namely modelling disease spread, public health, diagnostics and testing, mental health, and hospital mortality) throughout different stages of the pandemic, which may account for some of the fluctuation and overall lack of noticeable trend in our sample.
 
 To emphasize the ongoing need for open data and code in modelling a pandemic, we consider two high profile epidemiological models that emerged in early 2020.
-Modelling was conducted by Imperial College London (ICL) [@ferguson2020] and the Institute for Health Metrics and Evaluation (IHME) at the University of Washington [@murray2020], and both papers were initially posted to pre-print repositories.
+Modelling was conducted by Imperial College London (ICL) [@ferguson2020] and the Institute for Health Metrics and Evaluation (IHME) at the University of Washington [@murray2020], and both were initially posted to pre-print repositories.
 The ICL model went on to become the most cited pre-print as of December 2020 [@else2020], and both had significant influence over policy and public health decisions worldwide [@adam2020].
 An independent review of these two models by @jin2020 found that while code and data were openly available for both, only the ICL model was reproducible due to limited transparency on the underlying methodology of the IHME model.
-The open-source nature of these papers was fundamental to reproduction attempts and is a great example of the need for open data and code in reproducing COVID-19 research, particularly in evaluating pre-prints as they begin to influence public decision-making.
+The open-source nature of these models was fundamental to reproduction attempts and is an example of the need for open data and code in COVID-19 research, particularly as pre-prints influence public decision-making.
 
-In the context of the above factors, it was disheartening in our analysis to find that the proportion of modelling- and simulation-related pre-prints with open data or code increased only marginally from that of the entire sample.
-One might hope that modelling papers should universally be subject to the same analysis as conducted by @jin2020 as for the examples above, which is made possible by the availability of relevant code and data.
-Although our analysis was not particularly robust, this shows a need for future investigation and potential overall improvement in open science standards for these types of pre-prints (of course subject to the data and code considerations already discussed).
-This need is again emphasized by the new-found speed at which pre-print articles may gain public, media, and political attention in the context of the pandemic.
+In the context of the above factors, it was encouraging to find in our analysis that the proportion of pre-prints with open data or code posted to arXiv increased from 7 per cent pre-pandemic to 25 per cent for COVID-19-related pre-prints.
+This pattern, however, was not observed among the analyzed bioRxiv and medRxiv pre-prints, and may just reflect the nature of COVID-19 pre-prints.
+With many pre-prints from these repositories still pertaining to epidemiological modelling, one might hope that they should universally be subject to the same analysis as conducted by @jin2020 as for the examples above, which is made possible by the availability of relevant code and data.
+Our analysis suggests a need for future investigation and potential overall improvement in open science standards for these types of pre-prints (subject to the data and code considerations already discussed).
+This need is again emphasized by the new-found speed at which pre-prints may gain public, media, and political attention in the context of the pandemic, particularly those from medRxiv and bioRxiv.
 
@@
 
-Beyond pre-prints, COVID-19 has had great influence over publication and peer review processes as well, with expedited review timelines for COVID-19 papers at the expense of longer waits for other scientific research [@else2020].
-Needless to say, it is important that open data and code standards be maintained in published work as well.
-Our findings in this regard were two-fold: that open data or code markers do not appear to directly influence a pre-print's eventual publication, and that a lower proportion of published papers contain either open data or code markers than the general sample.
-Both of these raise concerns over publication bias, the potential that journals have favored novel yet less transparent or reproducible papers over those with null results but a high standard of open science practices.
-Concerns have already been raised through systemic reviews of COVID-19 publications [@raynaud2021], and oversights in data accessibility have led to high profile retractions of publications in the past, for example two papers from The Lancet and the New England Journal of Medicine that were withdrawn due to concerns over the private nature of their underlying dataset [@ledford2020].
+Beyond pre-prints, COVID-19 has influenced publication and peer review processes, with timelines for COVID-19 papers being expedited at the expense of longer waits for other scientific research [@else2020].
+It is important that open data and code standards be maintained in published work as well.
+In our sample, published pre-prints contain open data or code markers in similar proportions to their unpublished counterparts, a pattern that was present for pre-prints related to COVID-19 and those posted in 2019.
+This appears initially to alleviate some concerns over the relationship between open data and publication bias, that is, the potential that journals have favoured novel yet less transparent or reproducible papers over those with null results but a high standard of open science practices.
+However, publication bias is complex and this result should be approached with caution.
+Concerns have already been raised through systemic reviews of COVID-19 publications [@raynaud2021], and oversights in data accessibility have led to high profile retractions of publications in the past; for example, papers from *The Lancet* and the *New England Journal of Medicine* which were withdrawn due to concerns over the private nature of their underlying dataset [@ledford2020].
 
 In all fields of science, increasing access to data and code used for pre-printed or published research is a step in the direction of more transparent, reproducible, and reliable research.
-The ongoing COVID-19 pandemic has created a novel, constantly changing scientific culture that should be navigated with the utmost care so as to uphold standards of scientific practice for both the research community and the safety of the general public.
-Our analysis shows that there is much improvement to be made in the areas of open data and code availability within COVID-19 pre-print papers on medRxiv.
+The ongoing COVID-19 pandemic has created a novel, constantly changing scientific culture that should be navigated with care to uphold standards of scientific practice for both the research community and the safety of the public.
+Our analysis shows that there is room for improvement in the areas of open data and code availability within COVID-19 pre-print papers on arXiv, bioRxiv, medRxiv, and SocArXiv.
 
-Demand for timely research / results in high frequency as epidemic is rapidly evolving.
-Preprints are more efficient at doing this because there is no time spent on peer review.
-However, they also allow lesser-known researchers to better disperse their research, because of the possibility that fast-tracked peer review may be biased towards established researchers.
+There is demand for timely research and high frequency results because the pandemic rapidly evolves.
+Pre-prints are efficient in this role because there is no time spent on peer review.
+They also allow lesser-known researchers to better disperse their research because of the possibility that fast-tracked peer review may be biased towards established researchers.
 While there is a clear need for pre-prints, the point remains that they do not go through the peer review process.
-This question of quality and validity is particularly pertinent in the COVID-19 context because poorly validated results and false information may spread quickly, and have real effects.
-We are not saying that peer review implies that a paper is of a high-quality, we are instead saying that the provision of code and data alongside the preprint goes some way to allowing others to trust the findings of pre-prints even though they have not been peer-reviewed.
-One way this could be encouraged would be for pre-print repositories to have authors characterize the extent to which they have adopted open science practices as part of their submission.
-Although those papers that do not adopt these practices should not be rejected from pre-print repositories, greater clarity around this would be useful and might move the state-of-the-art forward.
+This question of quality and validity is particularly pertinent in the COVID-19 context because poorly validated results and false information may spread quickly and have real effects.
+We are not saying that peer review implies that a paper is of a high-quality; we are instead saying that the provision of code and data alongside the pre-print goes some way to allowing others to trust the findings of pre-prints, even though they have not been peer-reviewed.
+One way this could be encouraged would be for all pre-print repositories to have authors characterize the extent to which they have adopted open science practices as part of their submission, in the same way that is done in SocArXiv.
+Although those pre-prints that do not adopt these practices should not be rejected from pre-print repositories, greater clarity around this would be useful and might move the state-of-the-art forward.
 
@@
 
-In this paper we consider only pre-prints from medRxiv, but this analysis can and should be extended to other pre-print repositories including bioRxiv and arXiv.
+<!-- In this paper we consider only pre-prints from medRxiv, but this analysis can and should be extended to other pre-print repositories including bioRxiv and arXiv.
 The `medrxivr` package [@citemedrxivr] can be used with the bioRxiv API as well, and our code can be modified to conduct the same scraping and text mining procedure as was used for medRxiv data.
+-->
 
-We also wish to expand our analysis to consider the geographic distribution of research and the potential influence of different practices and policies concerning open science as pre-prints vary by location.
-This is pertinent to our current paper as the epicenter of the virus spread (and thus of scientific output) has shifted throughout the pandemic which has implications for our time-based analysis.
+We wish to expand our analysis to consider the geographic distribution of research and the potential influence of different practices and policies concerning open science as pre-prints vary by location.
+This is important because the epicenter of the pandemic changed throughout the pandemic, which has implications for our time-based analysis.
 
-An important weakness to note is the potential presence of false negatives in indicators of publication in our dataset.
-@abdill2019 estimate that the false-negative rate may be as high as 37.5 per cent for data pulled from the bioRxiv API, meaning analysis of published papers may represent only a fraction of those that have actually been published.
-It is unclear to what extent this is the case for medRxiv or what bias may exist in the subset of pre-prints for which publication was detected, as it is likely that this process relies on title-based text matching [@abdill2019].
-It is also likely that some of our more recent sampled pre-prints will be published in future which we could not account for at the time of our data collection.
+An important weakness is the potential presence of false negatives in indicators of publication in our dataset.
+@abdill2019 estimate that the false-negative rate may be as high as 37.5 per cent for data pulled from the bioRxiv API, meaning analysis of published papers may represent only a fraction of those that have been published.
+It is unclear to what extent this is the case for other repositories or what bias may exist in the subset of pre-prints for which publication was detected, because it is likely that this process relies on title-based text matching [@abdill2019].
+It is also likely that some of our more recent sampled pre-prints will be published in the future which we could not account for at the time of our data collection.
+
+Our paper depends on search responses from the various repositories, which are based on our selection of keywords.
+Our selection of keywords is not exhaustive, for instance, perhaps 'the pandemic' could result in additional papers.
+Future work could make this keyword approach more systematic, for instance following @king2017computer.
 
 We also recognize that this analysis relies heavily on text-based analysis which was not verified directly in most cases and may lead to higher levels of uncertainty.
-In future, we wish to take smaller sub-samples to validate factors like publication status or paper topic beyond simple keyword searches or API output.
+The `oddpub` package was built to analyze biomedical publications and it may be that some of the differences that we find between repositories are due to this.
+In future, we wish to take smaller sub-samples to validate factors like publication status, paper topic, and open code and data status, beyond the approaches that we used here.
 
@@
 
-# (APPENDIX) Appendix {-}
+<!-- # (APPENDIX) Appendix {-}  -->
 
-# Keywords
+<!-- # Markers -->
 
-Insert details on keyword search used to identify COVID-19 papers.
+<!-- Insert details on what markers the `oddpub::open_data_search()` uses. Include info here directly from package documentation (i.e. keywords/phrases used for text parsing)? -->
 
-# Markers
+<!-- # SocArXiv differences {#socarxivissues} -->
 
-Insert details on what markers the `oddpub::open_data_search()` uses. Include info here directly from package documentation (i.e. keywords/phrases used for text parsing)?
+<!-- Insert details... -->
 
-# Classification
-
-Insert details on keyword search used for machine learning/modelling/simulation
-
-\newpage
+<!-- \newpage -->
 

### 2021-07-22 outputs/paper/paper.tex
As submitted to arXiv

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
  \usepackage{amssymb}
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Reproducibility of COVID-19 pre-prints},
  pdfauthor={Annie Collins; Rohan Alexander},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\title{Reproducibility of COVID-19 pre-prints\thanks{We thank Amy Farrow, Jessica Gronsbell, Monica Alexander, and Thomas William Rosenthal for helpful comments. Collins thanks CANSSI Ontario and Monica Alexander for financial support. Code and data are available at: \url{https://github.com/anniecollins/reproducibility_markers_in_covid19_preprints}.}}
\author{Annie Collins\footnote{University of Toronto.} \and Rohan Alexander\footnote{University of Toronto, \href{mailto:rohan.alexander@utoronto.ca}{\nolinkurl{rohan.alexander@utoronto.ca}}.}}
\date{22 July 2021}

\begin{document}
\maketitle
\begin{abstract}
To examine the reproducibility of COVID-19 research, we create a dataset of pre-prints posted to arXiv, bioRxiv, medRxiv, and SocArXiv between 28 January 2020 and 30 June 2021 that are related to COVID-19. We extract the text from these pre-prints and parse them looking for keyword markers signalling the availability of the data and code underpinning the pre-print. For the pre-prints that are in our sample, we are unable to find markers of either open data or open code for 75 per cent of those on arXiv, 67 per cent of those on bioRxiv, 79 per cent of those on medRxiv, and 85 per cent of those on SocArXiv. We conclude that there may be value in having authors categorize the degree of openness of their pre-print as part of the pre-print submissions process, and more broadly, there is a need to better integrate open science training into a wide range of fields.
\end{abstract}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Scientists use open repositories of papers to disseminate their research more quickly than is possible in traditional journals or conference proceedings. These repositories, such as arXiv, bioRxiv, medRxiv, and SocArXiv, are a critical component of scientific communication and a lot of research builds on the pre-prints posted there. Pre-print repositories have been especially important during the 2019 novel coronavirus (COVID-19) pandemic and the changes it has imposed on the scientific community (Else 2020). The centrality of pre-prints to science means that it is important that the results that are posted are credible. These repositories are not peer-reviewed, and, in general, anyone with appropriate academic credentials can submit a pre-print.

Neither peer-review nor credentials are a panacea nor a guarantee of quality. And the gate-keeping and slow publication times of traditional journals mean pre-print repositories are important. But it is important that scientists impose standards on themselves, and arguably repositories have a role to play here. Following Weissgerber et al. (2021), we examine pre-prints about COVID-19 posted to arXiv, bioRxiv, medRxiv, and SocArXiv from 28 January 2020 through to 30 June 2021. By way of background, each of these four repositories has a different focus: arXiv is general, bioRxiv focuses on biological sciences, medRxiv focuses on health sciences, and SocArXiv focuses on social sciences. We search for markers of open science as indicators of reproducibility, specifically open data and open code.

We find that of the papers sampled, approximately 75 per cent of papers from arXiv, 67 per cent of papers from bioRxiv, 79 per cent of papers from medRxiv, and 85 per cent of papers from SocArXiv contain neither open data nor open code markers. A summary of our main results is contained in Figure \ref{fig:flowchart}. Examining trends over time, we find that the proportion of pre-prints containing open data or code markers has fluctuated but shown no obvious trend throughout the pandemic. We also find that the presence of open data or open code markers seems to have little association with a pre-print's subsequent publication, and the subset of sampled pre-prints that have been published contains approximately the same proportion of papers with these markers.

\begin{figure}

{\centering \includegraphics[width=0.9\linewidth]{paper_files/figure-latex/flowchart-1}

}

\caption{Summary of process and main results}\label{fig:flowchart}
\end{figure}

The remainder of this paper is structured as follows: in Section \ref{methodology} we discuss the process of constructing our dataset through retrieving pre-prints from the arXiv, bioRxiv, medRxiv, and SocArXiv repositories and mining them for open data and open code markers. In Section \ref{results}, we present the results and key findings of this process. Finally, in Section \ref{discussion} we discuss the implications of these findings in the broader context of reproducibility and science during the COVID-19 pandemic, as well as next steps to expand on our findings and questions raised in the research process.

\hypertarget{methodology}{%
\section{Methodology}\label{methodology}}

\hypertarget{pre-print-metadata}{%
\subsection{Pre-print metadata}\label{pre-print-metadata}}

Our primary dataset consists of pre-print metadata extracted from the arXiv, bioRxiv, medRxiv, and SocArXiv pre-print repositories via their respective Application Programming Interfaces (APIs). This metadata varies by repository, but generally includes the following information: title, abstract, author(s), date created, research field, DOI, version number, corresponding author, corresponding author's institutional affiliation, published DOI (if the pre-print has since been published in a peer-reviewed journal), and download link. The data collection process was conducted separately for COVID-19 and pre-COVID-19 papers.

For COVID-19-related pre-prints, we first created a local copy of each repository containing all metadata for pre-prints posted between 1 January, 2020, and 30 June, 2021. In the case of SocArXiv there are fields that are self-reported by the submitting author about the availability of code and data. We classified individual pre-prints as ``COVID-19-related'' based on whether they contained one or more of the following terms in their title or abstract (case insensitive): ``COVID-19,'' ``COVID 19,'' ``corona virus,'' ``coronavirus,'' ``coronavirus-2,'' ``SARS-CoV-2,'' ``SARSCoV-2,'' and ``2019-nCoV.'' We then randomly sampled pre-prints for further analysis, except for SocArXiv, for which we analyzed all pre-prints that matched the above criteria, because there were only 478.

For pre-COVID-19 pre-prints, we created a local copy of each repository containing all metadata for pre-prints posted between 1 January, 2019, and December 31, 2019. Since medRxiv was launched in June 2019, we used all pre-print data from the latter half of 2019. We then randomly sampled 1,200 pre-prints from each repository's dataset for analysis, except for medRxiv for which only 913 pre-prints were available over this time.

\hypertarget{open-data-and-code-detection}{%
\subsection{Open data and code detection}\label{open-data-and-code-detection}}

We checked our sampled pre-prints for open data and code markers using the Open Data Detection in Publications (ODDPub) text mining algorithm (Riedel, Kip, and Bobrov 2020) within the \texttt{oddpub} R package (Riedel 2019). This required downloading each pre-print as a PDF, which we did using \texttt{heapsofpapers} (Alexander and Mahfouz 2021) and then converting the PDFs to text files. Some papers from SocArXiv were only available in Word document format (.docx) and were downloaded as such and then converted to text format. We then conducted the open data and open code detection procedure, which involved searching for keywords and other markers of open data and open code availability. This was conducted using the \texttt{open\_data\_search()} function from the \texttt{oddpub} package. What constitutes open code or open data is complicated and discipline specific. The details of the \texttt{oddpub} approach are available in Riedel, Kip, and Bobrov (2020). The general criteria are that specific mention should be made of where the data and code are located, and that data should be as close to raw as possible. Our work was conducted using the statistical programming language R (R Core Team 2020).

The result of this process is a dataset indicating the presence of open data or open code markers in each pre-print (with a logical vector for each marker, followed by the relevant open data or open code statements where applicable). Our final dataset was formed by joining this output with the original sample metadata, typically using the DOI or the unique file name, to form a dataset including all original metadata for each pre-print alongside its open data and open code status and markers.

Although SocArXiv's metadata contained author-reported information concerning data and code availability for each pre-print, we elected to use the results of the ODDPub algorithm in our analysis to ensure comparability of results between pre-prints from all repositories.

\begin{figure}

{\centering \includegraphics[width=0.9\linewidth]{paper_files/figure-latex/monthly-papers-total-1}

}

\caption{Number of pre-prints related to COVID-19}\label{fig:monthly-papers-total}
\end{figure}

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{all-pre-prints-related-to-covid-19}{%
\subsection{All pre-prints related to COVID-19}\label{all-pre-prints-related-to-covid-19}}

The number of pre-prints posted per month increased in the first half of 2020 across all repositories, reaching a maximum sometime between April and June (depending on repository) and subsequently decreasing. The number of pre-prints posted monthly since August 2020 has remained reasonably steady, with the exception of medRxiv, which experienced an increase to nearly 1,000 pre-prints posted in March 2021 (Figure \ref{fig:monthly-papers-total}). For context, COVID-19 was declared a pandemic by the World Health Organization (WHO) on March 11, 2020, at which point the number of cases globally had just surpassed 118,000 (primarily in east Asia) and the virus had been reported in 114 countries (World Health Organization 2020).

\hypertarget{open-data-and-code}{%
\subsection{Open data and code}\label{open-data-and-code}}

From the collection of all pre-prints related to COVID-19, we randomly sampled 3,910 pre-prints to analyze, stratified by repository. This sample is broken down as follows: 1,500 from medRxiv, 1,000 from arXiv, 1,000 from bioRxiv, and 478 from SocArXiv. Broadly, we are unable to find markers of either open data or open code for 3,011 pre-prints or approximately 76 per cent of our sample (Table \ref{tab:summarycounts-repositories}). Of the remaining pre-prints, 7 per cent contained open code markers only, 10 per cent contained open data markers only, and 8 per cent included markers of both open data and open code.

When differentiated by repository, we observe that open data and code markers were absent from 75 per cent of the sampled arXiv pre-prints, 67 per cent of the sampled bioRxiv pre-prints, 79 per cent of the sampled medRxiv pre-prints, and 85 per cent of all COVID-19-related SocArXiv pre-prints. The distribution of the remaining portion of pre-prints also varies by repository (Table \ref{tab:summarycounts-repositories}). Notably, 28 per cent of sampled pre-prints from bioRxiv contained open data markers and 22 per cent of sampled arXiv pre-prints contained markers of open code, the highest proportions of any repository for each type of marker. Our results are similar to McGuinness and Sheppard (2021), who focus on medRxiv and find that 23 per cent describe open data.

\begin{table}

\caption{\label{tab:summarycounts-repositories}Count and proportions of open data and code markers by pre-print repository}
\centering
\begin{tabular}[t]{llrr}
\toprule
Open data markers & Open code markers & Count & Proportion of total\\
\midrule
\addlinespace[0.3em]
\multicolumn{4}{l}{\textbf{Total}}\\
\hspace{1em}No & No & 3,011 & 0.76\\
\hspace{1em}No & Yes & 262 & 0.07\\
\hspace{1em}Yes & No & 391 & 0.10\\
\hspace{1em}Yes & Yes & 314 & 0.08\\
\addlinespace[0.3em]
\multicolumn{4}{l}{\textbf{arXiv}}\\
\hspace{1em}No & No & 752 & 0.75\\
\hspace{1em}No & Yes & 115 & 0.12\\
\hspace{1em}Yes & No & 34 & 0.03\\
\hspace{1em}Yes & Yes & 99 & 0.10\\
\addlinespace[0.3em]
\multicolumn{4}{l}{\textbf{bioRxiv}}\\
\hspace{1em}No & No & 674 & 0.67\\
\hspace{1em}No & Yes & 44 & 0.04\\
\hspace{1em}Yes & No & 207 & 0.21\\
\hspace{1em}Yes & Yes & 75 & 0.07\\
\addlinespace[0.3em]
\multicolumn{4}{l}{\textbf{medRxiv}}\\
\hspace{1em}No & No & 1,180 & 0.79\\
\hspace{1em}No & Yes & 89 & 0.06\\
\hspace{1em}Yes & No & 108 & 0.07\\
\hspace{1em}Yes & Yes & 123 & 0.08\\
\addlinespace[0.3em]
\multicolumn{4}{l}{\textbf{SocArXiv}}\\
\hspace{1em}No & No & 405 & 0.85\\
\hspace{1em}No & Yes & 14 & 0.03\\
\hspace{1em}Yes & No & 42 & 0.09\\
\hspace{1em}Yes & Yes & 17 & 0.04\\
\bottomrule
\end{tabular}
\end{table}

The distribution of total sampled pre-prints and sampled pre-prints with open data or code markers roughly follows that of COVID-19-related pre-prints posted in general (Figure \ref{fig:monthly-papers-condition-stack}). The proportion of pre-prints with open data or code has fluctuated over time but shows no consistent overall increase or decrease throughout the course of the pandemic, nor in conjunction with increases or decreases in the total number of pre-prints posted to any given repository. In our datasets, very few (if any) pre-prints were sampled for the month of January 2020. None of these pre-prints contained open data or open code markers, thus the 0 per cent rate of open data and code for this month across all repositories should be considered an outlier.

\begin{figure}

{\centering \includegraphics[width=0.9\linewidth]{paper_files/figure-latex/monthly-papers-condition-stack-1}

}

\caption{Number of sampled pre-prints related to COVID-19, distinguished by presence of open data or code markers}\label{fig:monthly-papers-condition-stack}
\end{figure}

\hypertarget{publication-status}{%
\subsection{Publication status}\label{publication-status}}

Our metadata also contains an indication of whether a pre-print has been published, in the form of a DOI linking to the corresponding published paper. The proportion of pre-prints that have been published varies by repository (Table \ref{tab:published-sample-summary}). Notably, of all COVID-19-related pre-prints in our dataset, approximately 30 per cent of those posted to bioRxiv and nearly one third of those posted to medRxiv were published. This is high in comparison to the proportions from arXiv and SocArXiv, and although this might suggest that COVID-19-related pre-prints in biomedical fields have received greater attention overall than pre-prints from other fields, our results in Section \ref{pre-pandemic-pre-prints} suggest that this pattern pre-dates the pandemic.

\begin{table}

\caption{\label{tab:published-sample-summary}Counts and proportion of published COVID-19 pre-prints in each repository}
\centering
\begin{tabular}[t]{l|r|r}
\hline
Repository & Published pre-prints & Proportion published\\
\hline
arXiv & 717 & 0.17\\
\hline
bioRxiv & 1,230 & 0.30\\
\hline
medRxiv & 4,230 & 0.32\\
\hline
SocArXiv & 71 & 0.15\\
\hline
\end{tabular}
\end{table}

In Table \ref{tab:open-published-summary} we disaggregate sampled pre-prints by whether there is an indication of publication. We find that the proportion of pre-prints with open data or code markers among those that have been published is roughly the same as pre-prints that have not been published, differing by only a few percentage points.

\begin{table}

\caption{\label{tab:open-published-summary}Counts and proportions of open data markers by whether the pre-print was published}
\centering
\begin{tabular}[t]{lrrrrr}
\toprule
Published & Both & Neither & Open code & Open data & Proportion with neither\\
\midrule
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{arXiv}}\\
\hspace{1em}No & 79 & 622 & 100 & 27 & 0.75\\
\hspace{1em}Yes & 20 & 130 & 15 & 7 & 0.76\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{bioRxiv}}\\
\hspace{1em}No & 55 & 471 & 29 & 145 & 0.67\\
\hspace{1em}Yes & 20 & 203 & 15 & 62 & 0.68\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{medRxiv}}\\
\hspace{1em}No & 10 & 112 & 8 & 8 & 0.81\\
\hspace{1em}Yes & 113 & 1,068 & 81 & 100 & 0.78\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{SocArXiv}}\\
\hspace{1em}No & 14 & 345 & 14 & 34 & 0.85\\
\hspace{1em}Yes & 3 & 60 & 0 & 8 & 0.85\\
\bottomrule
\end{tabular}
\end{table}

Our dataset likely imperfectly characterizes publication and does not have the publication details for some papers that were published. And even if it were a perfect record, there is a publication lag (estimated at an average of around 60 days for COVID-19-related pre-prints, although that varies by discipline) that may especially skew the results for pre-prints in the latter portion of our sample (Kwon 2020).

\hypertarget{pre-pandemic-pre-prints}{%
\subsection{Pre-pandemic pre-prints}\label{pre-pandemic-pre-prints}}

To examine the influence of the COVID-19 pandemic on open science practices during the pandemic, we analyzed pre-prints posted between January and December 2019 from each of the four repositories using the same process as was done for the COVID-19-related pre-prints. Since medRxiv was founded in June 2019, all pre-prints posted in the latter half of 2019 were analyzed (a total of 913). For all other repositories, a random sample of 1,200 was taken from all non-COVID-19-related pre-prints posted in the relevant date range.

\begin{figure}

{\centering \includegraphics[width=0.9\linewidth]{paper_files/figure-latex/2019-results-med-arxiv-1}

}

\caption{Number of pre-prints posted per month to arXiv, bioRxiv, medRxiv, and SocArXiv in 2019}\label{fig:2019-results-med-arxiv}
\end{figure}

\begin{table}

\caption{\label{tab:2019-open-results}Count and proportions of open data and code markers by pre-print repository in 2019 sample}
\centering
\begin{tabular}[t]{llrr}
\toprule
Open data markers & Open code markers & Count & Proportion of total\\
\midrule
\addlinespace[0.3em]
\multicolumn{4}{l}{\textbf{Total}}\\
\hspace{1em}No & No & 3,651 & 0.81\\
\hspace{1em}No & Yes & 228 & 0.05\\
\hspace{1em}Yes & No & 421 & 0.09\\
\hspace{1em}Yes & Yes & 213 & 0.05\\
\addlinespace[0.3em]
\multicolumn{4}{l}{\textbf{arXiv}}\\
\hspace{1em}No & No & 1,112 & 0.93\\
\hspace{1em}No & Yes & 59 & 0.05\\
\hspace{1em}Yes & No & 12 & 0.01\\
\hspace{1em}Yes & Yes & 17 & 0.01\\
\addlinespace[0.3em]
\multicolumn{4}{l}{\textbf{bioRxiv}}\\
\hspace{1em}No & No & 752 & 0.63\\
\hspace{1em}No & Yes & 98 & 0.08\\
\hspace{1em}Yes & No & 234 & 0.20\\
\hspace{1em}Yes & Yes & 116 & 0.10\\
\addlinespace[0.3em]
\multicolumn{4}{l}{\textbf{medRxiv}}\\
\hspace{1em}No & No & 686 & 0.75\\
\hspace{1em}No & Yes & 55 & 0.06\\
\hspace{1em}Yes & No & 115 & 0.13\\
\hspace{1em}Yes & Yes & 57 & 0.06\\
\addlinespace[0.3em]
\multicolumn{4}{l}{\textbf{SocArXiv}}\\
\hspace{1em}No & No & 1,101 & 0.92\\
\hspace{1em}No & Yes & 16 & 0.01\\
\hspace{1em}Yes & No & 60 & 0.05\\
\hspace{1em}Yes & Yes & 23 & 0.02\\
\bottomrule
\end{tabular}
\end{table}

Between June and December 2019, the number of pre-prints posted to medRxiv monthly saw an overall increase, which may be expected as the repository gained recognition and popularity in the medical research community (Figure \ref{fig:2019-results-med-arxiv}). The number of pre-prints posted monthly to bioRxiv also saw a slight overall increase throughout 2019, while the number of those posted to arXiv and SocArXiv fluctuated throughout the year (Figure \ref{fig:2019-results-med-arxiv}). Due to its relative immaturity at the beginning of the COVID-19 pandemic, a significant portion of medRxiv's overall usage has been dedicated to COVID-19-related research. In total, 21,647 pre-prints were posted to medRxiv between June 2019 and 30 June, 2021, 13,194 of which (approximately 61 per cent) relate to COVID-19.

Of the analyzed pre-prints from 2019, 93 per cent of those posted to arXiv, 63 per cent of those posted to bioRxiv, 75 per cent of those posted to medRxiv, 92 per cent of those posted to SocArXiv showed no indication of open data or open code (Table \ref{tab:2019-published}). Both the bioRxiv and medRxiv rates are approximately four per cent lower than the corresponding proportions of COVID-19-related pre-prints, suggesting that the analyzed pre-prints from 2019 may contain an overall higher prevalence of open data and code markers than pre-prints concerning COVID-19. Specifically, we found that open data availability in medRxiv pre-prints was significantly associated with a pre-pandemic registration date (\(\chi\)\textsuperscript{2} = 4.8508, p \textless{} 0.005), as was open code availability for bioRxiv pre-prints (\(\chi\)\textsuperscript{2} = 14.491, p \textless{} 0.005). This would suggest that open data and code practices may have suffered in the context of COVID-19. Or it may be something that is backfilled after posting.

On the other hand, the analyzed arXiv and SocArXiv pre-prints from 2019 contain a lower proportion of open data and code markers overall than their COVID-19-related counterparts, with a decrease of seven per cent in sampled SocArXiv pre-prints and 18 per cent in sampled arXiv papers. For these repositories, the presence of both open data and open code markers was significantly associated with registration during the pandemic, suggesting that pre-prints related to COVID-19 in arXiv and SocArXiv may have more consistently adhered to open science practices than their pre-pandemic counterparts (\(\chi\)\textsuperscript{2} = 93.124, arXiv open data; \(\chi\)\textsuperscript{2} = 106.88, arXiv open code; \(\chi\)\textsuperscript{2} = 12.303, SocArXiv open data; \(\chi\)\textsuperscript{2} = 8.1598, SocArXiv open code; p \textless{} 0.005).

\begin{table}

\caption{\label{tab:2019-published}Counts and proportion of published COVID-19 pre-prints in each repository, 2019}
\centering
\begin{tabular}[t]{l|r|r}
\hline
Repositiory & Published pre-prints & Proportion published\\
\hline
arXiv & 62,045 & 0.41\\
\hline
bioRxiv & 20,445 & 0.64\\
\hline
medRxiv & 555 & 0.61\\
\hline
socArXiv & 605 & 0.37\\
\hline
\end{tabular}
\end{table}

\begin{table}

\caption{\label{tab:2019-open-publishing}Counts and proportions of open data markers by whether the pre-print was published, 2019}
\centering
\begin{tabular}[t]{lrrrrr}
\toprule
Published & Both & Neither & Open code & Open data & Proportion with neither\\
\midrule
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{arXiv}}\\
\hspace{1em}No & 11 & 645 & 44 & 3 & 0.92\\
\hspace{1em}Yes & 6 & 467 & 15 & 9 & 0.94\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{bioRxiv}}\\
\hspace{1em}No & 38 & 264 & 34 & 87 & 0.62\\
\hspace{1em}Yes & 78 & 488 & 64 & 147 & 0.63\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{medRxiv}}\\
\hspace{1em}No & 19 & 277 & 19 & 43 & 0.77\\
\hspace{1em}Yes & 38 & 409 & 36 & 72 & 0.74\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{socArXiv}}\\
\hspace{1em}No & 13 & 659 & 10 & 47 & 0.90\\
\hspace{1em}Yes & 10 & 442 & 6 & 13 & 0.94\\
\bottomrule
\end{tabular}
\end{table}

Examining publication rates for pre-pandemic papers, we observe that 41 per cent of pre-prints posted to arXiv, 64 per cent of pre-prints posted to bioRxiv, 61 per cent of pre-prints posted to medRxiv, and 37 per cent of pre-prints posted to SocArXiv during 2019 were eventually peer reviewed and published (Table \ref{tab:2019-published}). These rates are at least double those of the COVID-19-related pre-prints posted in each repository during 2020 and 2021. When disaggregated by open data and code status, we find that published and unpublished pre-prints contain open data and code markers in similar proportions (Table \ref{tab:2019-open-publishing}). This mimics the behaviour of published and unpublished COVID-19-related pre-prints.

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\hypertarget{on-the-role-of-transparency-and-reproducibility}{%
\subsection{On the role of transparency and reproducibility}\label{on-the-role-of-transparency-and-reproducibility}}

Transparency and reproducibility are hallmarks of quality scientific research due to their relationship with independent verification (Stodden 2020). Open data and open code contribute to both by allowing the scientific community to more easily verify the authenticity of purported scientific discoveries and their supporting evidence. This is especially important in cases where scientific research may quickly and directly impact clinical practice or public policy, such as research on the COVID-19 pandemic. Among many other impacts on the research landscape, COVID-19 has increased the popularity of pre-prints from both a production and consumption standpoint. The number of COVID-19 pre-prints posted to medRxiv increased in the early stages of the pandemic, while non-COVID-19 pre-print numbers were largely as expected. The same trends were apparent in abstracts accessed by medRxiv users, where COVID-19 pre-print abstracts were viewed over 15 times more than non-COVID-19 pre-print abstracts (Fraser et al. 2021). For these reasons, it is important to examine open science standards and reproducibility within pre-print repositories.

Open data is generally accepted to be beneficial to the scientific process and to a paper's reproducibility potential, hence it is concerning that around 75 per cent of pre-prints in our sample contained no open data markers. This concern is slightly mitigated by recognition of challenges in working with biomedical data compared with data in other fields, notably privacy and ethics concerns when working with personal data (Floca 2014). The COVID-19 pandemic has seen open science initiatives, as evidenced by the creation of open data repositories such as the dashboard maintained by the Center for Systems Science and Engineering at Johns Hopkins University (Dong, Du, and Gardner 2020) or the large number of publishers who have removed paywalls from published COVID-19 research (Gill 2020). While the intention at the start of the pandemic was that there would be `clear statements regarding the availability of underlying data' (Wellcome Trust 2020) some retractions of work have been based on `unreliable or nonexistent data' (Silva, Bornemann-Cimenti, and Tsigaris 2021). SocArXiv asks submitters to make explicit the degree of openness in the data, and this is something that could be easily adopted by other pre-print repositories.

Open code as an open science marker is context and field-dependent, as not all biomedical research papers will rely on computational methods for their analyses. However, in pre-prints where code comprises a large portion of the methodology or results, posting it openly to repositories like GitHub contributes to a pre-print's potential reproducibility. This is important when computational methods are used to form predictions about emerging situations with limited data or laboratory research, which was the case for modelling studies in the early days of the COVID-19 pandemic. We also see growing concern over the quality and consequences of this sort of research, with bioRxiv no longer allowing purely computational work (Kwon 2020).

The other concern is the adverse selection issue caused by meeting the open science aims of sharing code and data. Authors that share their data and code open their work up to criticism. If authors who make their data and code available make similar mistakes to authors who choose to not publish their data and code, it is more likely that the mistake would not be noticed in the case where data and code were not published. The current system is biased against those who follow best practice. McGuinness and Sheppard (2021) advocate for `(s)trict editorial policies that mandate data sharing,' and other changed norms are needed.

\hypertarget{the-role-of-pre-print-repositories}{%
\subsection{The role of pre-print repositories}\label{the-role-of-pre-print-repositories}}

There has been a large amount of research on COVID-19 (Silva, Tsigaris, and Erfanmanesh 2021). Many concerns have arisen from the rate at which COVID-19 research has been posted and consumed via pre-print repositories, particularly in the early stages of the pandemic (Raynaud et al. 2020). Rushed scientific research has potential to skip (or at least place less precedence on) open science practices, thus it may be reasonable to expect a decrease in open data or code markers in the initial few months of the pandemic. We found little relationship between date posted and likelihood of having open data or code markers, with the proportion of pre-prints containing these markers fluctuating from month to month. This suggests that open science practices are more influenced by other factors, perhaps including training, publication bias, or the nature of the pre-print itself. On the other hand, we do not see an overall long-term increase in either open data or open code markers throughout our period of analysis, which we may have expected in the context of the open science movements the pandemic has fostered. Although not pre-print specific, Else (2020) found that overall research output has fluctuated between different fields and topics (namely modelling disease spread, public health, diagnostics and testing, mental health, and hospital mortality) throughout different stages of the pandemic, which may account for some of the fluctuation and overall lack of noticeable trend in our sample.

To emphasize the ongoing need for open data and code in modelling a pandemic, we consider two high profile epidemiological models that emerged in early 2020. Modelling was conducted by Imperial College London (ICL) (Ferguson et al. 2020) and the Institute for Health Metrics and Evaluation (IHME) at the University of Washington (Murray 2020), and both were initially posted to pre-print repositories. The ICL model went on to become the most cited pre-print as of December 2020 (Else 2020), and both had significant influence over policy and public health decisions worldwide (Adam 2020). An independent review of these two models by Jin et al. (2020) found that while code and data were openly available for both, only the ICL model was reproducible due to limited transparency on the underlying methodology of the IHME model. The open-source nature of these models was fundamental to reproduction attempts and is an example of the need for open data and code in COVID-19 research, particularly as pre-prints influence public decision-making.

In the context of the above factors, it was encouraging to find in our analysis that the proportion of pre-prints with open data or code posted to arXiv increased from 7 per cent pre-pandemic to 25 per cent for COVID-19-related pre-prints. This pattern, however, was not observed among the analyzed bioRxiv and medRxiv pre-prints, and may just reflect the nature of COVID-19 pre-prints. With many pre-prints from these repositories still pertaining to epidemiological modelling, one might hope that they should universally be subject to the same analysis as conducted by Jin et al. (2020) as for the examples above, which is made possible by the availability of relevant code and data. Our analysis suggests a need for future investigation and potential overall improvement in open science standards for these types of pre-prints (subject to the data and code considerations already discussed). This need is again emphasized by the new-found speed at which pre-prints may gain public, media, and political attention in the context of the pandemic, particularly those from medRxiv and bioRxiv.

\hypertarget{the-importance-of-open-data-and-open-code}{%
\subsection{The importance of open data and open code}\label{the-importance-of-open-data-and-open-code}}

Beyond pre-prints, COVID-19 has influenced publication and peer review processes, with timelines for COVID-19 papers being expedited at the expense of longer waits for other scientific research (Else 2020). It is important that open data and code standards be maintained in published work as well. In our sample, published pre-prints contain open data or code markers in similar proportions to their unpublished counterparts, a pattern that was present for pre-prints related to COVID-19 and those posted in 2019. This appears initially to alleviate some concerns over the relationship between open data and publication bias, that is, the potential that journals have favoured novel yet less transparent or reproducible papers over those with null results but a high standard of open science practices. However, publication bias is complex and this result should be approached with caution. Concerns have already been raised through systemic reviews of COVID-19 publications (Raynaud et al. 2020), and oversights in data accessibility have led to high profile retractions of publications in the past; for example, papers from \emph{The Lancet} and the \emph{New England Journal of Medicine} which were withdrawn due to concerns over the private nature of their underlying dataset (Ledford and Noorden 2020).

In all fields of science, increasing access to data and code used for pre-printed or published research is a step in the direction of more transparent, reproducible, and reliable research. The ongoing COVID-19 pandemic has created a novel, constantly changing scientific culture that should be navigated with care to uphold standards of scientific practice for both the research community and the safety of the public. Our analysis shows that there is room for improvement in the areas of open data and code availability within COVID-19 pre-print papers on arXiv, bioRxiv, medRxiv, and SocArXiv.

There is demand for timely research and high frequency results because the pandemic rapidly evolves. Pre-prints are efficient in this role because there is no time spent on peer review. They also allow lesser-known researchers to better disperse their research because of the possibility that fast-tracked peer review may be biased towards established researchers. While there is a clear need for pre-prints, the point remains that they do not go through the peer review process. This question of quality and validity is particularly pertinent in the COVID-19 context because poorly validated results and false information may spread quickly and have real effects. We are not saying that peer review implies that a paper is of a high-quality; we are instead saying that the provision of code and data alongside the pre-print goes some way to allowing others to trust the findings of pre-prints, even though they have not been peer-reviewed. One way this could be encouraged would be for all pre-print repositories to have authors characterize the extent to which they have adopted open science practices as part of their submission, in the same way that is done in SocArXiv. Although those pre-prints that do not adopt these practices should not be rejected from pre-print repositories, greater clarity around this would be useful and might move the state-of-the-art forward.

\hypertarget{weaknesses-and-next-steps}{%
\subsection{Weaknesses and next steps}\label{weaknesses-and-next-steps}}

We wish to expand our analysis to consider the geographic distribution of research and the potential influence of different practices and policies concerning open science as pre-prints vary by location. This is important because the epicenter of the pandemic changed throughout the pandemic, which has implications for our time-based analysis.

An important weakness is the potential presence of false negatives in indicators of publication in our dataset. Abdill and Blekhman (2019) estimate that the false-negative rate may be as high as 37.5 per cent for data pulled from the bioRxiv API, meaning analysis of published papers may represent only a fraction of those that have been published. It is unclear to what extent this is the case for other repositories or what bias may exist in the subset of pre-prints for which publication was detected, because it is likely that this process relies on title-based text matching (Abdill and Blekhman 2019). It is also likely that some of our more recent sampled pre-prints will be published in the future which we could not account for at the time of our data collection.

Our paper depends on search responses from the various repositories, which are based on our selection of keywords. Our selection of keywords is not exhaustive, for instance, perhaps `the pandemic' could result in additional papers. Future work could make this keyword approach more systematic, for instance following King, Lam, and Roberts (2017).

We also recognize that this analysis relies heavily on text-based analysis which was not verified directly in most cases and may lead to higher levels of uncertainty. The \texttt{oddpub} package was built to analyze biomedical publications and it may be that some of the differences that we find between repositories are due to this. In future, we wish to take smaller sub-samples to validate factors like publication status, paper topic, and open code and data status, beyond the approaches that we used here.

\newpage

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-abdill2019}{}%
Abdill, Richard J, and Ran Blekhman. 2019. {``Meta-Research: Tracking the Popularity and Outcomes of All bioRxiv Preprints.''} Edited by Emma Pewsey, Peter Rodgers, and Casey S Greene. \emph{eLife} 8 (April): e45133. \url{https://doi.org/10.7554/eLife.45133}.

\leavevmode\hypertarget{ref-adam2020}{}%
Adam, David. 2020. {``Special Report: The Simulations Driving the World's Response to COVID-19.''} \emph{Nature} 580: 316--18. \url{https://doi.org/10.1038/d41586-020-01003-6}.

\leavevmode\hypertarget{ref-citealexandermafouz}{}%
Alexander, Rohan, and A Mahfouz. 2021. \emph{{heapsofpapers: Easily Download Heaps of Papers}}. \url{https://rohanalexander.github.io/heapsofpapers/}.

\leavevmode\hypertarget{ref-citeCSSE}{}%
Dong, Ensheng, Hongru Du, and Lauren Gardner. 2020. {``An Interactive Web-Based Dashboard to Track COVID-19 in Real Time.''} \emph{The Lancet Infectious Diseases} 20: 533--34. \url{https://doi.org/10.1016/S1473-3099(20)30120-1}.

\leavevmode\hypertarget{ref-else2020}{}%
Else, Holly. 2020. {``How a Torrent of COVID Science Changed Research Publishing --- in Seven Charts.''} \emph{Nature} 588: 553. \url{https://doi.org/10.1038/d41586-020-03564-y}.

\leavevmode\hypertarget{ref-ferguson2020}{}%
Ferguson, Neil M, Daniel Laydon, Gemma Nedjati-Gilani, Natsuko Imai, Kylie Ainslie, Marc Baguelin, Sangeeta Bhatia, et al. 2020. {``Report 9: Impact of Non-Pharmaceutical Interventions (NPIs) to Reduce COVID-19 Mortality and Healthcare Demand.''} \url{https://doi.org/10.25561/77482}.

\leavevmode\hypertarget{ref-Floca2014}{}%
Floca, Ralf. 2014. {``Challenges of Open Data in Medical Research.''} In \emph{Opening Science: The Evolving Guide on How the Internet Is Changing Research, Collaboration and Scholarly Publishing}, edited by Sönke Bartling and Sascha Friesike, 297--307. Cham: Springer International Publishing. \url{https://doi.org/10.1007/978-3-319-00026-8_22}.

\leavevmode\hypertarget{ref-citeFraser}{}%
Fraser, Nicholas, Liam Brierley, Gautam Dey, Jessica K Polka, Máté Pálfy, Federico Nanni, and Jonathon Alexis Coates. 2021. {``Preprinting the COVID-19 Pandemic.''} \emph{bioRxiv}. \url{https://doi.org/10.1101/2020.05.22.111294}.

\leavevmode\hypertarget{ref-gill2020}{}%
Gill, David. 2020. {``Immediate Free Access to Research: The Scholarly Response to COVID-19.''} \url{https://www.lib.sfu.ca/help/publish/scholarly-publishing/radical-access/scholarly-covid19}.

\leavevmode\hypertarget{ref-jin2020}{}%
Jin, Jin, Neha Agarwala, Prosenjit Kundu, Yi Wang, Ruzhang Zhao, and Nilanjan Chatterjee. 2020. {``Transparency, Reproducibility, and Validation of COVID-19 Projection Models.''} \url{https://www.jhsph.edu/covid-19/articles/transparency-reproducibility-and-validation-of-covid-19-projection-models.html}.

\leavevmode\hypertarget{ref-king2017computer}{}%
King, Gary, Patrick Lam, and Margaret E Roberts. 2017. {``Computer-Assisted Keyword and Document Set Discovery from Unstructured Text.''} \emph{American Journal of Political Science} 61 (4): 971--88.

\leavevmode\hypertarget{ref-kwon2020}{}%
Kwon, Diana. 2020. {``How Swamped Preprint Servers Are Blocking Bad Coronavirus Research.''} \emph{Nature} 580 (May): 130--31. \url{https://doi.org/10.1038/d41586-020-01394-6}.

\leavevmode\hypertarget{ref-ledford2020}{}%
Ledford, Heidi, and Richard Van Noorden. 2020. {``High-Profile Coronavirus Retractions Raise Concerns about Data Oversight.''} \emph{Nature} 582: 160. \url{https://doi.org/10.1038/d41586-020-01695-w}.

\leavevmode\hypertarget{ref-mcguinness2021descriptive}{}%
McGuinness, Luke A, and Athena L Sheppard. 2021. {``A Descriptive Analysis of the Data Availability Statements Accompanying medRxiv Preprints and a Comparison with Their Published Counterparts.''} \emph{PloS One} 16 (5): e0250887.

\leavevmode\hypertarget{ref-murray2020}{}%
Murray, Christopher JL. 2020. {``Forecasting the Impact of the First Wave of the COVID-19 Pandemic on Hospital Demand and Deaths for the USA and European Economic Area Countries.''} \emph{medRxiv}. \url{https://doi.org/10.1101/2020.04.21.20074732}.

\leavevmode\hypertarget{ref-citeR}{}%
R Core Team. 2020. \emph{{R: A Language and Environment for Statistical Computing}}. Vienna, Austria: R Foundation for Statistical Computing. \url{https://www.R-project.org/}.

\leavevmode\hypertarget{ref-raynaud2021}{}%
Raynaud, Marc, Huanxi Zhang, Kevin Louis, Valentin Goutaudier, Jiali Wang, Quentin Dubourg, Yongcheng Wei, et al. 2020. {``COVID-19-Related Medical Research: A Meta-Research and Critical Appraisal.''} \emph{BMC Medical Research Methodology} 21. \url{https://doi.org/10.1186/s12874-020-01190-w}.

\leavevmode\hypertarget{ref-citeODDPubpackage}{}%
Riedel, Nico. 2019. \emph{Oddpub: Detection of Open Data \& Open Code Statements in Biomedical Publications}. \url{https://github.com/quest-bih/oddpub}.

\leavevmode\hypertarget{ref-citePDDPub}{}%
Riedel, Nico, Miriam Kip, and Evgeny Bobrov. 2020. {``ODDPub -- a Text-Mining Algorithm to Detect Data Sharing in Biomedical Publications.''} \emph{Data Science Journal} 19 (1): 42. \url{https://doi.org/10.5334/dsj-2020-042}.

\leavevmode\hypertarget{ref-da2021optimizing}{}%
Silva, Jaime A Teixeira da, Helmar Bornemann-Cimenti, and Panagiotis Tsigaris. 2021. {``Optimizing Peer Review to Minimize the Risk of Retracting COVID-19-Related Literature.''} \emph{Medicine, Health Care and Philosophy} 24 (1): 21--26.

\leavevmode\hypertarget{ref-da2021publishing}{}%
Silva, Jaime A Teixeira da, Panagiotis Tsigaris, and Mohammadamin Erfanmanesh. 2021. {``Publishing Volumes in Major Databases Related to Covid-19.''} \emph{Scientometrics} 126 (1): 831--42.

\leavevmode\hypertarget{ref-Stodden2020Theme}{}%
Stodden, Victoria. 2020. {``Theme Editor's Introduction to Reproducibility and Replicability in Science.''} \emph{Harvard Data Science Review} 2 (4). \url{https://doi.org/10.1162/99608f92.c46a02d4}.

\leavevmode\hypertarget{ref-weissgerber2021automated}{}%
Weissgerber, Tracey, Nico Riedel, Halil Kilicoglu, Cyril Labbé, Peter Eckmann, Gerben Ter Riet, Jennifer Byrne, et al. 2021. {``Automated Screening of COVID-19 Preprints: Can We Help Authors to Improve Transparency and Reproducibility?''} \emph{Nature Medicine} 27 (1): 6--7.

\leavevmode\hypertarget{ref-citeWellcome}{}%
Wellcome Trust. 2020. \emph{Sharing Research Data and Findings Relevant to the Novel Coronavirus (COVID-19) Outbreak}. Vienna, Austria: Wellcome Trust. \url{https://wellcome.org/coronavirus-covid-19/open-data}.

\leavevmode\hypertarget{ref-citeWHOtimeline}{}%
World Health Organization. 2020. {``WHO Director-General's Opening Remarks at the Media Briefing on COVID-19 - 11 March 2020.''} \url{https://www.who.int/director-general/speeches/detail/who-director-general-s-opening-remarks-at-the-media-briefing-on-covid-19—11-march-2020}.

\end{CSLReferences}

\end{document}

### 2021-09-09 outputs/paper/paper.Rmd
Add tweaks for journal submission and also add link to the missing big dataset

@@
   - Rohan Alexander^[University of Toronto, rohan.alexander@utoronto.ca.]
-thanks: "We thank Amy Farrow, Jessica Gronsbell, Monica Alexander, and Thomas William Rosenthal for helpful comments.
-Collins thanks CANSSI Ontario and Monica Alexander for financial support.
-Code and data are available at: https://github.com/anniecollins/reproducibility_markers_in_covid19_preprints."
+thanks: "**Acknowledgements:** We thank Amy Farrow, Jessica Gronsbell, Monica Alexander, and Thomas William Rosenthal for helpful comments.
+**Funding statement:** Collins thanks CANSSI Ontario and Monica Alexander for financial support.
+**Data accessibility statement:** Code and data are available at: https://github.com/anniecollins/reproducibility_markers_in_covid19_preprints.
+**Author contributions:** Collins had the original idea and wrote the first draft of the paper.
+Collins and Alexander obtained and created the datasets.
+Collins and Alexander analysed the data.
+All authors interpreted the data and contributed writing the paper and approved the final version."
 date: "`r format(Sys.time(), '%d %B %Y')`"
@@
 bibliography: references.bib
+csl: vancouver.csl
 ---

### 2021-09-09 outputs/paper/paper.tex
Add tweaks for journal submission and also add link to the missing big dataset

@@
 ]{article}
+\usepackage{amsmath,amssymb}
 \usepackage{lmodern}
-\usepackage{amsmath}
 \usepackage{ifxetex,ifluatex}
@@
   \usepackage{textcomp} % provide euro and other symbols
-  \usepackage{amssymb}
 \else % if luatex or xetex
@@
 \usepackage[margin=1in]{geometry}
-\usepackage{longtable,booktabs}
+\usepackage{longtable,booktabs,array}
 \usepackage{calc} % for calculating minipage widths
@@
 
-\title{Reproducibility of COVID-19 pre-prints\thanks{We thank Amy Farrow, Jessica Gronsbell, Monica Alexander, and Thomas William Rosenthal for helpful comments.
-Collins thanks CANSSI Ontario and Monica Alexander for financial support.
-Code and data are available at: \url{https://github.com/anniecollins/reproducibility_markers_in_covid19_preprints}.}}
+\title{Reproducibility of COVID-19 pre-prints\thanks{\textbf{Acknowledgements:} We thank Amy Farrow, Jessica Gronsbell, Monica Alexander, and Thomas William Rosenthal for helpful comments.
+\textbf{Funding statement:} Collins thanks CANSSI Ontario and Monica Alexander for financial support.
+\textbf{Data accessibility statement:} Code and data are available at: \url{https://github.com/anniecollins/reproducibility_markers_in_covid19_preprints}.
+\textbf{Author contributions:} A.C.
+had the original idea and wrote the first draft of the paper.
+A.C.
+and R.A.
+obtained and created the datasets.
+A.C.
+and R.A.
+analysed the data.
+All authors interpreted the data and contributed writing the paper and approved the final version.}}
 \author{Annie Collins\footnote{University of Toronto.} \and Rohan Alexander\footnote{University of Toronto, \href{mailto:rohan.alexander@utoronto.ca}{\nolinkurl{rohan.alexander@utoronto.ca}}.}}
-\date{22 July 2021}
+\date{08 September 2021}
 
@@
 These repositories, such as arXiv, bioRxiv, medRxiv, and SocArXiv, are a critical component of scientific communication and a lot of research builds on the pre-prints posted there.
-Pre-print repositories have been especially important during the 2019 novel coronavirus (COVID-19) pandemic and the changes it has imposed on the scientific community (Else 2020).
+Pre-print repositories have been especially important during the 2019 novel coronavirus (COVID-19) pandemic and the changes it has imposed on the scientific community (1).
 The centrality of pre-prints to science means that it is important that the results that are posted are credible.
@@
 But it is important that scientists impose standards on themselves, and arguably repositories have a role to play here.
-Following Weissgerber et al.
-(2021), we examine pre-prints about COVID-19 posted to arXiv, bioRxiv, medRxiv, and SocArXiv from 28 January 2020 through to 30 June 2021.
+Following (2), we examine pre-prints about COVID-19 posted to arXiv, bioRxiv, medRxiv, and SocArXiv from 28 January 2020 through to 30 June 2021.
 By way of background, each of these four repositories has a different focus: arXiv is general, bioRxiv focuses on biological sciences, medRxiv focuses on health sciences, and SocArXiv focuses on social sciences.
@@
 
-We checked our sampled pre-prints for open data and code markers using the Open Data Detection in Publications (ODDPub) text mining algorithm (Riedel, Kip, and Bobrov 2020) within the \texttt{oddpub} R package (Riedel 2019).
-This required downloading each pre-print as a PDF, which we did using \texttt{heapsofpapers} (Alexander and Mahfouz 2021) and then converting the PDFs to text files.
+We checked our sampled pre-prints for open data and code markers using the Open Data Detection in Publications (ODDPub) text mining algorithm (3) within the \texttt{oddpub} R package (4).
+This required downloading each pre-print as a PDF, which we did using \texttt{heapsofpapers} (5) and then converting the PDFs to text files.
 Some papers from SocArXiv were only available in Word document format (.docx) and were downloaded as such and then converted to text format.
@@
 What constitutes open code or open data is complicated and discipline specific.
-The details of the \texttt{oddpub} approach are available in Riedel, Kip, and Bobrov (2020).
+The details of the \texttt{oddpub} approach are available in (3).
 The general criteria are that specific mention should be made of where the data and code are located, and that data should be as close to raw as possible.
-Our work was conducted using the statistical programming language R (R Core Team 2020).
+Our work was conducted using the statistical programming language R (6).
 
@@
 The number of pre-prints posted monthly since August 2020 has remained reasonably steady, with the exception of medRxiv, which experienced an increase to nearly 1,000 pre-prints posted in March 2021 (Figure \ref{fig:monthly-papers-total}).
-For context, COVID-19 was declared a pandemic by the World Health Organization (WHO) on March 11, 2020, at which point the number of cases globally had just surpassed 118,000 (primarily in east Asia) and the virus had been reported in 114 countries (World Health Organization 2020).
+For context, COVID-19 was declared a pandemic by the World Health Organization (WHO) on March 11, 2020, at which point the number of cases globally had just surpassed 118,000 (primarily in east Asia) and the virus had been reported in 114 countries (7).
 
@@
 Notably, 28 per cent of sampled pre-prints from bioRxiv contained open data markers and 22 per cent of sampled arXiv pre-prints contained markers of open code, the highest proportions of any repository for each type of marker.
-Our results are similar to McGuinness and Sheppard (2021), who focus on medRxiv and find that 23 per cent describe open data.
+Our results are similar to (8), who focus on medRxiv and find that 23 per cent describe open data.
 
@@
 Our dataset likely imperfectly characterizes publication and does not have the publication details for some papers that were published.
-And even if it were a perfect record, there is a publication lag (estimated at an average of around 60 days for COVID-19-related pre-prints, although that varies by discipline) that may especially skew the results for pre-prints in the latter portion of our sample (Kwon 2020).
+And even if it were a perfect record, there is a publication lag (estimated at an average of around 60 days for COVID-19-related pre-prints, although that varies by discipline) that may especially skew the results for pre-prints in the latter portion of our sample (9).
 
@@
 
-Transparency and reproducibility are hallmarks of quality scientific research due to their relationship with independent verification (Stodden 2020).
+Transparency and reproducibility are hallmarks of quality scientific research due to their relationship with independent verification (10).
 Open data and open code contribute to both by allowing the scientific community to more easily verify the authenticity of purported scientific discoveries and their supporting evidence.
@@
 The number of COVID-19 pre-prints posted to medRxiv increased in the early stages of the pandemic, while non-COVID-19 pre-print numbers were largely as expected.
-The same trends were apparent in abstracts accessed by medRxiv users, where COVID-19 pre-print abstracts were viewed over 15 times more than non-COVID-19 pre-print abstracts (Fraser et al.
-2021).
+The same trends were apparent in abstracts accessed by medRxiv users, where COVID-19 pre-print abstracts were viewed over 15 times more than non-COVID-19 pre-print abstracts (11).
 For these reasons, it is important to examine open science standards and reproducibility within pre-print repositories.
@@
 Open data is generally accepted to be beneficial to the scientific process and to a paper's reproducibility potential, hence it is concerning that around 75 per cent of pre-prints in our sample contained no open data markers.
-This concern is slightly mitigated by recognition of challenges in working with biomedical data compared with data in other fields, notably privacy and ethics concerns when working with personal data (Floca 2014).
-The COVID-19 pandemic has seen open science initiatives, as evidenced by the creation of open data repositories such as the dashboard maintained by the Center for Systems Science and Engineering at Johns Hopkins University (Dong, Du, and Gardner 2020) or the large number of publishers who have removed paywalls from published COVID-19 research (Gill 2020).
-While the intention at the start of the pandemic was that there would be `clear statements regarding the availability of underlying data' (Wellcome Trust 2020) some retractions of work have been based on `unreliable or nonexistent data' (Silva, Bornemann-Cimenti, and Tsigaris 2021).
+This concern is slightly mitigated by recognition of challenges in working with biomedical data compared with data in other fields, notably privacy and ethics concerns when working with personal data (12).
+The COVID-19 pandemic has seen open science initiatives, as evidenced by the creation of open data repositories such as the dashboard maintained by the Center for Systems Science and Engineering at Johns Hopkins University (13) or the large number of publishers who have removed paywalls from published COVID-19 research (14).
+While the intention at the start of the pandemic was that there would be `clear statements regarding the availability of underlying data' (15) some retractions of work have been based on `unreliable or nonexistent data' (16).
 SocArXiv asks submitters to make explicit the degree of openness in the data, and this is something that could be easily adopted by other pre-print repositories.
@@
 This is important when computational methods are used to form predictions about emerging situations with limited data or laboratory research, which was the case for modelling studies in the early days of the COVID-19 pandemic.
-We also see growing concern over the quality and consequences of this sort of research, with bioRxiv no longer allowing purely computational work (Kwon 2020).
+We also see growing concern over the quality and consequences of this sort of research, with bioRxiv no longer allowing purely computational work (9).
 
@@
 The current system is biased against those who follow best practice.
-McGuinness and Sheppard (2021) advocate for `(s)trict editorial policies that mandate data sharing,' and other changed norms are needed.
+(8) advocate for `(s)trict editorial policies that mandate data sharing,' and other changed norms are needed.
 
@@
 
-There has been a large amount of research on COVID-19 (Silva, Tsigaris, and Erfanmanesh 2021).
-Many concerns have arisen from the rate at which COVID-19 research has been posted and consumed via pre-print repositories, particularly in the early stages of the pandemic (Raynaud et al.
-2020).
+There has been a large amount of research on COVID-19 (17).
+Many concerns have arisen from the rate at which COVID-19 research has been posted and consumed via pre-print repositories, particularly in the early stages of the pandemic (18).
 Rushed scientific research has potential to skip (or at least place less precedence on) open science practices, thus it may be reasonable to expect a decrease in open data or code markers in the initial few months of the pandemic.
@@
 On the other hand, we do not see an overall long-term increase in either open data or open code markers throughout our period of analysis, which we may have expected in the context of the open science movements the pandemic has fostered.
-Although not pre-print specific, Else (2020) found that overall research output has fluctuated between different fields and topics (namely modelling disease spread, public health, diagnostics and testing, mental health, and hospital mortality) throughout different stages of the pandemic, which may account for some of the fluctuation and overall lack of noticeable trend in our sample.
+Although not pre-print specific, (1) found that overall research output has fluctuated between different fields and topics (namely modelling disease spread, public health, diagnostics and testing, mental health, and hospital mortality) throughout different stages of the pandemic, which may account for some of the fluctuation and overall lack of noticeable trend in our sample.
 
 To emphasize the ongoing need for open data and code in modelling a pandemic, we consider two high profile epidemiological models that emerged in early 2020.
-Modelling was conducted by Imperial College London (ICL) (Ferguson et al.
-2020) and the Institute for Health Metrics and Evaluation (IHME) at the University of Washington (Murray 2020), and both were initially posted to pre-print repositories.
-The ICL model went on to become the most cited pre-print as of December 2020 (Else 2020), and both had significant influence over policy and public health decisions worldwide (Adam 2020).
-An independent review of these two models by Jin et al.
-(2020) found that while code and data were openly available for both, only the ICL model was reproducible due to limited transparency on the underlying methodology of the IHME model.
+Modelling was conducted by Imperial College London (ICL) (19) and the Institute for Health Metrics and Evaluation (IHME) at the University of Washington (20), and both were initially posted to pre-print repositories.
+The ICL model went on to become the most cited pre-print as of December 2020 (1), and both had significant influence over policy and public health decisions worldwide (21).
+An independent review of these two models by (22) found that while code and data were openly available for both, only the ICL model was reproducible due to limited transparency on the underlying methodology of the IHME model.
 The open-source nature of these models was fundamental to reproduction attempts and is an example of the need for open data and code in COVID-19 research, particularly as pre-prints influence public decision-making.
@@
 This pattern, however, was not observed among the analyzed bioRxiv and medRxiv pre-prints, and may just reflect the nature of COVID-19 pre-prints.
-With many pre-prints from these repositories still pertaining to epidemiological modelling, one might hope that they should universally be subject to the same analysis as conducted by Jin et al.
-(2020) as for the examples above, which is made possible by the availability of relevant code and data.
+With many pre-prints from these repositories still pertaining to epidemiological modelling, one might hope that they should universally be subject to the same analysis as conducted by (22) as for the examples above, which is made possible by the availability of relevant code and data.
 Our analysis suggests a need for future investigation and potential overall improvement in open science standards for these types of pre-prints (subject to the data and code considerations already discussed).
@@
 
-Beyond pre-prints, COVID-19 has influenced publication and peer review processes, with timelines for COVID-19 papers being expedited at the expense of longer waits for other scientific research (Else 2020).
+Beyond pre-prints, COVID-19 has influenced publication and peer review processes, with timelines for COVID-19 papers being expedited at the expense of longer waits for other scientific research (1).
 It is important that open data and code standards be maintained in published work as well.
@@
 However, publication bias is complex and this result should be approached with caution.
-Concerns have already been raised through systemic reviews of COVID-19 publications (Raynaud et al.
-2020), and oversights in data accessibility have led to high profile retractions of publications in the past; for example, papers from \emph{The Lancet} and the \emph{New England Journal of Medicine} which were withdrawn due to concerns over the private nature of their underlying dataset (Ledford and Noorden 2020).
+Concerns have already been raised through systemic reviews of COVID-19 publications (18), and oversights in data accessibility have led to high profile retractions of publications in the past; for example, papers from \emph{The Lancet} and the \emph{New England Journal of Medicine} which were withdrawn due to concerns over the private nature of their underlying dataset (23).
 
@@
 An important weakness is the potential presence of false negatives in indicators of publication in our dataset.
-Abdill and Blekhman (2019) estimate that the false-negative rate may be as high as 37.5 per cent for data pulled from the bioRxiv API, meaning analysis of published papers may represent only a fraction of those that have been published.
-It is unclear to what extent this is the case for other repositories or what bias may exist in the subset of pre-prints for which publication was detected, because it is likely that this process relies on title-based text matching (Abdill and Blekhman 2019).
+(24) estimate that the false-negative rate may be as high as 37.5 per cent for data pulled from the bioRxiv API, meaning analysis of published papers may represent only a fraction of those that have been published.
+It is unclear to what extent this is the case for other repositories or what bias may exist in the subset of pre-prints for which publication was detected, because it is likely that this process relies on title-based text matching (24).
 It is also likely that some of our more recent sampled pre-prints will be published in the future which we could not account for at the time of our data collection.
@@
 Our selection of keywords is not exhaustive, for instance, perhaps `the pandemic' could result in additional papers.
-Future work could make this keyword approach more systematic, for instance following King, Lam, and Roberts (2017).
+Future work could make this keyword approach more systematic, for instance following (25).
 
@@
 \hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-abdill2019}{}%
-Abdill, Richard J, and Ran Blekhman.
-2019.
-{``Meta-Research: Tracking the Popularity and Outcomes of All bioRxiv Preprints.''} Edited by Emma Pewsey, Peter Rodgers, and Casey S Greene.
-\emph{eLife} 8 (April): e45133.
-\url{https://doi.org/10.7554/eLife.45133}.
+\begin{CSLReferences}{0}{0}
+\leavevmode\hypertarget{ref-else2020}{}%
+\CSLLeftMargin{1. }
+\CSLRightInline{Else H.
+How a torrent of COVID science changed research publishing --- in seven charts.
+Nature {[}Internet{]}.
+2020;588:553.
+Available from: \url{https://doi.org/10.1038/d41586-020-03564-y}}
+
+\leavevmode\hypertarget{ref-weissgerber2021automated}{}%
+\CSLLeftMargin{2. }
+\CSLRightInline{Weissgerber T, Riedel N, Kilicoglu H, Labbé C, Eckmann P, Ter Riet G, et al.
+Automated screening of COVID-19 preprints: Can we help authors to improve transparency and reproducibility?
+Nature Medicine.
+2021;27(1):6--7.
+}
+
+\leavevmode\hypertarget{ref-citePDDPub}{}%
+\CSLLeftMargin{3. }
+\CSLRightInline{Riedel N, Kip M, Bobrov E. ODDPub -- a text-mining algorithm to detect data sharing in biomedical publications. Data Science Journal. 2020;19(1):42. }
+
+\leavevmode\hypertarget{ref-citeODDPubpackage}{}%
+\CSLLeftMargin{4. }
+\CSLRightInline{Riedel N. Oddpub: Detection of open data \& open code statements in biomedical publications {[}Internet{]}. 2019. Available from: \url{https://github.com/quest-bih/oddpub}}
+
+\leavevmode\hypertarget{ref-citealexandermafouz}{}%
+\CSLLeftMargin{5. }
+\CSLRightInline{Alexander R, Mahfouz A. {heapsofpapers: Easily Download Heaps of Papers} {[}Internet{]}. 2021. Available from: \url{https://rohanalexander.github.io/heapsofpapers/}}
+
+\leavevmode\hypertarget{ref-citeR}{}%
+\CSLLeftMargin{6. }
+\CSLRightInline{R Core Team.
+{R: A Language and Environment for Statistical Computing} {[}Internet{]}.
+Vienna, Austria: R Foundation for Statistical Computing; 2020.
+Available from: \url{https://www.R-project.org/}}
+
+\leavevmode\hypertarget{ref-citeWHOtimeline}{}%
+\CSLLeftMargin{7. }
+\CSLRightInline{World Health Organization.
+WHO director-general's opening remarks at the media briefing on COVID-19 - 11 march 2020 {[}Internet{]}.
+2020.
+Available from: \url{https://www.who.int/director-general/speeches/detail/who-director-general-s-opening-remarks-at-the-media-briefing-on-covid-19---11-march-2020}}
+
+\leavevmode\hypertarget{ref-mcguinness2021descriptive}{}%
+\CSLLeftMargin{8. }
+\CSLRightInline{McGuinness LA, Sheppard AL.
+A descriptive analysis of the data availability statements accompanying medRxiv preprints and a comparison with their published counterparts.
+PloS one.
+2021;16(5):e0250887.
+}
+
+\leavevmode\hypertarget{ref-kwon2020}{}%
+\CSLLeftMargin{9. }
+\CSLRightInline{Kwon D.
+How swamped preprint servers are blocking bad coronavirus research.
+Nature {[}Internet{]}.
+2020 May;580:130--1.
+Available from: \url{https://doi.org/10.1038/d41586-020-01394-6}}
+
+\leavevmode\hypertarget{ref-Stodden2020Theme}{}%
+\CSLLeftMargin{10. }
+\CSLRightInline{Stodden V.
+Theme editor's introduction to reproducibility and replicability in science.
+Harvard Data Science Review {[}Internet{]}.
+2020 Dec 16;2(4).
+Available from: \url{https://hdsr.mitpress.mit.edu/pub/kincvy67}}
+
+\leavevmode\hypertarget{ref-citeFraser}{}%
+\CSLLeftMargin{11. }
+\CSLRightInline{Fraser N, Brierley L, Dey G, Polka JK, Pálfy M, Nanni F, et al.
+Preprinting the COVID-19 pandemic.
+bioRxiv {[}Internet{]}.
+2021; Available from: \url{https://www.biorxiv.org/content/early/2021/02/05/2020.05.22.111294}}
+
+\leavevmode\hypertarget{ref-Floca2014}{}%
+\CSLLeftMargin{12. }
+\CSLRightInline{Floca R.
+Challenges of open data in medical research.
+In: Bartling S, Friesike S, editors.
+Opening science: The evolving guide on how the internet is changing research, collaboration and scholarly publishing {[}Internet{]}.
+Cham: Springer International Publishing; 2014.
+p.
+297--307.
+Available from: \url{https://doi.org/10.1007/978-3-319-00026-8_22}}
+
+\leavevmode\hypertarget{ref-citeCSSE}{}%
+\CSLLeftMargin{13. }
+\CSLRightInline{Dong E, Du H, Gardner L.
+An interactive web-based dashboard to track COVID-19 in real time.
+The Lancet Infectious Diseases {[}Internet{]}.
+2020;20:533--4.
+Available from: \url{https://doi.org/10.1016/S1473-3099(20)30120-1}}
+
+\leavevmode\hypertarget{ref-gill2020}{}%
+\CSLLeftMargin{14. }
+\CSLRightInline{Gill D. Immediate free access to research: The scholarly response to COVID-19. \url{https://www.lib.sfu.ca/help/publish/scholarly-publishing/radical-access/scholarly-covid19}; 2020. }
+
+\leavevmode\hypertarget{ref-citeWellcome}{}%
+\CSLLeftMargin{15. }
+\CSLRightInline{Wellcome Trust.
+Sharing research data and findings relevant to the novel coronavirus (COVID-19) outbreak {[}Internet{]}.
+Vienna, Austria: Wellcome Trust; 2020.
+Available from: \url{https://wellcome.org/coronavirus-covid-19/open-data}}
+
+\leavevmode\hypertarget{ref-da2021optimizing}{}%
+\CSLLeftMargin{16. }
+\CSLRightInline{Silva JAT da, Bornemann-Cimenti H, Tsigaris P.
+Optimizing peer review to minimize the risk of retracting COVID-19-related literature.
+Medicine, Health Care and Philosophy.
+2021;24(1):21--6.
+}
+
+\leavevmode\hypertarget{ref-da2021publishing}{}%
+\CSLLeftMargin{17. }
+\CSLRightInline{Silva JAT da, Tsigaris P, Erfanmanesh M. Publishing volumes in major databases related to covid-19. Scientometrics. 2021;126(1):831--42. }
+
+\leavevmode\hypertarget{ref-raynaud2021}{}%
+\CSLLeftMargin{18. }
+\CSLRightInline{Raynaud M, Zhang H, Louis K, Goutaudier V, Wang J, Dubourg Q, et al.
+COVID-19-related medical research: A meta-research and critical appraisal.
+BMC Medical Research Methodology {[}Internet{]}.
+2020;21.
+Available from: \url{https://doi.org/10.1186/s12874-020-01190-w}}
+
+\leavevmode\hypertarget{ref-ferguson2020}{}%
+\CSLLeftMargin{19. }
+\CSLRightInline{Ferguson NM, Laydon D, Nedjati-Gilani G, Imai N, Ainslie K, Baguelin M, et al.
+Report 9: Impact of non-pharmaceutical interventions (NPIs) to reduce COVID-19 mortality and healthcare demand.
+2020; Available from: \url{https://doi.org/10.25561/77482}}
+
+\leavevmode\hypertarget{ref-murray2020}{}%
+\CSLLeftMargin{20. }
+\CSLRightInline{Murray CJ.
+Forecasting the impact of the first wave of the COVID-19 pandemic on hospital demand and deaths for the USA and european economic area countries.
+medRxiv {[}Internet{]}.
+2020; Available from: \url{https://www.medrxiv.org/content/early/2020/04/26/2020.04.21.20074732}}
 
 \leavevmode\hypertarget{ref-adam2020}{}%
-Adam, David. 2020. {``Special Report: The Simulations Driving the World's Response to COVID-19.''} \emph{Nature} 580: 316--18. \url{https://doi.org/10.1038/d41586-020-01003-6}.
-
-\leavevmode\hypertarget{ref-citealexandermafouz}{}%
-Alexander, Rohan, and A Mahfouz. 2021. \emph{{heapsofpapers: Easily Download Heaps of Papers}}. \url{https://rohanalexander.github.io/heapsofpapers/}.
-
-\leavevmode\hypertarget{ref-citeCSSE}{}%
-Dong, Ensheng, Hongru Du, and Lauren Gardner.
-2020.
-{``An Interactive Web-Based Dashboard to Track COVID-19 in Real Time.''} \emph{The Lancet Infectious Diseases} 20: 533--34.
-\url{https://doi.org/10.1016/S1473-3099(20)30120-1}.
-
-\leavevmode\hypertarget{ref-else2020}{}%
-Else, Holly. 2020. {``How a Torrent of COVID Science Changed Research Publishing --- in Seven Charts.''} \emph{Nature} 588: 553. \url{https://doi.org/10.1038/d41586-020-03564-y}.
-
-\leavevmode\hypertarget{ref-ferguson2020}{}%
-Ferguson, Neil M, Daniel Laydon, Gemma Nedjati-Gilani, Natsuko Imai, Kylie Ainslie, Marc Baguelin, Sangeeta Bhatia, et al.
-2020.
-{``Report 9: Impact of Non-Pharmaceutical Interventions (NPIs) to Reduce COVID-19 Mortality and Healthcare Demand.''} \url{https://doi.org/10.25561/77482}.
-
-\leavevmode\hypertarget{ref-Floca2014}{}%
-Floca, Ralf.
-2014.
-{``Challenges of Open Data in Medical Research.''} In \emph{Opening Science: The Evolving Guide on How the Internet Is Changing Research, Collaboration and Scholarly Publishing}, edited by Sönke Bartling and Sascha Friesike, 297--307.
-Cham: Springer International Publishing.
-\url{https://doi.org/10.1007/978-3-319-00026-8_22}.
-
-\leavevmode\hypertarget{ref-citeFraser}{}%
-Fraser, Nicholas, Liam Brierley, Gautam Dey, Jessica K Polka, Máté Pálfy, Federico Nanni, and Jonathon Alexis Coates.
-2021.
-{``Preprinting the COVID-19 Pandemic.''} \emph{bioRxiv}.
-\url{https://doi.org/10.1101/2020.05.22.111294}.
-
-\leavevmode\hypertarget{ref-gill2020}{}%
-Gill, David. 2020. {``Immediate Free Access to Research: The Scholarly Response to COVID-19.''} \url{https://www.lib.sfu.ca/help/publish/scholarly-publishing/radical-access/scholarly-covid19}.
+\CSLLeftMargin{21. }
+\CSLRightInline{Adam D.
+Special report: The simulations driving the world's response to COVID-19.
+Nature {[}Internet{]}.
+2020;580:316--8.
+Available from: \url{https://doi.org/10.1038/d41586-020-01003-6}}
 
 \leavevmode\hypertarget{ref-jin2020}{}%
-Jin, Jin, Neha Agarwala, Prosenjit Kundu, Yi Wang, Ruzhang Zhao, and Nilanjan Chatterjee.
-2020.
-{``Transparency, Reproducibility, and Validation of COVID-19 Projection Models.''} \url{https://www.jhsph.edu/covid-19/articles/transparency-reproducibility-and-validation-of-covid-19-projection-models.html}.
+\CSLLeftMargin{22. }
+\CSLRightInline{Jin J, Agarwala N, Kundu P, Wang Y, Zhao R, Chatterjee N.
+Transparency, reproducibility, and validation of COVID-19 projection models.
+\url{https://www.jhsph.edu/covid-19/articles/transparency-reproducibility-and-validation-of-covid-19-projection-models.html}; 2020.
+}
+
+\leavevmode\hypertarget{ref-ledford2020}{}%
+\CSLLeftMargin{23. }
+\CSLRightInline{Ledford H, Noorden RV.
+High-profile coronavirus retractions raise concerns about data oversight.
+Nature {[}Internet{]}.
+2020;582:160.
+Available from: \url{https://doi.org/10.1038/d41586-020-01695-w}}
+
+\leavevmode\hypertarget{ref-abdill2019}{}%
+\CSLLeftMargin{24. }
+\CSLRightInline{Abdill RJ, Blekhman R.
+Meta-research: Tracking the popularity and outcomes of all bioRxiv preprints.
+Pewsey E, Rodgers P, Greene CS, editors.
+eLife {[}Internet{]}.
+2019 Apr;8:e45133.
+Available from: \url{https://doi.org/10.7554/eLife.45133}}
 
 \leavevmode\hypertarget{ref-king2017computer}{}%
-King, Gary, Patrick Lam, and Margaret E Roberts. 2017. {``Computer-Assisted Keyword and Document Set Discovery from Unstructured Text.''} \emph{American Journal of Political Science} 61 (4): 971--88.
-
-\leavevmode\hypertarget{ref-kwon2020}{}%
-Kwon, Diana. 2020. {``How Swamped Preprint Servers Are Blocking Bad Coronavirus Research.''} \emph{Nature} 580 (May): 130--31. \url{https://doi.org/10.1038/d41586-020-01394-6}.
-
-\leavevmode\hypertarget{ref-ledford2020}{}%
-Ledford, Heidi, and Richard Van Noorden. 2020. {``High-Profile Coronavirus Retractions Raise Concerns about Data Oversight.''} \emph{Nature} 582: 160. \url{https://doi.org/10.1038/d41586-020-01695-w}.
-
-\leavevmode\hypertarget{ref-mcguinness2021descriptive}{}%
-McGuinness, Luke A, and Athena L Sheppard.
-2021.
-{``A Descriptive Analysis of the Data Availability Statements Accompanying medRxiv Preprints and a Comparison with Their Published Counterparts.''} \emph{PloS One} 16 (5): e0250887.
-
-\leavevmode\hypertarget{ref-murray2020}{}%
-Murray, Christopher JL.
-2020.
-{``Forecasting the Impact of the First Wave of the COVID-19 Pandemic on Hospital Demand and Deaths for the USA and European Economic Area Countries.''} \emph{medRxiv}.
-\url{https://doi.org/10.1101/2020.04.21.20074732}.
-
-\leavevmode\hypertarget{ref-citeR}{}%
-R Core Team. 2020. \emph{{R: A Language and Environment for Statistical Computing}}. Vienna, Austria: R Foundation for Statistical Computing. \url{https://www.R-project.org/}.
-
-\leavevmode\hypertarget{ref-raynaud2021}{}%
-Raynaud, Marc, Huanxi Zhang, Kevin Louis, Valentin Goutaudier, Jiali Wang, Quentin Dubourg, Yongcheng Wei, et al.
-2020.
-{``COVID-19-Related Medical Research: A Meta-Research and Critical Appraisal.''} \emph{BMC Medical Research Methodology} 21.
-\url{https://doi.org/10.1186/s12874-020-01190-w}.
-
-\leavevmode\hypertarget{ref-citeODDPubpackage}{}%
-Riedel, Nico. 2019. \emph{Oddpub: Detection of Open Data \& Open Code Statements in Biomedical Publications}. \url{https://github.com/quest-bih/oddpub}.
-
-\leavevmode\hypertarget{ref-citePDDPub}{}%
-Riedel, Nico, Miriam Kip, and Evgeny Bobrov.
-2020.
-{``ODDPub -- a Text-Mining Algorithm to Detect Data Sharing in Biomedical Publications.''} \emph{Data Science Journal} 19 (1): 42.
-\url{https://doi.org/10.5334/dsj-2020-042}.
-
-\leavevmode\hypertarget{ref-da2021optimizing}{}%
-Silva, Jaime A Teixeira da, Helmar Bornemann-Cimenti, and Panagiotis Tsigaris.
-2021.
-{``Optimizing Peer Review to Minimize the Risk of Retracting COVID-19-Related Literature.''} \emph{Medicine, Health Care and Philosophy} 24 (1): 21--26.
-
-\leavevmode\hypertarget{ref-da2021publishing}{}%
-Silva, Jaime A Teixeira da, Panagiotis Tsigaris, and Mohammadamin Erfanmanesh. 2021. {``Publishing Volumes in Major Databases Related to Covid-19.''} \emph{Scientometrics} 126 (1): 831--42.
-
-\leavevmode\hypertarget{ref-Stodden2020Theme}{}%
-Stodden, Victoria. 2020. {``Theme Editor's Introduction to Reproducibility and Replicability in Science.''} \emph{Harvard Data Science Review} 2 (4). \url{https://doi.org/10.1162/99608f92.c46a02d4}.
-
-\leavevmode\hypertarget{ref-weissgerber2021automated}{}%
-Weissgerber, Tracey, Nico Riedel, Halil Kilicoglu, Cyril Labbé, Peter Eckmann, Gerben Ter Riet, Jennifer Byrne, et al.
-2021.
-{``Automated Screening of COVID-19 Preprints: Can We Help Authors to Improve Transparency and Reproducibility?''} \emph{Nature Medicine} 27 (1): 6--7.
-
-\leavevmode\hypertarget{ref-citeWellcome}{}%
-Wellcome Trust.
-2020.
-\emph{Sharing Research Data and Findings Relevant to the Novel Coronavirus (COVID-19) Outbreak}.
-Vienna, Austria: Wellcome Trust.
-\url{https://wellcome.org/coronavirus-covid-19/open-data}.
-
-\leavevmode\hypertarget{ref-citeWHOtimeline}{}%
-World Health Organization.
-2020.
-{``WHO Director-General's Opening Remarks at the Media Briefing on COVID-19 - 11 March 2020.''} \url{https://www.who.int/director-general/speeches/detail/who-director-general-s-opening-remarks-at-the-media-briefing-on-covid-19—11-march-2020}.
+\CSLLeftMargin{25. }
+\CSLRightInline{King G, Lam P, Roberts ME. Computer-assisted keyword and document set discovery from unstructured text. American Journal of Political Science. 2017;61(4):971--88. }
 

### 2021-10-01 outputs/paper/paper.Rmd
Update Teixeira surname citation mistake

@@
 bibliography: references.bib
-csl: vancouver.csl
 ---

### 2021-10-01 outputs/paper/paper.tex
Update Teixeira surname citation mistake

--- 2021-07-22 outputs/paper/paper.tex
@@
 
-\title{Reproducibility of COVID-19 pre-prints\thanks{We thank Amy Farrow, Jessica Gronsbell, Monica Alexander, and Thomas William Rosenthal for helpful comments.
-Collins thanks CANSSI Ontario and Monica Alexander for financial support.
-Code and data are available at: \url{https://github.com/anniecollins/reproducibility_markers_in_covid19_preprints}.}}
+\title{Reproducibility of COVID-19 pre-prints\thanks{\textbf{Acknowledgements:} We thank Amy Farrow, Jessica Gronsbell, Monica Alexander, and Thomas William Rosenthal for helpful comments.
+\textbf{Funding statement:} Collins thanks CANSSI Ontario and Monica Alexander for financial support.
+\textbf{Data accessibility statement:} Code and data are available at: \url{https://github.com/anniecollins/reproducibility_markers_in_covid19_preprints}.
+\textbf{Author contributions:} Collins had the original idea and wrote the first draft of the paper.
+Collins and Alexander obtained and created the datasets.
+Collins and Alexander analysed the data.
+All authors interpreted the data and contributed writing the paper and approved the final version.}}
 \author{Annie Collins\footnote{University of Toronto.} \and Rohan Alexander\footnote{University of Toronto, \href{mailto:rohan.alexander@utoronto.ca}{\nolinkurl{rohan.alexander@utoronto.ca}}.}}
-\date{22 July 2021}
+\date{01 October 2021}
 
@@
 The COVID-19 pandemic has seen open science initiatives, as evidenced by the creation of open data repositories such as the dashboard maintained by the Center for Systems Science and Engineering at Johns Hopkins University (Dong, Du, and Gardner 2020) or the large number of publishers who have removed paywalls from published COVID-19 research (Gill 2020).
-While the intention at the start of the pandemic was that there would be `clear statements regarding the availability of underlying data' (Wellcome Trust 2020) some retractions of work have been based on `unreliable or nonexistent data' (Silva, Bornemann-Cimenti, and Tsigaris 2021).
+While the intention at the start of the pandemic was that there would be `clear statements regarding the availability of underlying data' (Wellcome Trust 2020) some retractions of work have been based on `unreliable or nonexistent data' (Teixeira da Silva, Bornemann-Cimenti, and Tsigaris 2021).
 SocArXiv asks submitters to make explicit the degree of openness in the data, and this is something that could be easily adopted by other pre-print repositories.
@@
 
-There has been a large amount of research on COVID-19 (Silva, Tsigaris, and Erfanmanesh 2021).
+There has been a large amount of research on COVID-19 (Teixeira da Silva, Tsigaris, and Erfanmanesh 2021).
 Many concerns have arisen from the rate at which COVID-19 research has been posted and consumed via pre-print repositories, particularly in the early stages of the pandemic (Raynaud et al.
@@
 
+\leavevmode\hypertarget{ref-Stodden2020Theme}{}%
+Stodden, Victoria. 2020. {``Theme Editor's Introduction to Reproducibility and Replicability in Science.''} \emph{Harvard Data Science Review} 2 (4). \url{https://doi.org/10.1162/99608f92.c46a02d4}.
+
 \leavevmode\hypertarget{ref-da2021optimizing}{}%
-Silva, Jaime A Teixeira da, Helmar Bornemann-Cimenti, and Panagiotis Tsigaris.
+Teixeira da Silva, Jaime A, Helmar Bornemann-Cimenti, and Panagiotis Tsigaris.
 2021.
@@
 \leavevmode\hypertarget{ref-da2021publishing}{}%
-Silva, Jaime A Teixeira da, Panagiotis Tsigaris, and Mohammadamin Erfanmanesh. 2021. {``Publishing Volumes in Major Databases Related to Covid-19.''} \emph{Scientometrics} 126 (1): 831--42.
-
-\leavevmode\hypertarget{ref-Stodden2020Theme}{}%
-Stodden, Victoria. 2020. {``Theme Editor's Introduction to Reproducibility and Replicability in Science.''} \emph{Harvard Data Science Review} 2 (4). \url{https://doi.org/10.1162/99608f92.c46a02d4}.
+Teixeira da Silva, Jaime A, Panagiotis Tsigaris, and Mohammadamin Erfanmanesh. 2021. {``Publishing Volumes in Major Databases Related to Covid-19.''} \emph{Scientometrics} 126 (1): 831--42.
 
@@
 2020.
-{``WHO Director-General's Opening Remarks at the Media Briefing on COVID-19 - 11 March 2020.''} \url{https://www.who.int/director-general/speeches/detail/who-director-general-s-opening-remarks-at-the-media-briefing-on-covid-19—11-march-2020}.
+{``WHO Director-General's Opening Remarks at the Media Briefing on COVID-19 - 11 March 2020.''} \url{https://www.who.int/director-general/speeches/detail/who-director-general-s-opening-remarks-at-the-media-briefing-on-covid-19---11-march-2020}.
 

### 2021-12-08 outputs/paper/paper.Rmd
Update references

@@
   - Rohan Alexander^[University of Toronto, rohan.alexander@utoronto.ca.]
-thanks: "**Acknowledgements:** We thank Amy Farrow, Jessica Gronsbell, Monica Alexander, and Thomas William Rosenthal for helpful comments.
+thanks: "**Preprint:** This present manuscript is a version of a preprint by the authors [@collins2021reproducibility].
+The text, tables and figures of this manuscript overlap with those of the preprint version by the authors.
+**Acknowledgements:** We thank Amy Farrow, Jessica Gronsbell, Monica Alexander, and Thomas William Rosenthal for helpful comments.
 **Funding statement:** Collins thanks CANSSI Ontario and Monica Alexander for financial support.
@@
 While the intention at the start of the pandemic was that there would be 'clear statements regarding the availability of underlying data' [@citeWellcome] some retractions of work have been based on 'unreliable or nonexistent data' [@da2021optimizing].
-SocArXiv asks submitters to make explicit the degree of openness in the data, and this is something that could be easily adopted by other pre-print repositories.
+SocArXiv asks submitters to make explicit the degree of openness in the data, and this is something that could be adopted by other pre-print repositories.
 
@@
 This need is again emphasized by the new-found speed at which pre-prints may gain public, media, and political attention in the context of the pandemic, particularly those from medRxiv and bioRxiv.
+One further concern is raised by @da2020silently, who show that there are pre-prints on those two pre-print servers---medRxiv and bioRxiv---that were withdrawn or retracted with relatively little information about the underlying reason, after gaining substantial media attention.
 
@@
 Concerns have already been raised through systemic reviews of COVID-19 publications [@raynaud2021], and oversights in data accessibility have led to high profile retractions of publications in the past; for example, papers from *The Lancet* and the *New England Journal of Medicine* which were withdrawn due to concerns over the private nature of their underlying dataset [@ledford2020].
+Further, @cabanac2021day show that not all pre-prints are linked to their subsequent peer-reviewed publication, which may further bias our results.
+And @oikonomidi2020changes and @Beroe051821 show that differences between updated versions of the same pre-print can be substantial; again this is something that we do not account for and could bias our results.
 

### 2021-12-08 outputs/paper/paper.tex
Update references

@@
 
-\title{Reproducibility of COVID-19 pre-prints\thanks{\textbf{Acknowledgements:} We thank Amy Farrow, Jessica Gronsbell, Monica Alexander, and Thomas William Rosenthal for helpful comments.
+\title{Reproducibility of COVID-19 pre-prints\thanks{\textbf{Preprint:} This present manuscript is a version of a preprint by the authors (Collins and Alexander 2021).
+The text, tables and figures of this manuscript overlap with those of the preprint version by the authors.
+\textbf{Acknowledgements:} We thank Amy Farrow, Jessica Gronsbell, Monica Alexander, and Thomas William Rosenthal for helpful comments.
 \textbf{Funding statement:} Collins thanks CANSSI Ontario and Monica Alexander for financial support.
@@
 \author{Annie Collins\footnote{University of Toronto.} \and Rohan Alexander\footnote{University of Toronto, \href{mailto:rohan.alexander@utoronto.ca}{\nolinkurl{rohan.alexander@utoronto.ca}}.}}
-\date{01 October 2021}
+\date{08 December 2021}
 
@@
 While the intention at the start of the pandemic was that there would be `clear statements regarding the availability of underlying data' (Wellcome Trust 2020) some retractions of work have been based on `unreliable or nonexistent data' (Teixeira da Silva, Bornemann-Cimenti, and Tsigaris 2021).
-SocArXiv asks submitters to make explicit the degree of openness in the data, and this is something that could be easily adopted by other pre-print repositories.
+SocArXiv asks submitters to make explicit the degree of openness in the data, and this is something that could be adopted by other pre-print repositories.
 
@@
 This need is again emphasized by the new-found speed at which pre-prints may gain public, media, and political attention in the context of the pandemic, particularly those from medRxiv and bioRxiv.
+One further concern is raised by Teixeira da Silva (2020), who show that there are pre-prints on those two pre-print servers---medRxiv and bioRxiv---that were withdrawn or retracted with relatively little information about the underlying reason, after gaining substantial media attention.
 
@@
 2020), and oversights in data accessibility have led to high profile retractions of publications in the past; for example, papers from \emph{The Lancet} and the \emph{New England Journal of Medicine} which were withdrawn due to concerns over the private nature of their underlying dataset (Ledford and Noorden 2020).
+Further, Cabanac, Oikonomidi, and Boutron (2021) show that not all pre-prints are linked to their subsequent peer-reviewed publication, which may further bias our results.
+And Oikonomidi et al.
+(2020) and Bero et al.
+(2021) show that differences between updated versions of the same pre-print can be substantial; again this is something that we do not account for and could bias our results.
 
@@
 Alexander, Rohan, and A Mahfouz. 2021. \emph{{heapsofpapers: Easily Download Heaps of Papers}}. \url{https://rohanalexander.github.io/heapsofpapers/}.
+
+\leavevmode\hypertarget{ref-Beroe051821}{}%
+Bero, Lisa, Rosa Lawrence, Louis Leslie, Kellia Chiu, Sally McDonald, Matthew J Page, Quinn Grundy, et al.
+2021.
+{``Cross-Sectional Study of Preprints and Final Journal Publications from COVID-19 Studies: Discrepancies in Results Reporting and Spin in Interpretation.''} \emph{BMJ Open} 11 (7).
+\url{https://doi.org/10.1136/bmjopen-2021-051821}.
+
+\leavevmode\hypertarget{ref-cabanac2021day}{}%
+Cabanac, Guillaume, Theodora Oikonomidi, and Isabelle Boutron. 2021. {``Day-to-Day Discovery of Preprint--Publication Links.''} \emph{Scientometrics} 126 (6): 5285--5304.
+
+\leavevmode\hypertarget{ref-collins2021reproducibility}{}%
+Collins, Annie, and Rohan Alexander. 2021. {``Reproducibility of COVID-19 Pre-Prints.''} \url{http://arxiv.org/abs/2107.10724}.
 
@@
 
+\leavevmode\hypertarget{ref-oikonomidi2020changes}{}%
+Oikonomidi, Theodora, Isabelle Boutron, Olivier Pierre, Guillaume Cabanac, and Philippe Ravaud.
+2020.
+{``Changes in Evidence for Studies Assessing Interventions for COVID-19 Reported in Preprints: Meta-Research Study.''} \emph{BMC Medicine} 18 (1): 1--10.
+
 \leavevmode\hypertarget{ref-citeR}{}%
@@
 Stodden, Victoria. 2020. {``Theme Editor's Introduction to Reproducibility and Replicability in Science.''} \emph{Harvard Data Science Review} 2 (4). \url{https://doi.org/10.1162/99608f92.c46a02d4}.
+
+\leavevmode\hypertarget{ref-da2020silently}{}%
+Teixeira da Silva, Jaime A.
+2020.
+{``Silently Withdrawn or Retracted Preprints Related to Covid-19 Are a Scholarly Threat and a Potential Public Health Risk: Theoretical Arguments and Suggested Recommendations.''} \emph{Online Information Review}.
 

### 2022-01-10 outputs/paper/paper.Rmd
Add reviewers comments doc and start of minor updates

@@
 **Acknowledgements:** We thank Amy Farrow, Jessica Gronsbell, Monica Alexander, and Thomas William Rosenthal for helpful comments.
+Two anonymous reviewers and the editor provided extensive comments that substantially improved this paper and we are grateful to them.
 **Funding statement:** Collins thanks CANSSI Ontario and Monica Alexander for financial support.
@@
 
-Scientists use open repositories of papers to disseminate their research more quickly than is possible in traditional journals or conference proceedings.
+Scientists use open repositories of papers to disseminate their research more quickly than is possible in traditional journals or conference proceedings, and also to obtain feedback on their work prior to publication.
 These repositories, such as arXiv, bioRxiv, medRxiv, and SocArXiv, are a critical component of scientific communication and a lot of research builds on the pre-prints posted there.
@@
 Following @weissgerber2021automated, we examine pre-prints about COVID-19 posted to arXiv, bioRxiv, medRxiv, and SocArXiv from 28 January 2020 through to 30 June 2021.
-By way of background, each of these four repositories has a different focus: arXiv is general, bioRxiv focuses on biological sciences, medRxiv focuses on health sciences, and SocArXiv focuses on social sciences.
+By way of background, each of these four repositories has a different focus: arXiv is general although it has especially high rates of usage from fields like mathematics, physics, and computer science, bioRxiv focuses on biological sciences, medRxiv focuses on health sciences, and SocArXiv focuses on social sciences.
 We search for markers of open science as indicators of reproducibility, specifically open data and open code.

### 2022-01-10 outputs/paper/paper.tex
Add reviewers comments doc and start of minor updates

@@
 \textbf{Acknowledgements:} We thank Amy Farrow, Jessica Gronsbell, Monica Alexander, and Thomas William Rosenthal for helpful comments.
+Two anonymous reviewers and the editor provided extensive comments that substantially improved this paper and we are grateful to them.
 \textbf{Funding statement:} Collins thanks CANSSI Ontario and Monica Alexander for financial support.
@@
 \author{Annie Collins\footnote{University of Toronto.} \and Rohan Alexander\footnote{University of Toronto, \href{mailto:rohan.alexander@utoronto.ca}{\nolinkurl{rohan.alexander@utoronto.ca}}.}}
-\date{08 December 2021}
+\date{16 December 2021}
 
@@
 (2021), we examine pre-prints about COVID-19 posted to arXiv, bioRxiv, medRxiv, and SocArXiv from 28 January 2020 through to 30 June 2021.
-By way of background, each of these four repositories has a different focus: arXiv is general, bioRxiv focuses on biological sciences, medRxiv focuses on health sciences, and SocArXiv focuses on social sciences.
+By way of background, each of these four repositories has a different focus: arXiv is general although it has especially high rates of usage from fields like mathematics, physics, and computer science, bioRxiv focuses on biological sciences, medRxiv focuses on health sciences, and SocArXiv focuses on social sciences.
 We search for markers of open science as indicators of reproducibility, specifically open data and open code.

### 2022-01-11 outputs/paper/paper.Rmd
Updates to paper structure and figures

@@
          updated = as_date(updated))
+
+cbPalette <- c("#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
+
 ```
@@
 
-```{r monthly-papers-total, fig.cap = "Number of pre-prints related to COVID-19", out.width="90%", fig.align = "center"}
+```{r monthly-papers-total, fig.cap = "Number of pre-prints related to COVID-19 posted to arXiv (N = 4,250), bioRxiv (N = 4,146), medRxiv (N = 13,194), and SocArXiv (N = 478) per month", out.width="90%", fig.align = "center", fig.pos="H"}
 just_arxiv <- 
@@
   labs(title = "COVID-19-related pre-prints posted per month",
-       subtitle = "Total of 4,250 relevant pre-prints on arXiv, 4,146 on bioRxiv, 13,194 on medRxiv, and \n478 on SocArXiv.",
        x = "Month",
@@
   theme_minimal() +
-  scale_fill_manual(values = wes_palette("Darjeeling1")) +
+  scale_fill_manual(values = cbPalette) +
   facet_wrap(~type,
@@
 # Results
+
+## Pre-pandemic pre-prints
+
+To examine the influence of the COVID-19 pandemic on open science practices during the pandemic, we analyzed pre-prints posted between January and December 2019 from each of the four repositories in question.
+Since medRxiv was founded in June 2019, all pre-prints posted in the latter half of 2019 were analyzed (a total of 913).
+For all other repositories, a random sample of 1,200 was taken from all non-COVID-19-related pre-prints posted in the relevant date range.
+
+```{r 2019-results-med-arxiv, out.width="90%", fig.align='center', fig.cap = "Number of pre-prints posted per month in 2019 to arXiv (N = 150,018), bioRxiv (N = 31,752), medRxiv (N = 913), and SocArXiv (N = 1,614) per month", fig.pos="H"}
+bio_2019 <- bio_2019_results %>%
+  select(date) %>%
+  mutate(type = "bioRxiv")
+
+med_2019 <- med_2019_open_data_results %>%
+  select(date) %>%
+  mutate(type = "medRxiv")
+
+socarxiv_2019 <- socarxiv_metadata_2019 %>%
+  select(date_created) %>%
+  mutate(type = "socArXiv") %>%
+  rename(date = date_created)
+
+arxiv_2019 <- all_arxiv_2019_results %>%
+  select(submitted) %>%
+  mutate(type = "arXiv") %>%
+  rename(date = submitted)
+
+all_2019 <- rbind(arxiv_2019, bio_2019, med_2019, socarxiv_2019)
+
+all_2019 %>% 
+  mutate(month = floor_date(date, "month")) %>% 
+  # filter(year(date) >= 2020) %>% 
+  ggplot(aes(x = month, fill = type)) + 
+  geom_histogram(stat="count", position = "dodge2") +
+  labs(title = "Pre-prints posted per month, 2019",
+       x = "Month",
+       y = "Number of pre-prints",
+       fill = "Repository") +
+  theme_minimal() +
+  scale_fill_manual(values = cbPalette) +
+  facet_wrap(~type,
+             scales = "free_y") +
+  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
+```
+
+Between June and December 2019, the number of pre-prints posted to medRxiv monthly saw an overall increase, which may be expected as the repository gained recognition and popularity in the medical research community (Figure \@ref(fig:2019-results-med-arxiv)).
+The number of pre-prints posted monthly to bioRxiv also saw a slight overall increase throughout 2019, while the number of those posted to arXiv and SocArXiv fluctuated throughout the year (Figure \@ref(fig:2019-results-med-arxiv)).
+Due to its relative immaturity at the beginning of the COVID-19 pandemic, a significant portion of medRxiv's overall usage has been dedicated to COVID-19-related research.
+In total, 21,647 pre-prints were posted to medRxiv between June 2019 and 30 June, 2021, 13,194 of which (approximately 61 per cent) relate to COVID-19.
+
+Of the analyzed pre-prints from 2019, 93 per cent of those posted to arXiv, 63 per cent of those posted to bioRxiv, 75 per cent of those posted to medRxiv, 92 per cent of those posted to SocArXiv showed no indication of open data or open code (Table \@ref(tab:2019-published)).
+
+```{r monthly-papers-condition-stack-2019, fig.cap = "Number of sampled pre-prints posted in 2019 from arXiv (n = 1,200), bioRxiv (n = 1,200), medRxiv (n = 913), and SocArXiv (n = 1,200) distinguished by presence of open data or code markers", out.width="90%", fig.align = "center"}
+# Number of papers for each open data/code status per month
+open_status_med_2019 <-
+  med_2019_open_data_results %>%
+  select(title, date, is_open_code, is_open_data) %>%
+  mutate(condition = is_open_data + is_open_code, repo = "medRxiv")
+
+open_status_bio_2019 <-
+  bio_2019_open_data_results %>%
+  select(title, date, is_open_code, is_open_data) %>%
+  mutate(condition = is_open_data + is_open_code, repo = "bioRxiv", date = as.character(date))
+
+open_status_arxiv_2019 <-
+  arxiv_2019_open_data_results %>%
+  select(title, submitted, is_open_code, is_open_data) %>%
+  mutate(condition = is_open_data + is_open_code, repo = "arXiv", date = as.character(submitted) %>% str_sub(end = 10)) %>%
+  select(title, date, is_open_code, is_open_data, condition, repo)
+
+open_status_socarxiv_2019 <-
+  socarxiv_2019_open_data_results %>%
+  select(title, date_created, is_open_code, is_open_data) %>%
+  mutate(condition = is_open_data + is_open_code, repo = "SocArXiv", date = as.character(date_created)) %>%
+  select(title, date, is_open_code, is_open_data, condition, repo)
+
+open_status <- rbind(open_status_med_2019, open_status_bio_2019, open_status_arxiv_2019, open_status_socarxiv_2019)
+
+open_status$date <- as.Date(open_status$date)
+open_status$condition[open_status$condition == 2] <- "Both"
+open_status$condition[open_status$condition == 0] <- "Neither"
+open_status$condition[open_status$condition == 1 & open_status$is_open_code == 1] <- "Open Code"
+open_status$condition[open_status$condition == 1 & open_status$is_open_data == 1] <- "Open Data"
+
+open_status %>%
+  ggplot() +
+  geom_bar(aes(x = factor(floor_date(date, "month")),
+              fill=factor(condition, levels = c("Neither", "Open Code", "Open Data", "Both")),
+              position = "stack")) +
+  labs(fill = "Type of marker") +
+  scale_x_discrete(breaks=c("2019-01-01","2019-07-01", "2019-12-01"),
+                   labels=c("Jan 2019", "Jul 2019", "Dec 2019")) +
+  ylab("Number of pre-prints") +
+  xlab("Month") +
+  labs(title="Sampled pre-prints by month, 2019", subtitle="Note the different y-axes.") +
+  theme_minimal() +
+  scale_fill_manual(values = cbPalette) +
+  facet_wrap(~repo,
+             scales = "free_y")
+```
+
+```{r 2019-published, fig.pos="H"}
+med_published_2019 <- 
+  med_2019_open_data_results %>% 
+  select(title, date, published) %>% 
+  mutate(repo = "medRxiv", published = as.numeric(published))
+
+bio_published_2019 <- 
+  bio_2019_results %>% 
+  select(title, date, published) %>% 
+  mutate(repo = "bioRxiv", published = as.numeric(!is.na(published)))
+
+socarxiv_published_2019 <- 
+  socarxiv_metadata_2019 %>% 
+  select(title, date_created, links.doi) %>% 
+  mutate(repo = "socArXiv", published = as.numeric(!is.na(links.doi))) %>%
+  rename(date = date_created) %>%
+  select(title, date, published, repo)
+
+arxiv_published_2019 <-
+  all_arxiv_2019_results %>%
+  select(title, submitted, doi) %>%
+  mutate(repo = "arXiv", published = as.numeric(!is.na(doi))) %>%
+  rename(date = submitted) %>%
+  select(title, date, published, repo)
+
+published_2019 <- rbind(med_published_2019, bio_published_2019, socarxiv_published_2019, arxiv_published_2019)
+
+published_2019 %>% 
+  group_by(repo) %>% 
+  summarise(`Published pre-prints` = sum(published), `Proportion published` = mean(published) %>% round(2)) %>%
+  kable(caption = "Counts and proportion of published COVID-19 pre-prints in each repository, 2019",
+        col.names = c("Repositiory", "Published pre-prints", "Proportion published"),
+        format.args = list(big.mark = ","))
+```
+
+```{r, 2019-open-publishing}
+med_2019_published_open_status <- 
+  med_2019_open_data_results %>% 
+  select(title, date, published, is_open_code, is_open_data) %>% 
+  mutate(condition = is_open_data + is_open_code, repo = "medRxiv")
+
+bio_2019_published_open_status <- 
+  bio_2019_open_data_results %>% 
+  select(title, date, published, is_open_code, is_open_data) %>% 
+  mutate(condition = is_open_data + is_open_code, repo = "bioRxiv")
+
+socarxiv_2019_published_open_status <- 
+  socarxiv_2019_open_data_results %>%
+  mutate(published = !is.na(links.doi) %>% as.numeric()) %>%
+  select(title, date_created, published, is_open_code, is_open_data) %>%
+  rename(date = date_created) %>%
+  mutate(condition = is_open_data + is_open_code, repo = "socArXiv")
+
+arxiv_2019_published_open_status <- 
+  arxiv_2019_open_data_results %>%
+  mutate(published = !is.na(doi) %>% as.numeric()) %>%
+  select(title, submitted, published, is_open_code, is_open_data) %>%
+  rename(date = submitted) %>%
+  mutate(condition = is_open_data + is_open_code, repo = "arXiv")
+
+published_2019_open_status <- rbind(med_2019_published_open_status, bio_2019_published_open_status, socarxiv_2019_published_open_status, arxiv_2019_published_open_status)
+
+published_2019_open_status$condition[published_2019_open_status$condition == 2] <- "Both"
+published_2019_open_status$condition[published_2019_open_status$condition == 0] <- "Neither"
+published_2019_open_status$condition[published_2019_open_status$condition == 1 & published_2019_open_status$is_open_code == 1] <- "Open code"
+published_2019_open_status$condition[published_2019_open_status$condition == 1 & published_2019_open_status$is_open_data == 1] <- "Open data"
+
+published_2019_open_status %>%
+  count(repo, published, condition) %>% 
+  pivot_wider(names_from = condition, values_from = n, values_fill = 0) %>%
+  mutate(Status = ifelse(published == 0, "Unpublished", "Published"), `Proportion with neither`= round((`Neither`)/(`Open data` + `Open code` + Both + Neither), 2)) %>%
+  select(Status, Both, Neither, `Open code`, `Open data`, `Proportion with neither`) %>%
+  kable(caption = "Counts and proportions of open data markers by whether the pre-print was published, 2019",
+        booktabs = TRUE,
+        format.args = list(big.mark = ",")) %>%
+  group_rows(index = c("arXiv" = 2, "bioRxiv" = 2, "medRxiv" = 2, "socArXiv" = 2))
+```
+
+Examining publication rates for pre-pandemic papers, we observe that 41 per cent of pre-prints posted to arXiv, 64 per cent of pre-prints posted to bioRxiv, 61 per cent of pre-prints posted to medRxiv, and 37 per cent of pre-prints posted to SocArXiv during 2019 were eventually peer reviewed and published (Table \@ref(tab:2019-published)).
+When disaggregated by open data and code status, we find that published and unpublished pre-prints contain open data and code markers in similar proportions (Table \@ref(tab:2019-open-publishing)).
+
+<!-- MOVE TO AFTER COVID PAPERS
+
+These rates are at least double those of the COVID-19-related pre-prints posted in each repository during 2020 and 2021.
+When disaggregated by open data and code status, we find that published and unpublished pre-prints contain open data and code markers in similar proportions (Table \@ref(tab:2019-open-publishing)).
+This mimics the behaviour of published and unpublished COVID-19-related pre-prints.
+-->
 
@@
   mutate(prop_total = n / sum(n)) %>%
-  mutate(is_open_data = ifelse(is_open_data == 0, "No", "Yes"),
-         is_open_code = ifelse(is_open_code == 0, "No", "Yes")) %>%
+  # mutate(is_open_data = ifelse(is_open_data == 0, "No", "Yes"),
+  #        is_open_code = ifelse(is_open_code == 0, "No", "Yes")) %>%
   select(is_open_data, is_open_code, n, prop_total)
-```
-
-```{r summarycounts-repositories}
-# open data/open code count summary table
-
-all_by_type <- 
-  all %>%
-  group_by(type) %>%
-  count(is_open_data, is_open_code) %>%
-  mutate(prop_total = n / sum(n)) %>%
-  mutate(is_open_data = ifelse(is_open_data == 0, "No", "Yes"),
-         is_open_code = ifelse(is_open_code == 0, "No", "Yes")) %>%
-  ungroup() %>%
-  select(is_open_data, is_open_code, n, prop_total)
-
-rbind(all_total, all_by_type) %>% 
-  kable(col.names = c("Open data markers", "Open code markers", "Count", "Proportion of total"),
-        caption = "Count and proportions of open data and code markers by pre-print repository",
-        booktabs = TRUE,
-        digits = 2,
-        format.args = list(big.mark = ",")) %>%
-  group_rows(index = c("Total" = 4, "arXiv" = 4, "bioRxiv" = 4, "medRxiv" = 4, "SocArXiv" = 4))
 ```
@@
 
-```{r monthly-papers-condition-stack, fig.cap = "Number of sampled pre-prints related to COVID-19, distinguished by presence of open data or code markers", out.width="90%", fig.align = "center"}
+The proportion of bioRxiv and medRxiv pre-prints lacking both open data and open code are approximately four per cent higher than the corresponding proportions of 2019 pre-prints, suggesting that the analyzed pre-prints from 2019 may contain an overall higher prevalence of open data and code markers than pre-prints concerning COVID-19.
+Specifically, we found that open data availability in medRxiv pre-prints was significantly associated with a pre-pandemic registration date ($\chi$^2^ = 4.8508, p < 0.005), as was open code availability for bioRxiv pre-prints ($\chi$^2^ = 14.491, p < 0.005).
+This would suggest that open data and code practices may have suffered in the context of COVID-19, or that it may be something that is backfilled after posting.
+
+On the other hand, the analyzed arXiv and SocArXiv COVID-19-related pre-prints contain a higher proportion of open data and code markers overall than their 2019 counterparts, with a increase of seven per cent in sampled SocArXiv pre-prints and 18 per cent in sampled arXiv papers.
+For these repositories, the presence of both open data and open code markers was significantly associated with registration during the pandemic, suggesting that pre-prints related to COVID-19 in arXiv and SocArXiv may have more consistently adhered to open science practices than their pre-pandemic counterparts ($\chi$^2^ = 93.124, arXiv open data;  $\chi$^2^ = 106.88, arXiv open code; $\chi$^2^ = 12.303, SocArXiv open data; $\chi$^2^ = 8.1598, SocArXiv open code; p < 0.005).
+
+```{r monthly-papers-condition-stack, fig.cap = "Number of sampled pre-prints related to COVID-19 from arXiv (n = 1,000), bioRxiv (n = 1,000), medRxiv (n = 1,500), and SocArXiv (n = 478) distinguished by presence of open data or code markers", out.width="90%", fig.align = "center"}
 # Number of papers for each open data/code status per month
@@
   xlab("Month") +
-  labs(title="Sampled pre-prints by month", subtitle="Sample size from arXiv is 1,000, from bioRxiv is 1,000, from medRxiv is 1,500, and from \nSocArXiv is 410. Note the different y-axes.") +
+  labs(title="Sampled pre-prints by month", subtitle="Note the different y-axes.") +
   theme_minimal() +
-  scale_fill_manual(values = wes_palette("Darjeeling1")) +
+  scale_fill_manual(values = cbPalette) +
   facet_wrap(~repo,
@@
 This is high in comparison to the proportions from arXiv and SocArXiv, and although this might suggest that COVID-19-related pre-prints in biomedical fields have received greater attention overall than pre-prints from other fields, our results in Section \@ref(pre-pandemic-pre-prints) suggest that this pattern pre-dates the pandemic.
+These rates are also low in comparison to 2019 pre-prints (approximately half), which is likely a result of publication delays and the high volume of research output related to COVID-19 posted as pre-prints.
+
+<!-- Does this make sense? Should find source, check citeFraser paper -->
 
@@
   pivot_wider(names_from = condition, values_from = n, values_fill = 0) %>%
-  mutate(Published = ifelse(published == 0, "No", "Yes"), `Proportion with neither`= round((`Neither`)/(`Open data` + `Open code` + Both + Neither), 2)) %>%
-  select(Published, Both, Neither, `Open code`, `Open data`, `Proportion with neither`) %>%
+  mutate(Status = ifelse(published == 0, "Unpublished", "Published"), `Proportion with neither`= round((`Neither`)/(`Open data` + `Open code` + Both + Neither), 2)) %>%
+  select(Status, Both, Neither, `Open code`, `Open data`, `Proportion with neither`) %>%
   kable(caption = "Counts and proportions of open data markers by whether the pre-print was published",
@@
 
-```{r open-published-stack, fig.cap= "Number of pre-prints in sample with open data or open code markers \nby publication status", out.width="90%", fig.align = "center"}
-
-# TODO: are these graphs even necessary?
-
-# published_open_status$published[published_open_status$published == 0] <- "Published"
-# published_open_status$published[published_open_status$published == 1] <- "Unpublished"
-
-# published_open_status %>% 
-#   mutate(published = ifelse(published == 0, "Unpublished", "Published")) %>%
-#   ggplot() + 
-#   geom_bar(aes(x = published, fill=factor(condition, levels = c("Neither", "Open code", "Open data", "Both")), position = "stack")) +
-#   labs(fill = "Type of marker",
-#        y = "Number of pre-prints",
-#        x = "Publication status") +
-#   ggtitle("Pre-prints by publication status") +
-#   theme_minimal() +
-#   facet_wrap(~repo) + 
-#   scale_fill_manual(values = wes_palette("Darjeeling1"))
-
-```
-
 Our dataset likely imperfectly characterizes publication and does not have the publication details for some papers that were published.
 And even if it were a perfect record, there is a publication lag (estimated at an average of around 60 days for COVID-19-related pre-prints, although that varies by discipline) that may especially skew the results for pre-prints in the latter portion of our sample [@kwon2020].
-
-## Pre-pandemic pre-prints
-
-To examine the influence of the COVID-19 pandemic on open science practices during the pandemic, we analyzed pre-prints posted between January and December 2019 from each of the four repositories using the same process as was done for the COVID-19-related pre-prints.
-Since medRxiv was founded in June 2019, all pre-prints posted in the latter half of 2019 were analyzed (a total of 913).
-For all other repositories, a random sample of 1,200 was taken from all non-COVID-19-related pre-prints posted in the relevant date range.
-
-```{r 2019-results-med-arxiv, out.width="90%", fig.align='center', fig.cap = "Number of pre-prints posted per month to arXiv, bioRxiv, medRxiv, and SocArXiv in 2019"}
-bio_2019 <- bio_2019_results %>%
-  select(date) %>%
-  mutate(type = "bioRxiv")
-
-med_2019 <- med_2019_open_data_results %>%
-  select(date) %>%
-  mutate(type = "medRxiv")
-
-socarxiv_2019 <- socarxiv_metadata_2019 %>%
-  select(date_created) %>%
-  mutate(type = "socArXiv") %>%
-  rename(date = date_created)
-
-arxiv_2019 <- all_arxiv_2019_results %>%
-  select(submitted) %>%
-  mutate(type = "arXiv") %>%
-  rename(date = submitted)
-
-all_2019 <- rbind(arxiv_2019, bio_2019, med_2019, socarxiv_2019)
-
-all_2019 %>% 
-  mutate(month = floor_date(date, "month")) %>% 
-  # filter(year(date) >= 2020) %>% 
-  ggplot(aes(x = month, fill = type)) + 
-  geom_histogram(stat="count", position = "dodge2") +
-  labs(title = "Pre-prints posted per month, 2019",
-       subtitle = "Total of 150,018 pre-prints on arXiv and 31,752 on bioRxiv, 913 pre-prints on \n medRxiv and 1,614 on SocArXiv",
-       x = "Month",
-       y = "Number of pre-prints",
-       fill = "Repository") +
-  theme_minimal() +
-  scale_fill_manual(values = wes_palette("Darjeeling1")) +
-  facet_wrap(~type,
-             scales = "free_y") +
-  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
-```
-
-```{r 2019-open-results}
-just_2019_medRxiv <-
-  med_2019_open_data_results  %>%
-  mutate(date = as.Date(date), type = "medRxiv")  %>%
-  select(date, is_open_data, is_open_code, type)
-
-just_2019_bioRxiv <-
-  bio_2019_open_data_results  %>%
-  select(date, is_open_data, is_open_code) %>%
-  mutate(date = as.Date(date), type = "bioRxiv")
-
-just_2019_socarxiv <- 
-  socarxiv_2019_open_data_results %>%
-  select(date_created, is_open_data, is_open_code) %>%
-  mutate(date = as.Date(date_created), type = "socArXiv") %>%
-  select(date, is_open_data, is_open_code, type)
-
-just_2019_arxiv <-
-  arxiv_2019_open_data_results %>%
-  select(submitted, is_open_data, is_open_code) %>%
-  mutate(date = as.Date(submitted), type = "arXiv") %>%
-  select(date, is_open_data, is_open_code, type)
-
-all_2019 <- rbind(just_2019_medRxiv, just_2019_bioRxiv, just_2019_socarxiv, just_2019_arxiv)
-
-all_2019_total <- 
-  all_2019 %>%
-  count(is_open_data, is_open_code) %>%
-  mutate(prop_total = n / sum(n)) %>%
-  mutate(is_open_data = ifelse(is_open_data == 0, "No", "Yes"),
-         is_open_code = ifelse(is_open_code == 0, "No", "Yes")) %>%
-  select(is_open_data, is_open_code, n, prop_total)
-
-all_2019_by_type <- 
-  all_2019 %>%
-  group_by(type) %>%
-  count(is_open_data, is_open_code) %>%
-  mutate(prop_total = n / sum(n)) %>%
-  mutate(is_open_data = ifelse(is_open_data == 0, "No", "Yes"),
-         is_open_code = ifelse(is_open_code == 0, "No", "Yes")) %>%
-  ungroup() %>%
-  select(is_open_data, is_open_code, n, prop_total)
-
-rbind(all_2019_total, all_2019_by_type) %>% 
-  kable(col.names = c("Open data markers", "Open code markers", "Count", "Proportion of total"),
-        caption = "Count and proportions of open data and code markers by pre-print repository in 2019 sample",
-        booktabs = TRUE,
-        digits = 2,
-        format.args = list(big.mark = ",")) %>%
-  group_rows(index = c("Total" = 4, "arXiv" = 4, "bioRxiv" = 4, "medRxiv" = 4, "SocArXiv" = 4))
-
-```
-
-Between June and December 2019, the number of pre-prints posted to medRxiv monthly saw an overall increase, which may be expected as the repository gained recognition and popularity in the medical research community (Figure \@ref(fig:2019-results-med-arxiv)).
-The number of pre-prints posted monthly to bioRxiv also saw a slight overall increase throughout 2019, while the number of those posted to arXiv and SocArXiv fluctuated throughout the year (Figure \@ref(fig:2019-results-med-arxiv)).
-Due to its relative immaturity at the beginning of the COVID-19 pandemic, a significant portion of medRxiv's overall usage has been dedicated to COVID-19-related research.
-In total, 21,647 pre-prints were posted to medRxiv between June 2019 and 30 June, 2021, 13,194 of which (approximately 61 per cent) relate to COVID-19.
-
-Of the analyzed pre-prints from 2019, 93 per cent of those posted to arXiv, 63 per cent of those posted to bioRxiv, 75 per cent of those posted to medRxiv, 92 per cent of those posted to SocArXiv showed no indication of open data or open code (Table \@ref(tab:2019-published)).
-Both the bioRxiv and medRxiv rates are approximately four per cent lower than the corresponding proportions of COVID-19-related pre-prints, suggesting that the analyzed pre-prints from 2019 may contain an overall higher prevalence of open data and code markers than pre-prints concerning COVID-19.
-Specifically, we found that open data availability in medRxiv pre-prints was significantly associated with a pre-pandemic registration date ($\chi$^2^ = 4.8508, p < 0.005), as was open code availability for bioRxiv pre-prints ($\chi$^2^ = 14.491, p < 0.005).
-This would suggest that open data and code practices may have suffered in the context of COVID-19.
-Or it may be something that is backfilled after posting.
-
-On the other hand, the analyzed arXiv and SocArXiv pre-prints from 2019 contain a lower proportion of open data and code markers overall than their COVID-19-related counterparts, with a decrease of seven per cent in sampled SocArXiv pre-prints and 18 per cent in sampled arXiv papers.
-For these repositories, the presence of both open data and open code markers was significantly associated with registration during the pandemic, suggesting that pre-prints related to COVID-19 in arXiv and SocArXiv may have more consistently adhered to open science practices than their pre-pandemic counterparts ($\chi$^2^ = 93.124, arXiv open data;  $\chi$^2^ = 106.88, arXiv open code; $\chi$^2^ = 12.303, SocArXiv open data; $\chi$^2^ = 8.1598, SocArXiv open code; p < 0.005).
-
-```{r 2019-published}
-med_published_2019 <- 
-  med_2019_open_data_results %>% 
-  select(title, date, published) %>% 
-  mutate(repo = "medRxiv", published = as.numeric(published))
-
-bio_published_2019 <- 
-  bio_2019_results %>% 
-  select(title, date, published) %>% 
-  mutate(repo = "bioRxiv", published = as.numeric(!is.na(published)))
-
-socarxiv_published_2019 <- 
-  socarxiv_metadata_2019 %>% 
-  select(title, date_created, links.doi) %>% 
-  mutate(repo = "socArXiv", published = as.numeric(!is.na(links.doi))) %>%
-  rename(date = date_created) %>%
-  select(title, date, published, repo)
-
-arxiv_published_2019 <-
-  all_arxiv_2019_results %>%
-  select(title, submitted, doi) %>%
-  mutate(repo = "arXiv", published = as.numeric(!is.na(doi))) %>%
-  rename(date = submitted) %>%
-  select(title, date, published, repo)
-
-published_2019 <- rbind(med_published_2019, bio_published_2019, socarxiv_published_2019, arxiv_published_2019)
-
-published_2019 %>% 
-  group_by(repo) %>% 
-  summarise(`Published pre-prints` = sum(published), `Proportion published` = mean(published) %>% round(2)) %>%
-  kable(caption = "Counts and proportion of published COVID-19 pre-prints in each repository, 2019",
-        col.names = c("Repositiory", "Published pre-prints", "Proportion published"),
-        format.args = list(big.mark = ","))
-```
-
-```{r, 2019-open-publishing}
-med_2019_published_open_status <- 
-  med_2019_open_data_results %>% 
-  select(title, date, published, is_open_code, is_open_data) %>% 
-  mutate(condition = is_open_data + is_open_code, repo = "medRxiv")
-
-bio_2019_published_open_status <- 
-  bio_2019_open_data_results %>% 
-  select(title, date, published, is_open_code, is_open_data) %>% 
-  mutate(condition = is_open_data + is_open_code, repo = "bioRxiv")
-
-socarxiv_2019_published_open_status <- 
-  socarxiv_2019_open_data_results %>%
-  mutate(published = !is.na(links.doi) %>% as.numeric()) %>%
-  select(title, date_created, published, is_open_code, is_open_data) %>%
-  rename(date = date_created) %>%
-  mutate(condition = is_open_data + is_open_code, repo = "socArXiv")
-
-arxiv_2019_published_open_status <- 
-  arxiv_2019_open_data_results %>%
-  mutate(published = !is.na(doi) %>% as.numeric()) %>%
-  select(title, submitted, published, is_open_code, is_open_data) %>%
-  rename(date = submitted) %>%
-  mutate(condition = is_open_data + is_open_code, repo = "arXiv")
-
-published_2019_open_status <- rbind(med_2019_published_open_status, bio_2019_published_open_status, socarxiv_2019_published_open_status, arxiv_2019_published_open_status)
-
-published_2019_open_status$condition[published_2019_open_status$condition == 2] <- "Both"
-published_2019_open_status$condition[published_2019_open_status$condition == 0] <- "Neither"
-published_2019_open_status$condition[published_2019_open_status$condition == 1 & published_2019_open_status$is_open_code == 1] <- "Open code"
-published_2019_open_status$condition[published_2019_open_status$condition == 1 & published_2019_open_status$is_open_data == 1] <- "Open data"
-
-published_2019_open_status %>%
-  count(repo, published, condition) %>% 
-  pivot_wider(names_from = condition, values_from = n, values_fill = 0) %>%
-  mutate(Published = ifelse(published == 0, "No", "Yes"), `Proportion with neither`= round((`Neither`)/(`Open data` + `Open code` + Both + Neither), 2)) %>%
-  select(Published, Both, Neither, `Open code`, `Open data`, `Proportion with neither`) %>%
-  kable(caption = "Counts and proportions of open data markers by whether the pre-print was published, 2019",
-        booktabs = TRUE,
-        format.args = list(big.mark = ",")) %>%
-  group_rows(index = c("arXiv" = 2, "bioRxiv" = 2, "medRxiv" = 2, "socArXiv" = 2))
-```
-
-Examining publication rates for pre-pandemic papers, we observe that 41 per cent of pre-prints posted to arXiv, 64 per cent of pre-prints posted to bioRxiv, 61 per cent of pre-prints posted to medRxiv, and 37 per cent of pre-prints posted to SocArXiv during 2019 were eventually peer reviewed and published (Table \@ref(tab:2019-published)).
-These rates are at least double those of the COVID-19-related pre-prints posted in each repository during 2020 and 2021.
-When disaggregated by open data and code status, we find that published and unpublished pre-prints contain open data and code markers in similar proportions (Table \@ref(tab:2019-open-publishing)).
-This mimics the behaviour of published and unpublished COVID-19-related pre-prints.
 
@@
 
-<!-- # (APPENDIX) Appendix {-}  -->
+# (APPENDIX) Appendix {-}
+
+# Tables
+
+```{r 2019-open-results, fig.pos="H"}
+just_2019_medRxiv <-
+  med_2019_open_data_results  %>%
+  mutate(date = as.Date(date), type = "medRxiv")  %>%
+  select(date, is_open_data, is_open_code, type)
+
+just_2019_bioRxiv <-
+  bio_2019_open_data_results  %>%
+  select(date, is_open_data, is_open_code) %>%
+  mutate(date = as.Date(date), type = "bioRxiv")
+
+just_2019_socarxiv <- 
+  socarxiv_2019_open_data_results %>%
+  select(date_created, is_open_data, is_open_code) %>%
+  mutate(date = as.Date(date_created), type = "socArXiv") %>%
+  select(date, is_open_data, is_open_code, type)
+
+just_2019_arxiv <-
+  arxiv_2019_open_data_results %>%
+  select(submitted, is_open_data, is_open_code) %>%
+  mutate(date = as.Date(submitted), type = "arXiv") %>%
+  select(date, is_open_data, is_open_code, type)
+
+all_2019 <- rbind(just_2019_medRxiv, just_2019_bioRxiv, just_2019_socarxiv, just_2019_arxiv)
+
+all_2019_total <- 
+  all_2019 %>%
+  count(is_open_data, is_open_code) %>%
+  mutate(prop_total = n / sum(n)) %>%
+  # mutate(is_open_data = ifelse(is_open_data == 0, "No", "Yes"),
+  #        is_open_code = ifelse(is_open_code == 0, "No", "Yes")) %>%
+  select(is_open_data, is_open_code, n, prop_total)
+
+all_2019_by_type <- 
+  all_2019 %>%
+  group_by(type) %>%
+  count(is_open_data, is_open_code) %>%
+  mutate(prop_total = n / sum(n)) %>%
+  # mutate(is_open_data = ifelse(is_open_data == 0, "No", "Yes"),
+  #        is_open_code = ifelse(is_open_code == 0, "No", "Yes")) %>%
+  ungroup() %>%
+  select(is_open_data, is_open_code, n, prop_total)
+
+rbind(all_2019_total, all_2019_by_type) %>% 
+  mutate(markers = case_when(is_open_data == 0 & is_open_code == 0 ~ "Neither",
+                             is_open_data == 0 & is_open_code == 1 ~ "Open code",
+                             is_open_data == 1 & is_open_code == 0 ~ "Open data",
+                             TRUE ~ "Both")) %>%
+  select(markers, n, prop_total) %>%
+  kable(col.names = c("Markers", "Count", "Proportion of total"),
+        caption = "Count and proportions of open data and code markers by pre-print repository in 2019 sample",
+        booktabs = TRUE,
+        digits = 2,
+        format.args = list(big.mark = ",")) %>%
+  group_rows(index = c("Total" = 4, "arXiv" = 4, "bioRxiv" = 4, "medRxiv" = 4, "SocArXiv" = 4))
+
+```
+
+```{r summarycounts-repositories}
+# open data/open code count summary table
+
+all_by_type <- 
+  all %>%
+  group_by(type) %>%
+  count(is_open_data, is_open_code) %>%
+  mutate(prop_total = n / sum(n)) %>%
+  # mutate(is_open_data = ifelse(is_open_data == 0, "No", "Yes"),
+  #        is_open_code = ifelse(is_open_code == 0, "No", "Yes")) %>%
+  ungroup() %>%
+  select(is_open_data, is_open_code, n, prop_total)
+
+rbind(all_total, all_by_type) %>%
+  mutate(markers = case_when(is_open_data == 0 & is_open_code == 0 ~ "Neither",
+                             is_open_data == 0 & is_open_code == 1 ~ "Open code",
+                             is_open_data == 1 & is_open_code == 0 ~ "Open data",
+                             TRUE ~ "Both")) %>%
+  select(markers, n, prop_total) %>%
+  kable(col.names = c("Markers", "Count", "Proportion of total"),
+        caption = "Count and proportions of open data and code markers by pre-print repository",
+        booktabs = TRUE,
+        digits = 2,
+        format.args = list(big.mark = ",")) %>%
+  group_rows(index = c("Total" = 4, "arXiv" = 4, "bioRxiv" = 4, "medRxiv" = 4, "SocArXiv" = 4))
+```
 

### 2022-01-11 outputs/paper/paper.tex
Updates to paper structure and figures

@@
 \author{Annie Collins\footnote{University of Toronto.} \and Rohan Alexander\footnote{University of Toronto, \href{mailto:rohan.alexander@utoronto.ca}{\nolinkurl{rohan.alexander@utoronto.ca}}.}}
-\date{16 December 2021}
+\date{10 January 2022}
 
@@
 
-\begin{figure}
+\begin{figure}[H]
 
@@
 
-\caption{Number of pre-prints related to COVID-19}\label{fig:monthly-papers-total}
+\caption{Number of pre-prints related to COVID-19 posted to arXiv (N = 4,250), bioRxiv (N = 4,146), medRxiv (N = 13,194), and SocArXiv (N = 478) per month}\label{fig:monthly-papers-total}
 \end{figure}
@@
 \section{Results}\label{results}}
+
+\hypertarget{pre-pandemic-pre-prints}{%
+\subsection{Pre-pandemic pre-prints}\label{pre-pandemic-pre-prints}}
+
+To examine the influence of the COVID-19 pandemic on open science practices during the pandemic, we analyzed pre-prints posted between January and December 2019 from each of the four repositories in question.
+Since medRxiv was founded in June 2019, all pre-prints posted in the latter half of 2019 were analyzed (a total of 913).
+For all other repositories, a random sample of 1,200 was taken from all non-COVID-19-related pre-prints posted in the relevant date range.
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=0.9\linewidth]{paper_files/figure-latex/2019-results-med-arxiv-1}
+
+}
+
+\caption{Number of pre-prints posted per month in 2019 to arXiv (N = 150,018), bioRxiv (N = 31,752), medRxiv (N = 913), and SocArXiv (N = 1,614) per month}\label{fig:2019-results-med-arxiv}
+\end{figure}
+
+Between June and December 2019, the number of pre-prints posted to medRxiv monthly saw an overall increase, which may be expected as the repository gained recognition and popularity in the medical research community (Figure \ref{fig:2019-results-med-arxiv}).
+The number of pre-prints posted monthly to bioRxiv also saw a slight overall increase throughout 2019, while the number of those posted to arXiv and SocArXiv fluctuated throughout the year (Figure \ref{fig:2019-results-med-arxiv}).
+Due to its relative immaturity at the beginning of the COVID-19 pandemic, a significant portion of medRxiv's overall usage has been dedicated to COVID-19-related research.
+In total, 21,647 pre-prints were posted to medRxiv between June 2019 and 30 June, 2021, 13,194 of which (approximately 61 per cent) relate to COVID-19.
+
+Of the analyzed pre-prints from 2019, 93 per cent of those posted to arXiv, 63 per cent of those posted to bioRxiv, 75 per cent of those posted to medRxiv, 92 per cent of those posted to SocArXiv showed no indication of open data or open code (Table \ref{tab:2019-published}).
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.9\linewidth]{paper_files/figure-latex/monthly-papers-condition-stack-2019-1}
+
+}
+
+\caption{Number of sampled pre-prints posted in 2019 from arXiv (n = 1,200), bioRxiv (n = 1,200), medRxiv (n = 913), and SocArXiv (n = 1,200) distinguished by presence of open data or code markers}\label{fig:monthly-papers-condition-stack-2019}
+\end{figure}
+
+\begin{table}
+
+\caption{\label{tab:2019-published}Counts and proportion of published COVID-19 pre-prints in each repository, 2019}
+\centering
+\begin{tabular}[t]{l|r|r}
+\hline
+Repositiory & Published pre-prints & Proportion published\\
+\hline
+arXiv & 62,045 & 0.41\\
+\hline
+bioRxiv & 20,445 & 0.64\\
+\hline
+medRxiv & 555 & 0.61\\
+\hline
+socArXiv & 605 & 0.37\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+
+\caption{\label{tab:2019-open-publishing}Counts and proportions of open data markers by whether the pre-print was published, 2019}
+\centering
+\begin{tabular}[t]{lrrrrr}
+\toprule
+Status & Both & Neither & Open code & Open data & Proportion with neither\\
+\midrule
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{arXiv}}\\
+\hspace{1em}Unpublished & 11 & 645 & 44 & 3 & 0.92\\
+\hspace{1em}Published & 6 & 467 & 15 & 9 & 0.94\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{bioRxiv}}\\
+\hspace{1em}Unpublished & 38 & 264 & 34 & 87 & 0.62\\
+\hspace{1em}Published & 78 & 488 & 64 & 147 & 0.63\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{medRxiv}}\\
+\hspace{1em}Unpublished & 19 & 277 & 19 & 43 & 0.77\\
+\hspace{1em}Published & 38 & 409 & 36 & 72 & 0.74\\
+\addlinespace[0.3em]
+\multicolumn{6}{l}{\textbf{socArXiv}}\\
+\hspace{1em}Unpublished & 13 & 659 & 10 & 47 & 0.90\\
+\hspace{1em}Published & 10 & 442 & 6 & 13 & 0.94\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+Examining publication rates for pre-pandemic papers, we observe that 41 per cent of pre-prints posted to arXiv, 64 per cent of pre-prints posted to bioRxiv, 61 per cent of pre-prints posted to medRxiv, and 37 per cent of pre-prints posted to SocArXiv during 2019 were eventually peer reviewed and published (Table \ref{tab:2019-published}).
+When disaggregated by open data and code status, we find that published and unpublished pre-prints contain open data and code markers in similar proportions (Table \ref{tab:2019-open-publishing}).
 
@@
 
-\begin{table}
-
-\caption{\label{tab:summarycounts-repositories}Count and proportions of open data and code markers by pre-print repository}
-\centering
-\begin{tabular}[t]{llrr}
-\toprule
-Open data markers & Open code markers & Count & Proportion of total\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{4}{l}{\textbf{Total}}\\
-\hspace{1em}No & No & 3,011 & 0.76\\
-\hspace{1em}No & Yes & 262 & 0.07\\
-\hspace{1em}Yes & No & 391 & 0.10\\
-\hspace{1em}Yes & Yes & 314 & 0.08\\
-\addlinespace[0.3em]
-\multicolumn{4}{l}{\textbf{arXiv}}\\
-\hspace{1em}No & No & 752 & 0.75\\
-\hspace{1em}No & Yes & 115 & 0.12\\
-\hspace{1em}Yes & No & 34 & 0.03\\
-\hspace{1em}Yes & Yes & 99 & 0.10\\
-\addlinespace[0.3em]
-\multicolumn{4}{l}{\textbf{bioRxiv}}\\
-\hspace{1em}No & No & 674 & 0.67\\
-\hspace{1em}No & Yes & 44 & 0.04\\
-\hspace{1em}Yes & No & 207 & 0.21\\
-\hspace{1em}Yes & Yes & 75 & 0.07\\
-\addlinespace[0.3em]
-\multicolumn{4}{l}{\textbf{medRxiv}}\\
-\hspace{1em}No & No & 1,180 & 0.79\\
-\hspace{1em}No & Yes & 89 & 0.06\\
-\hspace{1em}Yes & No & 108 & 0.07\\
-\hspace{1em}Yes & Yes & 123 & 0.08\\
-\addlinespace[0.3em]
-\multicolumn{4}{l}{\textbf{SocArXiv}}\\
-\hspace{1em}No & No & 405 & 0.85\\
-\hspace{1em}No & Yes & 14 & 0.03\\
-\hspace{1em}Yes & No & 42 & 0.09\\
-\hspace{1em}Yes & Yes & 17 & 0.04\\
-\bottomrule
-\end{tabular}
-\end{table}
-
 The distribution of total sampled pre-prints and sampled pre-prints with open data or code markers roughly follows that of COVID-19-related pre-prints posted in general (Figure \ref{fig:monthly-papers-condition-stack}).
@@
 None of these pre-prints contained open data or open code markers, thus the 0 per cent rate of open data and code for this month across all repositories should be considered an outlier.
+
+The proportion of bioRxiv and medRxiv pre-prints lacking both open data and open code are approximately four per cent higher than the corresponding proportions of 2019 pre-prints, suggesting that the analyzed pre-prints from 2019 may contain an overall higher prevalence of open data and code markers than pre-prints concerning COVID-19.
+Specifically, we found that open data availability in medRxiv pre-prints was significantly associated with a pre-pandemic registration date (\(\chi\)\textsuperscript{2} = 4.8508, p \textless{} 0.005), as was open code availability for bioRxiv pre-prints (\(\chi\)\textsuperscript{2} = 14.491, p \textless{} 0.005).
+This would suggest that open data and code practices may have suffered in the context of COVID-19, or that it may be something that is backfilled after posting.
+
+On the other hand, the analyzed arXiv and SocArXiv COVID-19-related pre-prints contain a higher proportion of open data and code markers overall than their 2019 counterparts, with a increase of seven per cent in sampled SocArXiv pre-prints and 18 per cent in sampled arXiv papers.
+For these repositories, the presence of both open data and open code markers was significantly associated with registration during the pandemic, suggesting that pre-prints related to COVID-19 in arXiv and SocArXiv may have more consistently adhered to open science practices than their pre-pandemic counterparts (\(\chi\)\textsuperscript{2} = 93.124, arXiv open data; \(\chi\)\textsuperscript{2} = 106.88, arXiv open code; \(\chi\)\textsuperscript{2} = 12.303, SocArXiv open data; \(\chi\)\textsuperscript{2} = 8.1598, SocArXiv open code; p \textless{} 0.005).
 
@@
 
-\caption{Number of sampled pre-prints related to COVID-19, distinguished by presence of open data or code markers}\label{fig:monthly-papers-condition-stack}
+\caption{Number of sampled pre-prints related to COVID-19 from arXiv (n = 1,000), bioRxiv (n = 1,000), medRxiv (n = 1,500), and SocArXiv (n = 478) distinguished by presence of open data or code markers}\label{fig:monthly-papers-condition-stack}
 \end{figure}
@@
 This is high in comparison to the proportions from arXiv and SocArXiv, and although this might suggest that COVID-19-related pre-prints in biomedical fields have received greater attention overall than pre-prints from other fields, our results in Section \ref{pre-pandemic-pre-prints} suggest that this pattern pre-dates the pandemic.
+These rates are also low in comparison to 2019 pre-prints (approximately half), which is likely a result of publication delays and the high volume of research output related to COVID-19 posted as pre-prints.
 
@@
 \toprule
-Published & Both & Neither & Open code & Open data & Proportion with neither\\
+Status & Both & Neither & Open code & Open data & Proportion with neither\\
 \midrule
@@
 \multicolumn{6}{l}{\textbf{arXiv}}\\
-\hspace{1em}No & 79 & 622 & 100 & 27 & 0.75\\
-\hspace{1em}Yes & 20 & 130 & 15 & 7 & 0.76\\
+\hspace{1em}Unpublished & 79 & 622 & 100 & 27 & 0.75\\
+\hspace{1em}Published & 20 & 130 & 15 & 7 & 0.76\\
 \addlinespace[0.3em]
 \multicolumn{6}{l}{\textbf{bioRxiv}}\\
-\hspace{1em}No & 55 & 471 & 29 & 145 & 0.67\\
-\hspace{1em}Yes & 20 & 203 & 15 & 62 & 0.68\\
+\hspace{1em}Unpublished & 55 & 471 & 29 & 145 & 0.67\\
+\hspace{1em}Published & 20 & 203 & 15 & 62 & 0.68\\
 \addlinespace[0.3em]
 \multicolumn{6}{l}{\textbf{medRxiv}}\\
-\hspace{1em}No & 10 & 112 & 8 & 8 & 0.81\\
-\hspace{1em}Yes & 113 & 1,068 & 81 & 100 & 0.78\\
+\hspace{1em}Unpublished & 10 & 112 & 8 & 8 & 0.81\\
+\hspace{1em}Published & 113 & 1,068 & 81 & 100 & 0.78\\
 \addlinespace[0.3em]
 \multicolumn{6}{l}{\textbf{SocArXiv}}\\
-\hspace{1em}No & 14 & 345 & 14 & 34 & 0.85\\
-\hspace{1em}Yes & 3 & 60 & 0 & 8 & 0.85\\
+\hspace{1em}Unpublished & 14 & 345 & 14 & 34 & 0.85\\
+\hspace{1em}Published & 3 & 60 & 0 & 8 & 0.85\\
 \bottomrule
@@
 And even if it were a perfect record, there is a publication lag (estimated at an average of around 60 days for COVID-19-related pre-prints, although that varies by discipline) that may especially skew the results for pre-prints in the latter portion of our sample (Kwon 2020).
-
-\hypertarget{pre-pandemic-pre-prints}{%
-\subsection{Pre-pandemic pre-prints}\label{pre-pandemic-pre-prints}}
-
-To examine the influence of the COVID-19 pandemic on open science practices during the pandemic, we analyzed pre-prints posted between January and December 2019 from each of the four repositories using the same process as was done for the COVID-19-related pre-prints.
-Since medRxiv was founded in June 2019, all pre-prints posted in the latter half of 2019 were analyzed (a total of 913).
-For all other repositories, a random sample of 1,200 was taken from all non-COVID-19-related pre-prints posted in the relevant date range.
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.9\linewidth]{paper_files/figure-latex/2019-results-med-arxiv-1}
-
-}
-
-\caption{Number of pre-prints posted per month to arXiv, bioRxiv, medRxiv, and SocArXiv in 2019}\label{fig:2019-results-med-arxiv}
-\end{figure}
-
-\begin{table}
-
-\caption{\label{tab:2019-open-results}Count and proportions of open data and code markers by pre-print repository in 2019 sample}
-\centering
-\begin{tabular}[t]{llrr}
-\toprule
-Open data markers & Open code markers & Count & Proportion of total\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{4}{l}{\textbf{Total}}\\
-\hspace{1em}No & No & 3,651 & 0.81\\
-\hspace{1em}No & Yes & 228 & 0.05\\
-\hspace{1em}Yes & No & 421 & 0.09\\
-\hspace{1em}Yes & Yes & 213 & 0.05\\
-\addlinespace[0.3em]
-\multicolumn{4}{l}{\textbf{arXiv}}\\
-\hspace{1em}No & No & 1,112 & 0.93\\
-\hspace{1em}No & Yes & 59 & 0.05\\
-\hspace{1em}Yes & No & 12 & 0.01\\
-\hspace{1em}Yes & Yes & 17 & 0.01\\
-\addlinespace[0.3em]
-\multicolumn{4}{l}{\textbf{bioRxiv}}\\
-\hspace{1em}No & No & 752 & 0.63\\
-\hspace{1em}No & Yes & 98 & 0.08\\
-\hspace{1em}Yes & No & 234 & 0.20\\
-\hspace{1em}Yes & Yes & 116 & 0.10\\
-\addlinespace[0.3em]
-\multicolumn{4}{l}{\textbf{medRxiv}}\\
-\hspace{1em}No & No & 686 & 0.75\\
-\hspace{1em}No & Yes & 55 & 0.06\\
-\hspace{1em}Yes & No & 115 & 0.13\\
-\hspace{1em}Yes & Yes & 57 & 0.06\\
-\addlinespace[0.3em]
-\multicolumn{4}{l}{\textbf{SocArXiv}}\\
-\hspace{1em}No & No & 1,101 & 0.92\\
-\hspace{1em}No & Yes & 16 & 0.01\\
-\hspace{1em}Yes & No & 60 & 0.05\\
-\hspace{1em}Yes & Yes & 23 & 0.02\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-Between June and December 2019, the number of pre-prints posted to medRxiv monthly saw an overall increase, which may be expected as the repository gained recognition and popularity in the medical research community (Figure \ref{fig:2019-results-med-arxiv}).
-The number of pre-prints posted monthly to bioRxiv also saw a slight overall increase throughout 2019, while the number of those posted to arXiv and SocArXiv fluctuated throughout the year (Figure \ref{fig:2019-results-med-arxiv}).
-Due to its relative immaturity at the beginning of the COVID-19 pandemic, a significant portion of medRxiv's overall usage has been dedicated to COVID-19-related research.
-In total, 21,647 pre-prints were posted to medRxiv between June 2019 and 30 June, 2021, 13,194 of which (approximately 61 per cent) relate to COVID-19.
-
-Of the analyzed pre-prints from 2019, 93 per cent of those posted to arXiv, 63 per cent of those posted to bioRxiv, 75 per cent of those posted to medRxiv, 92 per cent of those posted to SocArXiv showed no indication of open data or open code (Table \ref{tab:2019-published}).
-Both the bioRxiv and medRxiv rates are approximately four per cent lower than the corresponding proportions of COVID-19-related pre-prints, suggesting that the analyzed pre-prints from 2019 may contain an overall higher prevalence of open data and code markers than pre-prints concerning COVID-19.
-Specifically, we found that open data availability in medRxiv pre-prints was significantly associated with a pre-pandemic registration date (\(\chi\)\textsuperscript{2} = 4.8508, p \textless{} 0.005), as was open code availability for bioRxiv pre-prints (\(\chi\)\textsuperscript{2} = 14.491, p \textless{} 0.005).
-This would suggest that open data and code practices may have suffered in the context of COVID-19.
-Or it may be something that is backfilled after posting.
-
-On the other hand, the analyzed arXiv and SocArXiv pre-prints from 2019 contain a lower proportion of open data and code markers overall than their COVID-19-related counterparts, with a decrease of seven per cent in sampled SocArXiv pre-prints and 18 per cent in sampled arXiv papers.
-For these repositories, the presence of both open data and open code markers was significantly associated with registration during the pandemic, suggesting that pre-prints related to COVID-19 in arXiv and SocArXiv may have more consistently adhered to open science practices than their pre-pandemic counterparts (\(\chi\)\textsuperscript{2} = 93.124, arXiv open data; \(\chi\)\textsuperscript{2} = 106.88, arXiv open code; \(\chi\)\textsuperscript{2} = 12.303, SocArXiv open data; \(\chi\)\textsuperscript{2} = 8.1598, SocArXiv open code; p \textless{} 0.005).
-
-\begin{table}
-
-\caption{\label{tab:2019-published}Counts and proportion of published COVID-19 pre-prints in each repository, 2019}
-\centering
-\begin{tabular}[t]{l|r|r}
-\hline
-Repositiory & Published pre-prints & Proportion published\\
-\hline
-arXiv & 62,045 & 0.41\\
-\hline
-bioRxiv & 20,445 & 0.64\\
-\hline
-medRxiv & 555 & 0.61\\
-\hline
-socArXiv & 605 & 0.37\\
-\hline
-\end{tabular}
-\end{table}
-
-\begin{table}
-
-\caption{\label{tab:2019-open-publishing}Counts and proportions of open data markers by whether the pre-print was published, 2019}
-\centering
-\begin{tabular}[t]{lrrrrr}
-\toprule
-Published & Both & Neither & Open code & Open data & Proportion with neither\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{6}{l}{\textbf{arXiv}}\\
-\hspace{1em}No & 11 & 645 & 44 & 3 & 0.92\\
-\hspace{1em}Yes & 6 & 467 & 15 & 9 & 0.94\\
-\addlinespace[0.3em]
-\multicolumn{6}{l}{\textbf{bioRxiv}}\\
-\hspace{1em}No & 38 & 264 & 34 & 87 & 0.62\\
-\hspace{1em}Yes & 78 & 488 & 64 & 147 & 0.63\\
-\addlinespace[0.3em]
-\multicolumn{6}{l}{\textbf{medRxiv}}\\
-\hspace{1em}No & 19 & 277 & 19 & 43 & 0.77\\
-\hspace{1em}Yes & 38 & 409 & 36 & 72 & 0.74\\
-\addlinespace[0.3em]
-\multicolumn{6}{l}{\textbf{socArXiv}}\\
-\hspace{1em}No & 13 & 659 & 10 & 47 & 0.90\\
-\hspace{1em}Yes & 10 & 442 & 6 & 13 & 0.94\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-Examining publication rates for pre-pandemic papers, we observe that 41 per cent of pre-prints posted to arXiv, 64 per cent of pre-prints posted to bioRxiv, 61 per cent of pre-prints posted to medRxiv, and 37 per cent of pre-prints posted to SocArXiv during 2019 were eventually peer reviewed and published (Table \ref{tab:2019-published}).
-These rates are at least double those of the COVID-19-related pre-prints posted in each repository during 2020 and 2021.
-When disaggregated by open data and code status, we find that published and unpublished pre-prints contain open data and code markers in similar proportions (Table \ref{tab:2019-open-publishing}).
-This mimics the behaviour of published and unpublished COVID-19-related pre-prints.
 
@@
 \newpage
+
+\hypertarget{appendix-appendix}{%
+\appendix}
+
+\hypertarget{tables}{%
+\section{Tables}\label{tables}}
+
+\begin{table}
+
+\caption{\label{tab:2019-open-results}Count and proportions of open data and code markers by pre-print repository in 2019 sample}
+\centering
+\begin{tabular}[t]{lrr}
+\toprule
+Markers & Count & Proportion of total\\
+\midrule
+\addlinespace[0.3em]
+\multicolumn{3}{l}{\textbf{Total}}\\
+\hspace{1em}Neither & 3,651 & 0.81\\
+\hspace{1em}Open code & 228 & 0.05\\
+\hspace{1em}Open data & 421 & 0.09\\
+\hspace{1em}Both & 213 & 0.05\\
+\addlinespace[0.3em]
+\multicolumn{3}{l}{\textbf{arXiv}}\\
+\hspace{1em}Neither & 1,112 & 0.93\\
+\hspace{1em}Open code & 59 & 0.05\\
+\hspace{1em}Open data & 12 & 0.01\\
+\hspace{1em}Both & 17 & 0.01\\
+\addlinespace[0.3em]
+\multicolumn{3}{l}{\textbf{bioRxiv}}\\
+\hspace{1em}Neither & 752 & 0.63\\
+\hspace{1em}Open code & 98 & 0.08\\
+\hspace{1em}Open data & 234 & 0.20\\
+\hspace{1em}Both & 116 & 0.10\\
+\addlinespace[0.3em]
+\multicolumn{3}{l}{\textbf{medRxiv}}\\
+\hspace{1em}Neither & 686 & 0.75\\
+\hspace{1em}Open code & 55 & 0.06\\
+\hspace{1em}Open data & 115 & 0.13\\
+\hspace{1em}Both & 57 & 0.06\\
+\addlinespace[0.3em]
+\multicolumn{3}{l}{\textbf{SocArXiv}}\\
+\hspace{1em}Neither & 1,101 & 0.92\\
+\hspace{1em}Open code & 16 & 0.01\\
+\hspace{1em}Open data & 60 & 0.05\\
+\hspace{1em}Both & 23 & 0.02\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}
+
+\caption{\label{tab:summarycounts-repositories}Count and proportions of open data and code markers by pre-print repository}
+\centering
+\begin{tabular}[t]{lrr}
+\toprule
+Markers & Count & Proportion of total\\
+\midrule
+\addlinespace[0.3em]
+\multicolumn{3}{l}{\textbf{Total}}\\
+\hspace{1em}Neither & 3,011 & 0.76\\
+\hspace{1em}Open code & 262 & 0.07\\
+\hspace{1em}Open data & 391 & 0.10\\
+\hspace{1em}Both & 314 & 0.08\\
+\addlinespace[0.3em]
+\multicolumn{3}{l}{\textbf{arXiv}}\\
+\hspace{1em}Neither & 752 & 0.75\\
+\hspace{1em}Open code & 115 & 0.12\\
+\hspace{1em}Open data & 34 & 0.03\\
+\hspace{1em}Both & 99 & 0.10\\
+\addlinespace[0.3em]
+\multicolumn{3}{l}{\textbf{bioRxiv}}\\
+\hspace{1em}Neither & 674 & 0.67\\
+\hspace{1em}Open code & 44 & 0.04\\
+\hspace{1em}Open data & 207 & 0.21\\
+\hspace{1em}Both & 75 & 0.07\\
+\addlinespace[0.3em]
+\multicolumn{3}{l}{\textbf{medRxiv}}\\
+\hspace{1em}Neither & 1,180 & 0.79\\
+\hspace{1em}Open code & 89 & 0.06\\
+\hspace{1em}Open data & 108 & 0.07\\
+\hspace{1em}Both & 123 & 0.08\\
+\addlinespace[0.3em]
+\multicolumn{3}{l}{\textbf{SocArXiv}}\\
+\hspace{1em}Neither & 405 & 0.85\\
+\hspace{1em}Open code & 14 & 0.03\\
+\hspace{1em}Open data & 42 & 0.09\\
+\hspace{1em}Both & 17 & 0.04\\
+\bottomrule
+\end{tabular}
+\end{table}
 

### 2022-01-11 outputs/paper/paper.Rmd
Updates to paper, notes on reviewer response, beginning validation for ODDPub performance on non biomedical papers

@@
 library(stargazer)
-library(wesanderson)
+# library(wesanderson)
 library(kableExtra)
@@
 
+# Colour palette for all vizes
 cbPalette <- c("#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
@@
 By way of background, each of these four repositories has a different focus: arXiv is general although it has especially high rates of usage from fields like mathematics, physics, and computer science, bioRxiv focuses on biological sciences, medRxiv focuses on health sciences, and SocArXiv focuses on social sciences.
+
 We search for markers of open science as indicators of reproducibility, specifically open data and open code.
+The definition of reproducibility tends to vary by context and academic field.
+For the purposes of this paper, we define reproducibility to mean the ability for different researchers to achieve the same results given the same data and computational methods as the original source.
+This contrasts replicability, which we define as the ability for different researchers to achieve consistent results by conducting the full data collection and analysis process in lieu of reusing original data.
+These definitions match that of @NAP25303 and @cacioppo2015social.
 
@@
 We also find that the presence of open data or open code markers seems to have little association with a pre-print's subsequent publication, and the subset of sampled pre-prints that have been published contains approximately the same proportion of papers with these markers.
-<!-- Finally, we briefly examine the presence of open data and code markers in specific types of pre-prints, namely modelling, simulation, and machine learning research. -->
 
@@
 This was conducted using the `open_data_search()` function from the `oddpub` package.
+Under original validation process, the ODDPub algorithm performed with a sensitivity of 0.73 and a specificity of 1.00 for open code detection and a sensitivity of 0.73 and a specificity of 0.97 for open data detection compared with manual screening [@citePDDPub].
+
 What constitutes open code or open data is complicated and discipline specific.
@@
 The general criteria are that specific mention should be made of where the data and code are located, and that data should be as close to raw as possible.
+Data and code must also be freely accessible to anyone (no request, application, registration process, or affiliation required).
 Our work was conducted using the statistical programming language R [@citeR].
@@
 
+<!-- It is also important to note that pre-prints posted during the early months of the pandemic were likely using and reusing publicly available data sources due toan inability to collect original data within a short timeframe.
+-->
+
 The proportion of bioRxiv and medRxiv pre-prints lacking both open data and open code are approximately four per cent higher than the corresponding proportions of 2019 pre-prints, suggesting that the analyzed pre-prints from 2019 may contain an overall higher prevalence of open data and code markers than pre-prints concerning COVID-19.
@@
 
-Our metadata also contains an indication of whether a pre-print has been published, in the form of a DOI linking to the corresponding published paper.
 The proportion of pre-prints that have been published varies by repository (Table \@ref(tab:published-sample-summary)).
@@
 This is high in comparison to the proportions from arXiv and SocArXiv, and although this might suggest that COVID-19-related pre-prints in biomedical fields have received greater attention overall than pre-prints from other fields, our results in Section \@ref(pre-pandemic-pre-prints) suggest that this pattern pre-dates the pandemic.
-These rates are also low in comparison to 2019 pre-prints (approximately half), which is likely a result of publication delays and the high volume of research output related to COVID-19 posted as pre-prints.
+
+<!-- These rates are also low in comparison to 2019 pre-prints (approximately half), which is likely a result of publication delays and the high volume of research output related to COVID-19 posted as pre-prints.
+-->
 
@@
 We find that the proportion of pre-prints with open data or code markers among those that have been published is roughly the same as pre-prints that have not been published, differing by only a few percentage points.
+
+There is limited literature examining the relationship between data and code availability in manuscripts between the pre-print and publication stages.
+@mcguinness2021descriptive examine differences in data availability statements between medRxiv pre-prints and their published counterparts.
+They find that data availability was maintained for the vast majority of their sample, varying by journal data sharing policy with greater improvements in openness among manuscripts published in journals mandating data sharing.
+While limited to medRxiv, McGuinness and Sheppard's results mimic our own work and provide initial evidence to suggest that data availability is generally maintained or improved between the pre-print and publication stages.
 
@@
 Open data and open code contribute to both by allowing the scientific community to more easily verify the authenticity of purported scientific discoveries and their supporting evidence.
-This is especially important in cases where scientific research may quickly and directly impact clinical practice or public policy, such as research on the COVID-19 pandemic.
+Data sharing also allows others to reuse other researchers' data sets for further analysis or to supplement their own data, contributing to new insights within their field of study.
+
+These factors are especially important in cases where scientific research may quickly and directly impact clinical practice or public policy, such as research on the COVID-19 pandemic.
 Among many other impacts on the research landscape, COVID-19 has increased the popularity of pre-prints from both a production and consumption standpoint.
@@
 
+We recognize that factors beyond open data and code play a large role in the reproducibility of scientific research.
+Not all pre-prints providing open data or code will be reproducible.
+Factors such as data documentation, methodological reporting, software choice, and many others all play a role in the reproduction process and should be regarded with just as much gravity when disseminating results.
+
 An important weakness is the potential presence of false negatives in indicators of publication in our dataset.
@@
 The `oddpub` package was built to analyze biomedical publications and it may be that some of the differences that we find between repositories are due to this.
+We also note that the ODDPub algorithm is relatively narrow in its definition of "open", excluding data that is available via registration or in some other restricted form.
+Adopting a broader definition of openness, either through using a less restrictive algorithm or through manual verification, would likely produce different results particularly for pre-prints using clinical data.
 In future, we wish to take smaller sub-samples to validate factors like publication status, paper topic, and open code and data status, beyond the approaches that we used here.

### 2022-01-11 outputs/paper/paper.tex
Updates to paper, notes on reviewer response, beginning validation for ODDPub performance on non biomedical papers

@@
 \author{Annie Collins\footnote{University of Toronto.} \and Rohan Alexander\footnote{University of Toronto, \href{mailto:rohan.alexander@utoronto.ca}{\nolinkurl{rohan.alexander@utoronto.ca}}.}}
-\date{10 January 2022}
+\date{11 January 2022}
 
@@
 By way of background, each of these four repositories has a different focus: arXiv is general although it has especially high rates of usage from fields like mathematics, physics, and computer science, bioRxiv focuses on biological sciences, medRxiv focuses on health sciences, and SocArXiv focuses on social sciences.
+
 We search for markers of open science as indicators of reproducibility, specifically open data and open code.
+The definition of reproducibility tends to vary by context and academic field.
+For the purposes of this paper, we define reproducibility to mean the ability for different researchers to achieve the same results given the same data and computational methods as the original source.
+This contrasts replicability, which we define as the ability for different researchers to achieve consistent results by conducting the full data collection and analysis process in lieu of reusing original data.
+These definitions match that of National Academies of Sciences and Medicine (2019) and Cacioppo et al.
+(2015).
 
@@
 This was conducted using the \texttt{open\_data\_search()} function from the \texttt{oddpub} package.
+Under original validation process, the ODDPub algorithm performed with a sensitivity of 0.73 and a specificity of 1.00 for open code detection and a sensitivity of 0.73 and a specificity of 0.97 for open data detection compared with manual screening (Riedel, Kip, and Bobrov 2020).
+
 What constitutes open code or open data is complicated and discipline specific.
@@
 The general criteria are that specific mention should be made of where the data and code are located, and that data should be as close to raw as possible.
+Data and code must also be freely accessible to anyone (no request, application, registration process, or affiliation required).
 Our work was conducted using the statistical programming language R (R Core Team 2020).
@@
 
-Our metadata also contains an indication of whether a pre-print has been published, in the form of a DOI linking to the corresponding published paper.
 The proportion of pre-prints that have been published varies by repository (Table \ref{tab:published-sample-summary}).
@@
 This is high in comparison to the proportions from arXiv and SocArXiv, and although this might suggest that COVID-19-related pre-prints in biomedical fields have received greater attention overall than pre-prints from other fields, our results in Section \ref{pre-pandemic-pre-prints} suggest that this pattern pre-dates the pandemic.
-These rates are also low in comparison to 2019 pre-prints (approximately half), which is likely a result of publication delays and the high volume of research output related to COVID-19 posted as pre-prints.
 
@@
 We find that the proportion of pre-prints with open data or code markers among those that have been published is roughly the same as pre-prints that have not been published, differing by only a few percentage points.
+
+There is limited literature examining the relationship between data and code availability in manuscripts between the pre-print and publication stages.
+McGuinness and Sheppard (2021) examine differences in data availability statements between medRxiv pre-prints and their published counterparts.
+They find that data availability was maintained for the vast majority of their sample, varying by journal data sharing policy with greater improvements in openness among manuscripts published in journals mandating data sharing.
+While limited to medRxiv, McGuinness and Sheppard's results mimic our own work and provide initial evidence to suggest that data availability is generally maintained or improved between the pre-print and publication stages.
 
@@
 The \texttt{oddpub} package was built to analyze biomedical publications and it may be that some of the differences that we find between repositories are due to this.
+We also note that the ODDPub algorithm is relatively narrow in its definition of ``open,'' excluding data that is available via registration or in some other restricted form.
+Adopting a broader definition of openness, either through using a less restrictive algorithm or through manual verification, would likely produce different results particularly for pre-prints using clinical data.
 In future, we wish to take smaller sub-samples to validate factors like publication status, paper topic, and open code and data status, beyond the approaches that we used here.
@@
 
+\leavevmode\hypertarget{ref-cacioppo2015social}{}%
+Cacioppo, John T, Robert M Kaplan, Jon A Krosnick, James L Olds, and Heather Dean.
+2015.
+{``Social, Behavioral, and Economic Sciences Perspectives on Robust and Reliable Science.''} \emph{Report of the Subcommittee on Replicability in Science Advisory Committee to the National Science Foundation Directorate for Social, Behavioral, and Economic Sciences}.
+
 \leavevmode\hypertarget{ref-collins2021reproducibility}{}%
@@
 \url{https://doi.org/10.1101/2020.04.21.20074732}.
+
+\leavevmode\hypertarget{ref-NAP25303}{}%
+National Academies of Sciences, Engineering, and Medicine.
+2019.
+\emph{Reproducibility and Replicability in Science}.
+Washington, DC: The National Academies Press.
+\url{https://doi.org/10.17226/25303}.
 

### 2022-01-11 oddpub_validation.R

@@ -1,0 +1,52 @@
+library(tidyverse)
+
+arxiv_open_data_results <- 
+  read_csv(here::here("outputs/data/arxiv_open_data_results.csv"))
+# all_arxiv_results <- 
+#   read_csv(here::here("outputs/data/arxiv_results.csv")) # All COVID arXiv papers (3,812)
+arxiv_2019_open_data_results <- 
+  read_csv(here::here("outputs/control-data/arxiv_2019_open_data_results.csv"))
+# all_arxiv_2019_results <- 
+#   read_csv(here::here("outputs/control-data/arxiv_data_2019.csv"))
+
+# "attributes.has_data_links" gives indication of data availability
+socarxiv_open_data_results <- 
+  read_csv(here::here("outputs/data/socarxiv_open_data_results.csv"))
+socarxiv_2019_open_data_results <- 
+  read_csv(here::here("outputs/control-data/socarxiv_2019_open_data_results.csv"))
+# socarxiv_metadata_2019 <- 
+#   read_csv(here::here("outputs/control-data/socarxiv_metadata_2019.csv"))
+
+#### SocArXiv ####
+
+# 2019
+# Check what's up with NA values attributes.has_data_links
+# attributes.has_data_links: "available" means data link exists, everything else means data link does not exist. 
+# NA appears to be the same as "not_applicable", meaning no data link and no justification (i.e. "attributes.why_no_data" is also NA).
+# "no" means data was used but is not available. Justification must be provided in "attributes.why_no_data".
+# Since ODDPub does not check for areas where open data is not applicable, we should go by 0/1 according to attributes.data_links being populated (i.e. "data_link_available" as defined above)
+socarxiv_2019_open_data_results %>%
+  mutate(data_link_available = case_when(is.na(attributes.data_links) ~ "No data linked", TRUE ~ "Data linked")) %>%
+  count(data_link_available, is_open_data) %>%
+  pivot_wider(names_from = is_open_data, values_from = n) %>%
+  rename(`Open Data Detected` = `1`, `No Open Data Detected` = `0`)
+
+# Unusually high amount of false positives; manual check
+socarxiv_2019_open_data_results %>%
+  filter(is_open_data == 1 & is.na(attributes.data_links)) %>%
+  select(title, links.preprint_doi, attributes.has_data_links, attributes.why_no_data, attributes.data_links, is_open_data, open_data_category, open_data_statements) %>%
+  View()
+
[…]

### 2022-01-12 validation/oddpub_validation.Rmd
Validation data and docs

---
title: "ODDPub Validation for SocArXiv and arXiv"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(tidyverse)

arxiv_open_data_results <- 
  read_csv(here::here("outputs/data/arxiv_open_data_results.csv"))
# all_arxiv_results <- 
#   read_csv(here::here("outputs/data/arxiv_results.csv")) # All COVID arXiv papers (3,812)
arxiv_2019_open_data_results <- 
  read_csv(here::here("outputs/control-data/arxiv_2019_open_data_results.csv"))
# all_arxiv_2019_results <- 
#   read_csv(here::here("outputs/control-data/arxiv_data_2019.csv"))

# "attributes.has_data_links" gives indication of data availability
socarxiv_open_data_results <- 
  read_csv(here::here("outputs/data/socarxiv_open_data_results.csv"))
socarxiv_2019_open_data_results <- 
  read_csv(here::here("outputs/control-data/socarxiv_2019_open_data_results.csv"))
# socarxiv_metadata_2019 <- 
#   read_csv(here::here("outputs/control-data/socarxiv_metadata_2019.csv"))
```

# SocArXiv

## 2019

Under "attributes.has_data_links", "available" means data link exists, everything else means data link does not exist. NA appears to be the same as "not_applicable", meaning no data link and no justification (i.e. "attributes.why_no_data" is also NA). "no" means data was used but is not available. Justification should be provided in "attributes.why_no_data".

Since ODDPub does not check for areas where open data is not applicable, we should go by 0/1 according to attributes.data_links being populated (i.e. "data_link_available" as defined above).

We assume the attributes.data_links to be the "Gold Standard", i.e. indicating the true availability of data. It is possible, however, that some authors failed to indicate their data availability in the proper field upon posting to SocArXiv, and this some of the "false positive" may in fact be true positives.

```{r confusion-matrix-2019}
# SocArXiv 2019 Confusion Matrix
soc_2019_check <- socarxiv_2019_open_data_results %>%
  mutate(data_link_available = case_when(is.na(attributes.data_links) ~ "No data linked", TRUE ~ "Data linked")) %>%
  count(data_link_available, is_open_data) %>%
  pivot_wider(names_from = data_link_available, values_from = n) %>%
  mutate(is_open_data = case_when(is_open_data == 1 ~ "Open data detected", TRUE ~ "No open data detected")) %>%
  rename(Predicted = is_open_data) %>%
  arrange(desc(Predicted))
soc_2019_check
```

```{r accuracy-2019}
soc_2019_accuracy <- as.numeric(soc_2019_check[1,2] + soc_2019_check[2,3])/nrow(socarxiv_2019_open_data_results)
soc_2019_sensitivity <- as.numeric(soc_2019_check[1,2])/sum(soc_2019_check$`Data linked`) %>% as.numeric()
soc_2019_specificity <- as.numeric(soc_2019_check[2,3])/sum(soc_2019_check$`No data linked`)

tibble(Metric = c("Accuracy", "Sensitivity", "Specificity"),
      Value = c(soc_2019_accuracy, soc_2019_sensitivity, soc_2019_specificity))
```

```{r false-negatives-2019, eval = FALSE}
socarxiv_2019_open_data_results %>%
  filter(is_open_data == 0 & !is.na(attributes.data_links)) %>%
  select(title, links.preprint_doi, attributes.has_data_links, attributes.why_no_data, attributes.data_links, is_open_data, open_data_category, open_data_statements)
```

```{r false-positives-2019, eval = FALSE}
socarxiv_2019_open_data_results %>%
  filter(is_open_data == 1 & is.na(attributes.data_links)) %>%
  select(title, links.preprint_doi, attributes.has_data_links, attributes.why_no_data, attributes.data_links, is_open_data, open_data_category, open_data_statements)
```

## 2020/2021

```{r confusion-matrix-2020}
# SocArXiv 2019 Confusion Matrix
soc_2020_check <- socarxiv_open_data_results %>%
  mutate(data_link_available = case_when(is.na(attributes.data_links) ~ "No data linked", TRUE ~ "Data linked")) %>%
  count(data_link_available, is_open_data) %>%
  pivot_wider(names_from = data_link_available, values_from = n) %>%
  mutate(is_open_data = case_when(is_open_data == 1 ~ "Open data detected", TRUE ~ "No open data detected")) %>%
  rename(Predicted = is_open_data) %>%
  arrange(desc(Predicted))
soc_2020_check
```

```{r accuracy-2020}
soc_2020_accuracy <- as.numeric(soc_2020_check[1,2] + soc_2020_check[2,3])/nrow(socarxiv_open_data_results)
soc_2020_sensitivity <- as.numeric(soc_2020_check[1,2])/sum(soc_2020_check$`Data linked`) %>% as.numeric()
soc_2020_specificity <- as.numeric(soc_2020_check[2,3])/sum(soc_2020_check$`No data linked`)

tibble(Metric = c("Accuracy", "Sensitivity", "Specificity"),
      Value = c(soc_2020_accuracy, soc_2020_sensitivity, soc_2020_specificity))
```
```{r false-negatives-2020, eval = FALSE}
socarxiv_open_data_results %>%
  filter(is_open_data == 0 & !is.na(attributes.data_links)) %>%
  select(title, links.preprint_doi, attributes.has_data_links, attributes.why_no_data, attributes.data_links, is_open_data, open_data_category, open_data_statements)
```

```{r false-positives-2020, eval = FALSE}
socarxiv_open_data_results %>%
  filter(is_open_data == 1 & is.na(attributes.data_links)) %>%
  select(title, links.preprint_doi, attributes.has_data_links, attributes.why_no_data, attributes.data_links, is_open_data, open_data_category, open_data_statements)
```

# ArXiv

## 2019

We verified the accuracy of the ODDPub algorithm on a subset of our analyzed pre-prints from 2019 from arXiv. We took a simple random sample of 100 papers. In the original validation process, the annotators stratified by detection status prior to sampling to ensure relatively high representation of papers where open data/code was detected. Since the major concern for our manual verification is potential false negatives, this biased representation was unnecessary. Open data and code status were verified first via the "Code & Data" tab on each pre-print's page on the arXiv website, and then via checking for an explicit data availability section within the PDF and keyword search. Results were recorded manually in Excel (arxiv_2019_validation_sample.csv). This mimics the procedure outlined for the original validation of ODDPub.

Many of the pre-prints in arXiv did not use data or code, namely those from pure mathematics and physics. There were also several that reused other publicly or privately available data sets, and regardless of whether or not they were shared alongside the paper, these do not count as open data according to [ODDPub standards](https://www.biorxiv.org/content/10.1101/2020.05.11.088021v1.full.pdf).
```{r arxiv-2019-verification-sample, eval = FALSE}
set.seed(100)
arxiv_2019_sample <- arxiv_2019_open_data_results[sample.int(nrow(arxiv_2019_open_data_results), 100),] %>%
  select(id, title, link_pdf, link_abstract, is_open_data:open_data_statements) %>%
  mutate(file_path = paste0(id, ".pdf"), .before = id) %>%
  mutate(manual_open_data = NA, manual_data_statement = NA, manual_open_code = NA, manual_code_statement = NA, note = NA) # added for validation process
arxiv_2019_sample
# write_csv(arxiv_2019_sample, here::here("validation", "arxiv_2019_validation_sample.csv"))

open_pdf <- function(x){
  system2('open', args = here::here("outputs", "control-data", "pdf-arxiv", x))
}

open_link <- function(x){
  system2('open', args = x)
}

# Open pdfs in sets of 10 (run one at a time)
# lapply(arxiv_2019_sample$file_path[1:10], open_pdf)
# lapply(arxiv_2019_sample$link_abstract[1:10], open_link)
# 
# lapply(arxiv_2019_sample$file_path[11:20], open_pdf)
# lapply(arxiv_2019_sample$link_abstract[11:20], open_link)
# 
# lapply(arxiv_2019_sample$file_path[21:30], open_pdf)
# lapply(arxiv_2019_sample$link_abstract[21:30], open_link)
# 
# lapply(arxiv_2019_sample$file_path[31:40], open_pdf)
# lapply(arxiv_2019_sample$link_abstract[31:40], open_link)
# 
# lapply(arxiv_2019_sample$file_path[41:50], open_pdf)
# lapply(arxiv_2019_sample$link_abstract[41:50], open_link)
# 
# lapply(arxiv_2019_sample$file_path[51:60], open_pdf)
# lapply(arxiv_2019_sample$link_abstract[51:60], open_link)
# 
# lapply(arxiv_2019_sample$file_path[61:70], open_pdf)
# lapply(arxiv_2019_sample$link_abstract[61:70], open_link)
# 
# lapply(arxiv_2019_sample$file_path[71:80], open_pdf)
# lapply(arxiv_2019_sample$link_abstract[71:80], open_link)
# 
# lapply(arxiv_2019_sample$file_path[81:90], open_pdf)
# lapply(arxiv_2019_sample$link_abstract[81:90], open_link)
# 
# lapply(arxiv_2019_sample$file_path[91:100], open_pdf)
# lapply(arxiv_2019_sample$link_abstract[91:100], open_link)

```

```{r arxiv-confusion-data-2019}
arxiv_2019_manual_results <- read.csv(here::here("validation", "arxiv_2019_validation_sample_COMPLETE.csv"))

arxiv_2019_data_check <- arxiv_2019_manual_results %>%
  count(is_open_data, manual_open_data) %>%
  pivot_wider(names_from = manual_open_data, values_from = n) %>%
  mutate(is_open_data = case_when(is_open_data == 1 ~ "Open data detected", TRUE ~ "No open data detected")) %>%
  select(is_open_data, `1`, `0`) %>%
  rename(Predicted = is_open_data, `Data available` = `1`, `No data available` = `0`) %>%
  arrange(desc(Predicted))

arxiv_2019_data_check

```

```{r arxiv-confusion-code-2019}

arxiv_2019_code_check <- arxiv_2019_manual_results %>%
  count(is_open_code, manual_open_code) %>%
  pivot_wider(names_from = manual_open_code, values_from = n) %>%
  mutate(is_open_code = case_when(is_open_code == 1 ~ "Open code detected", TRUE ~ "No open code detected")) %>%
  select(is_open_code, `1`, `0`) %>%
  rename(Predicted = is_open_code, `Code available` = `1`, `No code available` = `0`) %>%
  arrange(desc(Predicted))

arxiv_2019_code_check
```

```{r arxiv-accuracy-data-2019}
arc_2019_accuracy <- as.numeric(arxiv_2019_data_check[1,2] + arxiv_2019_data_check[2,3])/nrow(arxiv_2019_manual_results)
arc_2019_sensitivity <- as.numeric(arxiv_2019_data_check[1,2])/sum(arxiv_2019_data_check$`Data available`) %>% as.numeric()
arc_2019_specificity <- as.numeric(arxiv_2019_data_check[2,3])/sum(arxiv_2019_data_check$`No data available`)

tibble(Metric = c("Accuracy", "Sensitivity", "Specificity"),
      Value = c(arc_2019_accuracy, arc_2019_sensitivity, arc_2019_specificity))
```
```{r arxiv-accuracy-code-2019}
arc_2019_code_accuracy <- as.numeric(arxiv_2019_code_check[1,2] + arxiv_2019_code_check[2,3])/nrow(arxiv_2019_manual_results)
arc_2019_code_sensitivity <- as.numeric(arxiv_2019_code_check[1,2])/sum(arxiv_2019_code_check$`Code available`) %>% as.numeric()
arc_2019_code_specificity <- as.numeric(arxiv_2019_code_check[2,3])/sum(arxiv_2019_code_check$`No code available`)

tibble(Metric = c("Accuracy", "Sensitivity", "Specificity"),
      Value = c(arc_2019_code_accuracy, arc_2019_code_sensitivity, arc_2019_code_specificity))
```

### 2022-01-12 oddpub_validation.R

@@ -1,52 +1,0 @@
-library(tidyverse)
-
-arxiv_open_data_results <- 
-  read_csv(here::here("outputs/data/arxiv_open_data_results.csv"))
-# all_arxiv_results <- 
-#   read_csv(here::here("outputs/data/arxiv_results.csv")) # All COVID arXiv papers (3,812)
-arxiv_2019_open_data_results <- 
-  read_csv(here::here("outputs/control-data/arxiv_2019_open_data_results.csv"))
-# all_arxiv_2019_results <- 
-#   read_csv(here::here("outputs/control-data/arxiv_data_2019.csv"))
-
-# "attributes.has_data_links" gives indication of data availability
-socarxiv_open_data_results <- 
-  read_csv(here::here("outputs/data/socarxiv_open_data_results.csv"))
-socarxiv_2019_open_data_results <- 
-  read_csv(here::here("outputs/control-data/socarxiv_2019_open_data_results.csv"))
-# socarxiv_metadata_2019 <- 
-#   read_csv(here::here("outputs/control-data/socarxiv_metadata_2019.csv"))
-
-#### SocArXiv ####
-
-# 2019
-# Check what's up with NA values attributes.has_data_links
-# attributes.has_data_links: "available" means data link exists, everything else means data link does not exist. 
-# NA appears to be the same as "not_applicable", meaning no data link and no justification (i.e. "attributes.why_no_data" is also NA).
-# "no" means data was used but is not available. Justification must be provided in "attributes.why_no_data".
-# Since ODDPub does not check for areas where open data is not applicable, we should go by 0/1 according to attributes.data_links being populated (i.e. "data_link_available" as defined above)
-socarxiv_2019_open_data_results %>%
-  mutate(data_link_available = case_when(is.na(attributes.data_links) ~ "No data linked", TRUE ~ "Data linked")) %>%
-  count(data_link_available, is_open_data) %>%
-  pivot_wider(names_from = is_open_data, values_from = n) %>%
-  rename(`Open Data Detected` = `1`, `No Open Data Detected` = `0`)
-
-# Unusually high amount of false positives; manual check
-socarxiv_2019_open_data_results %>%
-  filter(is_open_data == 1 & is.na(attributes.data_links)) %>%
-  select(title, links.preprint_doi, attributes.has_data_links, attributes.why_no_data, attributes.data_links, is_open_data, open_data_category, open_data_statements) %>%
-  View()
-
[…]

### 2022-01-13 outputs/paper/paper.Rmd
Address some more comments

@@
 date: "`r format(Sys.time(), '%d %B %Y')`"
-abstract: "To examine the reproducibility of COVID-19 research, we create a dataset of pre-prints posted to arXiv, bioRxiv, medRxiv, and SocArXiv between 28 January 2020 and 30 June 2021 that are related to COVID-19.
+abstract: "To examine the reproducibility of COVID-19 research, we create a dataset of pre-prints posted to arXiv, bioRxiv, and medRxiv between 28 January 2020 and 30 June 2021 that are related to COVID-19.
 We extract the text from these pre-prints and parse them looking for keyword markers signalling the availability of the data and code underpinning the pre-print.
-For the pre-prints that are in our sample, we are unable to find markers of either open data or open code for 75 per cent of those on arXiv, 67 per cent of those on bioRxiv, 79 per cent of those on medRxiv, and 85 per cent of those on SocArXiv.
+For the pre-prints that are in our sample, we are unable to find markers of either open data or open code for 75 per cent of those on arXiv, 67 per cent of those on bioRxiv, and 79 per cent of those on medRxiv.
 We conclude that there may be value in having authors categorize the degree of openness of their pre-print as part of the pre-print submissions process, and more broadly, there is a need to better integrate open science training into a wide range of fields."
@@
 library(DiagrammeR)
+library(patchwork)
 ```
@@
 
-socarxiv_open_data_results <- 
-  read_csv(here::here("outputs/data/socarxiv_open_data_results.csv"))
-socarxiv_2019_open_data_results <- 
-  read_csv(here::here("outputs/control-data/socarxiv_2019_open_data_results.csv"))
-socarxiv_metadata_2019 <- 
-  read_csv(here::here("outputs/control-data/socarxiv_metadata_2019.csv"))
+# socarxiv_open_data_results <- 
+#   read_csv(here::here("outputs/data/socarxiv_open_data_results.csv"))
+# socarxiv_2019_open_data_results <- 
+#   read_csv(here::here("outputs/control-data/socarxiv_2019_open_data_results.csv"))
+# socarxiv_metadata_2019 <- 
+#   read_csv(here::here("outputs/control-data/socarxiv_metadata_2019.csv"))
 
@@
 Scientists use open repositories of papers to disseminate their research more quickly than is possible in traditional journals or conference proceedings, and also to obtain feedback on their work prior to publication.
-These repositories, such as arXiv, bioRxiv, medRxiv, and SocArXiv, are a critical component of scientific communication and a lot of research builds on the pre-prints posted there.
+These repositories, such as arXiv, bioRxiv, and medRxiv, are a critical component of scientific communication and a lot of research builds on the pre-prints posted there.
 Pre-print repositories have been especially important during the 2019 novel coronavirus (COVID-19) pandemic and the changes it has imposed on the scientific community [@else2020].
@@
 But it is important that scientists impose standards on themselves, and arguably repositories have a role to play here.
-Following @weissgerber2021automated, we examine pre-prints about COVID-19 posted to arXiv, bioRxiv, medRxiv, and SocArXiv from 28 January 2020 through to 30 June 2021.
-By way of background, each of these four repositories has a different focus: arXiv is general although it has especially high rates of usage from fields like mathematics, physics, and computer science, bioRxiv focuses on biological sciences, medRxiv focuses on health sciences, and SocArXiv focuses on social sciences.
+Following @weissgerber2021automated, we examine pre-prints about COVID-19 posted to arXiv, bioRxiv, and medRxiv from 28 January 2020 through to 30 June 2021.
+By way of background, each of these three repositories has a different focus: arXiv is general although it has especially high rates of usage from fields like mathematics, physics, and computer science, bioRxiv focuses on biological sciences, and medRxiv focuses on health sciences.
 
 We search for markers of open science as indicators of reproducibility, specifically open data and open code.
-The definition of reproducibility tends to vary by context and academic field.
+The definition of reproducibility tends to vary by context and academic field [@barba2018terminologies].
 For the purposes of this paper, we define reproducibility to mean the ability for different researchers to achieve the same results given the same data and computational methods as the original source.
@@
 
-We find that of the papers sampled, approximately 75 per cent of papers from arXiv, 67 per cent of papers from bioRxiv, 79 per cent of papers from medRxiv, and 85 per cent of papers from SocArXiv contain neither open data nor open code markers.
+We find that of the papers sampled, approximately 75 per cent of papers from arXiv, 67 per cent of papers from bioRxiv, and 79 per cent of papers from medRxiv contain neither open data nor open code markers.
 A summary of our main results is contained in Figure \@ref(fig:flowchart).
@@
 medrxivcovidcount [label =  'medRxiv: 13,194 pre-prints']
-socarxivcovidcount [label =  'SocArXiv: 478 pre-prints']
+# socarxivcovidcount [label =  'SocArXiv: 478 pre-prints']
 randomsample [label =  'Random sampling stratified by repository']
@@
 medrxivsamplecount [label =  'medRxiv: 1,500 pre-prints']
-socarxivsamplecount [label =  'SocArXiv: 478 pre-prints']
+# socarxivsamplecount [label =  'SocArXiv: 478 pre-prints']
 opencodeanddata [label =  'Those with markers of open code or open data']
@@
 medrxivopencount [label =  'medRxiv: 320 pre-prints']
-socarxivopencount [label =  'SocArXiv: 73 pre-prints']
+# socarxivopencount [label =  'SocArXiv: 73 pre-prints']
 
 # edge definitions with the node IDs
-all -> onlycovid -> {arxivcovidcount biorxivcovidcount medrxivcovidcount socarxivcovidcount} -> randomsample -> {arxivsamplecount biorxivsamplecount medrxivsamplecount socarxivsamplecount} -> opencodeanddata -> {arxivopencount biorxivopencount medrxivopencount socarxivopencount}
+all -> onlycovid -> {arxivcovidcount biorxivcovidcount medrxivcovidcount} -> randomsample -> {arxivsamplecount biorxivsamplecount medrxivsamplecount} -> opencodeanddata -> {arxivopencount biorxivopencount medrxivopencount}
 }")
@@
 
-The remainder of this paper is structured as follows: in Section \@ref(methodology) we discuss the process of constructing our dataset through retrieving pre-prints from the arXiv, bioRxiv, medRxiv, and SocArXiv repositories and mining them for open data and open code markers.
+The remainder of this paper is structured as follows: in Section \@ref(methodology) we discuss the process of constructing our dataset through retrieving pre-prints from the arXiv, bioRxiv, and medRxiv repositories and mining them for open data and open code markers.
 In Section \@ref(results), we present the results and key findings of this process.
@@
 
-Our primary dataset consists of pre-print metadata extracted from the arXiv, bioRxiv, medRxiv, and SocArXiv pre-print repositories via their respective Application Programming Interfaces (APIs).
+Our primary dataset consists of pre-print metadata extracted from the arXiv, bioRxiv, and medRxiv pre-print repositories via their respective Application Programming Interfaces (APIs).
 This metadata varies by repository, but generally includes the following information: title, abstract, author(s), date created, research field, DOI, version number, corresponding author, corresponding author's institutional affiliation, published DOI (if the pre-print has since been published in a peer-reviewed journal), and download link.
@@
 For COVID-19-related pre-prints, we first created a local copy of each repository containing all metadata for pre-prints posted between 1 January, 2020, and 30 June, 2021. 
-In the case of SocArXiv there are fields that are self-reported by the submitting author about the availability of code and data.
+<!-- In the case of SocArXiv there are fields that are self-reported by the submitting author about the availability of code and data.  -->
 We classified individual pre-prints as "COVID-19-related" based on whether they contained one or more of the following terms in their title or abstract (case insensitive): "COVID-19", "COVID 19", "corona virus", "coronavirus", "coronavirus-2", "SARS-CoV-2", "SARSCoV-2", and "2019-nCoV".
-We then randomly sampled pre-prints for further analysis, except for SocArXiv, for which we analyzed all pre-prints that matched the above criteria, because there were only 478.
+We then randomly sampled pre-prints for further analysis.
+<!-- , except for SocArXiv, for which we analyzed all pre-prints that matched the above criteria, because there were only 478. -->
 
@@
 
-We checked our sampled pre-prints for open data and code markers using the Open Data Detection in Publications (ODDPub) text mining algorithm [@citePDDPub] within the `oddpub` R package [@citeODDPubpackage].
-This required downloading each pre-print as a PDF, which we did using `heapsofpapers` [@citealexandermafouz] and then converting the PDFs to text files.
-Some papers from SocArXiv were only available in Word document format (.docx) and were downloaded as such and then converted to text format.
+We checked our sampled pre-prints for open data and code markers using the Open Data Detection in Publications (ODDPub) text mining algorithm [@citePDDPub] within the `oddpub` R package [@citeODDPubpackage] (RRID:SCR_018385) .
+This required downloading each pre-print as a PDF and then converting the PDFs to text files.
+<!-- Some papers from SocArXiv were only available in Word document format (.docx) and were downloaded as such and then converted to text format.  -->
 We then conducted the open data and open code detection procedure, which involved searching for keywords and other markers of open data and open code availability.
@@
 Data and code must also be freely accessible to anyone (no request, application, registration process, or affiliation required).
-Our work was conducted using the statistical programming language R [@citeR].
+Our work was conducted using the statistical programming language R [@citeR] (RRID:SCR_001905).
 
@@
 
-Although SocArXiv's metadata contained author-reported information concerning data and code availability for each pre-print, we elected to use the results of the ODDPub algorithm in our analysis to ensure comparability of results between pre-prints from all repositories.
+<!-- Although SocArXiv's metadata contained author-reported information concerning data and code availability for each pre-print, we elected to use the results of the ODDPub algorithm in our analysis to ensure comparability of results between pre-prints from all repositories.
+-->
 <!-- Notable discrepancies between the ODDPub algorithm and authors' self-reported data and code availability are documented in Appendix \@ref(socarxivissues). -->
 
-```{r monthly-papers-total, fig.cap = "Number of pre-prints related to COVID-19 posted to arXiv (N = 4,250), bioRxiv (N = 4,146), medRxiv (N = 13,194), and SocArXiv (N = 478) per month", out.width="90%", fig.align = "center", fig.pos="H"}
+```{r monthly-papers-total, fig.cap = "Number of pre-prints related to COVID-19 posted to arXiv (N = 4,250), bioRxiv (N = 4,146), and medRxiv (N = 13,194) per month", out.width="90%", fig.align = "center", fig.pos="H"}
 just_arxiv <- 
@@
 
-just_socarxiv <- 
-  socarxiv_open_data_results  %>% 
-  select(date_created) %>%
-  rename(date = "date_created") %>%
-  mutate(date = as.Date(date), type = "SocArXiv")
+# just_socarxiv <- 
+#   socarxiv_open_data_results  %>% 
+#   select(date_created) %>%
+#   rename(date = "date_created") %>%
+#   mutate(date = as.Date(date), type = "SocArXiv")
 
-all <- rbind(just_arxiv, just_medRxiv, just_bioRxiv, just_socarxiv)
+all <- rbind(just_arxiv, 
+             just_medRxiv, 
+             just_bioRxiv
+             # , 
+             # just_socarxiv
+             )
 
@@
 
-```{r 2019-results-med-arxiv, out.width="90%", fig.align='center', fig.cap = "Number of pre-prints posted per month in 2019 to arXiv (N = 150,018), bioRxiv (N = 31,752), medRxiv (N = 913), and SocArXiv (N = 1,614) per month", fig.pos="H"}
+```{r 2019-results-med-arxiv, out.width="90%", fig.align='center', fig.cap = "Number of pre-prints posted per month in 2019 to arXiv (N = 150,018), bioRxiv (N = 31,752), medRxiv (N = 913)", fig.pos="H"}
 bio_2019 <- bio_2019_results %>%
@@
 
-socarxiv_2019 <- socarxiv_metadata_2019 %>%
-  select(date_created) %>%
-  mutate(type = "socArXiv") %>%
-  rename(date = date_created)
+# socarxiv_2019 <- socarxiv_metadata_2019 %>%
+#   select(date_created) %>%
+#   mutate(type = "socArXiv") %>%
+#   rename(date = date_created)
 
@@
 
-all_2019 <- rbind(arxiv_2019, bio_2019, med_2019, socarxiv_2019)
+all_2019 <- rbind(arxiv_2019, bio_2019, med_2019
+                  # , socarxiv_2019
+                  )
 
@@
 Between June and December 2019, the number of pre-prints posted to medRxiv monthly saw an overall increase, which may be expected as the repository gained recognition and popularity in the medical research community (Figure \@ref(fig:2019-results-med-arxiv)).
-The number of pre-prints posted monthly to bioRxiv also saw a slight overall increase throughout 2019, while the number of those posted to arXiv and SocArXiv fluctuated throughout the year (Figure \@ref(fig:2019-results-med-arxiv)).
+The number of pre-prints posted monthly to bioRxiv also saw a slight overall increase throughout 2019, while the number of those posted to arXiv fluctuated throughout the year (Figure \@ref(fig:2019-results-med-arxiv)).
 Due to its relative immaturity at the beginning of the COVID-19 pandemic, a significant portion of medRxiv's overall usage has been dedicated to COVID-19-related research.
@@
 
-Of the analyzed pre-prints from 2019, 93 per cent of those posted to arXiv, 63 per cent of those posted to bioRxiv, 75 per cent of those posted to medRxiv, 92 per cent of those posted to SocArXiv showed no indication of open data or open code (Table \@ref(tab:2019-published)).
+Of the analyzed pre-prints from 2019, 93 per cent of those posted to arXiv, 63 per cent of those posted to bioRxiv, and 75 per cent of those posted to medRxiv showed no indication of open data or open code (Table \@ref(tab:2019-published)).
 
-```{r monthly-papers-condition-stack-2019, fig.cap = "Number of sampled pre-prints posted in 2019 from arXiv (n = 1,200), bioRxiv (n = 1,200), medRxiv (n = 913), and SocArXiv (n = 1,200) distinguished by presence of open data or code markers", out.width="90%", fig.align = "center"}
+```{r monthly-papers-condition-stack-2019, fig.cap = "Number of sampled pre-prints posted in 2019 from arXiv (n = 1,200), bioRxiv (n = 1,200), and medRxiv (n = 913) distinguished by presence of open data or code markers", out.width="90%", fig.align = "center"}
 # Number of papers for each open data/code status per month
@@
 
-open_status_socarxiv_2019 <-
-  socarxiv_2019_open_data_results %>%
-  select(title, date_created, is_open_code, is_open_data) %>%
-  mutate(condition = is_open_data + is_open_code, repo = "SocArXiv", date = as.character(date_created)) %>%
-  select(title, date, is_open_code, is_open_data, condition, repo)
+# open_status_socarxiv_2019 <-
+#   socarxiv_2019_open_data_results %>%
+#   select(title, date_created, is_open_code, is_open_data) %>%
+#   mutate(condition = is_open_data + is_open_code, repo = "SocArXiv", date = as.character(date_created)) %>%
+#   select(title, date, is_open_code, is_open_data, condition, repo)
 
-open_status <- rbind(open_status_med_2019, open_status_bio_2019, open_status_arxiv_2019, open_status_socarxiv_2019)
+open_status <- rbind(open_status_med_2019, open_status_bio_2019, open_status_arxiv_2019
+                     # , open_status_socarxiv_2019
+                     )
 
@@
 
+figufour <- 
 open_status %>%
@@
   xlab("Month") +
-  labs(title="Sampled pre-prints by month, 2019", subtitle="Note the different y-axes.") +
+  labs(title="Sampled pre-prints by month in 2019", subtitle="Note the different y-axes.") +
   theme_minimal() +
@@
   facet_wrap(~repo,
-             scales = "free_y")
+             scales = "free_y") +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))
+
 ```
@@
 
-socarxiv_published_2019 <- 
-  socarxiv_metadata_2019 %>% 
-  select(title, date_created, links.doi) %>% 
-  mutate(repo = "socArXiv", published = as.numeric(!is.na(links.doi))) %>%
-  rename(date = date_created) %>%
-  select(title, date, published, repo)
+# socarxiv_published_2019 <- 
+#   socarxiv_metadata_2019 %>% 
+#   select(title, date_created, links.doi) %>% 
+#   mutate(repo = "socArXiv", published = as.numeric(!is.na(links.doi))) %>%
+#   rename(date = date_created) %>%
+#   select(title, date, published, repo)
 
@@
 
-published_2019 <- rbind(med_published_2019, bio_published_2019, socarxiv_published_2019, arxiv_published_2019)
+published_2019 <- rbind(med_published_2019, bio_published_2019, 
+                        # socarxiv_published_2019, 
+                        arxiv_published_2019)
 
@@
 
-socarxiv_2019_published_open_status <- 
-  socarxiv_2019_open_data_results %>%
-  mutate(published = !is.na(links.doi) %>% as.numeric()) %>%
-  select(title, date_created, published, is_open_code, is_open_data) %>%
-  rename(date = date_created) %>%
-  mutate(condition = is_open_data + is_open_code, repo = "socArXiv")
+# socarxiv_2019_published_open_status <- 
+#   socarxiv_2019_open_data_results %>%
+#   mutate(published = !is.na(links.doi) %>% as.numeric()) %>%
+#   select(title, date_created, published, is_open_code, is_open_data) %>%
+#   rename(date = date_created) %>%
+#   mutate(condition = is_open_data + is_open_code, repo = "socArXiv")
 
@@
 
-published_2019_open_status <- rbind(med_2019_published_open_status, bio_2019_published_open_status, socarxiv_2019_published_open_status, arxiv_2019_published_open_status)
+published_2019_open_status <- rbind(med_2019_published_open_status, bio_2019_published_open_status, 
+                                    # socarxiv_2019_published_open_status, 
+                                    arxiv_2019_published_open_status)
 
@@
         format.args = list(big.mark = ",")) %>%
-  group_rows(index = c("arXiv" = 2, "bioRxiv" = 2, "medRxiv" = 2, "socArXiv" = 2))
+  group_rows(index = c("arXiv" = 2, "bioRxiv" = 2, "medRxiv" = 2))
 ```
 
-Examining publication rates for pre-pandemic papers, we observe that 41 per cent of pre-prints posted to arXiv, 64 per cent of pre-prints posted to bioRxiv, 61 per cent of pre-prints posted to medRxiv, and 37 per cent of pre-prints posted to SocArXiv during 2019 were eventually peer reviewed and published (Table \@ref(tab:2019-published)).
+Examining publication rates for pre-pandemic papers, we observe that 41 per cent of pre-prints posted to arXiv, 64 per cent of pre-prints posted to bioRxiv, and 61 per cent of pre-prints posted to medRxiv during 2019 were eventually peer reviewed and published (Table \@ref(tab:2019-published)).
 When disaggregated by open data and code status, we find that published and unpublished pre-prints contain open data and code markers in similar proportions (Table \@ref(tab:2019-open-publishing)).
@@
 From the collection of all pre-prints related to COVID-19, we randomly sampled 3,910 pre-prints to analyze, stratified by repository.
-This sample is broken down as follows: 1,500 from medRxiv, 1,000 from arXiv, 1,000 from bioRxiv, and 478 from SocArXiv.
+This sample is broken down as follows: 1,500 from medRxiv, 1,000 from arXiv, and 1,000 from bioRxiv.
 Broadly, we are unable to find markers of either open data or open code for 3,011 pre-prints or approximately 76 per cent of our sample (Table \@ref(tab:summarycounts-repositories)).
@@
 
-When differentiated by repository, we observe that open data and code markers were absent from 75 per cent of the sampled arXiv pre-prints, 67 per cent of the sampled bioRxiv pre-prints, 79 per cent of the sampled medRxiv pre-prints, and 85 per cent of all COVID-19-related SocArXiv pre-prints.
+When differentiated by repository, we observe that open data and code markers were absent from 75 per cent of the sampled arXiv pre-prints, 67 per cent of the sampled bioRxiv pre-prints, 79 per cent of the sampled medRxiv pre-prints.
 The distribution of the remaining portion of pre-prints also varies by repository (Table \@ref(tab:summarycounts-repositories)).
@@
 
-just_socarxiv <-
-  socarxiv_open_data_results  %>%
-  select(date_created, is_open_data, is_open_code) %>%
-  rename(date = "date_created") %>%
-  mutate(type = "SocArXiv")
+# just_socarxiv <-
+#   socarxiv_open_data_results  %>%
+#   select(date_created, is_open_data, is_open_code) %>%
+#   rename(date = "date_created") %>%
+#   mutate(type = "SocArXiv")
 
-all <- rbind(just_arxiv, just_medRxiv, just_bioRxiv, just_socarxiv)
+all <- rbind(just_arxiv, just_medRxiv, just_bioRxiv
+             # , just_socarxiv
+             )
 
@@
 
-The distribution of total sampled pre-prints and sampled pre-prints with open data or code markers roughly follows that of COVID-19-related pre-prints posted in general (Figure \@ref(fig:monthly-papers-condition-stack)).
+The distribution of total sampled pre-prints and sampled pre-prints with open data or code markers roughly follows that of COVID-19-related pre-prints posted in general (Figure \@ref(fig:arxiv-and-monthly-papers-condition-stack)).
 The proportion of pre-prints with open data or code has fluctuated over time but shows no consistent overall increase or decrease throughout the course of the pandemic, nor in conjunction with increases or decreases in the total number of pre-prints posted to any given repository.
@@
 
-<!-- It is also important to note that pre-prints posted during the early months of the pandemic were likely using and reusing publicly available data sources due toan inability to collect original data within a short timeframe.
--->
+It is also important to note that pre-prints posted during the early months of the pandemic were likely using, and reusing, publicly available data sources due to an inability to collect original data within a short timeframe.
+Additionally, `oddpub` does not consider '[t]he reuse of data/code previously published by other researchers' [@citePDDPub].
+A different definition of open data could enable pre-prints that reuse publicly available data to have made theirdata available for reproducibility purposes.
 
@@
 
-On the other hand, the analyzed arXiv and SocArXiv COVID-19-related pre-prints contain a higher proportion of open data and code markers overall than their 2019 counterparts, with a increase of seven per cent in sampled SocArXiv pre-prints and 18 per cent in sampled arXiv papers.
-For these repositories, the presence of both open data and open code markers was significantly associated with registration during the pandemic, suggesting that pre-prints related to COVID-19 in arXiv and SocArXiv may have more consistently adhered to open science practices than their pre-pandemic counterparts ($\chi$^2^ = 93.124, arXiv open data;  $\chi$^2^ = 106.88, arXiv open code; $\chi$^2^ = 12.303, SocArXiv open data; $\chi$^2^ = 8.1598, SocArXiv open code; p < 0.005).
+On the other hand, the analyzed arXiv COVID-19-related pre-prints contain a higher proportion of open data and code markers overall than their 2019 counterparts, with a increase of 18 per cent in sampled arXiv papers.
+For these repositories, the presence of both open data and open code markers was significantly associated with registration during the pandemic, suggesting that pre-prints related to COVID-19 in arXiv may have more consistently adhered to open science practices than their pre-pandemic counterparts ($\chi$^2^ = 93.124, arXiv open data;  $\chi$^2^ = 106.88, arXiv open code; $\chi$^2^ = 12.303).
 
-```{r monthly-papers-condition-stack, fig.cap = "Number of sampled pre-prints related to COVID-19 from arXiv (n = 1,000), bioRxiv (n = 1,000), medRxiv (n = 1,500), and SocArXiv (n = 478) distinguished by presence of open data or code markers", out.width="90%", fig.align = "center"}
+```{r monthly-papers-condition-stack, fig.cap = "Number of sampled pre-prints related to COVID-19 from arXiv (n = 1,000), bioRxiv (n = 1,000), and medRxiv (n = 1,500) distinguished by presence of open data or code markers", out.width="90%", fig.align = "center"}
 # Number of papers for each open data/code status per month
@@
 
-open_status_socarxiv <- 
-  socarxiv_open_data_results %>% 
-  select(title, date_created, is_open_code, is_open_data) %>% 
-  mutate(condition = is_open_data + is_open_code, repo = "SocArXiv", date = as.character(date_created)) %>%
-  select(title, date, is_open_code, is_open_data, condition, repo)
+# open_status_socarxiv <- 
+#   socarxiv_open_data_results %>% 
+#   select(title, date_created, is_open_code, is_open_data) %>% 
+#   mutate(condition = is_open_data + is_open_code, repo = "SocArXiv", date = as.character(date_created)) %>%
+#   select(title, date, is_open_code, is_open_data, condition, repo)
 
-open_status <- rbind(open_status_med, open_status_bio, open_status_arxiv, open_status_socarxiv)
+open_status <- rbind(open_status_med, open_status_bio, open_status_arxiv
+                     # , open_status_socarxiv
+                     )
 
@@
 
+figfive <- 
 open_status %>% 
@@
   xlab("Month") +
-  labs(title="Sampled pre-prints by month", subtitle="Note the different y-axes.") +
+  labs(title="Sampled pre-prints by month related to COVID-19", subtitle="Note the different y-axes.") +
   theme_minimal() +
@@
   facet_wrap(~repo,
-             scales = "free_y")
+             scales = "free_y") +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))
+```
+
+```{r arxiv-and-monthly-papers-condition-stack, fig.cap = "Number of sampled pre-prints posted in 2019, compared with those related to COVID-19: from arXiv (n in 2019 = 1,000; n related to COVID = 1,200), bioRxiv (n in 2019 = 1,000; n related to COVID n = 1,200), and medRxiv (n in 2019 = 1,500; n related to COVID n = 913) distinguished by presence of open data or code markers", out.width="90%", fig.align = "center"}
+
+figufour / figfive + plot_layout(guides = 'collect')
 ```
@@
 
-socarxiv_month_sum_cov <- 
-  socarxiv_open_data_results %>% 
-  group_by(month = floor_date(as.Date(date_created), "month")) %>% 
-  summarise(count = n(), "Open Code" = mean(is_open_code), "Open Data" = mean(is_open_data)) %>% 
-  mutate(daily_rate = count/days_in_month(month), repo = "SocArXiv")
+# socarxiv_month_sum_cov <- 
+#   socarxiv_open_data_results %>% 
+#   group_by(month = floor_date(as.Date(date_created), "month")) %>% 
+#   summarise(count = n(), "Open Code" = mean(is_open_code), "Open Data" = mean(is_open_data)) %>% 
+#   mutate(daily_rate = count/days_in_month(month), repo = "SocArXiv")
 
-month_sum_cov <- rbind(med_month_sum_cov, bio_month_sum_cov, arxiv_month_sum_cov, socarxiv_month_sum_cov) %>%
+month_sum_cov <- rbind(med_month_sum_cov, bio_month_sum_cov, arxiv_month_sum_cov) %>%
   pivot_longer(cols = c("Open Data", "Open Code")) %>%
@@
 Notably, of all COVID-19-related pre-prints in our dataset, approximately 30 per cent of those posted to bioRxiv and nearly one third of those posted to medRxiv were published.
-This is high in comparison to the proportions from arXiv and SocArXiv, and although this might suggest that COVID-19-related pre-prints in biomedical fields have received greater attention overall than pre-prints from other fields, our results in Section \@ref(pre-pandemic-pre-prints) suggest that this pattern pre-dates the pandemic.
+This is high in comparison to the proportions from arXiv, and although this might suggest that COVID-19-related pre-prints in biomedical fields have received greater attention overall than pre-prints from other fields, our results in Section \@ref(pre-pandemic-pre-prints) suggest that this pattern pre-dates the pandemic.
 
@@
 
-socarxiv_published <- 
-  socarxiv_open_data_results %>% 
-  select(title, date_created, links.doi) %>%
-  mutate(links.doi = as.numeric(!is.na(links.doi)), repo = "SocArXiv") %>%
-  rename(published = links.doi, date = date_created)
+# socarxiv_published <- 
+#   socarxiv_open_data_results %>% 
+#   select(title, date_created, links.doi) %>%
+#   mutate(links.doi = as.numeric(!is.na(links.doi)), repo = "SocArXiv") %>%
+#   rename(published = links.doi, date = date_created)
 
-published <- rbind(med_published, bio_published, arxiv_published, socarxiv_published)
+published <- rbind(med_published, bio_published, arxiv_published
+                   # , socarxiv_published
+                   )
 
@@
 They find that data availability was maintained for the vast majority of their sample, varying by journal data sharing policy with greater improvements in openness among manuscripts published in journals mandating data sharing.
-While limited to medRxiv, McGuinness and Sheppard's results mimic our own work and provide initial evidence to suggest that data availability is generally maintained or improved between the pre-print and publication stages.
+While limited to medRxiv, the results of @mcguinness2021descriptive align with our own work and provide initial evidence to suggest that data availability is generally maintained or improved between the pre-print and publication stages.
 
@@
 
-socarxiv_published_open_status <- 
-  socarxiv_open_data_results %>% 
-  select(title, date_created, links.doi, is_open_code, is_open_data) %>%
-  mutate(links.doi = as.numeric(!is.na(links.doi)), condition = is_open_data + is_open_code, repo = "SocArXiv") %>%
-  rename(published = links.doi, date = date_created)
+# socarxiv_published_open_status <- 
+#   socarxiv_open_data_results %>% 
+#   select(title, date_created, links.doi, is_open_code, is_open_data) %>%
+#   mutate(links.doi = as.numeric(!is.na(links.doi)), condition = is_open_data + is_open_code, repo = "SocArXiv") %>%
+#   rename(published = links.doi, date = date_created)
 
-published_open_status <- rbind(med_published_open_status, bio_published_open_status, arxiv_published_open_status, socarxiv_published_open_status)
+published_open_status <- rbind(med_published_open_status, 
+                               bio_published_open_status, 
+                               arxiv_published_open_status
+                               # , socarxiv_published_open_status
+                               )
 
@@
         format.args = list(big.mark = ",")) %>%
-  group_rows(index = c("arXiv" = 2, "bioRxiv" = 2, "medRxiv" = 2, "SocArXiv" = 2))
+  group_rows(index = c("arXiv" = 2, "bioRxiv" = 2, "medRxiv" = 2))
 ```
@@
 This concern is slightly mitigated by recognition of challenges in working with biomedical data compared with data in other fields, notably privacy and ethics concerns when working with personal data [@Floca2014].
-The COVID-19 pandemic has seen open science initiatives, as evidenced by the creation of open data repositories such as the dashboard maintained by the Center for Systems Science and Engineering at Johns Hopkins University [@citeCSSE] or the large number of publishers who have removed paywalls from published COVID-19 research [@gill2020].
+The COVID-19 pandemic has seen open science initiatives, as evidenced by the creation of open data repositories such as the dashboard maintained by the Center for Systems Science and Engineering at Johns Hopkins University [@citeCSSE] or the large number of publishers who removed paywalls from published COVID-19 research [@gill2020].
 While the intention at the start of the pandemic was that there would be 'clear statements regarding the availability of underlying data' [@citeWellcome] some retractions of work have been based on 'unreliable or nonexistent data' [@da2021optimizing].
-SocArXiv asks submitters to make explicit the degree of openness in the data, and this is something that could be adopted by other pre-print repositories.
+<!-- SocArXiv asks submitters to make explicit the degree of openness in the data, and this is something that could be adopted by other pre-print repositories. -->
 
@@
 Further, @cabanac2021day show that not all pre-prints are linked to their subsequent peer-reviewed publication, which may further bias our results.
+Further, there is the potential for bias due to older pre-prints having had more time to be published than newer pre-prints.
 And @oikonomidi2020changes and @Beroe051821 show that differences between updated versions of the same pre-print can be substantial; again this is something that we do not account for and could bias our results.
@@
 The ongoing COVID-19 pandemic has created a novel, constantly changing scientific culture that should be navigated with care to uphold standards of scientific practice for both the research community and the safety of the public.
-Our analysis shows that there is room for improvement in the areas of open data and code availability within COVID-19 pre-print papers on arXiv, bioRxiv, medRxiv, and SocArXiv.
+Our analysis shows that there is room for improvement in the areas of open data and code availability within COVID-19 pre-print papers on arXiv, bioRxiv, and medRxiv
+<!-- , and SocArXiv. -->
 
@@
 
-# Tables
+# Tables with specific values displayed in the graphs
 
@@
 
-just_2019_socarxiv <- 
-  socarxiv_2019_open_data_results %>%
-  select(date_created, is_open_data, is_open_code) %>%
-  mutate(date = as.Date(date_created), type = "socArXiv") %>%
-  select(date, is_open_data, is_open_code, type)
+# just_2019_socarxiv <- 
+#   socarxiv_2019_open_data_results %>%
+#   select(date_created, is_open_data, is_open_code) %>%
+#   mutate(date = as.Date(date_created), type = "socArXiv") %>%
+#   select(date, is_open_data, is_open_code, type)
 
@@
 
-all_2019 <- rbind(just_2019_medRxiv, just_2019_bioRxiv, just_2019_socarxiv, just_2019_arxiv)
+all_2019 <- rbind(just_2019_medRxiv, just_2019_bioRxiv, 
+                  # just_2019_socarxiv, 
+                  just_2019_arxiv)
 
@@
         format.args = list(big.mark = ",")) %>%
-  group_rows(index = c("Total" = 4, "arXiv" = 4, "bioRxiv" = 4, "medRxiv" = 4, "SocArXiv" = 4))
+  group_rows(index = c("Total" = 4, "arXiv" = 4, "bioRxiv" = 4, "medRxiv" = 4))  %>%
+  kableExtra::kable_styling(latex_options = "hold_position")
 
@@
         format.args = list(big.mark = ",")) %>%
-  group_rows(index = c("Total" = 4, "arXiv" = 4, "bioRxiv" = 4, "medRxiv" = 4, "SocArXiv" = 4))
+  group_rows(index = c("Total" = 4, "arXiv" = 4, "bioRxiv" = 4, "medRxiv" = 4))  %>%
+  kableExtra::kable_styling(latex_options = "hold_position")
+```
+
+# Table of proportion of all preprints in each category, for each preprint server
+
+```{r propbyserverandcategory, fig.cap = "Proportion of all preprints in each category, for each preprint server", fig.align = "center"}
+# Number of papers for each open data/code status per month
+open_status %>% 
+  group_by(repo, condition) %>% 
+  count() %>% 
+  ungroup() %>% 
+  group_by(repo) %>% 
+  mutate(proportion = n/(sum(n))) %>% 
+   kable(caption = "Number and proportion of all preprints in each category, for each preprint server", 
+        col.names = c("Repository", "Condition", "Number", "Proportion"),
+        digits = 2,
+        booktabs = TRUE,
+        linesep = ""
+        )
 ```
@@
 
-<!-- \newpage -->
+\newpage
 

### 2022-01-13 outputs/paper/paper.tex
Figure and paper file updates
Address some more comments

@@
 \author{Annie Collins\footnote{University of Toronto.} \and Rohan Alexander\footnote{University of Toronto, \href{mailto:rohan.alexander@utoronto.ca}{\nolinkurl{rohan.alexander@utoronto.ca}}.}}
-\date{11 January 2022}
+\date{13 January 2022}
 
@@
 \begin{abstract}
-To examine the reproducibility of COVID-19 research, we create a dataset of pre-prints posted to arXiv, bioRxiv, medRxiv, and SocArXiv between 28 January 2020 and 30 June 2021 that are related to COVID-19.
+To examine the reproducibility of COVID-19 research, we create a dataset of pre-prints posted to arXiv, bioRxiv, and medRxiv between 28 January 2020 and 30 June 2021 that are related to COVID-19.
 We extract the text from these pre-prints and parse them looking for keyword markers signalling the availability of the data and code underpinning the pre-print.
-For the pre-prints that are in our sample, we are unable to find markers of either open data or open code for 75 per cent of those on arXiv, 67 per cent of those on bioRxiv, 79 per cent of those on medRxiv, and 85 per cent of those on SocArXiv.
+For the pre-prints that are in our sample, we are unable to find markers of either open data or open code for 75 per cent of those on arXiv, 67 per cent of those on bioRxiv, and 79 per cent of those on medRxiv.
 We conclude that there may be value in having authors categorize the degree of openness of their pre-print as part of the pre-print submissions process, and more broadly, there is a need to better integrate open science training into a wide range of fields.
@@
 Scientists use open repositories of papers to disseminate their research more quickly than is possible in traditional journals or conference proceedings, and also to obtain feedback on their work prior to publication.
-These repositories, such as arXiv, bioRxiv, medRxiv, and SocArXiv, are a critical component of scientific communication and a lot of research builds on the pre-prints posted there.
+These repositories, such as arXiv, bioRxiv, and medRxiv, are a critical component of scientific communication and a lot of research builds on the pre-prints posted there.
 Pre-print repositories have been especially important during the 2019 novel coronavirus (COVID-19) pandemic and the changes it has imposed on the scientific community (Else 2020).
@@
 Following Weissgerber et al.
-(2021), we examine pre-prints about COVID-19 posted to arXiv, bioRxiv, medRxiv, and SocArXiv from 28 January 2020 through to 30 June 2021.
-By way of background, each of these four repositories has a different focus: arXiv is general although it has especially high rates of usage from fields like mathematics, physics, and computer science, bioRxiv focuses on biological sciences, medRxiv focuses on health sciences, and SocArXiv focuses on social sciences.
+(2021), we examine pre-prints about COVID-19 posted to arXiv, bioRxiv, and medRxiv from 28 January 2020 through to 30 June 2021.
+By way of background, each of these three repositories has a different focus: arXiv is general although it has especially high rates of usage from fields like mathematics, physics, and computer science, bioRxiv focuses on biological sciences, and medRxiv focuses on health sciences.
 
 We search for markers of open science as indicators of reproducibility, specifically open data and open code.
-The definition of reproducibility tends to vary by context and academic field.
+The definition of reproducibility tends to vary by context and academic field (Barba 2018).
 For the purposes of this paper, we define reproducibility to mean the ability for different researchers to achieve the same results given the same data and computational methods as the original source.
@@
 
-We find that of the papers sampled, approximately 75 per cent of papers from arXiv, 67 per cent of papers from bioRxiv, 79 per cent of papers from medRxiv, and 85 per cent of papers from SocArXiv contain neither open data nor open code markers.
+We find that of the papers sampled, approximately 75 per cent of papers from arXiv, 67 per cent of papers from bioRxiv, and 79 per cent of papers from medRxiv contain neither open data nor open code markers.
 A summary of our main results is contained in Figure \ref{fig:flowchart}.
@@
 
-The remainder of this paper is structured as follows: in Section \ref{methodology} we discuss the process of constructing our dataset through retrieving pre-prints from the arXiv, bioRxiv, medRxiv, and SocArXiv repositories and mining them for open data and open code markers.
+The remainder of this paper is structured as follows: in Section \ref{methodology} we discuss the process of constructing our dataset through retrieving pre-prints from the arXiv, bioRxiv, and medRxiv repositories and mining them for open data and open code markers.
 In Section \ref{results}, we present the results and key findings of this process.
@@
 For COVID-19-related pre-prints, we first created a local copy of each repository containing all metadata for pre-prints posted between 1 January, 2020, and 30 June, 2021.
-In the case of SocArXiv there are fields that are self-reported by the submitting author about the availability of code and data.
-We classified individual pre-prints as ``COVID-19-related'' based on whether they contained one or more of the following terms in their title or abstract (case insensitive): ``COVID-19,'' ``COVID 19,'' ``corona virus,'' ``coronavirus,'' ``coronavirus-2,'' ``SARS-CoV-2,'' ``SARSCoV-2,'' and ``2019-nCoV.'' We then randomly sampled pre-prints for further analysis, except for SocArXiv, for which we analyzed all pre-prints that matched the above criteria, because there were only 478.
+We classified individual pre-prints as ``COVID-19-related'' based on whether they contained one or more of the following terms in their title or abstract (case insensitive): ``COVID-19,'' ``COVID 19,'' ``corona virus,'' ``coronavirus,'' ``coronavirus-2,'' ``SARS-CoV-2,'' ``SARSCoV-2,'' and ``2019-nCoV.'' We then randomly sampled pre-prints for further analysis.
 
@@
 
-We checked our sampled pre-prints for open data and code markers using the Open Data Detection in Publications (ODDPub) text mining algorithm (Riedel, Kip, and Bobrov 2020) within the \texttt{oddpub} R package (Riedel 2019).
-This required downloading each pre-print as a PDF, which we did using \texttt{heapsofpapers} (Alexander and Mahfouz 2021) and then converting the PDFs to text files.
-Some papers from SocArXiv were only available in Word document format (.docx) and were downloaded as such and then converted to text format.
+We checked our sampled pre-prints for open data and code markers using the Open Data Detection in Publications (ODDPub) text mining algorithm (Riedel, Kip, and Bobrov 2020) within the \texttt{oddpub} R package (Riedel 2019) (RRID:SCR\_018385) .
+This required downloading each pre-print as a PDF and then converting the PDFs to text files.
 We then conducted the open data and open code detection procedure, which involved searching for keywords and other markers of open data and open code availability.
@@
 Data and code must also be freely accessible to anyone (no request, application, registration process, or affiliation required).
-Our work was conducted using the statistical programming language R (R Core Team 2020).
+Our work was conducted using the statistical programming language R (R Core Team 2020) (RRID:SCR\_001905).
 
@@
 Our final dataset was formed by joining this output with the original sample metadata, typically using the DOI or the unique file name, to form a dataset including all original metadata for each pre-print alongside its open data and open code status and markers.
-
-Although SocArXiv's metadata contained author-reported information concerning data and code availability for each pre-print, we elected to use the results of the ODDPub algorithm in our analysis to ensure comparability of results between pre-prints from all repositories.
 
@@
 
-\caption{Number of pre-prints related to COVID-19 posted to arXiv (N = 4,250), bioRxiv (N = 4,146), medRxiv (N = 13,194), and SocArXiv (N = 478) per month}\label{fig:monthly-papers-total}
+\caption{Number of pre-prints related to COVID-19 posted to arXiv (N = 4,250), bioRxiv (N = 4,146), and medRxiv (N = 13,194) per month}\label{fig:monthly-papers-total}
 \end{figure}
@@
 
-\caption{Number of pre-prints posted per month in 2019 to arXiv (N = 150,018), bioRxiv (N = 31,752), medRxiv (N = 913), and SocArXiv (N = 1,614) per month}\label{fig:2019-results-med-arxiv}
+\caption{Number of pre-prints posted per month in 2019 to arXiv (N = 150,018), bioRxiv (N = 31,752), medRxiv (N = 913)}\label{fig:2019-results-med-arxiv}
 \end{figure}
@@
 Between June and December 2019, the number of pre-prints posted to medRxiv monthly saw an overall increase, which may be expected as the repository gained recognition and popularity in the medical research community (Figure \ref{fig:2019-results-med-arxiv}).
-The number of pre-prints posted monthly to bioRxiv also saw a slight overall increase throughout 2019, while the number of those posted to arXiv and SocArXiv fluctuated throughout the year (Figure \ref{fig:2019-results-med-arxiv}).
+The number of pre-prints posted monthly to bioRxiv also saw a slight overall increase throughout 2019, while the number of those posted to arXiv fluctuated throughout the year (Figure \ref{fig:2019-results-med-arxiv}).
 Due to its relative immaturity at the beginning of the COVID-19 pandemic, a significant portion of medRxiv's overall usage has been dedicated to COVID-19-related research.
@@
 
-Of the analyzed pre-prints from 2019, 93 per cent of those posted to arXiv, 63 per cent of those posted to bioRxiv, 75 per cent of those posted to medRxiv, 92 per cent of those posted to SocArXiv showed no indication of open data or open code (Table \ref{tab:2019-published}).
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.9\linewidth]{paper_files/figure-latex/monthly-papers-condition-stack-2019-1}
-
-}
-
-\caption{Number of sampled pre-prints posted in 2019 from arXiv (n = 1,200), bioRxiv (n = 1,200), medRxiv (n = 913), and SocArXiv (n = 1,200) distinguished by presence of open data or code markers}\label{fig:monthly-papers-condition-stack-2019}
-\end{figure}
+Of the analyzed pre-prints from 2019, 93 per cent of those posted to arXiv, 63 per cent of those posted to bioRxiv, and 75 per cent of those posted to medRxiv showed no indication of open data or open code (Table \ref{tab:2019-published}).
 
@@
 medRxiv & 555 & 0.61\\
-\hline
-socArXiv & 605 & 0.37\\
 \hline
@@
 \hspace{1em}Published & 38 & 409 & 36 & 72 & 0.74\\
-\addlinespace[0.3em]
-\multicolumn{6}{l}{\textbf{socArXiv}}\\
-\hspace{1em}Unpublished & 13 & 659 & 10 & 47 & 0.90\\
-\hspace{1em}Published & 10 & 442 & 6 & 13 & 0.94\\
 \bottomrule
@@
 
-Examining publication rates for pre-pandemic papers, we observe that 41 per cent of pre-prints posted to arXiv, 64 per cent of pre-prints posted to bioRxiv, 61 per cent of pre-prints posted to medRxiv, and 37 per cent of pre-prints posted to SocArXiv during 2019 were eventually peer reviewed and published (Table \ref{tab:2019-published}).
+Examining publication rates for pre-pandemic papers, we observe that 41 per cent of pre-prints posted to arXiv, 64 per cent of pre-prints posted to bioRxiv, and 61 per cent of pre-prints posted to medRxiv during 2019 were eventually peer reviewed and published (Table \ref{tab:2019-published}).
 When disaggregated by open data and code status, we find that published and unpublished pre-prints contain open data and code markers in similar proportions (Table \ref{tab:2019-open-publishing}).
@@
 From the collection of all pre-prints related to COVID-19, we randomly sampled 3,910 pre-prints to analyze, stratified by repository.
-This sample is broken down as follows: 1,500 from medRxiv, 1,000 from arXiv, 1,000 from bioRxiv, and 478 from SocArXiv.
+This sample is broken down as follows: 1,500 from medRxiv, 1,000 from arXiv, and 1,000 from bioRxiv.
 Broadly, we are unable to find markers of either open data or open code for 3,011 pre-prints or approximately 76 per cent of our sample (Table \ref{tab:summarycounts-repositories}).
@@
 
-When differentiated by repository, we observe that open data and code markers were absent from 75 per cent of the sampled arXiv pre-prints, 67 per cent of the sampled bioRxiv pre-prints, 79 per cent of the sampled medRxiv pre-prints, and 85 per cent of all COVID-19-related SocArXiv pre-prints.
+When differentiated by repository, we observe that open data and code markers were absent from 75 per cent of the sampled arXiv pre-prints, 67 per cent of the sampled bioRxiv pre-prints, 79 per cent of the sampled medRxiv pre-prints.
 The distribution of the remaining portion of pre-prints also varies by repository (Table \ref{tab:summarycounts-repositories}).
@@
 
-The distribution of total sampled pre-prints and sampled pre-prints with open data or code markers roughly follows that of COVID-19-related pre-prints posted in general (Figure \ref{fig:monthly-papers-condition-stack}).
+The distribution of total sampled pre-prints and sampled pre-prints with open data or code markers roughly follows that of COVID-19-related pre-prints posted in general (Figure \ref{fig:arxiv-and-monthly-papers-condition-stack}).
 The proportion of pre-prints with open data or code has fluctuated over time but shows no consistent overall increase or decrease throughout the course of the pandemic, nor in conjunction with increases or decreases in the total number of pre-prints posted to any given repository.
@@
 None of these pre-prints contained open data or open code markers, thus the 0 per cent rate of open data and code for this month across all repositories should be considered an outlier.
+
+It is also important to note that pre-prints posted during the early months of the pandemic were likely using, and reusing, publicly available data sources due to an inability to collect original data within a short timeframe.
+Additionally, \texttt{oddpub} does not consider `{[}t{]}he reuse of data/code previously published by other researchers' (Riedel, Kip, and Bobrov 2020).
+A different definition of open data could enable pre-prints that reuse publicly available data to have made theirdata available for reproducibility purposes.
 
@@
 
-On the other hand, the analyzed arXiv and SocArXiv COVID-19-related pre-prints contain a higher proportion of open data and code markers overall than their 2019 counterparts, with a increase of seven per cent in sampled SocArXiv pre-prints and 18 per cent in sampled arXiv papers.
-For these repositories, the presence of both open data and open code markers was significantly associated with registration during the pandemic, suggesting that pre-prints related to COVID-19 in arXiv and SocArXiv may have more consistently adhered to open science practices than their pre-pandemic counterparts (\(\chi\)\textsuperscript{2} = 93.124, arXiv open data; \(\chi\)\textsuperscript{2} = 106.88, arXiv open code; \(\chi\)\textsuperscript{2} = 12.303, SocArXiv open data; \(\chi\)\textsuperscript{2} = 8.1598, SocArXiv open code; p \textless{} 0.005).
+On the other hand, the analyzed arXiv COVID-19-related pre-prints contain a higher proportion of open data and code markers overall than their 2019 counterparts, with a increase of 18 per cent in sampled arXiv papers.
+For these repositories, the presence of both open data and open code markers was significantly associated with registration during the pandemic, suggesting that pre-prints related to COVID-19 in arXiv may have more consistently adhered to open science practices than their pre-pandemic counterparts (\(\chi\)\textsuperscript{2} = 93.124, arXiv open data; \(\chi\)\textsuperscript{2} = 106.88, arXiv open code; \(\chi\)\textsuperscript{2} = 12.303).
 
@@
 
-{\centering \includegraphics[width=0.9\linewidth]{paper_files/figure-latex/monthly-papers-condition-stack-1}
+{\centering \includegraphics[width=0.9\linewidth]{paper_files/figure-latex/arxiv-and-monthly-papers-condition-stack-1}
 
@@
 
-\caption{Number of sampled pre-prints related to COVID-19 from arXiv (n = 1,000), bioRxiv (n = 1,000), medRxiv (n = 1,500), and SocArXiv (n = 478) distinguished by presence of open data or code markers}\label{fig:monthly-papers-condition-stack}
+\caption{Number of sampled pre-prints posted in 2019, compared with those related to COVID-19: from arXiv (n in 2019 = 1,000; n related to COVID = 1,200), bioRxiv (n in 2019 = 1,000; n related to COVID n = 1,200), and medRxiv (n in 2019 = 1,500; n related to COVID n = 913) distinguished by presence of open data or code markers}\label{fig:arxiv-and-monthly-papers-condition-stack}
 \end{figure}
@@
 Notably, of all COVID-19-related pre-prints in our dataset, approximately 30 per cent of those posted to bioRxiv and nearly one third of those posted to medRxiv were published.
-This is high in comparison to the proportions from arXiv and SocArXiv, and although this might suggest that COVID-19-related pre-prints in biomedical fields have received greater attention overall than pre-prints from other fields, our results in Section \ref{pre-pandemic-pre-prints} suggest that this pattern pre-dates the pandemic.
+This is high in comparison to the proportions from arXiv, and although this might suggest that COVID-19-related pre-prints in biomedical fields have received greater attention overall than pre-prints from other fields, our results in Section \ref{pre-pandemic-pre-prints} suggest that this pattern pre-dates the pandemic.
 
@@
 \hline
-SocArXiv & 71 & 0.15\\
-\hline
 \end{tabular}
@@
 They find that data availability was maintained for the vast majority of their sample, varying by journal data sharing policy with greater improvements in openness among manuscripts published in journals mandating data sharing.
-While limited to medRxiv, McGuinness and Sheppard's results mimic our own work and provide initial evidence to suggest that data availability is generally maintained or improved between the pre-print and publication stages.
+While limited to medRxiv, the results of McGuinness and Sheppard (2021) align with our own work and provide initial evidence to suggest that data availability is generally maintained or improved between the pre-print and publication stages.
 
@@
 \hspace{1em}Published & 113 & 1,068 & 81 & 100 & 0.78\\
-\addlinespace[0.3em]
-\multicolumn{6}{l}{\textbf{SocArXiv}}\\
-\hspace{1em}Unpublished & 14 & 345 & 14 & 34 & 0.85\\
-\hspace{1em}Published & 3 & 60 & 0 & 8 & 0.85\\
 \bottomrule
@@
 This concern is slightly mitigated by recognition of challenges in working with biomedical data compared with data in other fields, notably privacy and ethics concerns when working with personal data (Floca 2014).
-The COVID-19 pandemic has seen open science initiatives, as evidenced by the creation of open data repositories such as the dashboard maintained by the Center for Systems Science and Engineering at Johns Hopkins University (Dong, Du, and Gardner 2020) or the large number of publishers who have removed paywalls from published COVID-19 research (Gill 2020).
+The COVID-19 pandemic has seen open science initiatives, as evidenced by the creation of open data repositories such as the dashboard maintained by the Center for Systems Science and Engineering at Johns Hopkins University (Dong, Du, and Gardner 2020) or the large number of publishers who removed paywalls from published COVID-19 research (Gill 2020).
 While the intention at the start of the pandemic was that there would be `clear statements regarding the availability of underlying data' (Wellcome Trust 2020) some retractions of work have been based on `unreliable or nonexistent data' (Teixeira da Silva, Bornemann-Cimenti, and Tsigaris 2021).
-SocArXiv asks submitters to make explicit the degree of openness in the data, and this is something that could be adopted by other pre-print repositories.
 
@@
 Further, Cabanac, Oikonomidi, and Boutron (2021) show that not all pre-prints are linked to their subsequent peer-reviewed publication, which may further bias our results.
+Further, there is the potential for bias due to older pre-prints having had more time to be published than newer pre-prints.
 And Oikonomidi et al.
@@
 The ongoing COVID-19 pandemic has created a novel, constantly changing scientific culture that should be navigated with care to uphold standards of scientific practice for both the research community and the safety of the public.
-Our analysis shows that there is room for improvement in the areas of open data and code availability within COVID-19 pre-print papers on arXiv, bioRxiv, medRxiv, and SocArXiv.
+Our analysis shows that there is room for improvement in the areas of open data and code availability within COVID-19 pre-print papers on arXiv, bioRxiv, and medRxiv
 
@@
 
-\hypertarget{tables}{%
-\section{Tables}\label{tables}}
+\hypertarget{tables-with-specific-values-displayed-in-the-graphs}{%
+\section{Tables with specific values displayed in the graphs}\label{tables-with-specific-values-displayed-in-the-graphs}}
 
-\begin{table}
+\begin{table}[!h]
 
@@
 \multicolumn{3}{l}{\textbf{Total}}\\
-\hspace{1em}Neither & 3,651 & 0.81\\
-\hspace{1em}Open code & 228 & 0.05\\
-\hspace{1em}Open data & 421 & 0.09\\
-\hspace{1em}Both & 213 & 0.05\\
+\hspace{1em}Neither & 2,550 & 0.77\\
+\hspace{1em}Open code & 212 & 0.06\\
+\hspace{1em}Open data & 361 & 0.11\\
+\hspace{1em}Both & 190 & 0.06\\
 \addlinespace[0.3em]
@@
 \hspace{1em}Both & 57 & 0.06\\
-\addlinespace[0.3em]
-\multicolumn{3}{l}{\textbf{SocArXiv}}\\
-\hspace{1em}Neither & 1,101 & 0.92\\
-\hspace{1em}Open code & 16 & 0.01\\
-\hspace{1em}Open data & 60 & 0.05\\
-\hspace{1em}Both & 23 & 0.02\\
 \bottomrule
@@
 
-\begin{table}
+\begin{table}[!h]
 
@@
 \multicolumn{3}{l}{\textbf{Total}}\\
-\hspace{1em}Neither & 3,011 & 0.76\\
-\hspace{1em}Open code & 262 & 0.07\\
-\hspace{1em}Open data & 391 & 0.10\\
-\hspace{1em}Both & 314 & 0.08\\
+\hspace{1em}Neither & 2,606 & 0.74\\
+\hspace{1em}Open code & 248 & 0.07\\
+\hspace{1em}Open data & 349 & 0.10\\
+\hspace{1em}Both & 297 & 0.08\\
 \addlinespace[0.3em]
@@
 \hspace{1em}Both & 123 & 0.08\\
-\addlinespace[0.3em]
-\multicolumn{3}{l}{\textbf{SocArXiv}}\\
-\hspace{1em}Neither & 405 & 0.85\\
-\hspace{1em}Open code & 14 & 0.03\\
-\hspace{1em}Open data & 42 & 0.09\\
-\hspace{1em}Both & 17 & 0.04\\
 \bottomrule
@@
 \end{table}
+
+\hypertarget{table-of-proportion-of-all-preprints-in-each-category-for-each-preprint-server}{%
+\section{Table of proportion of all preprints in each category, for each preprint server}\label{table-of-proportion-of-all-preprints-in-each-category-for-each-preprint-server}}
+
+\begin{table}
+
+\caption{\label{tab:propbyserverandcategory}Number and proportion of all preprints in each category, for each preprint server}
+\centering
+\begin{tabular}[t]{llrr}
+\toprule
+Repository & Condition & Number & Proportion\\
+\midrule
+arXiv & Both & 99 & 0.10\\
+arXiv & Neither & 752 & 0.75\\
+arXiv & Open Code & 115 & 0.12\\
+arXiv & Open Data & 34 & 0.03\\
+bioRxiv & Both & 75 & 0.07\\
+bioRxiv & Neither & 674 & 0.67\\
+bioRxiv & Open Code & 44 & 0.04\\
+bioRxiv & Open Data & 207 & 0.21\\
+medRxiv & Both & 123 & 0.08\\
+medRxiv & Neither & 1180 & 0.79\\
+medRxiv & Open Code & 89 & 0.06\\
+medRxiv & Open Data & 108 & 0.07\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\newpage
 
@@
 
-\leavevmode\hypertarget{ref-citealexandermafouz}{}%
-Alexander, Rohan, and A Mahfouz. 2021. \emph{{heapsofpapers: Easily Download Heaps of Papers}}. \url{https://rohanalexander.github.io/heapsofpapers/}.
+\leavevmode\hypertarget{ref-barba2018terminologies}{}%
+Barba, Lorena A. 2018. {``Terminologies for Reproducible Research.''} \url{http://arxiv.org/abs/1802.03311}.
 

### 2022-01-13 outputs/paper/paper.Rmd
Final review paper updates - added appendices, arxiv and socarxiv validation data

@@
 
-# socarxiv_open_data_results <- 
-#   read_csv(here::here("outputs/data/socarxiv_open_data_results.csv"))
-# socarxiv_2019_open_data_results <- 
-#   read_csv(here::here("outputs/control-data/socarxiv_2019_open_data_results.csv"))
-# socarxiv_metadata_2019 <- 
-#   read_csv(here::here("outputs/control-data/socarxiv_metadata_2019.csv"))
+socarxiv_open_data_results <-
+  read_csv(here::here("outputs/data/socarxiv_open_data_results.csv"))
+socarxiv_2019_open_data_results <-
+  read_csv(here::here("outputs/control-data/socarxiv_2019_open_data_results.csv"))
+socarxiv_metadata_2019 <-
+  read_csv(here::here("outputs/control-data/socarxiv_metadata_2019.csv"))
 
@@
 This was conducted using the `open_data_search()` function from the `oddpub` package.
-Under original validation process, the ODDPub algorithm performed with a sensitivity of 0.73 and a specificity of 1.00 for open code detection and a sensitivity of 0.73 and a specificity of 0.97 for open data detection compared with manual screening [@citePDDPub].
+Under the validation procedure from the original authors, the ODDPub algorithm performed with a sensitivity of 0.73 and a specificity of 1.00 for open code detection and a sensitivity of 0.73 and a specificity of 0.97 for open data detection compared with manual screening [@citePDDPub].
+Since the ODDPub algorithm was developed specifically for biomedical publications, we conducted our own validation process for its performance on arXiv pre-prints.
+We found that the ODDPub algorithm performed with a sensitivity of 0.60 and a specificity of 0.98 for open code detection and a sensitivity of 0.67 and a specificity of 0.98 for open data detection compared with manual screening.
+Details of our validation procedure are contained in Appendix \@ref(oddpub-algorithm-performance-on-arxiv-pre-prints).
 
@@
   theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45)) +
   scale_fill_manual(values = cbPalette) +
@@
 
-Of the analyzed pre-prints from 2019, 93 per cent of those posted to arXiv, 63 per cent of those posted to bioRxiv, and 75 per cent of those posted to medRxiv showed no indication of open data or open code (Table \@ref(tab:2019-published)).
+Of the analyzed pre-prints from 2019, 93 per cent of those posted to arXiv, 63 per cent of those posted to bioRxiv, and 75 per cent of those posted to medRxiv showed no indication of open data or open code.
 
@@
              scales = "free_y") +
-  theme(axis.text.x = element_text(angle = 90, hjust = 1))
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
 
@@
 This sample is broken down as follows: 1,500 from medRxiv, 1,000 from arXiv, and 1,000 from bioRxiv.
-Broadly, we are unable to find markers of either open data or open code for 3,011 pre-prints or approximately 76 per cent of our sample (Table \@ref(tab:summarycounts-repositories)).
+Broadly, we are unable to find markers of either open data or open code for 3,011 pre-prints or approximately 76 per cent of our sample (Appendix \@ref(tables-with-specific-values-displayed-in-the-graphs) Table \@ref(tab:summarycounts-repositories)).
 Of the remaining pre-prints, 7 per cent contained open code markers only, 10 per cent contained open data markers only, and 8 per cent included markers of both open data and open code.
@@
 When differentiated by repository, we observe that open data and code markers were absent from 75 per cent of the sampled arXiv pre-prints, 67 per cent of the sampled bioRxiv pre-prints, 79 per cent of the sampled medRxiv pre-prints.
-The distribution of the remaining portion of pre-prints also varies by repository (Table \@ref(tab:summarycounts-repositories)).
+The distribution of the remaining portion of pre-prints also varies by repository (Appendix \@ref(tables-with-specific-values-displayed-in-the-graphs) Table \@ref(tab:summarycounts-repositories)).
 Notably, 28 per cent of sampled pre-prints from bioRxiv contained open data markers and 22 per cent of sampled arXiv pre-prints contained markers of open code, the highest proportions of any repository for each type of marker.
@@
 Additionally, `oddpub` does not consider '[t]he reuse of data/code previously published by other researchers' [@citePDDPub].
-A different definition of open data could enable pre-prints that reuse publicly available data to have made theirdata available for reproducibility purposes.
+A different definition of open data could enable pre-prints that reuse publicly available data to be considered as having their data available for reproducibility purposes.
 
@@
              scales = "free_y") +
-  theme(axis.text.x = element_text(angle = 90, hjust = 1))
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
 ```
@@
 Notably, of all COVID-19-related pre-prints in our dataset, approximately 30 per cent of those posted to bioRxiv and nearly one third of those posted to medRxiv were published.
-This is high in comparison to the proportions from arXiv, and although this might suggest that COVID-19-related pre-prints in biomedical fields have received greater attention overall than pre-prints from other fields, our results in Section \@ref(pre-pandemic-pre-prints) suggest that this pattern pre-dates the pandemic.
+This is high in comparison to the proportion from arXiv, and although this might suggest that COVID-19-related pre-prints in biomedical fields have received greater attention overall than pre-prints from other fields, our results in Section \@ref(pre-pandemic-pre-prints) suggest that this pattern pre-dates the pandemic.
 
@@
 This need is again emphasized by the new-found speed at which pre-prints may gain public, media, and political attention in the context of the pandemic, particularly those from medRxiv and bioRxiv.
-One further concern is raised by @da2020silently, who show that there are pre-prints on those two pre-print servers---medRxiv and bioRxiv---that were withdrawn or retracted with relatively little information about the underlying reason, after gaining substantial media attention.
+One further concern is raised by @da2020silently, who shows that there are pre-prints on those two pre-print servers---medRxiv and bioRxiv---that were withdrawn or retracted with relatively little information about the underlying reason, after gaining substantial media attention.
 
@@
 This is important because the epicenter of the pandemic changed throughout the pandemic, which has implications for our time-based analysis.
+
+A logical next step would be to extend this analysis to additional pre-print servers.
+An initial iteration of our analyses included samples of pre-pandemic and COVID-19-related pre-prints posted to SocArXiv, a social sciences pre-print server hosted by the Center for Open Science.
+We validated the ODDPub algorithm against the presence of data links provided by pre-print authors upon submission (available in the pre-print metadata drawn from the Open Science Framework API) and found that the algorithm performed with 52 per cent sensitivity on the 2019 sample and 29 per cent sensitivity for COVID-19-related pre-prints.
+The high rate of false negatives for open data detection is concerning, and it was decided that the ODDPub algorithm is not suitable for use on pre-prints from this server.
+A more generalized (or perhaps field specific) algorithm would be necessary for analysis of open data and code availability in SocArXiv and other more specialized servers.
+Details on validation are available in Appendix \@ref(oddpub-algorithm-performance-on-socarxiv-pre-prints).
 
@@
   mutate(proportion = n/(sum(n))) %>%
-   kable(caption = "Number and proportion of all preprints in each category, for each preprint server", 
-        col.names = c("Repository", "Condition", "Number", "Proportion"),
+  ungroup() %>%
+  select(condition, n, proportion) %>%
+   # kable(caption = "Number and proportion of all preprints in each category, for each preprint server",
+   #      col.names = c("Repository", "Condition", "Number", "Proportion"),
+   #      digits = 2,
+   #      booktabs = TRUE,
+   #      linesep = ""
+   #      )
+  kable(col.names = c("Markers", "Count", "Proportion of total"),
+        caption = "Number and proportion of all preprints in each category, for each preprint server",
+        booktabs = TRUE,
         digits = 2,
-        booktabs = TRUE,
-        linesep = ""
-        )
+        format.args = list(big.mark = ",")) %>%
+  group_rows(index = c("arXiv" = 4, "bioRxiv" = 4, "medRxiv" = 4))  %>%
+  kableExtra::kable_styling(latex_options = "hold_position")
+
+```
+
+# ODDPub algorithm performance on arXiv pre-prints
+
+We verified the accuracy of the ODDPub algorithm on a subset of our analyzed pre-prints from 2019 from arXiv.
+We took a simple random sample of 100 papers.
+In the original validation process, the annotators stratified by detection status prior to sampling to ensure relatively high representation of papers where open data or code was detected.
+Since the major concern for our manual verification is potential false negatives, this skewed representation was unnecessary.
+Open data and code status were verified first via the "Code & Data" tab on each pre-print's page on the arXiv website, then by checking for an explicit data availability section within the pre-print PDF, and finally by manually checking the body of the paper using keyword searches.
+Results were recorded manually in Excel.
+This mimics the procedure outlined for the original validation of ODDPub [@citePDDPub].
+
+Many of the pre-prints in arXiv did not use data or code, namely those from pure mathematics and physics.
+There were also several that reused other publicly or privately available data sets, and regardless of whether or not they were shared alongside the paper, these do not count as open data according to the standards outlined by the original authors of the ODDPub algorithm [@citePDDPub].
+Algorithmic performance is specified in Table \@ref(tab:arxiv-accuracy-data-2019) and Table \@ref(tab:arxiv-accuracy-code-2019).
+
+```{r arxiv-confusion-data-2019}
+arxiv_2019_manual_results <- read.csv(here::here("validation", "arxiv_2019_validation_sample_COMPLETE.csv"))
+
+arxiv_2019_data_check <- arxiv_2019_manual_results %>%
+  count(is_open_data, manual_open_data) %>%
+  pivot_wider(names_from = manual_open_data, values_from = n) %>%
+  mutate(is_open_data = case_when(is_open_data == 1 ~ "Open data detected", TRUE ~ "No open data detected")) %>%
+  select(is_open_data, `1`, `0`) %>%
+  rename(Predicted = is_open_data, `Data available` = `1`, `No data available` = `0`) %>%
+  arrange(desc(Predicted))
+
+arxiv_2019_data_check %>% kable(caption = "ODDPub predictions for open data compared with manual check, arXiv sample")
+
+```
+
+```{r arxiv-accuracy-data-2019}
+arc_2019_accuracy <- (as.numeric(arxiv_2019_data_check[1,2] + arxiv_2019_data_check[2,3])/nrow(arxiv_2019_manual_results)) %>% round(2)
+arc_2019_sensitivity <- (as.numeric(arxiv_2019_data_check[1,2])/sum(arxiv_2019_data_check$`Data available`)) %>% round(2)
+arc_2019_specificity <- (as.numeric(arxiv_2019_data_check[2,3])/sum(arxiv_2019_data_check$`No data available`)) %>% round(2)
+
+tibble(Metric = c("Accuracy", "Sensitivity", "Specificity"),
+      Value = c(arc_2019_accuracy, arc_2019_sensitivity, arc_2019_specificity)) %>% kable(caption = "ODDPub prediction accuracy, open data, arXiv sample")
+```
+
+```{r arxiv-confusion-code-2019}
+
+arxiv_2019_code_check <- arxiv_2019_manual_results %>%
+  count(is_open_code, manual_open_code) %>%
+  pivot_wider(names_from = manual_open_code, values_from = n) %>%
+  mutate(is_open_code = case_when(is_open_code == 1 ~ "Open code detected", TRUE ~ "No open code detected")) %>%
+  select(is_open_code, `1`, `0`) %>%
+  rename(Predicted = is_open_code, `Code available` = `1`, `No code available` = `0`) %>%
+  arrange(desc(Predicted))
+
+arxiv_2019_code_check %>% kable(caption = "ODDPub predictions for open code compared with manual check, arXiv sample")
+```
+
+```{r arxiv-accuracy-code-2019}
+arc_2019_code_accuracy <- (as.numeric(arxiv_2019_code_check[1,2] + arxiv_2019_code_check[2,3])/nrow(arxiv_2019_manual_results)) %>% round(2)
+arc_2019_code_sensitivity <- (as.numeric(arxiv_2019_code_check[1,2])/sum(arxiv_2019_code_check$`Code available`)) %>% round(2)
+arc_2019_code_specificity <- (as.numeric(arxiv_2019_code_check[2,3])/sum(arxiv_2019_code_check$`No code available`)) %>% round(2)
+
+tibble(Metric = c("Accuracy", "Sensitivity", "Specificity"),
+      Value = c(arc_2019_code_accuracy, arc_2019_code_sensitivity, arc_2019_code_specificity)) %>% kable(caption = "ODDPub prediction accuracy, open code, arXiv sample")
+```
+
+# ODDPub algorithm performance on SocArXiv pre-prints
+
+SocArXiv allows authors to input a link to their data source/repository upon submission of a pre-print.
+This link can then be accessed via the API metadata.
+The presence of a data link was used as an indicator that a pre-print provides open data for the purposes of validating the ODDPub algorithm.
+When available, a data link is stored under the variable name "attributes.data_links".
+The data was manipulated using functions from the R package tidyverse [@citetidyverse] to create a binary variable indicating data availability or lack thereof.
+We assume "attributes.data_links" to indicate the true availability of data for the purposes of validating the ODDPub algorithm.
+It is possible, however, that some authors failed to indicate their data availability in the proper field upon posting to SocArXiv, and thus some of the false positive may in fact be true positives.
+
+Against the data availability indicated by pre-print authors in our 2019 sample, the ODDPub algorithm performed with an accuracy of 93 percent, a sensitivity of 52 percent, and a specificity of 94 percent.
+In our 2020 and 2021 sample, the algorithm performed with an accuracy of 79 percent, a sensitivity of 29 percent, and a specificity of 92 percent.
+Specific predictions are broken down in Table \@ref(tab:confusion-matrix-2019) and Table \@ref(tab:confusion-matrix-2020).
+
+It is unclear the precise inclusion criteria for data submitted to the data link field.
+It is possible that some of the links provided lead to data sets that are publicly available for reuse, which would not constitute "open data" by the ODDPub algorithm's definition, in which case the accuracy could potentially be higher in reality than 93 percent and 79 percent in the samples considered.
+
+```{r, confusion-matrix-2019}
+# SocArXiv 2019 Confusion Matrix
+soc_2019_check <- socarxiv_2019_open_data_results %>%
+  mutate(data_link_available = case_when(is.na(attributes.data_links) ~ "No data linked", TRUE ~ "Data linked")) %>%
+  count(data_link_available, is_open_data) %>%
+  pivot_wider(names_from = data_link_available, values_from = n) %>%
+  mutate(is_open_data = case_when(is_open_data == 1 ~ "Open data detected", TRUE ~ "No open data detected")) %>%
+  rename(`ODDPub algorithm`= is_open_data) %>%
+  arrange(desc(`ODDPub algorithm`))
+soc_2019_check %>% kable(caption = "ODDPub predictions for open data compared with data links provided by authors, 2019 SocArXiv sample")
+```
+
+```{r, accuracy-2019}
+soc_2019_accuracy <- (as.numeric(soc_2019_check[1,2] + soc_2019_check[2,3])/nrow(socarxiv_2019_open_data_results)) %>% round(2)
+soc_2019_sensitivity <- (as.numeric(soc_2019_check[1,2])/sum(soc_2019_check$`Data linked`)) %>% round(2)
+soc_2019_specificity <- (as.numeric(soc_2019_check[2,3])/sum(soc_2019_check$`No data linked`)) %>% round(2)
+
+tibble(Metric = c("Accuracy", "Sensitivity", "Specificity"),
+      Value = c(soc_2019_accuracy, soc_2019_sensitivity, soc_2019_specificity)) %>% kable(caption = "ODDPub prediction accuracy, open data, 2019 SocArXiv sample")
+```
+
+```{r confusion-matrix-2020}
+# SocArXiv 2019 Confusion Matrix
+soc_2020_check <- socarxiv_open_data_results %>%
+  mutate(data_link_available = case_when(is.na(attributes.data_links) ~ "No data linked", TRUE ~ "Data linked")) %>%
+  count(data_link_available, is_open_data) %>%
+  pivot_wider(names_from = data_link_available, values_from = n) %>%
+  mutate(is_open_data = case_when(is_open_data == 1 ~ "Open data detected", TRUE ~ "No open data detected")) %>%
+  rename(`ODDPub algorithm`= is_open_data) %>%
+  arrange(desc(`ODDPub algorithm`))
+soc_2020_check %>% kable(caption = "ODDPub predictions for open data compared with data links provided by authors, COVID-19-related SocArXiv pre-prints sample")
+```
+
+```{r accuracy-2020}
+soc_2020_accuracy <- (as.numeric(soc_2020_check[1,2] + soc_2020_check[2,3])/nrow(socarxiv_open_data_results)) %>% round(2)
+soc_2020_sensitivity <- (as.numeric(soc_2020_check[1,2])/sum(soc_2020_check$`Data linked`)) %>% round(2)
+soc_2020_specificity <- (as.numeric(soc_2020_check[2,3])/sum(soc_2020_check$`No data linked`)) %>% round(2)
+
+tibble(Metric = c("Accuracy", "Sensitivity", "Specificity"),
+      Value = c(soc_2020_accuracy, soc_2020_sensitivity, soc_2020_specificity)) %>% kable(caption = "ODDPub prediction accuracy, open data, COVID-19-related SocArXiv pre-prints sample")
 ```

### 2022-01-13 outputs/paper/paper.tex
Final review paper updates - added appendices, arxiv and socarxiv validation data

@@
 This was conducted using the \texttt{open\_data\_search()} function from the \texttt{oddpub} package.
-Under original validation process, the ODDPub algorithm performed with a sensitivity of 0.73 and a specificity of 1.00 for open code detection and a sensitivity of 0.73 and a specificity of 0.97 for open data detection compared with manual screening (Riedel, Kip, and Bobrov 2020).
+Under the validation procedure from the original authors, the ODDPub algorithm performed with a sensitivity of 0.73 and a specificity of 1.00 for open code detection and a sensitivity of 0.73 and a specificity of 0.97 for open data detection compared with manual screening (Riedel, Kip, and Bobrov 2020).
+Since the ODDPub algorithm was developed specifically for biomedical publications, we conducted our own validation process for its performance on arXiv pre-prints.
+We found that the ODDPub algorithm performed with a sensitivity of 0.60 and a specificity of 0.98 for open code detection and a sensitivity of 0.67 and a specificity of 0.98 for open data detection compared with manual screening.
+Details of our validation procedure are contained in Appendix \ref{oddpub-algorithm-performance-on-arxiv-pre-prints}.
 
@@
 
-Of the analyzed pre-prints from 2019, 93 per cent of those posted to arXiv, 63 per cent of those posted to bioRxiv, and 75 per cent of those posted to medRxiv showed no indication of open data or open code (Table \ref{tab:2019-published}).
+Of the analyzed pre-prints from 2019, 93 per cent of those posted to arXiv, 63 per cent of those posted to bioRxiv, and 75 per cent of those posted to medRxiv showed no indication of open data or open code.
 
@@
 This sample is broken down as follows: 1,500 from medRxiv, 1,000 from arXiv, and 1,000 from bioRxiv.
-Broadly, we are unable to find markers of either open data or open code for 3,011 pre-prints or approximately 76 per cent of our sample (Table \ref{tab:summarycounts-repositories}).
+Broadly, we are unable to find markers of either open data or open code for 3,011 pre-prints or approximately 76 per cent of our sample (Appendix \ref{tables-with-specific-values-displayed-in-the-graphs} Table \ref{tab:summarycounts-repositories}).
 Of the remaining pre-prints, 7 per cent contained open code markers only, 10 per cent contained open data markers only, and 8 per cent included markers of both open data and open code.
@@
 When differentiated by repository, we observe that open data and code markers were absent from 75 per cent of the sampled arXiv pre-prints, 67 per cent of the sampled bioRxiv pre-prints, 79 per cent of the sampled medRxiv pre-prints.
-The distribution of the remaining portion of pre-prints also varies by repository (Table \ref{tab:summarycounts-repositories}).
+The distribution of the remaining portion of pre-prints also varies by repository (Appendix \ref{tables-with-specific-values-displayed-in-the-graphs} Table \ref{tab:summarycounts-repositories}).
 Notably, 28 per cent of sampled pre-prints from bioRxiv contained open data markers and 22 per cent of sampled arXiv pre-prints contained markers of open code, the highest proportions of any repository for each type of marker.
@@
 Additionally, \texttt{oddpub} does not consider `{[}t{]}he reuse of data/code previously published by other researchers' (Riedel, Kip, and Bobrov 2020).
-A different definition of open data could enable pre-prints that reuse publicly available data to have made theirdata available for reproducibility purposes.
+A different definition of open data could enable pre-prints that reuse publicly available data to be considered as having their data available for reproducibility purposes.
 
@@
 Notably, of all COVID-19-related pre-prints in our dataset, approximately 30 per cent of those posted to bioRxiv and nearly one third of those posted to medRxiv were published.
-This is high in comparison to the proportions from arXiv, and although this might suggest that COVID-19-related pre-prints in biomedical fields have received greater attention overall than pre-prints from other fields, our results in Section \ref{pre-pandemic-pre-prints} suggest that this pattern pre-dates the pandemic.
+This is high in comparison to the proportion from arXiv, and although this might suggest that COVID-19-related pre-prints in biomedical fields have received greater attention overall than pre-prints from other fields, our results in Section \ref{pre-pandemic-pre-prints} suggest that this pattern pre-dates the pandemic.
 
@@
 This need is again emphasized by the new-found speed at which pre-prints may gain public, media, and political attention in the context of the pandemic, particularly those from medRxiv and bioRxiv.
-One further concern is raised by Teixeira da Silva (2020), who show that there are pre-prints on those two pre-print servers---medRxiv and bioRxiv---that were withdrawn or retracted with relatively little information about the underlying reason, after gaining substantial media attention.
+One further concern is raised by Teixeira da Silva (2020), who shows that there are pre-prints on those two pre-print servers---medRxiv and bioRxiv---that were withdrawn or retracted with relatively little information about the underlying reason, after gaining substantial media attention.
 
@@
 This is important because the epicenter of the pandemic changed throughout the pandemic, which has implications for our time-based analysis.
+
+A logical next step would be to extend this analysis to additional pre-print servers.
+An initial iteration of our analyses included samples of pre-pandemic and COVID-19-related pre-prints posted to SocArXiv, a social sciences pre-print server hosted by the Center for Open Science.
+We validated the ODDPub algorithm against the presence of data links provided by pre-print authors upon submission (available in the pre-print metadata drawn from the Open Science Framework API) and found that the algorithm performed with 52 per cent sensitivity on the 2019 sample and 29 per cent sensitivity for COVID-19-related pre-prints.
+The high rate of false negatives for open data detection is concerning, and it was decided that the ODDPub algorithm is not suitable for use on pre-prints from this server.
+A more generalized (or perhaps field specific) algorithm would be necessary for analysis of open data and code availability in SocArXiv and other more specialized servers.
+Details on validation are available in Appendix \ref{oddpub-algorithm-performance-on-socarxiv-pre-prints}.
 
@@
 \centering
-\begin{tabular}[t]{llrr}
+\begin{tabular}[t]{lrr}
 \toprule
-Repository & Condition & Number & Proportion\\
+Markers & Count & Proportion of total\\
 \midrule
-arXiv & Both & 99 & 0.10\\
-arXiv & Neither & 752 & 0.75\\
-arXiv & Open Code & 115 & 0.12\\
-arXiv & Open Data & 34 & 0.03\\
-bioRxiv & Both & 75 & 0.07\\
-bioRxiv & Neither & 674 & 0.67\\
-bioRxiv & Open Code & 44 & 0.04\\
-bioRxiv & Open Data & 207 & 0.21\\
-medRxiv & Both & 123 & 0.08\\
-medRxiv & Neither & 1180 & 0.79\\
-medRxiv & Open Code & 89 & 0.06\\
-medRxiv & Open Data & 108 & 0.07\\
+\addlinespace[0.3em]
+\multicolumn{3}{l}{\textbf{arXiv}}\\
+\hspace{1em}Both & 99 & 0.10\\
+\hspace{1em}Neither & 752 & 0.75\\
+\hspace{1em}Open Code & 115 & 0.12\\
+\hspace{1em}Open Data & 34 & 0.03\\
+\addlinespace[0.3em]
+\multicolumn{3}{l}{\textbf{bioRxiv}}\\
+\hspace{1em}Both & 75 & 0.07\\
+\hspace{1em}Neither & 674 & 0.67\\
+\hspace{1em}Open Code & 44 & 0.04\\
+\hspace{1em}Open Data & 207 & 0.21\\
+\addlinespace[0.3em]
+\multicolumn{3}{l}{\textbf{medRxiv}}\\
+\hspace{1em}Both & 123 & 0.08\\
+\hspace{1em}Neither & 1,180 & 0.79\\
+\hspace{1em}Open Code & 89 & 0.06\\
+\hspace{1em}Open Data & 108 & 0.07\\
 \bottomrule
+\end{tabular}
+\end{table}
+
+\hypertarget{oddpub-algorithm-performance-on-arxiv-pre-prints}{%
+\section{ODDPub algorithm performance on arXiv pre-prints}\label{oddpub-algorithm-performance-on-arxiv-pre-prints}}
+
+We verified the accuracy of the ODDPub algorithm on a subset of our analyzed pre-prints from 2019 from arXiv.
+We took a simple random sample of 100 papers.
+In the original validation process, the annotators stratified by detection status prior to sampling to ensure relatively high representation of papers where open data or code was detected.
+Since the major concern for our manual verification is potential false negatives, this skewed representation was unnecessary.
+Open data and code status were verified first via the ``Code \& Data'' tab on each pre-print's page on the arXiv website, then by checking for an explicit data availability section within the pre-print PDF, and finally by manually checking the body of the paper using keyword searches.
+Results were recorded manually in Excel.
+This mimics the procedure outlined for the original validation of ODDPub (Riedel, Kip, and Bobrov 2020).
+
+Many of the pre-prints in arXiv did not use data or code, namely those from pure mathematics and physics.
+There were also several that reused other publicly or privately available data sets, and regardless of whether or not they were shared alongside the paper, these do not count as open data according to the standards outlined by the original authors of the ODDPub algorithm (Riedel, Kip, and Bobrov 2020).
+Algorithmic performance is specified in Table \ref{tab:arxiv-accuracy-data-2019} and Table \ref{tab:arxiv-accuracy-code-2019}.
+
+\begin{table}
+
+\caption{\label{tab:arxiv-confusion-data-2019}ODDPub predictions for open data compared with manual check, arXiv sample}
+\centering
+\begin{tabular}[t]{l|r|r}
+\hline
+Predicted & Data available & No data available\\
+\hline
+Open data detected & 2 & 2\\
+\hline
+No open data detected & 1 & 95\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+
+\caption{\label{tab:arxiv-accuracy-data-2019}ODDPub prediction accuracy, open data, arXiv sample}
+\centering
+\begin{tabular}[t]{l|r}
+\hline
+Metric & Value\\
+\hline
+Accuracy & 0.97\\
+\hline
+Sensitivity & 0.67\\
+\hline
+Specificity & 0.98\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+
+\caption{\label{tab:arxiv-confusion-code-2019}ODDPub predictions for open code compared with manual check, arXiv sample}
+\centering
+\begin{tabular}[t]{l|r|r}
+\hline
+Predicted & Code available & No code available\\
+\hline
+Open code detected & 3 & 2\\
+\hline
+No open code detected & 2 & 93\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+
+\caption{\label{tab:arxiv-accuracy-code-2019}ODDPub prediction accuracy, open code, arXiv sample}
+\centering
+\begin{tabular}[t]{l|r}
+\hline
+Metric & Value\\
+\hline
+Accuracy & 0.96\\
+\hline
+Sensitivity & 0.60\\
+\hline
+Specificity & 0.98\\
+\hline
+\end{tabular}
+\end{table}
+
+\hypertarget{oddpub-algorithm-performance-on-socarxiv-pre-prints}{%
+\section{ODDPub algorithm performance on SocArXiv pre-prints}\label{oddpub-algorithm-performance-on-socarxiv-pre-prints}}
+
+SocArXiv allows authors to input a link to their data source/repository upon submission of a pre-print.
+This link can then be accessed via the API metadata.
+The presence of a data link was used as an indicator that a pre-print provides open data for the purposes of validating the ODDPub algorithm.
+When available, a data link is stored under the variable name ``attributes.data\_links.'' The data was manipulated using functions from the R package tidyverse (Wickham et al.
+2019) to create a binary variable indicating data availability or lack thereof.
+We assume ``attributes.data\_links'' to indicate the true availability of data for the purposes of validating the ODDPub algorithm.
+It is possible, however, that some authors failed to indicate their data availability in the proper field upon posting to SocArXiv, and thus some of the false positive may in fact be true positives.
+
+Against the data availability indicated by pre-print authors in our 2019 sample, the ODDPub algorithm performed with an accuracy of 93 percent, a sensitivity of 52 percent, and a specificity of 94 percent.
+In our 2020 and 2021 sample, the algorithm performed with an accuracy of 79 percent, a sensitivity of 29 percent, and a specificity of 92 percent.
+Specific predictions are broken down in Table \ref{tab:confusion-matrix-2019} and Table \ref{tab:confusion-matrix-2020}.
+
+It is unclear the precise inclusion criteria for data submitted to the data link field.
+It is possible that some of the links provided lead to data sets that are publicly available for reuse, which would not constitute ``open data'' by the ODDPub algorithm's definition, in which case the accuracy could potentially be higher in reality than 93 percent and 79 percent in the samples considered.
+
+\begin{table}
+
+\caption{\label{tab:confusion-matrix-2019}ODDPub predictions for open data compared with data links provided by authors, 2019 SocArXiv sample}
+\centering
+\begin{tabular}[t]{l|r|r}
+\hline
+ODDPub algorithm & Data linked & No data linked\\
+\hline
+Open data detected & 11 & 72\\
+\hline
+No open data detected & 10 & 1107\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+
+\caption{\label{tab:accuracy-2019}ODDPub prediction accuracy, open data, 2019 SocArXiv sample}
+\centering
+\begin{tabular}[t]{l|r}
+\hline
+Metric & Value\\
+\hline
+Accuracy & 0.93\\
+\hline
+Sensitivity & 0.52\\
+\hline
+Specificity & 0.94\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+
+\caption{\label{tab:confusion-matrix-2020}ODDPub predictions for open data compared with data links provided by authors, COVID-19-related SocArXiv pre-prints sample}
+\centering
+\begin{tabular}[t]{l|r|r}
+\hline
+ODDPub algorithm & Data linked & No data linked\\
+\hline
+Open data detected & 28 & 31\\
+\hline
+No open data detected & 69 & 350\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+
+\caption{\label{tab:accuracy-2020}ODDPub prediction accuracy, open data, COVID-19-related SocArXiv pre-prints sample}
+\centering
+\begin{tabular}[t]{l|r}
+\hline
+Metric & Value\\
+\hline
+Accuracy & 0.79\\
+\hline
+Sensitivity & 0.29\\
+\hline
+Specificity & 0.92\\
+\hline
 \end{tabular}
@@
 
+\leavevmode\hypertarget{ref-citetidyverse}{}%
+Wickham, Hadley, Mara Averick, Jennifer Bryan, Winston Chang, Lucy D'Agostino McGowan, Romain François, Garrett Grolemund, et al.
+2019.
+{``Welcome to the {tidyverse}.''} \emph{Journal of Open Source Software} 4 (43): 1686.
+\url{https://doi.org/10.21105/joss.01686}.
+
 \leavevmode\hypertarget{ref-citeWHOtimeline}{}%

### 2022-01-13 validation/oddpub_validation.Rmd
Figure and paper file updates
Final review paper updates - added appendices, arxiv and socarxiv validation data

@@
 title: "ODDPub Validation for SocArXiv and arXiv"
-output: html_document
+output: pdf_document
 ---
@@
 library(tidyverse)
+library(knitr)
 
@@
 
-Under "attributes.has_data_links", "available" means data link exists, everything else means data link does not exist.
-NA appears to be the same as "not_applicable", meaning no data link and no justification (i.e.
-"attributes.why_no_data" is also NA).
-"no" means data was used but is not available.
-Justification should be provided in "attributes.why_no_data".
+### Data
 
-Since ODDPub does not check for areas where open data is not applicable, we should go by 0/1 according to attributes.data_links being populated (i.e. "data_link_available" as defined above).
+SocArXiv allows authors to input a link to their data source/repository upon submission of a pre-print.
+This link can then be accessed via the API metadata.
+The presence of a data link was used as an indicator that a pre-print provides open data for the purposes of validating the ODDPub algorithm.
+When available, a data link is stored under the variable name "attributes.data_links".
+The data was manipulated using functions from the R package tidyverse [@tidyverse] to create a binary variable indicating data availability or lack thereof.
+We assume "attributes.data_links" to indicate the true availability of data for the purposes of validating the ODDPub algorithm.
+It is possible, however, that some authors failed to indicate their data availability in the proper field upon posting to SocArXiv, and thus some of the false positive may in fact be true positives.
+This was not verified directly in order to allow us to more easily consider the whole sample in our validation.
 
-We assume the attributes.data_links to be the "Gold Standard", i.e.
-indicating the true availability of data.
-It is possible, however, that some authors failed to indicate their data availability in the proper field upon posting to SocArXiv, and this some of the "false positive" may in fact be true positives.
+Against the data availability indicated by pre-print authors in our 2019 sample, the ODDPub algorithm performed with an accuracy of 93 percent, a sensitivity of 52 percent, and a specificity of 94 percent.
+In our 2020 and 2021 sample, the algorithm performed with an accuracy of 79 percent, a sensitivity of 29 percent, and a specificity of 92 percent.
+Specific predictions are broken down in Table \@ref(tab:confusion-matrix-2019) and Table \@ref(tab:confusion-matrix-2020).
 
-```{r confusion-matrix-2019}
+It is unclear the precise inclusion criteria for data submitted to the data link field.
+It is possible that some of the links provided lead to data sets that are publicly available for reuse, which would not constitute "open data" by the ODDPub algorithm's definition, in which case the accuracy could potentially be higher in reality than 93 percent and 79 percent in the samples considered.
+
+```{r, confusion-matrix-2019}
 # SocArXiv 2019 Confusion Matrix
@@
   mutate(is_open_data = case_when(is_open_data == 1 ~ "Open data detected", TRUE ~ "No open data detected")) %>%
-  rename(Predicted = is_open_data) %>%
-  arrange(desc(Predicted))
-soc_2019_check
+  rename(`ODDPub algorithm`= is_open_data) %>%
+  arrange(desc(`ODDPub algorithm`))
+soc_2019_check %>% kable(caption = "ODDPub predictions for open data compared with data links provided by authors, 2019 sample")
 ```
 
-```{r accuracy-2019}
-soc_2019_accuracy <- as.numeric(soc_2019_check[1,2] + soc_2019_check[2,3])/nrow(socarxiv_2019_open_data_results)
-soc_2019_sensitivity <- as.numeric(soc_2019_check[1,2])/sum(soc_2019_check$`Data linked`) %>% as.numeric()
-soc_2019_specificity <- as.numeric(soc_2019_check[2,3])/sum(soc_2019_check$`No data linked`)
+```{r, accuracy-2019}
+soc_2019_accuracy <- (as.numeric(soc_2019_check[1,2] + soc_2019_check[2,3])/nrow(socarxiv_2019_open_data_results)) %>% round(2)
+soc_2019_sensitivity <- (as.numeric(soc_2019_check[1,2])/sum(soc_2019_check$`Data linked`)) %>% round(2)
+soc_2019_specificity <- (as.numeric(soc_2019_check[2,3])/sum(soc_2019_check$`No data linked`)) %>% round(2)
 
 tibble(Metric = c("Accuracy", "Sensitivity", "Specificity"),
-      Value = c(soc_2019_accuracy, soc_2019_sensitivity, soc_2019_specificity))
+      Value = c(soc_2019_accuracy, soc_2019_sensitivity, soc_2019_specificity)) %>% kable(caption = "ODDPub prediction accuracy, 2019 sample")
 ```
@@
 
+### Code
+
 ## 2020/2021
+
+Code was not manually verified for COVID-19 related papers.
 
@@
   mutate(is_open_data = case_when(is_open_data == 1 ~ "Open data detected", TRUE ~ "No open data detected")) %>%
-  rename(Predicted = is_open_data) %>%
-  arrange(desc(Predicted))
-soc_2020_check
+  rename(`ODDPub algorithm`= is_open_data) %>%
+  arrange(desc(`ODDPub algorithm`))
+soc_2020_check %>% kable(caption = "ODDPub predictions for open data compared with data links provided by authors, COVID-19-related pre-prints sample")
 ```
@@
 ```{r accuracy-2020}
-soc_2020_accuracy <- as.numeric(soc_2020_check[1,2] + soc_2020_check[2,3])/nrow(socarxiv_open_data_results)
-soc_2020_sensitivity <- as.numeric(soc_2020_check[1,2])/sum(soc_2020_check$`Data linked`) %>% as.numeric()
-soc_2020_specificity <- as.numeric(soc_2020_check[2,3])/sum(soc_2020_check$`No data linked`)
+soc_2020_accuracy <- (as.numeric(soc_2020_check[1,2] + soc_2020_check[2,3])/nrow(socarxiv_open_data_results)) %>% round(2)
+soc_2020_sensitivity <- (as.numeric(soc_2020_check[1,2])/sum(soc_2020_check$`Data linked`)) %>% round(2)
+soc_2020_specificity <- (as.numeric(soc_2020_check[2,3])/sum(soc_2020_check$`No data linked`)) %>% round(2)
 
 tibble(Metric = c("Accuracy", "Sensitivity", "Specificity"),
-      Value = c(soc_2020_accuracy, soc_2020_sensitivity, soc_2020_specificity))
+      Value = c(soc_2020_accuracy, soc_2020_sensitivity, soc_2020_specificity)) %>% kable(caption = "ODDPub prediction accuracy, COVID-19-related pre-prints sample")
 ```

### 2022-01-14 outputs/paper/paper.Rmd
revised and resubmitted

@@
 The text, tables and figures of this manuscript overlap with those of the preprint version by the authors.
-**Acknowledgements:** We thank Amy Farrow, Jessica Gronsbell, Monica Alexander, and Thomas William Rosenthal for helpful comments.
-Two anonymous reviewers and the editor provided extensive comments that substantially improved this paper and we are grateful to them.
+**Acknowledgements:** Two anonymous reviewers and the editor provided extensive comments that substantially improved this paper and we are grateful to them.
+We thank Amy Farrow, Jessica Gronsbell, Monica Alexander, and Thomas William Rosenthal for helpful comments.
 **Funding statement:** Collins thanks CANSSI Ontario and Monica Alexander for financial support.
@@
 Collins and Alexander obtained and created the datasets.
-Collins and Alexander analysed the data.
+Collins and Alexander analyzed the data.
 All authors interpreted the data and contributed writing the paper and approved the final version."
@@
 abstract: "To examine the reproducibility of COVID-19 research, we create a dataset of pre-prints posted to arXiv, bioRxiv, and medRxiv between 28 January 2020 and 30 June 2021 that are related to COVID-19.
-We extract the text from these pre-prints and parse them looking for keyword markers signalling the availability of the data and code underpinning the pre-print.
-For the pre-prints that are in our sample, we are unable to find markers of either open data or open code for 75 per cent of those on arXiv, 67 per cent of those on bioRxiv, and 79 per cent of those on medRxiv.
-We conclude that there may be value in having authors categorize the degree of openness of their pre-print as part of the pre-print submissions process, and more broadly, there is a need to better integrate open science training into a wide range of fields."
+We extract the text from these pre-prints and parse them looking for keyword markers signaling the availability of the data and code underpinning the pre-print.
+For the pre-prints that are in our sample, we are unable to find markers of either open data or open code for 75 per cent of those on arXiv, 67 per cent of those on bioRxiv, and 79 per cent of those on medRxiv."
 output:
@@
 
-Scientists use open repositories of papers to disseminate their research more quickly than is possible in traditional journals or conference proceedings, and also to obtain feedback on their work prior to publication.
+Scientists use open repositories of papers to disseminate their research more quickly than is possible in traditional journals or conference proceedings, and to obtain feedback on their work prior to publication.
 These repositories, such as arXiv, bioRxiv, and medRxiv, are a critical component of scientific communication and a lot of research builds on the pre-prints posted there.
@@
 For the purposes of this paper, we define reproducibility to mean the ability for different researchers to achieve the same results given the same data and computational methods as the original source.
-This contrasts replicability, which we define as the ability for different researchers to achieve consistent results by conducting the full data collection and analysis process in lieu of reusing original data.
+This contrasts with replicability, which we define as the ability for different researchers to achieve consistent results by conducting the full data collection and analysis process in lieu of reusing original data.
 These definitions match that of @NAP25303 and @cacioppo2015social.
+What constitutes open code or open data is complicated and discipline specific.
+The details of the `oddpub` approach are available in @citePDDPub.
+The general criteria are that specific mention should be made of where the data and code are located, and that data should be as close to raw as possible.
+Data and code must also be freely accessible to anyone (no request, application, registration process, or affiliation required).
 
@@
 
-all [label =  'All pre-prints posted between 28 January 2020 and 30 June 2021']
-onlycovid [label =  'Those about COVID-19']
+all [shape = oval, label =  'All pre-prints posted between 28 January 2020 and 30 June 2021']
+onlycovid [shape = oval, label =  'Those about COVID-19']
 arxivcovidcount [label =  'arXiv: 4,250 pre-prints']
@@
 # socarxivcovidcount [label =  'SocArXiv: 478 pre-prints']
-randomsample [label =  'Random sampling stratified by repository']
+randomsample [shape = oval, label =  'Random sampling stratified by repository']
 arxivsamplecount [label =  'arXiv: 1,000 pre-prints']
@@
 # socarxivsamplecount [label =  'SocArXiv: 478 pre-prints']
-opencodeanddata [label =  'Those with markers of open code or open data']
+opencodeanddata [shape = oval, label =  'Those with markers of open code or open data']
 arxivopencount [label =  'arXiv: 248 pre-prints']
@@
 Our primary dataset consists of pre-print metadata extracted from the arXiv, bioRxiv, and medRxiv pre-print repositories via their respective Application Programming Interfaces (APIs).
-This metadata varies by repository, but generally includes the following information: title, abstract, author(s), date created, research field, DOI, version number, corresponding author, corresponding author's institutional affiliation, published DOI (if the pre-print has since been published in a peer-reviewed journal), and download link.
+This metadata varies by repository, but generally includes: title, abstract, author(s), date created, research field, DOI, version number, corresponding author, corresponding author's institutional affiliation, published DOI (if the pre-print has since been published in a peer-reviewed journal), and download link.
 The data collection process was conducted separately for COVID-19 and pre-COVID-19 papers.
@@
 This was conducted using the `open_data_search()` function from the `oddpub` package.
-Under the validation procedure from the original authors, the ODDPub algorithm performed with a sensitivity of 0.73 and a specificity of 1.00 for open code detection and a sensitivity of 0.73 and a specificity of 0.97 for open data detection compared with manual screening [@citePDDPub].
+In the validation conducted by the authors of the package, the ODDPub algorithm had a sensitivity of 0.73 and a specificity of 1.00 for open code detection, and a sensitivity of 0.73 and a specificity of 0.97 for open data detection compared with manual screening [@citePDDPub].
 Since the ODDPub algorithm was developed specifically for biomedical publications, we conducted our own validation process for its performance on arXiv pre-prints.
-We found that the ODDPub algorithm performed with a sensitivity of 0.60 and a specificity of 0.98 for open code detection and a sensitivity of 0.67 and a specificity of 0.98 for open data detection compared with manual screening.
+We found that the ODDPub algorithm performed with a sensitivity of 0.60 and a specificity of 0.98 for open code detection, and a sensitivity of 0.67 and a specificity of 0.98 for open data detection compared with manual screening.
 Details of our validation procedure are contained in Appendix \@ref(oddpub-algorithm-performance-on-arxiv-pre-prints).
-
-What constitutes open code or open data is complicated and discipline specific.
-The details of the `oddpub` approach are available in @citePDDPub.
-The general criteria are that specific mention should be made of where the data and code are located, and that data should be as close to raw as possible.
-Data and code must also be freely accessible to anyone (no request, application, registration process, or affiliation required).
 Our work was conducted using the statistical programming language R [@citeR] (RRID:SCR_001905).
@@
 <!-- Notable discrepancies between the ODDPub algorithm and authors' self-reported data and code availability are documented in Appendix \@ref(socarxivissues). -->
-
-```{r monthly-papers-total, fig.cap = "Number of pre-prints related to COVID-19 posted to arXiv (N = 4,250), bioRxiv (N = 4,146), and medRxiv (N = 13,194) per month", out.width="90%", fig.align = "center", fig.pos="H"}
-just_arxiv <- 
-  all_arxiv_results  %>% 
-  select(submitted) %>% 
-  mutate(type = "arXiv") %>% 
-  rename(date = submitted)
-
-just_medRxiv <- 
-  med_results  %>% 
-  select(date) %>% 
-  mutate(type = "medRxiv")
-
-just_bioRxiv <- 
-  bio_results  %>% 
-  select(date) %>% 
-  mutate(type = "bioRxiv")
-
-# just_socarxiv <- 
-#   socarxiv_open_data_results  %>% 
-#   select(date_created) %>%
-#   rename(date = "date_created") %>%
-#   mutate(date = as.Date(date), type = "SocArXiv")
-
-all <- rbind(just_arxiv, 
-             just_medRxiv, 
-             just_bioRxiv
-             # , 
-             # just_socarxiv
-             )
-
-all %>% 
-  mutate(month = floor_date(date, "month")) %>% 
-  filter(year(date) >= 2020) %>%
-  filter(date < "2021-06-30") %>% 
-  ggplot(aes(x = month)) + 
-  geom_histogram(aes(fill = type), stat="count", position = "dodge") + 
-  labs(title = "COVID-19-related pre-prints posted per month",
-       x = "Month",
-       y = "Number of pre-prints",
-       fill = "Repository") +
-  scale_x_date(breaks=as.Date(c("2020-01-01","2020-07-01", "2021-01-01")),
-                   labels=c("Jan 2020", "Jul 2020", "Jan 2021")) +
-  theme_minimal() +
-  theme(axis.text.x = element_text(angle = 45)) +
-  scale_fill_manual(values = cbPalette) +
-  facet_wrap(~type,
-             scales = "free_y")
-```
 
@@
              scales = "free_y") +
-  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
+  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
+  theme(legend.position="bottom")
 ```
@@
         col.names = c("Repositiory", "Published pre-prints", "Proportion published"),
-        format.args = list(big.mark = ","))
+        format.args = list(big.mark = ","),
+        booktabs = TRUE)
 ```
@@
 When disaggregated by open data and code status, we find that published and unpublished pre-prints contain open data and code markers in similar proportions (Table \@ref(tab:2019-open-publishing)).
-This mimics the behaviour of published and unpublished COVID-19-related pre-prints.
+This mimics the behavior of published and unpublished COVID-19-related pre-prints.
 -->
@@
 
+```{r monthly-papers-total, fig.cap = "Number of pre-prints related to COVID-19 posted to arXiv (N = 4,250), bioRxiv (N = 4,146), and medRxiv (N = 13,194) per month", out.width="90%", fig.align = "center", fig.pos="H"}
+just_arxiv <- 
+  all_arxiv_results  %>% 
+  select(submitted) %>% 
+  mutate(type = "arXiv") %>% 
+  rename(date = submitted)
+
+just_medRxiv <- 
+  med_results  %>% 
+  select(date) %>% 
+  mutate(type = "medRxiv")
+
+just_bioRxiv <- 
+  bio_results  %>% 
+  select(date) %>% 
+  mutate(type = "bioRxiv")
+
+# just_socarxiv <- 
+#   socarxiv_open_data_results  %>% 
+#   select(date_created) %>%
+#   rename(date = "date_created") %>%
+#   mutate(date = as.Date(date), type = "SocArXiv")
+
+all <- rbind(just_arxiv, 
+             just_medRxiv, 
+             just_bioRxiv
+             # , 
+             # just_socarxiv
+             )
+
+all %>% 
+  mutate(month = floor_date(date, "month")) %>% 
+  filter(year(date) >= 2020) %>%
+  filter(date < "2021-06-30") %>% 
+  ggplot(aes(x = month)) + 
+  geom_histogram(aes(fill = type), stat="count", position = "dodge") + 
+  labs(title = "COVID-19-related pre-prints posted per month",
+       x = "Month",
+       y = "Number of pre-prints",
+       fill = "Repository") +
+  scale_x_date(breaks=as.Date(c("2020-01-01","2020-07-01", "2021-01-01")),
+                   labels=c("Jan 2020", "Jul 2020", "Jan 2021")) +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45)) +
+  scale_fill_manual(values = cbPalette) +
+  facet_wrap(~type,
+             scales = "free_y") +
+  theme(legend.position="bottom")
+```
+
 ## Open data and code
 
-From the collection of all pre-prints related to COVID-19, we randomly sampled 3,910 pre-prints to analyze, stratified by repository.
+From the collection of all pre-prints related to COVID-19, we randomly sampled 3,500 pre-prints to analyze, stratified by repository.
 This sample is broken down as follows: 1,500 from medRxiv, 1,000 from arXiv, and 1,000 from bioRxiv.
-Broadly, we are unable to find markers of either open data or open code for 3,011 pre-prints or approximately 76 per cent of our sample (Appendix \@ref(tables-with-specific-values-displayed-in-the-graphs) Table \@ref(tab:summarycounts-repositories)).
+Broadly, we are unable to find markers of either open data or open code for 2,606 pre-prints or approximately 74 per cent of our sample (Appendix \@ref(supporting-tables) Table \@ref(tab:summarycounts-repositories)).
 Of the remaining pre-prints, 7 per cent contained open code markers only, 10 per cent contained open data markers only, and 8 per cent included markers of both open data and open code.
@@
 When differentiated by repository, we observe that open data and code markers were absent from 75 per cent of the sampled arXiv pre-prints, 67 per cent of the sampled bioRxiv pre-prints, 79 per cent of the sampled medRxiv pre-prints.
-The distribution of the remaining portion of pre-prints also varies by repository (Appendix \@ref(tables-with-specific-values-displayed-in-the-graphs) Table \@ref(tab:summarycounts-repositories)).
+The distribution of the remaining portion of pre-prints also varies by repository (Appendix \@ref(supporting-tables) Table \@ref(tab:summarycounts-repositories)).
 Notably, 28 per cent of sampled pre-prints from bioRxiv contained open data markers and 22 per cent of sampled arXiv pre-prints contained markers of open code, the highest proportions of any repository for each type of marker.
@@
 
-On the other hand, the analyzed arXiv COVID-19-related pre-prints contain a higher proportion of open data and code markers overall than their 2019 counterparts, with a increase of 18 per cent in sampled arXiv papers.
+On the other hand, the analyzed arXiv COVID-19-related pre-prints contain a higher proportion of open data and code markers overall than their 2019 counterparts, with an increase of 18 per cent in sampled arXiv papers.
 For these repositories, the presence of both open data and open code markers was significantly associated with registration during the pandemic, suggesting that pre-prints related to COVID-19 in arXiv may have more consistently adhered to open science practices than their pre-pandemic counterparts ($\chi$^2^ = 93.124, arXiv open data;  $\chi$^2^ = 106.88, arXiv open code; $\chi$^2^ = 12.303).
@@
 The proportion of pre-prints that have been published varies by repository (Table \@ref(tab:published-sample-summary)).
-Notably, of all COVID-19-related pre-prints in our dataset, approximately 30 per cent of those posted to bioRxiv and nearly one third of those posted to medRxiv were published.
+Notably, of all COVID-19-related pre-prints in our dataset, approximately 30 per cent of those posted to bioRxiv and nearly one-third of those posted to medRxiv were published.
 This is high in comparison to the proportion from arXiv, and although this might suggest that COVID-19-related pre-prints in biomedical fields have received greater attention overall than pre-prints from other fields, our results in Section \@ref(pre-pandemic-pre-prints) suggest that this pattern pre-dates the pandemic.
@@
         col.names = c("Repository", "Published pre-prints", "Proportion published"),
-        format.args = list(big.mark = ","))
+        format.args = list(big.mark = ","),
+        booktabs = TRUE)
 ```
@@
 @mcguinness2021descriptive examine differences in data availability statements between medRxiv pre-prints and their published counterparts.
-They find that data availability was maintained for the vast majority of their sample, varying by journal data sharing policy with greater improvements in openness among manuscripts published in journals mandating data sharing.
+They find that data availability was maintained for most of their sample, varying by journal data sharing policy with greater improvements in openness among manuscripts published in journals mandating data sharing.
 While limited to medRxiv, the results of @mcguinness2021descriptive align with our own work and provide initial evidence to suggest that data availability is generally maintained or improved between the pre-print and publication stages.
@@
 
-Open code as an open science marker is context and field-dependent, as not all biomedical research papers will rely on computational methods for their analyses.
+Open code as an open science marker is context and field-dependent; for instance, not all biomedical research papers will rely on computational methods for their analyses.
 However, in pre-prints where code comprises a large portion of the methodology or results, posting it openly to repositories like GitHub contributes to a pre-print's potential reproducibility.
@@
 There has been a large amount of research on COVID-19 [@da2021publishing].
-Many concerns have arisen from the rate at which COVID-19 research has been posted and consumed via pre-print repositories, particularly in the early stages of the pandemic [@raynaud2021].
-Rushed scientific research has potential to skip (or at least place less precedence on) open science practices, thus it may be reasonable to expect a decrease in open data or code markers in the initial few months of the pandemic.
+Many concerns have arisen from the rate at which COVID-19 research has been posted and consumed through pre-print repositories, particularly in the early stages of the pandemic [@raynaud2021].
+Rushed scientific research has the potential to skip (or at least place less importance on) open science practices, so it may be reasonable to expect a decrease in open data or code markers in the initial few months of the pandemic.
 We found little relationship between date posted and likelihood of having open data or code markers, with the proportion of pre-prints containing these markers fluctuating from month to month.
@@
 In our sample, published pre-prints contain open data or code markers in similar proportions to their unpublished counterparts, a pattern that was present for pre-prints related to COVID-19 and those posted in 2019.
-This appears initially to alleviate some concerns over the relationship between open data and publication bias, that is, the potential that journals have favoured novel yet less transparent or reproducible papers over those with null results but a high standard of open science practices.
-However, publication bias is complex and this result should be approached with caution.
+This appears initially to alleviate some concerns over the relationship between open data and publication bias, that is, the potential that journals have favored novel yet less transparent or reproducible papers over those with null results but a high standard of open science practices.
+However, publication bias is complex, and this result should be approached with caution.
 Concerns have already been raised through systemic reviews of COVID-19 publications [@raynaud2021], and oversights in data accessibility have led to high profile retractions of publications in the past; for example, papers from *The Lancet* and the *New England Journal of Medicine* which were withdrawn due to concerns over the private nature of their underlying dataset [@ledford2020].
-Further, @cabanac2021day show that not all pre-prints are linked to their subsequent peer-reviewed publication, which may further bias our results.
-Further, there is the potential for bias due to older pre-prints having had more time to be published than newer pre-prints.
-And @oikonomidi2020changes and @Beroe051821 show that differences between updated versions of the same pre-print can be substantial; again this is something that we do not account for and could bias our results.
+@cabanac2021day show that not all pre-prints are linked to their subsequent peer-reviewed publication, which may further bias our results.
+Additionally, there is the potential for bias due to older pre-prints having had more time to be published than newer pre-prints.
+And @oikonomidi2020changes and @Beroe051821 show that differences between updated versions of the same pre-print can be substantial; again, this is something that we do not account for and could bias our results.
 
 In all fields of science, increasing access to data and code used for pre-printed or published research is a step in the direction of more transparent, reproducible, and reliable research.
-The ongoing COVID-19 pandemic has created a novel, constantly changing scientific culture that should be navigated with care to uphold standards of scientific practice for both the research community and the safety of the public.
+The COVID-19 pandemic has created a novel, constantly changing scientific culture that should be navigated with care to uphold standards of scientific practice for both the research community and the safety of the public.
 Our analysis shows that there is room for improvement in the areas of open data and code availability within COVID-19 pre-print papers on arXiv, bioRxiv, and medRxiv
@@
 
-We wish to expand our analysis to consider the geographic distribution of research and the potential influence of different practices and policies concerning open science as pre-prints vary by location.
-This is important because the epicenter of the pandemic changed throughout the pandemic, which has implications for our time-based analysis.
+Future work would expand our analysis to consider the geographic distribution of research and the potential influence of different practices and policies concerning open science.
+This is important because the epicenter of the pandemic changed throughout the pandemic, which may have implications for our time-based analysis.
 
 A logical next step would be to extend this analysis to additional pre-print servers.
-An initial iteration of our analyses included samples of pre-pandemic and COVID-19-related pre-prints posted to SocArXiv, a social sciences pre-print server hosted by the Center for Open Science.
+We have begun considering samples of pre-pandemic and COVID-19-related pre-prints posted to SocArXiv, a social sciences pre-print server hosted by the Center for Open Science.
 We validated the ODDPub algorithm against the presence of data links provided by pre-print authors upon submission (available in the pre-print metadata drawn from the Open Science Framework API) and found that the algorithm performed with 52 per cent sensitivity on the 2019 sample and 29 per cent sensitivity for COVID-19-related pre-prints.
-The high rate of false negatives for open data detection is concerning, and it was decided that the ODDPub algorithm is not suitable for use on pre-prints from this server.
-A more generalized (or perhaps field specific) algorithm would be necessary for analysis of open data and code availability in SocArXiv and other more specialized servers.
-Details on validation are available in Appendix \@ref(oddpub-algorithm-performance-on-socarxiv-pre-prints).
+The high rate of false negatives for open data detection is concerning, and it was decided that the ODDPub algorithm is not suitable for use on pre-prints from this server without modification.
+A more generalized (or perhaps field-specific) algorithm would be necessary for analysis of open data and code availability in SocArXiv and other more specialized servers.
+Details of this validation are available in Appendix \@ref(oddpub-algorithm-performance-on-socarxiv-pre-prints).
 
@@
 We also note that the ODDPub algorithm is relatively narrow in its definition of "open", excluding data that is available via registration or in some other restricted form.
-Adopting a broader definition of openness, either through using a less restrictive algorithm or through manual verification, would likely produce different results particularly for pre-prints using clinical data.
-In future, we wish to take smaller sub-samples to validate factors like publication status, paper topic, and open code and data status, beyond the approaches that we used here.
+Considering a broader definition of openness, either through using a less restrictive algorithm or through manual verification, would likely produce different results particularly for pre-prints using clinical data.
+Future work could take smaller sub-samples to validate factors like publication status, paper topic, and open code and data status, beyond the approaches we used here.
 
@@
 
-# Tables with specific values displayed in the graphs
+# ODDPub algorithm performance on arXiv pre-prints
+
+We verified the accuracy of the ODDPub algorithm on a subset of our analyzed pre-prints from 2019 from arXiv.
+We took a simple random sample of 100 papers.
+In the original validation process, the annotators stratified by detection status prior to sampling to ensure relatively high representation of papers where open data or code was detected.
+Since the major concern for our manual verification is potential false negatives, this skewed representation was unnecessary.
+Open data and code status were verified first via the "Code & Data" tab on each pre-print's page on the arXiv website, then by checking for an explicit data availability section within the pre-print PDF, and finally by manually checking the body of the paper using keyword searches.
+Results were recorded manually in Excel.
+This mimics the procedure outlined for the original validation of ODDPub [@citePDDPub].
+
+Many of the pre-prints in arXiv did not use data or code, namely those from pure mathematics and physics.
+There were also several that reused other publicly or privately available data sets, and regardless of whether or not they were shared alongside the paper, these do not count as open data according to the standards outlined by the original authors of the ODDPub algorithm [@citePDDPub].
+Algorithmic performance is specified in Table \@ref(tab:arxiv-accuracy-data-2019) and Table \@ref(tab:arxiv-accuracy-code-2019).
+
+```{r arxiv-confusion-data-2019}
+arxiv_2019_manual_results <- read.csv(here::here("validation", "arxiv_2019_validation_sample_COMPLETE.csv"))
+
+arxiv_2019_data_check <- arxiv_2019_manual_results %>%
+  count(is_open_data, manual_open_data) %>%
+  pivot_wider(names_from = manual_open_data, values_from = n) %>%
+  mutate(is_open_data = case_when(is_open_data == 1 ~ "Open data detected", TRUE ~ "No open data detected")) %>%
+  select(is_open_data, `1`, `0`) %>%
+  rename(Predicted = is_open_data, `Data available` = `1`, `No data available` = `0`) %>%
+  arrange(desc(Predicted))
+
+arxiv_2019_data_check %>% 
+  kable(caption = "ODDPub predictions for open data compared with manual check, arXiv sample",
+        booktabs = TRUE) %>%
+  kableExtra::kable_styling(latex_options = "hold_position")
+
+```
+
+```{r arxiv-accuracy-data-2019}
+arc_2019_accuracy <- (as.numeric(arxiv_2019_data_check[1,2] + arxiv_2019_data_check[2,3])/nrow(arxiv_2019_manual_results)) %>% round(2)
+arc_2019_sensitivity <- (as.numeric(arxiv_2019_data_check[1,2])/sum(arxiv_2019_data_check$`Data available`)) %>% round(2)
+arc_2019_specificity <- (as.numeric(arxiv_2019_data_check[2,3])/sum(arxiv_2019_data_check$`No data available`)) %>% round(2)
+
+tibble(Metric = c("Accuracy", "Sensitivity", "Specificity"),
+      Value = c(arc_2019_accuracy, arc_2019_sensitivity, arc_2019_specificity)) %>% 
+  kable(caption = "ODDPub prediction accuracy, open data, arXiv sample",
+        booktabs = TRUE) %>%
+  kableExtra::kable_styling(latex_options = "hold_position")
+```
+
+```{r arxiv-confusion-code-2019}
+
+arxiv_2019_code_check <- arxiv_2019_manual_results %>%
+  count(is_open_code, manual_open_code) %>%
+  pivot_wider(names_from = manual_open_code, values_from = n) %>%
+  mutate(is_open_code = case_when(is_open_code == 1 ~ "Open code detected", TRUE ~ "No open code detected")) %>%
+  select(is_open_code, `1`, `0`) %>%
+  rename(Predicted = is_open_code, `Code available` = `1`, `No code available` = `0`) %>%
+  arrange(desc(Predicted))
+
+arxiv_2019_code_check %>% 
+  kable(caption = "ODDPub predictions for open code compared with manual check, arXiv sample",
+        booktabs = TRUE) %>%
+  kableExtra::kable_styling(latex_options = "hold_position")
+```
+
+```{r arxiv-accuracy-code-2019}
+arc_2019_code_accuracy <- (as.numeric(arxiv_2019_code_check[1,2] + arxiv_2019_code_check[2,3])/nrow(arxiv_2019_manual_results)) %>% round(2)
+arc_2019_code_sensitivity <- (as.numeric(arxiv_2019_code_check[1,2])/sum(arxiv_2019_code_check$`Code available`)) %>% round(2)
+arc_2019_code_specificity <- (as.numeric(arxiv_2019_code_check[2,3])/sum(arxiv_2019_code_check$`No code available`)) %>% round(2)
+
+tibble(Metric = c("Accuracy", "Sensitivity", "Specificity"),
+      Value = c(arc_2019_code_accuracy, arc_2019_code_sensitivity, arc_2019_code_specificity)) %>% 
+  kable(caption = "ODDPub prediction accuracy, open code, arXiv sample",
+        booktabs = TRUE) %>%
+  kableExtra::kable_styling(latex_options = "hold_position")
+```
+
+\newpage
+
+# Supporting tables
 
@@
 ```
-
-# Table of proportion of all preprints in each category, for each preprint server
 
@@
 
-# ODDPub algorithm performance on arXiv pre-prints
-
-We verified the accuracy of the ODDPub algorithm on a subset of our analyzed pre-prints from 2019 from arXiv.
-We took a simple random sample of 100 papers.
-In the original validation process, the annotators stratified by detection status prior to sampling to ensure relatively high representation of papers where open data or code was detected.
-Since the major concern for our manual verification is potential false negatives, this skewed representation was unnecessary.
-Open data and code status were verified first via the "Code & Data" tab on each pre-print's page on the arXiv website, then by checking for an explicit data availability section within the pre-print PDF, and finally by manually checking the body of the paper using keyword searches.
-Results were recorded manually in Excel.
-This mimics the procedure outlined for the original validation of ODDPub [@citePDDPub].
-
-Many of the pre-prints in arXiv did not use data or code, namely those from pure mathematics and physics.
-There were also several that reused other publicly or privately available data sets, and regardless of whether or not they were shared alongside the paper, these do not count as open data according to the standards outlined by the original authors of the ODDPub algorithm [@citePDDPub].
-Algorithmic performance is specified in Table \@ref(tab:arxiv-accuracy-data-2019) and Table \@ref(tab:arxiv-accuracy-code-2019).
-
-```{r arxiv-confusion-data-2019}
-arxiv_2019_manual_results <- read.csv(here::here("validation", "arxiv_2019_validation_sample_COMPLETE.csv"))
-
-arxiv_2019_data_check <- arxiv_2019_manual_results %>%
-  count(is_open_data, manual_open_data) %>%
-  pivot_wider(names_from = manual_open_data, values_from = n) %>%
-  mutate(is_open_data = case_when(is_open_data == 1 ~ "Open data detected", TRUE ~ "No open data detected")) %>%
-  select(is_open_data, `1`, `0`) %>%
-  rename(Predicted = is_open_data, `Data available` = `1`, `No data available` = `0`) %>%
-  arrange(desc(Predicted))
-
-arxiv_2019_data_check %>% kable(caption = "ODDPub predictions for open data compared with manual check, arXiv sample")
-
-```
-
-```{r arxiv-accuracy-data-2019}
-arc_2019_accuracy <- (as.numeric(arxiv_2019_data_check[1,2] + arxiv_2019_data_check[2,3])/nrow(arxiv_2019_manual_results)) %>% round(2)
-arc_2019_sensitivity <- (as.numeric(arxiv_2019_data_check[1,2])/sum(arxiv_2019_data_check$`Data available`)) %>% round(2)
-arc_2019_specificity <- (as.numeric(arxiv_2019_data_check[2,3])/sum(arxiv_2019_data_check$`No data available`)) %>% round(2)
-
-tibble(Metric = c("Accuracy", "Sensitivity", "Specificity"),
-      Value = c(arc_2019_accuracy, arc_2019_sensitivity, arc_2019_specificity)) %>% kable(caption = "ODDPub prediction accuracy, open data, arXiv sample")
-```
-
-```{r arxiv-confusion-code-2019}
-
-arxiv_2019_code_check <- arxiv_2019_manual_results %>%
-  count(is_open_code, manual_open_code) %>%
-  pivot_wider(names_from = manual_open_code, values_from = n) %>%
-  mutate(is_open_code = case_when(is_open_code == 1 ~ "Open code detected", TRUE ~ "No open code detected")) %>%
-  select(is_open_code, `1`, `0`) %>%
-  rename(Predicted = is_open_code, `Code available` = `1`, `No code available` = `0`) %>%
-  arrange(desc(Predicted))
-
-arxiv_2019_code_check %>% kable(caption = "ODDPub predictions for open code compared with manual check, arXiv sample")
-```
-
-```{r arxiv-accuracy-code-2019}
-arc_2019_code_accuracy <- (as.numeric(arxiv_2019_code_check[1,2] + arxiv_2019_code_check[2,3])/nrow(arxiv_2019_manual_results)) %>% round(2)
-arc_2019_code_sensitivity <- (as.numeric(arxiv_2019_code_check[1,2])/sum(arxiv_2019_code_check$`Code available`)) %>% round(2)
-arc_2019_code_specificity <- (as.numeric(arxiv_2019_code_check[2,3])/sum(arxiv_2019_code_check$`No code available`)) %>% round(2)
-
-tibble(Metric = c("Accuracy", "Sensitivity", "Specificity"),
-      Value = c(arc_2019_code_accuracy, arc_2019_code_sensitivity, arc_2019_code_specificity)) %>% kable(caption = "ODDPub prediction accuracy, open code, arXiv sample")
-```
+\newpage
 
@@
 When available, a data link is stored under the variable name "attributes.data_links".
-The data was manipulated using functions from the R package tidyverse [@citetidyverse] to create a binary variable indicating data availability or lack thereof.
+The data was manipulated using functions from the R package `tidyverse` [@citetidyverse] to create a binary variable indicating data availability or lack thereof.
 We assume "attributes.data_links" to indicate the true availability of data for the purposes of validating the ODDPub algorithm.
@@
   arrange(desc(`ODDPub algorithm`))
-soc_2019_check %>% kable(caption = "ODDPub predictions for open data compared with data links provided by authors, 2019 SocArXiv sample")
+soc_2019_check %>% 
+  kable(caption = "ODDPub predictions for open data compared with data links provided by authors, 2019 SocArXiv sample",
+        booktabs = TRUE) %>%
+  kableExtra::kable_styling(latex_options = "hold_position")
 ```
@@
 tibble(Metric = c("Accuracy", "Sensitivity", "Specificity"),
-      Value = c(soc_2019_accuracy, soc_2019_sensitivity, soc_2019_specificity)) %>% kable(caption = "ODDPub prediction accuracy, open data, 2019 SocArXiv sample")
+      Value = c(soc_2019_accuracy, soc_2019_sensitivity, soc_2019_specificity)) %>% 
+  kable(caption = "ODDPub prediction accuracy, open data, 2019 SocArXiv sample",
+        booktabs = TRUE)
 ```
@@
   arrange(desc(`ODDPub algorithm`))
-soc_2020_check %>% kable(caption = "ODDPub predictions for open data compared with data links provided by authors, COVID-19-related SocArXiv pre-prints sample")
+soc_2020_check %>% 
+  kable(caption = "ODDPub predictions for open data compared with data links provided by authors, COVID-19-related SocArXiv pre-prints sample",
+        booktabs = TRUE) %>%
+  kableExtra::kable_styling(latex_options = "hold_position")
 ```
@@
 tibble(Metric = c("Accuracy", "Sensitivity", "Specificity"),
-      Value = c(soc_2020_accuracy, soc_2020_sensitivity, soc_2020_specificity)) %>% kable(caption = "ODDPub prediction accuracy, open data, COVID-19-related SocArXiv pre-prints sample")
+      Value = c(soc_2020_accuracy, soc_2020_sensitivity, soc_2020_specificity)) %>% 
+  kable(caption = "ODDPub prediction accuracy, open data, COVID-19-related SocArXiv pre-prints sample",
+        booktabs = TRUE) %>%
+  kableExtra::kable_styling(latex_options = "hold_position")
 ```

### 2022-01-14 outputs/paper/paper.tex
revised and resubmitted

@@
 The text, tables and figures of this manuscript overlap with those of the preprint version by the authors.
-\textbf{Acknowledgements:} We thank Amy Farrow, Jessica Gronsbell, Monica Alexander, and Thomas William Rosenthal for helpful comments.
-Two anonymous reviewers and the editor provided extensive comments that substantially improved this paper and we are grateful to them.
+\textbf{Acknowledgements:} Two anonymous reviewers and the editor provided extensive comments that substantially improved this paper and we are grateful to them.
+We thank Amy Farrow, Jessica Gronsbell, Monica Alexander, and Thomas William Rosenthal for helpful comments.
 \textbf{Funding statement:} Collins thanks CANSSI Ontario and Monica Alexander for financial support.
@@
 Collins and Alexander obtained and created the datasets.
-Collins and Alexander analysed the data.
+Collins and Alexander analyzed the data.
 All authors interpreted the data and contributed writing the paper and approved the final version.}}
@@
 To examine the reproducibility of COVID-19 research, we create a dataset of pre-prints posted to arXiv, bioRxiv, and medRxiv between 28 January 2020 and 30 June 2021 that are related to COVID-19.
-We extract the text from these pre-prints and parse them looking for keyword markers signalling the availability of the data and code underpinning the pre-print.
+We extract the text from these pre-prints and parse them looking for keyword markers signaling the availability of the data and code underpinning the pre-print.
 For the pre-prints that are in our sample, we are unable to find markers of either open data or open code for 75 per cent of those on arXiv, 67 per cent of those on bioRxiv, and 79 per cent of those on medRxiv.
-We conclude that there may be value in having authors categorize the degree of openness of their pre-print as part of the pre-print submissions process, and more broadly, there is a need to better integrate open science training into a wide range of fields.
 \end{abstract}
@@
 For the purposes of this paper, we define reproducibility to mean the ability for different researchers to achieve the same results given the same data and computational methods as the original source.
-This contrasts replicability, which we define as the ability for different researchers to achieve consistent results by conducting the full data collection and analysis process in lieu of reusing original data.
+This contrasts with replicability, which we define as the ability for different researchers to achieve consistent results by conducting the full data collection and analysis process in lieu of reusing original data.
 These definitions match that of National Academies of Sciences and Medicine (2019) and Cacioppo et al.
 (2015).
+What constitutes open code or open data is complicated and discipline specific.
+The details of the \texttt{oddpub} approach are available in Riedel, Kip, and Bobrov (2020).
+The general criteria are that specific mention should be made of where the data and code are located, and that data should be as close to raw as possible.
+Data and code must also be freely accessible to anyone (no request, application, registration process, or affiliation required).
 
@@
 This was conducted using the \texttt{open\_data\_search()} function from the \texttt{oddpub} package.
-Under the validation procedure from the original authors, the ODDPub algorithm performed with a sensitivity of 0.73 and a specificity of 1.00 for open code detection and a sensitivity of 0.73 and a specificity of 0.97 for open data detection compared with manual screening (Riedel, Kip, and Bobrov 2020).
+In the validation conducted by the authors of the package, the ODDPub algorithm had a sensitivity of 0.73 and a specificity of 1.00 for open code detection, and a sensitivity of 0.73 and a specificity of 0.97 for open data detection compared with manual screening (Riedel, Kip, and Bobrov 2020).
 Since the ODDPub algorithm was developed specifically for biomedical publications, we conducted our own validation process for its performance on arXiv pre-prints.
-We found that the ODDPub algorithm performed with a sensitivity of 0.60 and a specificity of 0.98 for open code detection and a sensitivity of 0.67 and a specificity of 0.98 for open data detection compared with manual screening.
+We found that the ODDPub algorithm performed with a sensitivity of 0.60 and a specificity of 0.98 for open code detection, and a sensitivity of 0.67 and a specificity of 0.98 for open data detection compared with manual screening.
 Details of our validation procedure are contained in Appendix \ref{oddpub-algorithm-performance-on-arxiv-pre-prints}.
-
-What constitutes open code or open data is complicated and discipline specific.
-The details of the \texttt{oddpub} approach are available in Riedel, Kip, and Bobrov (2020).
-The general criteria are that specific mention should be made of where the data and code are located, and that data should be as close to raw as possible.
-Data and code must also be freely accessible to anyone (no request, application, registration process, or affiliation required).
 Our work was conducted using the statistical programming language R (R Core Team 2020) (RRID:SCR\_001905).
@@
 Our final dataset was formed by joining this output with the original sample metadata, typically using the DOI or the unique file name, to form a dataset including all original metadata for each pre-print alongside its open data and open code status and markers.
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=0.9\linewidth]{paper_files/figure-latex/monthly-papers-total-1}
-
-}
-
-\caption{Number of pre-prints related to COVID-19 posted to arXiv (N = 4,250), bioRxiv (N = 4,146), and medRxiv (N = 13,194) per month}\label{fig:monthly-papers-total}
-\end{figure}
 
@@
 \centering
-\begin{tabular}[t]{l|r|r}
-\hline
+\begin{tabular}[t]{lrr}
+\toprule
 Repositiory & Published pre-prints & Proportion published\\
-\hline
+\midrule
 arXiv & 62,045 & 0.41\\
-\hline
 bioRxiv & 20,445 & 0.64\\
-\hline
 medRxiv & 555 & 0.61\\
-\hline
+\bottomrule
 \end{tabular}
@@
 
+\begin{figure}[H]
+
+{\centering \includegraphics[width=0.9\linewidth]{paper_files/figure-latex/monthly-papers-total-1}
+
+}
+
+\caption{Number of pre-prints related to COVID-19 posted to arXiv (N = 4,250), bioRxiv (N = 4,146), and medRxiv (N = 13,194) per month}\label{fig:monthly-papers-total}
+\end{figure}
+
 \hypertarget{open-data-and-code}{%
@@
 
-From the collection of all pre-prints related to COVID-19, we randomly sampled 3,910 pre-prints to analyze, stratified by repository.
+From the collection of all pre-prints related to COVID-19, we randomly sampled 3,500 pre-prints to analyze, stratified by repository.
 This sample is broken down as follows: 1,500 from medRxiv, 1,000 from arXiv, and 1,000 from bioRxiv.
-Broadly, we are unable to find markers of either open data or open code for 3,011 pre-prints or approximately 76 per cent of our sample (Appendix \ref{tables-with-specific-values-displayed-in-the-graphs} Table \ref{tab:summarycounts-repositories}).
+Broadly, we are unable to find markers of either open data or open code for 2,606 pre-prints or approximately 74 per cent of our sample (Appendix \ref{supporting-tables} Table \ref{tab:summarycounts-repositories}).
 Of the remaining pre-prints, 7 per cent contained open code markers only, 10 per cent contained open data markers only, and 8 per cent included markers of both open data and open code.
@@
 When differentiated by repository, we observe that open data and code markers were absent from 75 per cent of the sampled arXiv pre-prints, 67 per cent of the sampled bioRxiv pre-prints, 79 per cent of the sampled medRxiv pre-prints.
-The distribution of the remaining portion of pre-prints also varies by repository (Appendix \ref{tables-with-specific-values-displayed-in-the-graphs} Table \ref{tab:summarycounts-repositories}).
+The distribution of the remaining portion of pre-prints also varies by repository (Appendix \ref{supporting-tables} Table \ref{tab:summarycounts-repositories}).
 Notably, 28 per cent of sampled pre-prints from bioRxiv contained open data markers and 22 per cent of sampled arXiv pre-prints contained markers of open code, the highest proportions of any repository for each type of marker.
@@
 
-On the other hand, the analyzed arXiv COVID-19-related pre-prints contain a higher proportion of open data and code markers overall than their 2019 counterparts, with a increase of 18 per cent in sampled arXiv papers.
+On the other hand, the analyzed arXiv COVID-19-related pre-prints contain a higher proportion of open data and code markers overall than their 2019 counterparts, with an increase of 18 per cent in sampled arXiv papers.
 For these repositories, the presence of both open data and open code markers was significantly associated with registration during the pandemic, suggesting that pre-prints related to COVID-19 in arXiv may have more consistently adhered to open science practices than their pre-pandemic counterparts (\(\chi\)\textsuperscript{2} = 93.124, arXiv open data; \(\chi\)\textsuperscript{2} = 106.88, arXiv open code; \(\chi\)\textsuperscript{2} = 12.303).
@@
 The proportion of pre-prints that have been published varies by repository (Table \ref{tab:published-sample-summary}).
-Notably, of all COVID-19-related pre-prints in our dataset, approximately 30 per cent of those posted to bioRxiv and nearly one third of those posted to medRxiv were published.
+Notably, of all COVID-19-related pre-prints in our dataset, approximately 30 per cent of those posted to bioRxiv and nearly one-third of those posted to medRxiv were published.
 This is high in comparison to the proportion from arXiv, and although this might suggest that COVID-19-related pre-prints in biomedical fields have received greater attention overall than pre-prints from other fields, our results in Section \ref{pre-pandemic-pre-prints} suggest that this pattern pre-dates the pandemic.
@@
 \centering
-\begin{tabular}[t]{l|r|r}
-\hline
+\begin{tabular}[t]{lrr}
+\toprule
 Repository & Published pre-prints & Proportion published\\
-\hline
+\midrule
 arXiv & 717 & 0.17\\
-\hline
 bioRxiv & 1,230 & 0.30\\
-\hline
 medRxiv & 4,230 & 0.32\\
-\hline
+\bottomrule
 \end{tabular}
@@
 McGuinness and Sheppard (2021) examine differences in data availability statements between medRxiv pre-prints and their published counterparts.
-They find that data availability was maintained for the vast majority of their sample, varying by journal data sharing policy with greater improvements in openness among manuscripts published in journals mandating data sharing.
+They find that data availability was maintained for most of their sample, varying by journal data sharing policy with greater improvements in openness among manuscripts published in journals mandating data sharing.
 While limited to medRxiv, the results of McGuinness and Sheppard (2021) align with our own work and provide initial evidence to suggest that data availability is generally maintained or improved between the pre-print and publication stages.
@@
 There has been a large amount of research on COVID-19 (Teixeira da Silva, Tsigaris, and Erfanmanesh 2021).
-Many concerns have arisen from the rate at which COVID-19 research has been posted and consumed via pre-print repositories, particularly in the early stages of the pandemic (Raynaud et al.
+Many concerns have arisen from the rate at which COVID-19 research has been posted and consumed through pre-print repositories, particularly in the early stages of the pandemic (Raynaud et al.
 2020).
-Rushed scientific research has potential to skip (or at least place less precedence on) open science practices, thus it may be reasonable to expect a decrease in open data or code markers in the initial few months of the pandemic.
+Rushed scientific research has the potential to skip (or at least place less importance on) open science practices, so it may be reasonable to expect a decrease in open data or code markers in the initial few months of the pandemic.
 We found little relationship between date posted and likelihood of having open data or code markers, with the proportion of pre-prints containing these markers fluctuating from month to month.
@@
 In our sample, published pre-prints contain open data or code markers in similar proportions to their unpublished counterparts, a pattern that was present for pre-prints related to COVID-19 and those posted in 2019.
-This appears initially to alleviate some concerns over the relationship between open data and publication bias, that is, the potential that journals have favoured novel yet less transparent or reproducible papers over those with null results but a high standard of open science practices.
-However, publication bias is complex and this result should be approached with caution.
+This appears initially to alleviate some concerns over the relationship between open data and publication bias, that is, the potential that journals have favored novel yet less transparent or reproducible papers over those with null results but a high standard of open science practices.
+However, publication bias is complex, and this result should be approached with caution.
 Concerns have already been raised through systemic reviews of COVID-19 publications (Raynaud et al.
 2020), and oversights in data accessibility have led to high profile retractions of publications in the past; for example, papers from \emph{The Lancet} and the \emph{New England Journal of Medicine} which were withdrawn due to concerns over the private nature of their underlying dataset (Ledford and Noorden 2020).
-Further, Cabanac, Oikonomidi, and Boutron (2021) show that not all pre-prints are linked to their subsequent peer-reviewed publication, which may further bias our results.
-Further, there is the potential for bias due to older pre-prints having had more time to be published than newer pre-prints.
+Cabanac, Oikonomidi, and Boutron (2021) show that not all pre-prints are linked to their subsequent peer-reviewed publication, which may further bias our results.
+Additionally, there is the potential for bias due to older pre-prints having had more time to be published than newer pre-prints.
 And Oikonomidi et al.
 (2020) and Bero et al.
-(2021) show that differences between updated versions of the same pre-print can be substantial; again this is something that we do not account for and could bias our results.
+(2021) show that differences between updated versions of the same pre-print can be substantial; again, this is something that we do not account for and could bias our results.
 
 In all fields of science, increasing access to data and code used for pre-printed or published research is a step in the direction of more transparent, reproducible, and reliable research.
-The ongoing COVID-19 pandemic has created a novel, constantly changing scientific culture that should be navigated with care to uphold standards of scientific practice for both the research community and the safety of the public.
+The COVID-19 pandemic has created a novel, constantly changing scientific culture that should be navigated with care to uphold standards of scientific practice for both the research community and the safety of the public.
 Our analysis shows that there is room for improvement in the areas of open data and code availability within COVID-19 pre-print papers on arXiv, bioRxiv, and medRxiv
@@
 
-We wish to expand our analysis to consider the geographic distribution of research and the potential influence of different practices and policies concerning open science as pre-prints vary by location.
-This is important because the epicenter of the pandemic changed throughout the pandemic, which has implications for our time-based analysis.
+Future work would expand our analysis to consider the geographic distribution of research and the potential influence of different practices and policies concerning open science.
+This is important because the epicenter of the pandemic changed throughout the pandemic, which may have implications for our time-based analysis.
 
 A logical next step would be to extend this analysis to additional pre-print servers.
-An initial iteration of our analyses included samples of pre-pandemic and COVID-19-related pre-prints posted to SocArXiv, a social sciences pre-print server hosted by the Center for Open Science.
+We have begun considering samples of pre-pandemic and COVID-19-related pre-prints posted to SocArXiv, a social sciences pre-print server hosted by the Center for Open Science.
 We validated the ODDPub algorithm against the presence of data links provided by pre-print authors upon submission (available in the pre-print metadata drawn from the Open Science Framework API) and found that the algorithm performed with 52 per cent sensitivity on the 2019 sample and 29 per cent sensitivity for COVID-19-related pre-prints.
-The high rate of false negatives for open data detection is concerning, and it was decided that the ODDPub algorithm is not suitable for use on pre-prints from this server.
-A more generalized (or perhaps field specific) algorithm would be necessary for analysis of open data and code availability in SocArXiv and other more specialized servers.
-Details on validation are available in Appendix \ref{oddpub-algorithm-performance-on-socarxiv-pre-prints}.
+The high rate of false negatives for open data detection is concerning, and it was decided that the ODDPub algorithm is not suitable for use on pre-prints from this server without modification.
+A more generalized (or perhaps field-specific) algorithm would be necessary for analysis of open data and code availability in SocArXiv and other more specialized servers.
+Details of this validation are available in Appendix \ref{oddpub-algorithm-performance-on-socarxiv-pre-prints}.
 
@@
 We also note that the ODDPub algorithm is relatively narrow in its definition of ``open,'' excluding data that is available via registration or in some other restricted form.
-Adopting a broader definition of openness, either through using a less restrictive algorithm or through manual verification, would likely produce different results particularly for pre-prints using clinical data.
-In future, we wish to take smaller sub-samples to validate factors like publication status, paper topic, and open code and data status, beyond the approaches that we used here.
+Considering a broader definition of openness, either through using a less restrictive algorithm or through manual verification, would likely produce different results particularly for pre-prints using clinical data.
+Future work could take smaller sub-samples to validate factors like publication status, paper topic, and open code and data status, beyond the approaches we used here.
 
@@
 
-\hypertarget{tables-with-specific-values-displayed-in-the-graphs}{%
-\section{Tables with specific values displayed in the graphs}\label{tables-with-specific-values-displayed-in-the-graphs}}
+\hypertarget{oddpub-algorithm-performance-on-arxiv-pre-prints}{%
+\section{ODDPub algorithm performance on arXiv pre-prints}\label{oddpub-algorithm-performance-on-arxiv-pre-prints}}
+
+We verified the accuracy of the ODDPub algorithm on a subset of our analyzed pre-prints from 2019 from arXiv.
+We took a simple random sample of 100 papers.
+In the original validation process, the annotators stratified by detection status prior to sampling to ensure relatively high representation of papers where open data or code was detected.
+Since the major concern for our manual verification is potential false negatives, this skewed representation was unnecessary.
+Open data and code status were verified first via the ``Code \& Data'' tab on each pre-print's page on the arXiv website, then by checking for an explicit data availability section within the pre-print PDF, and finally by manually checking the body of the paper using keyword searches.
+Results were recorded manually in Excel.
+This mimics the procedure outlined for the original validation of ODDPub (Riedel, Kip, and Bobrov 2020).
+
+Many of the pre-prints in arXiv did not use data or code, namely those from pure mathematics and physics.
+There were also several that reused other publicly or privately available data sets, and regardless of whether or not they were shared alongside the paper, these do not count as open data according to the standards outlined by the original authors of the ODDPub algorithm (Riedel, Kip, and Bobrov 2020).
+Algorithmic performance is specified in Table \ref{tab:arxiv-accuracy-data-2019} and Table \ref{tab:arxiv-accuracy-code-2019}.
+
+\begin{table}[!h]
+
+\caption{\label{tab:arxiv-confusion-data-2019}ODDPub predictions for open data compared with manual check, arXiv sample}
+\centering
+\begin{tabular}[t]{lrr}
+\toprule
+Predicted & Data available & No data available\\
+\midrule
+Open data detected & 2 & 2\\
+No open data detected & 1 & 95\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}[!h]
+
+\caption{\label{tab:arxiv-accuracy-data-2019}ODDPub prediction accuracy, open data, arXiv sample}
+\centering
+\begin{tabular}[t]{lr}
+\toprule
+Metric & Value\\
+\midrule
+Accuracy & 0.97\\
+Sensitivity & 0.67\\
+Specificity & 0.98\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}[!h]
+
+\caption{\label{tab:arxiv-confusion-code-2019}ODDPub predictions for open code compared with manual check, arXiv sample}
+\centering
+\begin{tabular}[t]{lrr}
+\toprule
+Predicted & Code available & No code available\\
+\midrule
+Open code detected & 3 & 2\\
+No open code detected & 2 & 93\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}[!h]
+
+\caption{\label{tab:arxiv-accuracy-code-2019}ODDPub prediction accuracy, open code, arXiv sample}
+\centering
+\begin{tabular}[t]{lr}
+\toprule
+Metric & Value\\
+\midrule
+Accuracy & 0.96\\
+Sensitivity & 0.60\\
+Specificity & 0.98\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\newpage
+
+\hypertarget{supporting-tables}{%
+\section{Supporting tables}\label{supporting-tables}}
 
@@
 
-\hypertarget{table-of-proportion-of-all-preprints-in-each-category-for-each-preprint-server}{%
-\section{Table of proportion of all preprints in each category, for each preprint server}\label{table-of-proportion-of-all-preprints-in-each-category-for-each-preprint-server}}
-
 \begin{table}[!h]
@@
 
-\hypertarget{oddpub-algorithm-performance-on-arxiv-pre-prints}{%
-\section{ODDPub algorithm performance on arXiv pre-prints}\label{oddpub-algorithm-performance-on-arxiv-pre-prints}}
-
-We verified the accuracy of the ODDPub algorithm on a subset of our analyzed pre-prints from 2019 from arXiv.
-We took a simple random sample of 100 papers.
-In the original validation process, the annotators stratified by detection status prior to sampling to ensure relatively high representation of papers where open data or code was detected.
-Since the major concern for our manual verification is potential false negatives, this skewed representation was unnecessary.
-Open data and code status were verified first via the ``Code \& Data'' tab on each pre-print's page on the arXiv website, then by checking for an explicit data availability section within the pre-print PDF, and finally by manually checking the body of the paper using keyword searches.
-Results were recorded manually in Excel.
-This mimics the procedure outlined for the original validation of ODDPub (Riedel, Kip, and Bobrov 2020).
-
-Many of the pre-prints in arXiv did not use data or code, namely those from pure mathematics and physics.
-There were also several that reused other publicly or privately available data sets, and regardless of whether or not they were shared alongside the paper, these do not count as open data according to the standards outlined by the original authors of the ODDPub algorithm (Riedel, Kip, and Bobrov 2020).
-Algorithmic performance is specified in Table \ref{tab:arxiv-accuracy-data-2019} and Table \ref{tab:arxiv-accuracy-code-2019}.
-
-\begin{table}
-
-\caption{\label{tab:arxiv-confusion-data-2019}ODDPub predictions for open data compared with manual check, arXiv sample}
-\centering
-\begin{tabular}[t]{l|r|r}
-\hline
-Predicted & Data available & No data available\\
-\hline
-Open data detected & 2 & 2\\
-\hline
-No open data detected & 1 & 95\\
-\hline
-\end{tabular}
-\end{table}
-
-\begin{table}
-
-\caption{\label{tab:arxiv-accuracy-data-2019}ODDPub prediction accuracy, open data, arXiv sample}
-\centering
-\begin{tabular}[t]{l|r}
-\hline
-Metric & Value\\
-\hline
-Accuracy & 0.97\\
-\hline
-Sensitivity & 0.67\\
-\hline
-Specificity & 0.98\\
-\hline
-\end{tabular}
-\end{table}
-
-\begin{table}
-
-\caption{\label{tab:arxiv-confusion-code-2019}ODDPub predictions for open code compared with manual check, arXiv sample}
-\centering
-\begin{tabular}[t]{l|r|r}
-\hline
-Predicted & Code available & No code available\\
-\hline
-Open code detected & 3 & 2\\
-\hline
-No open code detected & 2 & 93\\
-\hline
-\end{tabular}
-\end{table}
-
-\begin{table}
-
-\caption{\label{tab:arxiv-accuracy-code-2019}ODDPub prediction accuracy, open code, arXiv sample}
-\centering
-\begin{tabular}[t]{l|r}
-\hline
-Metric & Value\\
-\hline
-Accuracy & 0.96\\
-\hline
-Sensitivity & 0.60\\
-\hline
-Specificity & 0.98\\
-\hline
-\end{tabular}
-\end{table}
+\newpage
 
@@
 The presence of a data link was used as an indicator that a pre-print provides open data for the purposes of validating the ODDPub algorithm.
-When available, a data link is stored under the variable name ``attributes.data\_links.'' The data was manipulated using functions from the R package tidyverse (Wickham et al.
+When available, a data link is stored under the variable name ``attributes.data\_links.'' The data was manipulated using functions from the R package \texttt{tidyverse} (Wickham et al.
 2019) to create a binary variable indicating data availability or lack thereof.
@@
 \centering
-\begin{tabular}[t]{l|r|r}
-\hline
+\begin{tabular}[t]{lrr}
+\toprule
 ODDPub algorithm & Data linked & No data linked\\
-\hline
+\midrule
 Open data detected & 11 & 72\\
-\hline
 No open data detected & 10 & 1107\\
-\hline
+\bottomrule
 \end{tabular}
@@
 \centering
-\begin{tabular}[t]{l|r}
-\hline
+\begin{tabular}[t]{lr}
+\toprule
 Metric & Value\\
-\hline
+\midrule
 Accuracy & 0.93\\
-\hline
 Sensitivity & 0.52\\
-\hline
 Specificity & 0.94\\
-\hline
+\bottomrule
 \end{tabular}
@@
 \centering
-\begin{tabular}[t]{l|r|r}
-\hline
+\begin{tabular}[t]{lrr}
+\toprule
 ODDPub algorithm & Data linked & No data linked\\
-\hline
+\midrule
 Open data detected & 28 & 31\\
-\hline
 No open data detected & 69 & 350\\
-\hline
+\bottomrule
 \end{tabular}
@@
 \centering
-\begin{tabular}[t]{l|r}
-\hline
+\begin{tabular}[t]{lr}
+\toprule
 Metric & Value\\
-\hline
+\midrule
 Accuracy & 0.79\\
-\hline
 Sensitivity & 0.29\\
-\hline
 Specificity & 0.92\\
-\hline
+\bottomrule
 \end{tabular}
